### 2016-08-02 Paper-magnetic-elipsoid.tex
Tex model paper

%% Copernicus Publications Manuscript Preparation Template for LaTeX Submissions
%% ---------------------------------
%% This template should be used for copernicus.cls
%% The class file and some style files are bundled in the Copernicus Latex Package which can be downloaded from the different journal webpages.
%% For further assistance please contact the Copernicus Publications at: publications@copernicus.org
%% http://publications.copernicus.org

%% Please use the following documentclass and Journal Abbreviations for Discussion Papers and Final Revised Papers.

%% 2-Column Papers and Discussion Papers
\documentclass[journal abbreviation, manuscript]{copernicus}

%% Journal Abbreviations (Please use the same for Discussion Papers and Final Revised Papers)

% Archives Animal Breeding (aab)
% Atmospheric Chemistry and Physics (acp)
% Advances in Geosciences (adgeo)
% Advances in Statistical Climatology, Meteorology and Oceanography (ascmo)
% Annales Geophysicae (angeo)
% ASTRA Proceedings (ap)
% Atmospheric Measurement Techniques (amt)
% Advances in Radio Science (ars)
% Advances in Science and Research (asr)
% Biogeosciences (bg)
% Climate of the Past (cp)
% Drinking Water Engineering and Science (dwes)
% Earth System Dynamics (esd)
% Earth Surface Dynamics (esurf)
% Earth System Science Data (essd)
% Fossil Record (fr)
% Geographica Helvetica (gh)
% Geoscientific Instrumentation, Methods and Data Systems (gi)
% Geoscientific Model Development (gmd)
% Geothermal Energy Science (gtes)
% Hydrology and Earth System Sciences (hess)
% History of Geo- and Space Sciences (hgss)
% Journal of Sensors and Sensor Systems (jsss)
% Mechanical Sciences (ms)
% Natural Hazards and Earth System Sciences (nhess)
% Nonlinear Processes in Geophysics (npg)
% Ocean Science (os)
% Proceedings of the International Association of Hydrological Sciences (piahs)
% Primate Biology (pb)
% Scientific Drilling (sd)
% SOIL (soil)
% Solid Earth (se)
% The Cryosphere (tc)
% Web Ecology (we)
% Wind Energy Science (wes)

%% \usepackage commands included in the copernicus.cls:
%\usepackage[german, english]{babel}
%\usepackage{tabularx}
%\usepackage{cancel}
%\usepackage{multirow}
%\usepackage{supertabular}
%\usepackage{algorithmic}
%\usepackage{algorithm}
%\usepackage{amsthm}
%\usepackage{float}
%\usepackage{subfig}
%\usepackage{rotating}

\begin{document}

\title{3D MAGNETIC MODELLING FOR ELLIPSOIDS}

% \Author[affil]{given_name}{surname}

\Author[1]{Diego}{Takahashi Tomazella}
\Author[1]{Vanderlei}{Coelho Oliveira Junior}

\affil[1]{Department of Geophysics, Observatorio Nacional, Rio de Janeiro, Brazil}
%\affil[]{}

%% The [] brackets identify the author with the corresponding affiliation. 1, 2, 3, etc. should be inserted.

\runningtitle{TEXT}

\runningauthor{TEXT}

\correspondence{DIEGO TAKAHASHI TOMAZELLA (diego.takahashi@gmail.com)}

\received{}
\pubdiscuss{} %% only important for two-stage journals
\revised{}
\accepted{}
\published{}

%% These dates will be inserted by Copernicus Publications during the typesetting process.

\firstpage{1}

\maketitle

\begin{abstract}
In this work we will present results from a numerical modeling of the magnetic field and total field anomaly, represented by prolate and triaxial ellipsoids sources. Such approach provide analytical results for anisotropy of magnetic susceptibility as well as for self-demagnetization effects, which can be easily adapted for distinctive geologic structures - hence being an useful tool for educational (e.g., potential methods and rock magnetism) and applied geophysics (e.g., characterization of high magnetic susceptibility, mineralized bodies) purposes. Numerical tests by means of a Python code (currently under development) allowed us to compared the effects of different geometries (ellipsoidal sources, spheres, dipole lines and elliptic cylinders), which were used to validate our computational implementation. This code will be freely available to the scientific community by the end of the year.
\end{abstract}

\introduction  %% \introduction[modified heading if necessary]
TEXT

\section{Methodology}
TEXT

\subsection{Triaxial Ellipsoid}
The implementation of the forward problem of a triaxial ellipsoid's magnetic field (three semi-axis $a > b > c$) is done in a new coordinate system, where its center is the center of this ellipsoidal body.

We will define this new coordinate system ($x_1,x_2,x_3$) by the unit vectors $\hat{v}_h (h=1,2,3)$ with the respect to the geographic axis $x$, $y$ e $z$:
\loadeq{043}
\loadeq{044}\
\loadeq{045} 
\\

The angles refering to the unit vectors are determined by the orientations of the ellipsoid's semi-axis. The angle $\alpha$ is the azimuth of semi-major axe ($a$) plus 180º. Meanwhile $\delta$ is the inclination of semi-major axe ($a$) in relation to the geographic plane. Lastly, $\gamma$ is the angle between the semi-mid axe ($b$) and the vertical projection of the ellipsoid's center with the geographic plane.

Thus, the coordinates of the body's semi-axis are given by:
\loadeq{046}

Where $x_c$, $y_c$ e $z_c$ are the coordinates of the ellipsoid's center in the geographic system $x$, $y$ e $z$.

For an ellipsoid of semi-axis $a > b > c$, the equation that defines yours surface is:
\loadeq{030}

The parameter $s$ controls the ellipsoid form. When $s$ gets close to $\infty$ the equation \eqref{eq:elipsoide} tends to the sphere equation of radius $r=\sqrt{\lambda}$. When $s = -c^2$, the last term of the ellipsoid's equation is less than zero and she becomes the equation of a circle.

There is, however, a set of values for $s (\lambda,\mu,\nu)$, which are roots of the cubic equation:
\loadeq{031}

This set of roots, called ellipsoidal coordinates, correspond to parameters of a point ($x_1,x_2,x_3$) which are under the intersection of three ortogonal surfaces related to the body coordinates. Their expressions are:
\loadeq{038}\
\loadeq{039}\
\loadeq{040}

Where:
\loadeq{032}\
\loadeq{033}\
\loadeq{034}\
\loadeq{035}\
\loadeq{036}\
\loadeq{037}\

The calculation of the largest root $\lambda$ of the equation \eqref{eq:cubica} is essential, since the magnetic field depends on the spatial derivatives of the equation \ref{eq:elipsoide}, where $s$ admits the value of $\lambda$.
\loadeq{010}

\begin{equation}
\dfrac{\partial \lambda}{\partial x_2} = \dfrac{2x_2/(b^2+\lambda)}{\left(\dfrac{x_1}{a^2+\lambda}\right)^2 + \left(\dfrac{x_2}{b^2+\lambda}\right)^2 + \left(\dfrac{x_3}{c^2+\lambda}\right)^2}
\end{equation}

\begin{equation}
\dfrac{\partial \lambda}{\partial x_3} = \dfrac{2x_3/(c^2+\lambda)}{\left(\dfrac{x_1}{a^2+\lambda}\right)^2 + \left(\dfrac{x_2}{b^2+\lambda}\right)^2 + \left(\dfrac{x_3}{c^2+\lambda}\right)^2}
\end{equation}\\

The desmagnetization factors are given by:
\loadeq{047}
\loadeq{048}
\loadeq{049}

Where $F(\theta,k)$ e $E(\theta,k)$ are first and second Legendre's normal elliptical integrals, respectively. To calculate $k$ and $\theta$ we have the following expressions:
\begin{equation}
k = \sqrt{\left(\dfrac{a^2-b^2}{a^2-c^2} \right)}
\end{equation}

\begin{equation}
\theta = \cos^{-1}(c/a) \quad (0 \le \theta \le \pi/2)
\end{equation}

The susceptibility tensor matrix is:
\loadeq{050}

The Earth's field vector, $F$, and the remanent magnetization ,$d$, also must be converted to the body's coordinates:
\loadeq{051}
\loadeq{052}

Note that $L_r, M_r, N_r$ ($r = 1,2,3$), $l,m,n$ e $l_N, m_N, n_N$ depends on their respective vector's inclinations and declinations:
\begin{equation}
L_R,l,l_N = \cos(dec) \, \cos(inc)
\end{equation}

\begin{equation}
M_R,m,m_N = \sin(dec) \, \cos(inc)
\end{equation}

\begin{equation}
N_R,n,n_N = \sin(inc)
\end{equation}

In the case that the body has a very low susceptibility ($\chi < 0.1$ SI) the self-demagnatization is negligible and the resultant magnetic vector is given by:
\loadeq{053}

For values bigger than 0.1 SI the resultant magnetic vector is:
\loadeq{055}

Where:
\loadeq{054}

This way, the components of the magnetic field produced by a triaxial ellipsoid in the body's coordinates outside of it is:

\loadeq{056}
\loadeq{057}
\loadeq{058}

where:
\loadeq{059}\\
\loadeq{060}\\
\loadeq{061}\\
\loadeq{062}\\

And:
\loadeq{063}\\

Both $F(\theta^{'}, k)$ as $E(\theta^{'}, k)$ are again the first and second  noraml Legendre's elliptical integrals. While $A(\lambda), B(\lambda), C(\lambda)$ are analytic solutions of the integrals of the potential equation of an ellpsoid. This problem was solved by Dirichlet in 1839 \citep{clark1986magnetic} for the gravitational potential given by:
\begin{equation}
U_i(x_1,x_2,x_3) = \pi abc G \rho \int_{0}^{\infty} \left[1 - \dfrac{x_1^2}{a^2+u} - \dfrac{x_2^2}{b^2+u} - \dfrac{x_3^2}{c^2+u}\right] \dfrac{du}{R(u)}
\end{equation}

That can be rewritten as:
\begin{equation}
U_i(x_1,x_2,x_3) = \pi abc G \rho \int_{0}^{\infty} [D(\lambda) - A(\lambda) - B(\lambda) - C(\lambda)] \dfrac{du}{R(u)}
\end{equation}

Where $G$ is the gravitational constant and $\rho$ the body's density.

Using the equations from \eqref{eq:campo_e} to \eqref{eq:integralC}, we can rearrange them in a matrix format that will be more computationally efficient and will help us better see the inverse problem ahead. Thus, the magnetic field generated by the ellipsoid is:
\loadeq{007}

With:
\loadeq{009}\\
\loadeq{011}\\

For $j = 1,...,L$, the number of ellipsoids been modeled and $i = 1,...,N$  for the $i$th element of the calculated field. The total magnetic field then is:
\loadeq{006}

We must remember that every calculation so far was done using the body's coordinates, however the notation in equation \eqref{eq:campoGeo} the magnetic field is already in geographics coordinates. To calculate each component of the magnetic field's vector back:
\loadeq{064}
\loadeq{065}
\loadeq{066}

Been $\Delta T^0$, $i = 1,...,N$, the total field anomaly observed in positions (xi, yi, zi), mathematically it can be rewritten as:
\loadeq{001}

The total field vector $T_i$ can be represented by:
\loadeq{002}

Where $F_i$ is the magnetic field's vector and $B_i$ the magnetic induction's vector generated by the magnetic sources.
Considering $F_i$ a constant vector $F_0$ for local ou regional scale, and that $||F_0|| \gg ||B_0||$, since, $B_i$ is a small pertubation of the magnetic field $F_i$, we can approximate the euclidian norm of the vector $T_i$ by a Taylor's expansion of first order:
\loadeq{003}

where $T$ indicates transposition and
\loadeq{004}

is a unit vector that represents the gradient of the function $||T_i||$ in relation to the vector's components $T_i$. This way, we can approximate the equation \eqref{eq:anomalia} of total-field anomaly to:
\loadeq{005}

Substituting the magnetic induction' equation \eqref{eq:campoGeo} in the total magnetic induction \eqref{eq:campoGeoNL} and using the total-field anomaly approximation \eqref{Anomaliaaproximada} we obtain the predict anomaly for the total field produced by the $L$ ellipsoids:
\loadeq{018}

The equation \eqref{eq:anomaliaCompleta} can be rewritten as:
\loadeq{019}

Where:
\loadeq{020}

And:
\loadeq{021}

The equation \eqref{eq:anomaliaJ} shows the dependence for the predicted total-field anomaly related to the vector $h$. We can rewrite it in matrix notation:
\loadeq{022}

Been $A$ the matrix:
\loadeq{023}

With $a_i$, $i= 1,...,N$ the vector of dimension $3L$ defined in equation \eqref{eq:matrizsensibilidade}.

\subsubsection{HEADING}
TEXT

\conclusions  %% \conclusions[modified heading if necessary]
TEXT

\appendix
\section{}    %% Appendix A

\subsection{}                               %% Appendix A1, A2, etc.

\authorcontribution{TEXT}

\begin{acknowledgements}
TEXT
\end{acknowledgements}

%% REFERENCES

%% The reference list is compiled as follows:

\begin{thebibliography}{}

\bibitem[AUTHOR(YEAR)]{LABEL}
REFERENCE 1

\bibitem[AUTHOR(YEAR)]{LABEL}
REFERENCE 2

\end{thebibliography}

%% Since the Copernicus LaTeX package includes the BibTeX style file copernicus.bst,
%% authors experienced with BibTeX only have to include the following two lines:
%%
%% \bibliographystyle{copernicus}
%% \bibliography{example.bib}
%%
%% URLs and DOIs can be entered in your BibTeX file as:
%%
%% URL = {http://www.xyz.org/~jones/idx_g.htm}
%% DOI = {10.5194/xyz}

%% LITERATURE CITATIONS
%%
%% command                        & example result
%% \citet{jones90}|               & Jones et al. (1990)
%% \citep{jones90}|               & (Jones et al., 1990)
%% \citep{jones90,jones93}|       & (Jones et al., 1990, 1993)
%% \citep[p.~32]{jones90}|        & (Jones et al., 1990, p.~32)
%% \citep[e.g.,][]{jones90}|      & (e.g., Jones et al., 1990)
%% \citep[e.g.,][p.~32]{jones90}| & (e.g., Jones et al., 1990, p.~32)
%% \citeauthor{jones90}|          & Jones et al.
%% \citeyear{jones90}|            & 1990

%% FIGURES

%% ONE-COLUMN FIGURES

%%f
%\begin{figure}[t]
%\includegraphics[width=8.3cm]{FILE NAME}
%\caption{TEXT}
%\end{figure}
%
%%% TWO-COLUMN FIGURES
%
%%f
%\begin{figure*}[t]
%\includegraphics[width=12cm]{FILE NAME}
%\caption{TEXT}
%\end{figure*}
%
%
%%% TABLES
%%%
%%% The different columns must be seperated with a & command and should
%%% end with \\ to identify the column brake.
%
%%% ONE-COLUMN TABLE
%
%%t
%\begin{table}[t]
%\caption{TEXT}
%\begin{tabular}{column = lcr}
%\tophline
%
%\middlehline
%
%\bottomhline
%\end{tabular}
%\belowtable{} % Table Footnotes
%\end{table}
%
%%% TWO-COLUMN TABLE
%
%%t
%\begin{table*}[t]
%\caption{TEXT}
%\begin{tabular}{column = lcr}
%\tophline
%
%\middlehline
%
%\bottomhline
%\end{tabular}
%\belowtable{} % Table Footnotes
%\end{table*}
%
%
%%% NUMBERING OF FIGURES AND TABLES
%%%
%%% If figures and tables must be numbered 1a, 1b, etc. the following command
%%% should be inserted before the begin{} command.
%
%\addtocounter{figure}{-1}\renewcommand{\thefigure}{\arabic{figure}a}
%
%
%%% MATHEMATICAL EXPRESSIONS
%
%%% All papers typeset by Copernicus Publications follow the math typesetting regulations
%%% given by the IUPAC Green Book (IUPAC: Quantities, Units and Symbols in Physical Chemistry,
%%% 2nd Edn., Blackwell Science, available at: http://old.iupac.org/publications/books/gbook/green_book_2ed.pdf, 1993).
%%%
%%% Physical quantities/variables are typeset in italic font (t for time, T for Temperature)
%%% Indices which are not defined are typeset in italic font (x, y, z, a, b, c)
%%% Items/objects which are defined are typeset in roman font (Car A, Car B)
%%% Descriptions/specifications which are defined by itself are typeset in roman font (abs, rel, ref, tot, net, ice)
%%% Abbreviations from 2 letters are typeset in roman font (RH, LAI)
%%% Vectors are identified in bold italic font using \vec{x}
%%% Matrices are identified in bold roman font
%%% Multiplication signs are typeset using the LaTeX commands \times (for vector products, grids, and exponential notations) or \cdot
%%% The character * should not be applied as mutliplication sign
%
%
%%% EQUATIONS
%
%%% Single-row equation
%
%\begin{equation}
%
%\end{equation}
%
%%% Multiline equation
%
%\begin{align}
%& 3 + 5 = 8\\
%& 3 + 5 = 8\\
%& 3 + 5 = 8
%\end{align}
%
%
%%% MATRICES
%
%\begin{matrix}
%x & y & z\\
%x & y & z\\
%x & y & z\\
%\end{matrix}
%
%
%%% ALGORITHM
%
%\begin{algorithm}
%\caption{…}
%\label{a1}
%\begin{algorithmic}
%…
%\end{algorithmic}
%\end{algorithm}
%
%
%%% CHEMICAL FORMULAS AND REACTIONS
%
%%% For formulas embedded in the text, please use \chem{}
%
%%% The reaction environment creates labels including the letter R, i.e. (R1), (R2), etc.
%
%\begin{reaction}
%%% \rightarrow should be used for normal (one-way) chemical reactions
%%% \rightleftharpoons should be used for equilibria
%%% \leftrightarrow should be used for resonance structures
%\end{reaction}
%
%
%%% PHYSICAL UNITS
%%%
%%% Please use \unit{} and apply the exponential notation

\end{document}

### 2016-09-27 manuscript/Paper-magnetic-elipsoid_metodologia.tex
paper-elipsoid introducao e metodologia do elipsoide

--- 2016-08-02 Paper-magnetic-elipsoid.tex
@@
 %% 2-Column Papers and Discussion Papers
-\documentclass[journal abbreviation, manuscript]{copernicus}
+\documentclass[gmd, manuscript]{copernicus}
 
@@
 \introduction  %% \introduction[modified heading if necessary]
-TEXT
+
+The magnetic method is considered one of the oldest geophysics techniques.
+The greek philosofer Thales supposedly did the first obsevations on magnetism in the sixth century.
+The chineses in the XII century, already used magnetic compasses as an instrument for marine orientation \citep{nabighian2005historical}.
+During the World War II there was a need for instruments of several magnitudes of precision higher than was available at the time for detection of submarines by aeromagntic exploration.
+Thus, the fluxgate magnetometer was invented, expanding the use of this method for geophysic exploration \citep{reford1964aeromagnetics,hanna1924some}.
+The diffusion of this method was quick and well accepted whereas the possiblity  of covering large areas in a relativey short time \citep{blakely1996potential,nabighian2005historical}.
+
+The applications of magnetic exploration includes several important study situations as estimating the average of basement relief, mapping geologic structures like faults and lithologic contacts; and also for mineral exploration, identifying mineral deposits and mapping geologic traps for oil and gas  \citep{oliveira2015estimation}.
+
+In the decade of 1970 \cite{farrar1979some} showed in his work the value of the ellipsoidal model in geophysic exploration, where it was used for analysis of magnetic anomalies of Tennant Crees's gold mine in Australia.
+The ellipsoid demonstrated to be the most competent geometry to model bodies of lenticular pipe shape and the most appropriate to handle self-desmagnetization of bodies of high susceptibilty - magnetic susceptibility higher than 0.1 SI \citep{clark2014methods}.
+
+In his book \textit{A Treatise on Electricity and Magnetism}, \cite{maxwell1881treatise} demonstrated that only shapes bounded by second degree surfaces are uniformly magnetized when placed in a uniform field.
+In the particular case of the ellipsoidal geometry, the intern magnetic field is independent of spatial coordinates, therefore its magnetization is completely homogeneous, making it the only geometric shape that has a true anlitic solution for self-desmagnetization \citep{clark1986magnetic}.
+
+The magnetic field resultant of an ellipsoid was presented the first time in full modeling in the space domain by \cite{emerson1985magnetic}, along a compilation of several others geometric shapes.
+Through a consistent notation this work tapped a hole in the literature that missed the ellipsoidal model.
+This model, however, consists in a division between prolate and oblate ellipsoids, with some differences in the algorithm.
+
+In this work, we will implement a generalized model for triaxial ellipsoids published by \cite{clark1986magnetic}.
+From the solution of gravitational potential for uniform ellipsoids, formally solved by \cite{dirichlet1839nouvelle} in his article \textit{Sur un nouvelle methode pour la determination des integrales multiples}, that uses first and second Legendre's normal elliptic integrals, and using the Poisson's relation \citep{grant1965interpretation} it is possible to calculate the magnetic potential, and posteriorly the magnetic field generated by the body calculating the gradient of this potential.
 
 \section{Methodology}
-TEXT
+The total-field anomaly can be described as a difference between the total field vector and the induced magnetization of the crust of the Earth, thats includes any anomalous distribuition of magnetization that can occur by magnetizied bodies in subsurface.
+This difference can be written as:
+\begin{equation} \label{eq:1}
+\Delta T^0_i = ||T_i|| - ||F_i||,
+\end{equation}
+where $\Delta T^0_i$ is the observed vector of total-field anomaly in the $i$-th position ($x_i$, $y_i$, $z_i$), $i = 1,...N$, $F_i$ is the geomagnetic field and $||.||$ is the Euclidian norm.
+The total-field vector $T_i$ is:
+\begin{equation}\label{eq:2}
+T_i = F_i + B_i,
+\end{equation}
+and $B_i$ is the total induced magnetization vector produced by all sources of anomalous susceptibility distribuition.
+Considering $F_i$ a constant vector, $F_0$ for local ou regional scale, and that $||F_0|| \gg ||B_0||$, since, $B_i$ is a small pertubation of the magnetic field $F_i$, we can approximate the euclidian norm of the vector $T_i$ by a Taylor's expansion of first order:
+\begin{equation}\label{eq:3}
+||T_i|| \approx ||F_0 + B_i|| \approx ||F_0|| + F^T B_i
+\end{equation}
+where $T$ indicates transposition and
+\begin{equation}\label{eq:4}
+\hat{F} = \dfrac{F_o}{||F_0||}
+\end{equation}
 
-\subsection{Triaxial Ellipsoid}
+is a unit vector that represents the gradient of the function $||T_i||$ in relation to the vector's components $T_i$. This way, we can approximate the Eq.(\ref{eq:1}) of total-field anomaly to:
+\begin{equation}\label{eq:5}
+\Delta T \approx \hat{F^T} B_i, \quad i=1,...,N
+\end{equation}
+
+\subsection{The Forward model of a sphere}
+
+\subsection{The Forward model of a triaxial elipsoid}
 The implementation of the forward problem of a triaxial ellipsoid's magnetic field (three semi-axis $a > b > c$) is done in a new coordinate system, where its center is the center of this ellipsoidal body.
@@
 We will define this new coordinate system ($x_1,x_2,x_3$) by the unit vectors $\hat{v}_h (h=1,2,3)$ with the respect to the geographic axis $x$, $y$ e $z$:
-\loadeq{043}
-\loadeq{044}\
-\loadeq{045} 
-\\
+\begin{equation}
+\hat{v_1} = (l_1,m_1,n_1) = (-\cos\alpha \cos\delta, -\sin\alpha \cos\delta, -\sin\delta)
+\end{equation}
 
-The angles refering to the unit vectors are determined by the orientations of the ellipsoid's semi-axis.
-The angle $\alpha$ is the azimuth of semi-major axe ($a$) plus 180º.
+\begin{equation}
+\begin{split}
+\hat{v_2} = (l_2,m_2,n_2) = (\cos\alpha \cos\gamma \sin\delta + \sin\alpha \sin\gamma,\\ \sin\alpha \cos\gamma \sin\delta - \cos\alpha \sin\gamma, -\cos\gamma \cos\delta)
+\end{split}
+\end{equation}
+
+\begin{equation}
+\begin{split}
+\hat{v_3} = (l_3,m_3,n_3) = (\sin\alpha \cos\gamma - \cos\alpha \sin\gamma \sin\delta,\\ -\cos\alpha \cos\gamma - \sin\alpha \sin\gamma \sin\delta, \sin\gamma \cos\delta)
+\end{split}
+\end{equation}
+
+The angles refering to the unit vectors are determined by the orientations of the elipsoid's semi-axis.
+The angle $\alpha$ is the azimuth of semi-major axe ($a$) plus 180$^{\circ}$.
 Meanwhile $\delta$ is the inclination of semi-major axe ($a$) in relation to the geographic plane.
@@
 Thus, the coordinates of the body's semi-axis are given by:
-\loadeq{046}
+
+\begin{equation}
+x_h = (x-xc)l_h + (y-yc)m_h + (z-zc)n_h \quad (h= 1,2,3)
+\end{equation}
 
@@
 For an ellipsoid of semi-axis $a > b > c$, the equation that defines yours surface is:
-\loadeq{030}
+
+\begin{equation} \label{eq:elipsoide}
+\dfrac{x_1^2}{(a^2+s)} + \dfrac{x_2^2}{(b^2+s)} + \dfrac{x_3^2}{(c^2+s)} = 1
+\end{equation}
 
@@
 There is, however, a set of values for $s (\lambda,\mu,\nu)$, which are roots of the cubic equation:
-\loadeq{031}
+
+\begin{equation} \label{eq:cubica}
+s^3 + p_2s^2 + p_1s + p_0 = 0
+\end{equation}
 
@@
 Their expressions are:
-\loadeq{038}\
-\loadeq{039}\
-\loadeq{040}
+
+\begin{equation}
+\lambda = 2 \sqrt{\left (\dfrac{-p}{3} \right)} \cos \left(\dfrac{\theta}{3} \right) - \dfrac{p_2}{3}
+\end{equation}
+
+\begin{equation}
+\mu = -2 \sqrt{\left (\dfrac{-p}{3} \right)} \cos \left(\dfrac{\theta}{3} + \dfrac{\pi}{3} \right) - \dfrac{p_2}{3}
+\end{equation}
+
+\begin{equation}
+\mu = -2 \sqrt{\left (\dfrac{-p}{3} \right)} \cos \left(\dfrac{\theta}{3} - \dfrac{\pi}{3} \right) - \dfrac{p_2}{3}
+\end{equation}
 
 Where:
-\loadeq{032}\
-\loadeq{033}\
-\loadeq{034}\
-\loadeq{035}\
-\loadeq{036}\
-\loadeq{037}\
+
+\begin{equation}
+p_0 = a^2b^2c^2 - b^2c^2x_1^2 - c^2a^2x_2^2 - a^2b^2x_3^2
+\end{equation}
+
+\begin{equation}
+p_1 = a^2b^2 + b^2c^2 + c^2a^2 - (b^2+c^2)x_1^2 - (c^2+a^2)x_2^2 - (a^2+b^2)x_3^2
+\end{equation}
+
+\begin{equation}
+p_2 = a^2 + b^2 + c^2 - x_1^2 - x_2^2 - x_3^2
+\end{equation}
+
+\begin{equation}
+p = p_1 - \dfrac{p_2^2}{3}
+\end{equation}
+
+\begin{equation}
+q = p_0 - \dfrac{p_1p_2}{3} + 2 \left(\dfrac{p_2}{3} \right)^3
+\end{equation}
+
+\begin{equation}
+\theta = \cos^{-1} \left[\dfrac{-q}{2} \sqrt{\left(\dfrac{-p}{3} \right)^3} \right]
+\end{equation}
 
 The calculation of the largest root $\lambda$ of the equation \eqref{eq:cubica} is essential, since the magnetic field depends on the spatial derivatives of the equation \ref{eq:elipsoide}, where $s$ admits the value of $\lambda$.
-\loadeq{010}
+
+\begin{equation}
+\dfrac{\partial \lambda}{\partial x_1} = \dfrac{2x_1/(a^2+\lambda)}{\left(\dfrac{x_1}{a^2+\lambda}\right)^2 + \left(\dfrac{x_2}{b^2+\lambda}\right)^2 + \left(\dfrac{x_3}{c^2+\lambda}\right)^2}
+\end{equation}
 
@@
 The desmagnetization factors are given by:
-\loadeq{047}
-\loadeq{048}
-\loadeq{049}
+
+\begin{equation}
+N_1 = \dfrac{4 \pi abc}{(a^2-b^2)\sqrt{(a^2-c^2)}} [F(\theta,k) - E(\theta,k)]
+\end{equation}
+
+\begin{equation}
+N_2 = \dfrac{4 \pi abc \sqrt{(a^2-c^2)}}{(a^2-b^2)(b^2-c^2)} \left[E(\theta,k) - \left(\dfrac{b^2-c^2}{a^2-c^2} \right) F(\theta,k) - \dfrac{c(a^2-b^2)}{ab \sqrt{(a^2-c^2)}} \right]
+\end{equation}
+
+\begin{equation}
+N_3 = \dfrac{4 \pi abc}{(b^2-c^2)\sqrt{(a^2-c^2)}} \left[\dfrac{b \sqrt{(a^2-c^2)}}{ac} - E(\theta,k) \right]
+\end{equation}
 
 Where $F(\theta,k)$ e $E(\theta,k)$ are first and second Legendre's normal elliptical integrals, respectively. To calculate $k$ and $\theta$ we have the following expressions:
+
 \begin{equation}
@@
 The susceptibility tensor matrix is:
-\loadeq{050}
+
+\begin{equation}
+k_{ij} = \sum_r k_r (L_r l_i + M_r m_i + N_r n_i) (L_r l_j + M_r m_j + N_r n_j) \quad (r = 1,2,3)
+\end{equation}
 
 The Earth's field vector, $F$, and the remanent magnetization ,$d$, also must be converted to the body's coordinates:
-\loadeq{051}
-\loadeq{052}
+
+\begin{equation}
+F_h = F(l \, l_h + m \, m_h + n \, n_h)
+\end{equation}
+
+\begin{equation}
+(J_N)_h = J_N (l_N l_h + m_n m_h + n_N n_h)
+\end{equation}
 
@@
 In the case that the body has a very low susceptibility ($\chi < 0.1$ SI) the self-demagnatization is negligible and the resultant magnetic vector is given by:
-\loadeq{053}
+
+\begin{equation}
+\tilde{J}_R = K\tilde{F} + \tilde{J}_{NRM}
+\end{equation}
 
 For values bigger than 0.1 SI the resultant magnetic vector is:
-\loadeq{055}
+
+\begin{equation}
+\tilde{J}_{Rc} = A^{-1} \tilde{J}_R
+\end{equation}
 
 Where:
-\loadeq{054}
+
+\begin{equation}
+A = I + KN = \left[\begin{matrix} 
+1+k_{11}N_1 \quad & k_{12}N_2 \quad & k_{13}N_3 \\\\
+k_{21}N_1 \quad & 1+k_{22}N_2 \quad & k_{23}N_3 \\\\
+k_{31}N_1 \quad & k_{23}N_2 \quad & 1+k_{33}N_3
+\end{matrix}\right]
+\end{equation}
 
@@
 
-\loadeq{056}
-\loadeq{057}
-\loadeq{058}
+\begin{equation} \label{eq:campo_e}
+\Delta B_1 = f_1 \dfrac{\partial \lambda}{\partial x_1} - 2 \pi abc \, J_1 \, A(\lambda) 
+\end{equation}
+
+\begin{equation}
+\Delta B_2 = f_1 \dfrac{\partial \lambda}{\partial x_2} - 2 \pi abc \, J_2 \, B(\lambda)
+\end{equation}
+
+\begin{equation}
+\Delta B_3 = f_1 \dfrac{\partial \lambda}{\partial x_3} - 2 \pi abc \, J_3 \, C(\lambda)
+\end{equation}
 
 where:
-\loadeq{059}\\
-\loadeq{060}\\
-\loadeq{061}\\
-\loadeq{062}\\
+
+\begin{equation}
+f_1 = \dfrac{2\pi abc}{\sqrt{[(a^2+\lambda)(b^2+\lambda)(c^2+\lambda)]}} \left[\dfrac{J_1x_1}{a^2+\lambda} + \dfrac{J_2x_2}{b^2+\lambda} + \dfrac{J_3x_3}{c^2+\lambda}\right]
+\end{equation}
+
+\begin{equation}
+A(\lambda) = \dfrac{2}{(a^2-b^2) \sqrt{(a^2-c^2)}} [F(\theta^{'},k) - E(\theta^{'},k)]
+\end{equation}
+
+\begin{equation}
+B(\lambda) = \dfrac{2 \sqrt{(a^2-c^2)}}{(a^2-b^2)(b^2-c^2)} \left[ E(\theta^{'},k) - \left(\dfrac{b^2-c^2}{a^2-c^2} \right) F(\theta^{'},k) - \dfrac{k^2\sin\theta^{'}\cos\theta^{'}}{\sqrt{(1-k^2\sin^2\theta^{'})}} \right]
+\end{equation}
+
+\begin{equation} \label{eq:integralC}
+C(\lambda) = \dfrac{2}{(b^2-c^2) \sqrt{(a^2-c^2)}} \left[\dfrac{\sin\theta^{'} \sqrt{(1-k^2\sin^2\theta^{'})}} {\cos\theta^{'}} - E(\theta^{'},k) \right]
+\end{equation}
 
 And:
-\loadeq{063}\\
+
+\begin{equation}
+\theta^{'} = \sin^{-1} \left(\dfrac{a^2-c^2}{a^2+\lambda}\right)^{0.5} \quad (0 \le \theta^{'} \le \pi/2) 
+\end{equation}
 
@@
 This problem was solved by Dirichlet in 1839 \citep{clark1986magnetic} for the gravitational potential given by:
+
 \begin{equation}
@@
 Thus, the magnetic field generated by the ellipsoid is:
-\loadeq{007}
+
+\begin{equation}\label{eq:campoGeo}
+b_i^j = 2\pi a_j b_j c_j \times [M_i^j - D_i^j] \times J^j \quad j=1,...,L
+\end{equation}
 
 With:
-\loadeq{009}\\
-\loadeq{011}\\
+
+\begin{equation}
+M_i^j = \dfrac{1}{\sqrt{[(a^2+\lambda)(b^2+\lambda)(c^2+\lambda)]}}
+\left[\begin{matrix} 
+\dfrac{\partial \lambda}{\partial x_1} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_1} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_1} \dfrac{x_3}{c^2+\lambda} \\\\
+\dfrac{\partial \lambda}{\partial x_2} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_2} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_2} \dfrac{x_3}{c^2+\lambda} \\\\
+\dfrac{\partial \lambda}{\partial x_3} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_3} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_3} \dfrac{x_3}{c^2+\lambda}
+\end{matrix}\right]_{3 \times 3}
+\end{equation}
+
+\begin{equation}
+D_i^j =
+\left[\begin{matrix} 
+A(\lambda) & 0 & 0 \\
+0 & B(\lambda) & 0 \\
+0 & 0 & C(\lambda)
+\end{matrix}\right]
+\end{equation}
 
 For $j = 1,...,L$, the number of ellipsoids been modeled and $i = 1,...,N$  for the $i$th element of the calculated field. The total magnetic field then is:
-\loadeq{006}
+
+\begin{equation}\label{eq:campoGeoNL}
+B_i = \sum_{j=1}^{L} b_i^j, \quad i=1,...,N
+\end{equation}
 
@@
 To calculate each component of the magnetic field's vector back:
-\loadeq{064}
-\loadeq{065}
-\loadeq{066}
 
-Been $\Delta T^0$, $i = 1,...,N$, the total field anomaly observed in positions (xi, yi, zi), mathematically it can be rewritten as:
-\loadeq{001}
+\begin{equation}
+\Delta B_x = \Delta B_1l_1 + \Delta B_2l_2 + \Delta B_3l_3
+\end{equation}
 
-The total field vector $T_i$ can be represented by:
-\loadeq{002}
+\begin{equation}
+\Delta B_y = \Delta B_1m_1 + \Delta B_2m_2 + \Delta B_3m_3
+\end{equation}
 
-Where $F_i$ is the magnetic field's vector and $B_i$ the magnetic induction's vector generated by the magnetic sources.
-Considering $F_i$ a constant vector $F_0$ for local ou regional scale, and that $||F_0|| \gg ||B_0||$, since, $B_i$ is a small pertubation of the magnetic field $F_i$, we can approximate the euclidian norm of the vector $T_i$ by a Taylor's expansion of first order:
-\loadeq{003}
-
-where $T$ indicates transposition and
-\loadeq{004}
-
-is a unit vector that represents the gradient of the function $||T_i||$ in relation to the vector's components $T_i$.
-This way, we can approximate the equation \eqref{eq:anomalia} of total-field anomaly to:
-\loadeq{005}
-
-Substituting the magnetic induction' equation \eqref{eq:campoGeo} in the total magnetic induction \eqref{eq:campoGeoNL} and using the total-field anomaly approximation \eqref{Anomaliaaproximada} we obtain the predict anomaly for the total field produced by the $L$ ellipsoids:
-\loadeq{018}
-
-The equation \eqref{eq:anomaliaCompleta} can be rewritten as:
-\loadeq{019}
-
-Where:
-\loadeq{020}
-
-And:
-\loadeq{021}
-
-The equation \eqref{eq:anomaliaJ} shows the dependence for the predicted total-field anomaly related to the vector $h$. We can rewrite it in matrix notation:
-\loadeq{022}
-
-Been $A$ the matrix:
-\loadeq{023}
-
-With $a_i$, $i= 1,...,N$ the vector of dimension $3L$ defined in equation \eqref{eq:matrizsensibilidade}.
+\begin{equation}
+\Delta B_z = \Delta B_1n_1 + \Delta B_2n_2 + \Delta B_3n_3
+\end{equation}
 
@@
 
-\begin{thebibliography}{}
+%%\begin{thebibliography}{}
 
-\bibitem[AUTHOR(YEAR)]{LABEL}
-REFERENCE 1
+%%\bibitem[AUTHOR(YEAR)]{LABEL}
+%%REFERENCE 1
 
-\bibitem[AUTHOR(YEAR)]{LABEL}
-REFERENCE 2
+%%\bibitem[AUTHOR(YEAR)]{LABEL}
+%%REFERENCE 2
 
-\end{thebibliography}
+%%\end{thebibliography}
+
+\bibliographystyle{copernicus}
+\bibliography{references}
 

### 2016-10-06 manuscript/Paper-magnetic-elipsoid_metodologia.tex
paper-elipsoid modificacao metodologia do elipsoide

@@
 
-\title{3D MAGNETIC MODELLING FOR ELLIPSOIDS}
+\title{3D MAGNETIC MODELLING FOR ELIPSOIDS}
 
@@
 \begin{abstract}
-In this work we will present results from a numerical modeling of the magnetic field and total field anomaly, represented by prolate and triaxial ellipsoids sources.
+In this work we will present results from a numerical modeling of the magnetic field and total field anomaly, represented by triaxial and prolate elipsoidal sources.
 Such approach provide analytical results for anisotropy of magnetic susceptibility as well as for self-demagnetization effects, which can be easily adapted for distinctive geologic structures - hence being an useful tool for educational (e.g., potential methods and rock magnetism) and applied geophysics (e.g., characterization of high magnetic susceptibility, mineralized bodies) purposes.
@@
 The chineses in the XII century, already used magnetic compasses as an instrument for marine orientation \citep{nabighian2005historical}.
-During the World War II there was a need for instruments of several magnitudes of precision higher than was available at the time for detection of submarines by aeromagntic exploration.
+During the World War II there was a need for instruments of several magnitudes of precision higher than was available at the time for the detection of submarines trough aeromagnetic exploration.
 Thus, the fluxgate magnetometer was invented, expanding the use of this method for geophysic exploration \citep{reford1964aeromagnetics,hanna1924some}.
-The diffusion of this method was quick and well accepted whereas the possiblity  of covering large areas in a relativey short time \citep{blakely1996potential,nabighian2005historical}.
+The diffusion of this method was quick and well accepted whereas the possiblity  of covering large areas in a relatively short time \citep{blakely1996potential,nabighian2005historical}.
 
-The applications of magnetic exploration includes several important study situations as estimating the average of basement relief, mapping geologic structures like faults and lithologic contacts; and also for mineral exploration, identifying mineral deposits and mapping geologic traps for oil and gas  \citep{oliveira2015estimation}.
+The applications of magnetic exploration includes several important study situations, as estimating the average of basement relief, mapping geologic structures as faults and lithologic contacts; and also for mineral exploration, identifying mineral deposits and mapping geologic traps for oil and gas  \citep{oliveira2015estimation}.
 
-In the decade of 1970 \cite{farrar1979some} showed in his work the value of the ellipsoidal model in geophysic exploration, where it was used for analysis of magnetic anomalies of Tennant Crees's gold mine in Australia.
-The ellipsoid demonstrated to be the most competent geometry to model bodies of lenticular pipe shape and the most appropriate to handle self-desmagnetization of bodies of high susceptibilty - magnetic susceptibility higher than 0.1 SI \citep{clark2014methods}.
+In the decade of 1970 \cite{farrar1979some} showed in his work the value of the elipsoidal model in geophysic exploration, where it was used for analysis of magnetic anomalies in Tennant Creeks's gold mine in Australia.
+The elipsoid was the most correct geometry to model bodies of lenticular pipe shape and the most appropriate to handle self-desmagnetization of bodies of high susceptibilty - magnetic susceptibility higher than 0.1 SI \citep{clark2014methods}.
 
 In his book \textit{A Treatise on Electricity and Magnetism}, \cite{maxwell1881treatise} demonstrated that only shapes bounded by second degree surfaces are uniformly magnetized when placed in a uniform field.
-In the particular case of the ellipsoidal geometry, the intern magnetic field is independent of spatial coordinates, therefore its magnetization is completely homogeneous, making it the only geometric shape that has a true anlitic solution for self-desmagnetization \citep{clark1986magnetic}.
+In the particular case of the elipsoidal geometry, the intern magnetic field is independent of spatial coordinates, therefore its magnetization is completely homogeneous, making it the only geometric shape that has a true analitic solution for self-desmagnetization \citep{clark1986magnetic}.
 
-The magnetic field resultant of an ellipsoid was presented the first time in full modeling in the space domain by \cite{emerson1985magnetic}, along a compilation of several others geometric shapes.
-Through a consistent notation this work tapped a hole in the literature that missed the ellipsoidal model.
-This model, however, consists in a division between prolate and oblate ellipsoids, with some differences in the algorithm.
+The magnetic field resultant of an elipsoid was presented the first time in full modeling in the space domain by \cite{emerson1985magnetic}, along a compilation of several others geometric shapes.
+Through a consistent notation this work tapped a hole in the literature that missed the elipsoidal model.
+This model, however, consists in a division between prolate and oblate ellipsoids, with a few differences in the algorithm.
 
 In this work, we will implement a generalized model for triaxial ellipsoids published by \cite{clark1986magnetic}.
-From the solution of gravitational potential for uniform ellipsoids, formally solved by \cite{dirichlet1839nouvelle} in his article \textit{Sur un nouvelle methode pour la determination des integrales multiples}, that uses first and second Legendre's normal elliptic integrals, and using the Poisson's relation \citep{grant1965interpretation} it is possible to calculate the magnetic potential, and posteriorly the magnetic field generated by the body calculating the gradient of this potential.
+From the solution of gravitational potential for uniform elipsoids, formally solved by \cite{dirichlet1839nouvelle} in his article \textit{Sur un nouvelle methode pour la determination des integrales multiples}, that uses first and second Legendre's normal elliptic integrals, and using the Poisson's relation \citep{grant1965interpretation} it is possible to calculate the magnetic potential, and posteriorly the magnetic field generated by the body calculating the gradient of this potential.
 
 \section{Methodology}
-The total-field anomaly can be described as a difference between the total field vector and the induced magnetization of the crust of the Earth, thats includes any anomalous distribuition of magnetization that can occur by magnetizied bodies in subsurface.
+The total-field anomaly can be described as a difference between the total field vector and the induced magnetization of the crust of the Earth, that includes any anomalous distribuition of magnetization that can occur by magnetizied bodies in subsurface.
 This difference can be written as:
@@
 \subsection{The Forward model of a triaxial elipsoid}
-The implementation of the forward problem of a triaxial ellipsoid's magnetic field (three semi-axis $a > b > c$) is done in a new coordinate system, where its center is the center of this ellipsoidal body.
+The implementation of the forward problem of a triaxial elipsoid's magnetic field (three semi-axis $a > b > c$) is done in a new coordinate system, where its origin is the center of this elipsoidal body.
 
-We will define this new coordinate system ($x_1,x_2,x_3$) by the unit vectors $\hat{v}_h (h=1,2,3)$ with the respect to the geographic axis $x$, $y$ e $z$:
+This new coordinate system ($x_1,x_2,x_3$) is defined by the unit vectors $\hat{v}_h (h=1,2,3)$ with the respect with the geographic axis $x$, $y$ e $z$:
 \begin{equation}
@@
 
-The angles refering to the unit vectors are determined by the orientations of the elipsoid's semi-axis.
+The angles referring to the unit vectors are determined by the orientations of the elipsoid's semi-axis.
 The angle $\alpha$ is the azimuth of semi-major axe ($a$) plus 180$^{\circ}$.
-Meanwhile $\delta$ is the inclination of semi-major axe ($a$) in relation to the geographic plane.
-Lastly, $\gamma$ is the angle between the semi-mid axe ($b$) and the vertical projection of the ellipsoid's center with the geographic plane.
+While $\delta$ is the inclination of semi-major axe ($a$) in relation to the geographic plane.
+Lastly, $\gamma$ is the angle between the semi-mid axe ($b$) and the vertical projection of the elipsoid's center with the geographic plane.
 
@@
 
-Where $x_c$, $y_c$ e $z_c$ are the coordinates of the ellipsoid's center in the geographic system $x$, $y$ e $z$.
+Where $x_c$, $y_c$ e $z_c$ are the coordinates of the elipsoid's center in the geographic system $x$, $y$ e $z$.
 
-For an ellipsoid of semi-axis $a > b > c$, the equation that defines yours surface is:
+For an elipsoid of semi-axis $a > b > c$, the equation that defines your surface is:
 
@@
 
-The parameter $s$ controls the ellipsoid form.
+The parameter $s$ controls the elipsoid form.
 When $s$ gets close to $\infty$ the equation \eqref{eq:elipsoide} tends to the sphere equation of radius $r=\sqrt{\lambda}$.
-When $s = -c^2$, the last term of the ellipsoid's equation is less than zero and she becomes the equation of a circle.
+When $s = -c^2$, the last term of the elipsoid's equation is less than zero and it becomes the equation of a circle.
 
@@
 
-This set of roots, called ellipsoidal coordinates, correspond to parameters of a point ($x_1,x_2,x_3$) which are under the intersection of three ortogonal surfaces related to the body coordinates.
+This set of roots, called elipsoidal coordinates, correspond to the parameters of a point ($x_1,x_2,x_3$) which are under the intersection of three ortogonal surfaces related to the body coordinates.
 Their expressions are:
@@
 
-Where $F(\theta,k)$ e $E(\theta,k)$ are first and second Legendre's normal elliptical integrals, respectively. To calculate $k$ and $\theta$ we have the following expressions:
+Where $F(\theta,k)$ e $E(\theta,k)$ are first and second Legendre's normal eliptical integrals, respectively. To calculate $k$ and $\theta$ we have the following expressions:
 
@@
 
-Note that $L_r, M_r, N_r$ ($r = 1,2,3$), $l,m,n$ e $l_N, m_N, n_N$ depends on their respective vector's inclinations and declinations:
+Note that $L_r, M_r, N_r$ ($r = 1,2,3$), $l,m,n$ e $l_N, m_N, n_N$ depends on their respective vectors of inclinations and declinations:
 \begin{equation}
@@
 
-This way, the components of the magnetic field produced by a triaxial ellipsoid in the body's coordinates outside of it is:
+This way, the components of the magnetic field produced by a triaxial elipsoid in the body's coordinates outside of it is:
 
@@
 
-Both $F(\theta^{'}, k)$ as $E(\theta^{'}, k)$ are again the first and second  noraml Legendre's elliptical integrals.
-While $A(\lambda), B(\lambda), C(\lambda)$ are analytic solutions of the integrals of the potential equation of an ellpsoid.
+Both $F(\theta^{'}, k)$ as $E(\theta^{'}, k)$ are again the first and second  noraml Legendre's eliptical integrals.
+While $A(\lambda), B(\lambda), C(\lambda)$ are analytic solutions of the integrals of the potential equation of an elipsoid.
 This problem was solved by Dirichlet in 1839 \citep{clark1986magnetic} for the gravitational potential given by:
@@
 
-Using the equations from \eqref{eq:campo_e} to \eqref{eq:integralC}, we can rearrange them in a matrix format that will be more computationally efficient and will help us better see the inverse problem ahead.
-Thus, the magnetic field generated by the ellipsoid is:
+Using the equations from \eqref{eq:campo_e} to \eqref{eq:integralC}, we can rearrange them in a matrix format that will be more computationally efficient.
+Thus, the magnetic field generated by the elipsoid is:
 
@@
 
-For $j = 1,...,L$, the number of ellipsoids been modeled and $i = 1,...,N$  for the $i$th element of the calculated field. The total magnetic field then is:
+For $j = 1,...,L$, the number of elipsoids been modeled and $i = 1,...,N$  for the $i$th element of the calculated field. The total magnetic field then is:
 

### 2016-11-28 manuscript/Paper-magnetic-elipsoid_metodologia.tex
Atualizacao da introducao

@@
 
-The magnetic method is considered one of the oldest geophysics techniques.
-The greek philosofer Thales supposedly did the first obsevations on magnetism in the sixth century.
-The chineses in the XII century, already used magnetic compasses as an instrument for marine orientation \citep{nabighian2005historical}.
-During the World War II there was a need for instruments of several magnitudes of precision higher than was available at the time for the detection of submarines trough aeromagnetic exploration.
-Thus, the fluxgate magnetometer was invented, expanding the use of this method for geophysic exploration \citep{reford1964aeromagnetics,hanna1924some}.
-The diffusion of this method was quick and well accepted whereas the possiblity  of covering large areas in a relatively short time \citep{blakely1996potential,nabighian2005historical}.
+In the 19th century \cite{dirichlet1839nouvelle}, manage to solve the problem of the potential of a homogeneous ellipsoid with semi-axes $a \ge b \ge c$ by using the first and second Legendre's normal elliptic integrals.
 
-The applications of magnetic exploration includes several important study situations, as estimating the average of basement relief, mapping geologic structures as faults and lithologic contacts; and also for mineral exploration, identifying mineral deposits and mapping geologic traps for oil and gas  \citep{oliveira2015estimation}.
+In the late 19th century \cite{maxwell1881treatise}, showed that only bodies of second degree can be uniformly magnetized when placed in a uniform field.
+He also presented the formulae of the demagnetizing field in a uniformly magnetized ellipsoid of revolution.
+
+\cite{osborn1945demagnetizing}, published formulas for the demagnetizing factors of the general ellipsoid alongside with a table of values for different proportions of semi-axis
+
+\cite{stoner1945xcvii}, presented a more simple and friendly formulae of the demagnetizing factors for an ellipsoid, with step-by-step deduction.
+This work includes formulae for different parametrizations for the ellipsoid (triaxial, prolate, oblate).
+
+\cite{peake1953magnetic} published the formulas for the external field of ellipsoid of revolution in terms of elliptical integrals for external fields.
+
+\cite{chang1961fields} published the formulas for the external field of triaxial, prolate and oblate ellipsoids in terms of elliptical integrals for external fields.
 
@@
 
-In his book \textit{A Treatise on Electricity and Magnetism}, \cite{maxwell1881treatise} demonstrated that only shapes bounded by second degree surfaces are uniformly magnetized when placed in a uniform field.
-In the particular case of the elipsoidal geometry, the intern magnetic field is independent of spatial coordinates, therefore its magnetization is completely homogeneous, making it the only geometric shape that has a true analitic solution for self-desmagnetization \citep{clark1986magnetic}.
+The magnetic field resultant of an ellipsoid was presented the first time in full modeling in the space domain by \cite{emerson1985magnetic}, along a compilation of several others geometric shapes.
+Through a consistent notation this work tapped a hole in the literature that missed the ellipsoidal model.
+This model, however, consists in a division between prolate and oblate ellipsoids, with a few differences in the algorithm.
+A generalized model for triaxials ellipsoids was published by \cite{clark1986magnetic}.
+Both in Emerson et al.
+and Clark et al.
+works, they were the firsts to include the calculations of the magnetic field in a different coordinate system other than with the position $(0,0,0)$ in the center of the ellipsoid (through a matrix of rotation).
+However, the codes presented for HP-41C are outdated and doesn't have a detailed descrition of the algorithm.
 
-The magnetic field resultant of an elipsoid was presented the first time in full modeling in the space domain by \cite{emerson1985magnetic}, along a compilation of several others geometric shapes.
-Through a consistent notation this work tapped a hole in the literature that missed the elipsoidal model.
-This model, however, consists in a division between prolate and oblate ellipsoids, with a few differences in the algorithm.
+\cite{tejedor1995external}, presented a work where they calculate the external field generated by ellipsoids using a variational method, in contrast to the usual method of Dirichlet.
 
-In this work, we will implement a generalized model for triaxial ellipsoids published by \cite{clark1986magnetic}.
-From the solution of gravitational potential for uniform elipsoids, formally solved by \cite{dirichlet1839nouvelle} in his article \textit{Sur un nouvelle methode pour la determination des integrales multiples}, that uses first and second Legendre's normal elliptic integrals, and using the Poisson's relation \citep{grant1965interpretation} it is possible to calculate the magnetic potential, and posteriorly the magnetic field generated by the body calculating the gradient of this potential.
+\cite{guo1998self}, showed three case studies of the importance of self-demagnetization of high susceptibilties bodies when modelling magnetic sources.
+A magnetic-iron deposit, volcanic-hosted iron deposit and an ultramafic-hoste nickel andcopper deposits.
+
+\cite{guo2001systematic}, published another paper analysing the errors of what an uncorrected by demagnetization data can affect on anmalies interpretation.
 

### 2016-11-29 manuscript/Paper-magnetic-elipsoid_metodologia.tex
Atualizacao da introducao

@@
 
-In the 19th century \cite{dirichlet1839nouvelle}, manage to solve the problem of the potential of a homogeneous ellipsoid with semi-axes $a \ge b \ge c$ by using the first and second Legendre's normal elliptic integrals.
-
-In the late 19th century \cite{maxwell1881treatise}, showed that only bodies of second degree can be uniformly magnetized when placed in a uniform field.
+In the 19th century, \cite{dirichlet1839nouvelle} manage to solve the problem of the potential of a homogeneous ellipsoid with semi-axes $a \ge b \ge c$ by using the first and second Legendre's normal elliptic integrals.
+Later, \cite{maxwell1881treatise} showed that only bodies of second degree can be uniformly magnetized when placed in a uniform field.
 He also presented the formulae of the demagnetizing field in a uniformly magnetized ellipsoid of revolution.
 
-\cite{osborn1945demagnetizing}, published formulas for the demagnetizing factors of the general ellipsoid alongside with a table of values for different proportions of semi-axis
+The formulas for the demagnetizing factors of the general ellipsoid alongside a table of values for different proportions of semi-axis was published by \cite{osborn1945demagnetizing}.
+In the same year, \cite{stoner1945xcvii} presented a more simple and friendly formulas of the demagnetizing factors for an ellipsoid, with step-by-step deduction.
+This work includes formulas for different parametrizations for the ellipsoid (triaxial, prolate, oblate).
 
-\cite{stoner1945xcvii}, presented a more simple and friendly formulae of the demagnetizing factors for an ellipsoid, with step-by-step deduction.
-This work includes formulae for different parametrizations for the ellipsoid (triaxial, prolate, oblate).
+A decade later, \cite{peake1953magnetic} published a paper with the formulas for the external field of ellipsoid of revolution.
+Some years after that, \cite{chang1961fields} showed the formulas for the external field of triaxial, prolate and oblate ellipsoids.
+Both used the Dirichlet solution in terms of elliptical integrals for external fields.
+More recently, \cite{tejedor1995external}, gave the calculations of the external field generated by ellipsoids using a variational method, in contrast to the usual method of Dirichlet.
 
-\cite{peake1953magnetic} published the formulas for the external field of ellipsoid of revolution in terms of elliptical integrals for external fields.
-
-\cite{chang1961fields} published the formulas for the external field of triaxial, prolate and oblate ellipsoids in terms of elliptical integrals for external fields.
-
-In the decade of 1970 \cite{farrar1979some} showed in his work the value of the elipsoidal model in geophysic exploration, where it was used for analysis of magnetic anomalies in Tennant Creeks's gold mine in Australia.
-The elipsoid was the most correct geometry to model bodies of lenticular pipe shape and the most appropriate to handle self-desmagnetization of bodies of high susceptibilty - magnetic susceptibility higher than 0.1 SI \citep{clark2014methods}.
+In the decade of 1970 \cite{farrar1979some} showed in his work the value of the ellipsoidal model in geophysic exploration, where it was used for analysis of magnetic anomalies in Tennant Creeks's gold mine in Australia.
+The ellipsoid was the most correct geometry to model bodies of lenticular pipe shape and the most appropriate to handle self-desmagnetization of bodies of high susceptibilty - magnetic susceptibility higher than 0.1 SI \citep{clark2014methods}.
+\cite{guo1998self}, showed three case studies of the importance of self-demagnetization of high susceptibilties bodies when modelling magnetic sources.
+A magnetic-iron deposit, volcanic-hosted iron deposit and an ultramafic-hoste nickel andcopper deposits.
+The same author years later,\cite{guo2001systematic}, published another paper analysing the errors of what an uncorrected by demagnetization data can affect on anmalies interpretation.
 
@@
 works, they were the firsts to include the calculations of the magnetic field in a different coordinate system other than with the position $(0,0,0)$ in the center of the ellipsoid (through a matrix of rotation).
-However, the codes presented for HP-41C are outdated and doesn't have a detailed descrition of the algorithm.
-
-\cite{tejedor1995external}, presented a work where they calculate the external field generated by ellipsoids using a variational method, in contrast to the usual method of Dirichlet.
-
-\cite{guo1998self}, showed three case studies of the importance of self-demagnetization of high susceptibilties bodies when modelling magnetic sources.
-A magnetic-iron deposit, volcanic-hosted iron deposit and an ultramafic-hoste nickel andcopper deposits.
-
-\cite{guo2001systematic}, published another paper analysing the errors of what an uncorrected by demagnetization data can affect on anmalies interpretation.
+However, the codes presented for HP-41C are outdated and doesn't have a descrition of the algorithm, difficulting the reproduction by the cientific commnunity.
+This may the reason why the magnetic field modelling of the ellipsoid, in general, is only used through comercial softwares.
 

### 2016-11-30 manuscript/Paper-magnetic-elipsoid_metodologia.tex
correcao no meu nome
Atualizacao introducao e metodologia

@@
 \Author[1]{Diego}{Takahashi Tomazella}
-\Author[1]{Vanderlei}{Coelho Oliveira Junior}
+\Author[1]{Vanderlei}{C. Oliveira Jr}
 
@@
 Later, \cite{maxwell1881treatise} showed that only bodies of second degree can be uniformly magnetized when placed in a uniform field.
-He also presented the formulae of the demagnetizing field in a uniformly magnetized ellipsoid of revolution.
+\cite{thomson1879and} presented the formulas of the potential and demagnetizing field using the standard integrals expressions for the ellispoid of revolution.
 
@@
 In the same year, \cite{stoner1945xcvii} presented a more simple and friendly formulas of the demagnetizing factors for an ellipsoid, with step-by-step deduction.
-This work includes formulas for different parametrizations for the ellipsoid (triaxial, prolate, oblate).
+This work includes formulas for different parametrizations of the ellipsoid (triaxial, prolate, oblate).
 
@@
 
-In the decade of 1970 \cite{farrar1979some} showed in his work the value of the ellipsoidal model in geophysic exploration, where it was used for analysis of magnetic anomalies in Tennant Creeks's gold mine in Australia.
+In the decade of 1970, \cite{farrar1979some} showed in his work the value of the ellipsoidal model in geophysic exploration, where it was used for analysis of magnetic anomalies in Tennant Creeks's gold mine in Australia.
 The ellipsoid was the most correct geometry to model bodies of lenticular pipe shape and the most appropriate to handle self-desmagnetization of bodies of high susceptibilty - magnetic susceptibility higher than 0.1 SI \citep{clark2014methods}.
 \cite{guo1998self}, showed three case studies of the importance of self-demagnetization of high susceptibilties bodies when modelling magnetic sources.
-A magnetic-iron deposit, volcanic-hosted iron deposit and an ultramafic-hoste nickel andcopper deposits.
-The same author years later,\cite{guo2001systematic}, published another paper analysing the errors of what an uncorrected by demagnetization data can affect on anmalies interpretation.
+A magnetic-iron deposit, a volcanic-hosted iron deposit and an ultramafic-hosted nickel and copper deposits.
+The same author years later,\cite{guo2001systematic}, published another paper analysing the errors of what an uncorrected by demagnetization data can affect in anomalies interpretation.
 
@@
 and Clark et al.
-works, they were the firsts to include the calculations of the magnetic field in a different coordinate system other than with the position $(0,0,0)$ in the center of the ellipsoid (through a matrix of rotation).
-However, the codes presented for HP-41C are outdated and doesn't have a descrition of the algorithm, difficulting the reproduction by the cientific commnunity.
-This may the reason why the magnetic field modelling of the ellipsoid, in general, is only used through comercial softwares.
+works, they were the firsts to include the calculations of the magnetic field in a different coordinate system other than with the origin in the center of the ellipsoid (through a matrix of rotation).
+However, the codes presented for HP-41C calculators are outdated and don't have a descrition of the algorithm, difficulting the reproduction by the cientific commnunity.
+This may be the reason why the magnetic field modelling of the ellipsoid, in general, is manly used through commercial softwares.
+
+As shown, the problem of the magnetic field of the ellipsoid is scattered through the literature, wich can difficult the access to many.
+This article come as a junction of previous works, making the problem easier and more understandable.
+Together we present an algorithm in a modern language with a complete descrition of it.
+The code will be available for free usage of the geophysics community.
 
 \section{Methodology}
+
 The total-field anomaly can be described as a difference between the total field vector and the induced magnetization of the crust of the Earth, that includes any anomalous distribuition of magnetization that can occur by magnetizied bodies in subsurface.
@@
 \begin{equation}\label{eq:5}
-\Delta T \approx \hat{F^T} B_i, \quad i=1,...,N
+\Delta T \approx \hat{F}^T \bar{B}_i, \quad i=1,...,NF
+\end{equation}
+
+The field now $\bar{B}_i$ is represented this way to show that is in the geographic coordinates.
+One of the main steps to calculate the magnetic field of an ellipsoid is to change this system of coordinates to the body coordinates with origin in the center of it.
+The conversion can be done through a matrix of rotation $\bar{\bar{V}}$ that differs with the geometric type of ellipsoid, so the formulas will be shown later, separately for each one.
+But, in a general way, the conversion is:
+\begin{equation}\label{eq:5}
+\bar{r}_i = \bar{\bar{V}} \tilde{r}_i + \bar{r}_c,
+\end{equation}
+
+The vector $\bar{r}_i$ has the positions $x,y,z$ in the geographic coordinates, $\bar{r}_i$ has the positions $x1,x2,x3$ in the body coordinates and $\bar{r}_c$ is the position of the center of the body in the geographic coordinates.
+
+The same way the matrix of conversion can be used to change the magnetic field calculate in the body coordinates, back to the geopraphic, where is more useful to us:
+\begin{equation}\label{eq:5}
+\bar{B}_i = \bar{\bar{V}} \tilde{B}_i
 \end{equation}
@@
 \begin{equation}
-\hat{v_1} = (l_1,m_1,n_1) = (-\cos\alpha \cos\delta, -\sin\alpha \cos\delta, -\sin\delta)
+\textbf{v}_1 = (l_1,m_1,n_1) = (-\cos\alpha \cos\delta, -\sin\alpha \cos\delta, -\sin\delta)
 \end{equation}
@@
 \begin{split}
-\hat{v_2} = (l_2,m_2,n_2) = (\cos\alpha \cos\gamma \sin\delta + \sin\alpha \sin\gamma,\\ \sin\alpha \cos\gamma \sin\delta - \cos\alpha \sin\gamma, -\cos\gamma \cos\delta)
+\textbf{v}_2 = (l_2,m_2,n_2) = (\cos\alpha \cos\gamma \sin\delta + \sin\alpha \sin\gamma,\\ \sin\alpha \cos\gamma \sin\delta - \cos\alpha \sin\gamma, -\cos\gamma \cos\delta)
 \end{split}
@@
 \begin{split}
-\hat{v_3} = (l_3,m_3,n_3) = (\sin\alpha \cos\gamma - \cos\alpha \sin\gamma \sin\delta,\\ -\cos\alpha \cos\gamma - \sin\alpha \sin\gamma \sin\delta, \sin\gamma \cos\delta)
+\textbf{v}_3 = (l_3,m_3,n_3) = (\sin\alpha \cos\gamma - \cos\alpha \sin\gamma \sin\delta,\\ -\cos\alpha \cos\gamma - \sin\alpha \sin\gamma \sin\delta, \sin\gamma \cos\delta)
 \end{split}
@@
 Where:
-
 \begin{equation}
@@
 \begin{equation}
-\tilde{J}_R = K\tilde{F} + \tilde{J}_{NRM}
+\textbf{J}_R = K\textbf{F} + \textbf{J}_{NRM}
 \end{equation}
@@
 \begin{equation}
-\tilde{J}_{Rc} = A^{-1} \tilde{J}_R
+\textbf{J}_{Rc} = A^{-1} \textbf{J}_R
 \end{equation}

### 2016-12-02 manuscript/Paper-magnetic-elipsoid_metodologia.tex
Atualizacao da metodologia equacao superficie elipsoide

@@
 \end{equation}
+
+The equation of the surface of an ellipsoid can be written in a matrix form as:
+\begin{equation}
+(\bar{\textbf{r}} - \bar{\textbf{r}}_c)^T \bar{\bar{A}} (\bar{\textbf{r}} - \bar{\textbf{r}}_c) = 1,
+\end{equation}
+
+and $\bar{\bar{A}}$ is a 3X3 matrix formed by:
+\begin{equation}
+\bar{\bar{A}} = \bar{\bar{V}} 
+\left[\begin{matrix} 
+\dfrac{1}{a^2+s} & 0 & 0 \\
+0 & \dfrac{1}{b^2+s} & 0 \\
+0 & 0 & \dfrac{1}{c^2+s}
+\end{matrix}\right]
+\bar{\bar{V}}^T,
+\end{equation}
+
+where the columns of $\bar{\bar{V}}$ are the eigenvectors that represents the principal axes of the ellipsoid and the diagonal of the middle matrix the eigenvalues that represents the reciprocals of the square of the semi-axes $a^{-2}$, $b^{-2}$ and $c^{-2}$.
 

### 2016-12-02 code/auxiliary_functions.py
cria um arquivo de funcoes auxiliares para facilitar os testes do lambida

@@ -1,0 +1,248 @@
+from mpl_toolkits.mplot3d import axes3d
+import matplotlib.pyplot as plt
+import numpy as np
+
+def draw_main_system(ax, length_axes = 1., label_size = 22, elev=200, azim=-20):
+    '''
+    Plot the axes forming the main coordinate system.
+    
+    input
+    ax: axes of a matplotlib figure.
+    length_axes: float - length of the axes (in meters).
+        Default is 1.
+    label_size: float - size of the label font. Default is 22.
+    elev and azim: floats - parameters controlling the view
+        of the figure. Default is 200 and -20, respectively.
+        
+    output
+    matplotlib objects
+    '''
+
+    # x-axis
+    ax.quiver(length_axes, 0., 0., length_axes, 0., 0., 
+              length = length_axes, color='k', linewidth=2.0, linestyle='-',
+              arrow_length_ratio=0.1)
+    ax.text(1.05*length_axes, 0., 0., '$x$', color='k', fontsize=label_size)
+
+    # y-axis
+    ax.quiver(0., length_axes, 0., 0., length_axes, 0., 
+              length = length_axes, color='k', linewidth=2.0, linestyle='-',
+              arrow_length_ratio=0.1)
+    ax.text(0., 1.05*length_axes, 0., '$y$', color='k', fontsize=label_size)
+
+    # z-axis
+    ax.quiver(0., 0., length_axes, 0., 0., length_axes, 
+              length = length_axes, color='k', linewidth=2.0, linestyle='-',
+              arrow_length_ratio=0.1)
+    ax.text(0., 0., 1.05*length_axes, '$z$', color='k', fontsize=label_size)
+
+    ax.axis('off')
+
+    #ax.set_xlim(0., 1.1)
+    #ax.set_ylim(0., 1.1)
+    #ax.set_zlim(0., 1.1)
+
+    ax.view_init(elev=elev, azim=azim)
+    
+def draw_ellipsoid(ax, xc, yc, zc, a, b, c, alpha, gamma, delta,
+                   u, v, body_color, body_alpha,
+                   plot_axes=True, axes_color=(0,0,0), label_size=16):
+    '''
+    Plot an ellipsoidal body with axes a, b, c and
+    origin at (xc, yc, zc).
+    
+    input
+    ax: axes of a matplotlib figure.
[…]

### 2017-01-11 manuscript/Paper-magnetic-elipsoid_metodologia.tex
Update metodologia

--- 2016-11-30 manuscript/Paper-magnetic-elipsoid_metodologia.tex
@@
 \begin{abstract}
-In this work we will present results from a numerical modeling of the magnetic field and total field anomaly, represented by triaxial and prolate elipsoidal sources.
+In this work we will present results from a numerical modeling of the magnetic field and total field anomaly, represented by triaxial and prolate ellipsoidal sources.
 Such approach provide analytical results for anisotropy of magnetic susceptibility as well as for self-demagnetization effects, which can be easily adapted for distinctive geologic structures - hence being an useful tool for educational (e.g., potential methods and rock magnetism) and applied geophysics (e.g., characterization of high magnetic susceptibility, mineralized bodies) purposes.
@@
 \begin{equation} \label{eq:1}
-\Delta T^0_i = ||T_i|| - ||F_i||,
+\Delta \textbf{T}^0_i = ||\textbf{T}_i|| - ||\textbf{F}_i||,
 \end{equation}
-where $\Delta T^0_i$ is the observed vector of total-field anomaly in the $i$-th position ($x_i$, $y_i$, $z_i$), $i = 1,...N$, $F_i$ is the geomagnetic field and $||.||$ is the Euclidian norm.
+where $\Delta \textbf{T}^0_i$ is the observed vector of total-field anomaly in the $i$-th position ($x_i$, $y_i$, $z_i$), $i = 1,...N$, $F_i$ is the geomagnetic field and $||.||$ is the Euclidian norm.
 The total-field vector $T_i$ is:
 \begin{equation}\label{eq:2}
-T_i = F_i + B_i,
+\textbf{T}_i = \textbf{F}_i + \textbf{B}_i,
 \end{equation}
@@
 \begin{equation}\label{eq:3}
-||T_i|| \approx ||F_0 + B_i|| \approx ||F_0|| + F^T B_i
+||\textbf{T}_i|| \approx ||\textbf{F}_0 + \textbf{B}_i|| \approx ||\textbf{F}_0|| + \textbf{F}^T \textbf{B}_i
 \end{equation}
@@
 \begin{equation}\label{eq:4}
-\hat{F} = \dfrac{F_o}{||F_0||}
+\textbf{F} = \dfrac{\textbf{F}_o}{||\textbf{F}_0||}
 \end{equation}
@@
 \begin{equation}\label{eq:5}
-\Delta T \approx \hat{F}^T \bar{B}_i, \quad i=1,...,NF
+\Delta T \approx \textbf{F}^T \textbf{B}_i, \quad i=1,...,NF
 \end{equation}
 
-The field now $\bar{B}_i$ is represented this way to show that is in the geographic coordinates.
+The field now $\textbf{B}_i$ is represented this way to show that is in the geographic coordinates.
 One of the main steps to calculate the magnetic field of an ellipsoid is to change this system of coordinates to the body coordinates with origin in the center of it.
-The conversion can be done through a matrix of rotation $\bar{\bar{V}}$ that differs with the geometric type of ellipsoid, so the formulas will be shown later, separately for each one.
+The conversion can be done through a matrix of rotation $\textbf{V}$ that differs with the geometric type of ellipsoid, so the formulas will be shown later, separately for each one.
 But, in a general way, the conversion is:
-\begin{equation}\label{eq:5}
-\bar{r}_i = \bar{\bar{V}} \tilde{r}_i + \bar{r}_c,
+\begin{equation}\label{eq:6}
+\textbf{r}_i = \textbf{\textbf{V}} \tilde{\textbf{r}}_i + \textbf{r}_c,
 \end{equation}
 
-The vector $\bar{r}_i$ has the positions $x,y,z$ in the geographic coordinates, $\bar{r}_i$ has the positions $x1,x2,x3$ in the body coordinates and $\bar{r}_c$ is the position of the center of the body in the geographic coordinates.
-
-The same way the matrix of conversion can be used to change the magnetic field calculate in the body coordinates, back to the geopraphic, where is more useful to us:
-\begin{equation}\label{eq:5}
-\bar{B}_i = \bar{\bar{V}} \tilde{B}_i
+The vector $\textbf{r}_i$ has the positions $x,y,z$ in the geographic coordinates, $\tilde{\textbf{r}}_i$ has the positions $x1,x2,x3$ in the body coordinates and $\textbf{r}_c$ is the position of the center of the body in the geographic coordinates.
+The columns of $\textbf{\textbf{V}}$ are the eigenvectors that represents the directions cosines of the semi axes of the ellipsoid:
+\begin{equation}
+\textbf{\textbf{V}} =
+\left[\begin{matrix} 
+l_1 & l_2 & l_3 \\
+m_1 & m_2 & m_3 \\
+n_1 & n_2 & n_3
+\end{matrix}\right] = 
+\left[\begin{matrix} 
+\textbf{v}_1 \\
+\textbf{v}_2 \\
+\textbf{v}_3
+\end{matrix}\right]
 \end{equation}
 
-\subsection{The Forward model of a sphere}
+The equation of the surface of an ellipsoid can be written in a matrix form as:
+\begin{equation}
+(\textbf{r} - \textbf{r}_c)^T \textbf{A} (\textbf{r} - \textbf{r}_c) = 1,
+\end{equation}
 
-\subsection{The Forward model of a triaxial elipsoid}
-The implementation of the forward problem of a triaxial elipsoid's magnetic field (three semi-axis $a > b > c$) is done in a new coordinate system, where its origin is the center of this elipsoidal body.
+and $\textbf{\textbf{A}}$ is a 3X3 matrix formed by:
+\begin{equation}
+\textbf{\textbf{A}} = \textbf{\textbf{V}} 
+\left[\begin{matrix} 
+\dfrac{1}{a^2+s} & 0 & 0 \\
+0 & \dfrac{1}{b^2+s} & 0 \\
+0 & 0 & \dfrac{1}{c^2+s}
+\end{matrix}\right]
+\textbf{\textbf{V}}^T,
+\end{equation}
 
-This new coordinate system ($x_1,x_2,x_3$) is defined by the unit vectors $\hat{v}_h (h=1,2,3)$ with the respect with the geographic axis $x$, $y$ e $z$:
+The diagonal of the middle matrix, the eigenvalues that represents the reciprocals of the square of the semi-axes $a^{-2}$, $b^{-2}$ and $c^{-2}$.
+
+For all types of ellipsoids the magnetic field can be written as:
+\begin{equation}\label{eq:campoGeoNL}
+\tilde{\textbf{B}}_i = \sum_{j=1}^{L} \tilde{\textbf{b}}_i^j, \quad i=1,...,N
+\end{equation}
+
+where $\textbf{b}_i^j$ is:
+\begin{equation}\label{eq:campoGeo}
+\tilde{\textbf{b}}_i^j = 2\pi a_j b_j c_j \times [\textbf{M}_i^j - \textbf{D}_i^j] \times \tilde{\textbf{J}}^j \quad j=1,...,L
+\end{equation}
+
+The matrices $\textbf{M}_i^j$ and $\textbf{D}_i^j$ are different for each one, therefore they will be shown separately in the next sections.
+
+The same way the matrix of conversion can be used to change the magnetic field $\tilde{\textbf{B}}_i$ calculated in the body coordinates, back to the geopraphic, where is more useful to us:
+\begin{equation}\label{eq:7}
+\textbf{B}_i = \textbf{V} \tilde{\textbf{B}}_i
+\end{equation}
+
+Leading to:
 \begin{equation}
-\textbf{v}_1 = (l_1,m_1,n_1) = (-\cos\alpha \cos\delta, -\sin\alpha \cos\delta, -\sin\delta)
+\Delta \textbf{B}_x = \Delta \tilde{\textbf{B}}_1l_1 + \Delta \tilde{\textbf{B}}_2l_2 + \Delta \tilde{\textbf{B}}_3l_3
+\end{equation}
+\begin{equation}
+\Delta \textbf{B}_y = \Delta \tilde{\textbf{B}}_1m_1 + \Delta \tilde{\textbf{B}}_2m_2 + \Delta \tilde{\textbf{B}}_3m_3
+\end{equation}
+\begin{equation}
+\Delta \textbf{B}_z = \Delta \tilde{\textbf{B}}_1n_1 + \Delta \tilde{\textbf{B}}_2n_2 + \Delta \tilde{\textbf{B}}_3n_3
+\end{equation}
+
+\subsection{The forward model of a triaxial ellipsoid}
+
+The implementation of the forward problem of a triaxial ellipsoid's magnetic field (three semi-axis $a > b > c$) is done in a new coordinate system, where its origin is the center of this ellipsoidal body.
+
+This new coordinate system ($x_1,x_2,x_3$) is defined by the unit vectors $\textbf{v}_h (h=1,2,3)$ with the respect with the geographic axis $x$, $y$ e $z$:
+\begin{equation}
+\textbf{v}_1 = (l_1,l_2,l_3) = (-\cos\alpha \cos\delta, \cos\alpha \cos\gamma \sin\delta + \sin\alpha \sin\gamma, \sin\alpha \cos\gamma - \cos\alpha \sin\gamma \sin\delta)
 \end{equation}
@@
 \begin{equation}
-\begin{split}
-\textbf{v}_2 = (l_2,m_2,n_2) = (\cos\alpha \cos\gamma \sin\delta + \sin\alpha \sin\gamma,\\ \sin\alpha \cos\gamma \sin\delta - \cos\alpha \sin\gamma, -\cos\gamma \cos\delta)
-\end{split}
+\textbf{v}_2 = (m_1,m_2,m_3) = (-\sin\alpha \cos\delta, \sin\alpha \cos\gamma \sin\delta - \cos\alpha \sin\gamma, -\cos\alpha \cos\gamma - \sin\alpha \sin\gamma \sin\delta)
 \end{equation}
@@
 \begin{equation}
-\begin{split}
-\textbf{v}_3 = (l_3,m_3,n_3) = (\sin\alpha \cos\gamma - \cos\alpha \sin\gamma \sin\delta,\\ -\cos\alpha \cos\gamma - \sin\alpha \sin\gamma \sin\delta, \sin\gamma \cos\delta)
-\end{split}
+\textbf{v}_3 = (n_1,n_2,n_3) = (-\sin\delta,-\cos\gamma \cos\delta, \sin\gamma \cos\delta)
 \end{equation}
 
-The angles referring to the unit vectors are determined by the orientations of the elipsoid's semi-axis.
+The angles referring to the unit vectors are determined by the orientations of the ellipsoid's semi-axis.
 The angle $\alpha$ is the azimuth of semi-major axe ($a$) plus 180$^{\circ}$.
 While $\delta$ is the inclination of semi-major axe ($a$) in relation to the geographic plane.
-Lastly, $\gamma$ is the angle between the semi-mid axe ($b$) and the vertical projection of the elipsoid's center with the geographic plane.
+Lastly, $\gamma$ is the angle between the semi-mid axe ($b$) and the vertical projection of the ellipsoid's center with the geographic plane.
 
-Thus, the coordinates of the body's semi-axis are given by:
+Thus, the body's coordinates are given by:
 
-\begin{equation}
+\begin{equation} \label{eq:bodyco}
 x_h = (x-xc)l_h + (y-yc)m_h + (z-zc)n_h \quad (h= 1,2,3)
@@
 
-Where $x_c$, $y_c$ e $z_c$ are the coordinates of the elipsoid's center in the geographic system $x$, $y$ e $z$.
+Where $x_c$, $y_c$ e $z_c$ are the coordinates of the ellipsoid's center in the geographic system $x$, $y$ e $z$.
 
-For an elipsoid of semi-axis $a > b > c$, the equation that defines your surface is:
+For an ellipsoid of semi-axis $a > b > c$, the equation that defines your surface is:
 
-\begin{equation} \label{eq:elipsoide}
+\begin{equation} \label{eq:ellipsoide}
 \dfrac{x_1^2}{(a^2+s)} + \dfrac{x_2^2}{(b^2+s)} + \dfrac{x_3^2}{(c^2+s)} = 1
@@
 
-The parameter $s$ controls the elipsoid form.
-When $s$ gets close to $\infty$ the equation \eqref{eq:elipsoide} tends to the sphere equation of radius $r=\sqrt{\lambda}$.
-When $s = -c^2$, the last term of the elipsoid's equation is less than zero and it becomes the equation of a circle.
+The parameter $s$ controls the ellipsoid form.
+When $s$ gets close to $\infty$ the equation \eqref{eq:ellipsoide} tends to the sphere equation of radius $r=\sqrt{\lambda}$.
+When $s = -c^2$, the last term of the ellipsoid's equation is less than zero and it becomes the equation of a circle.
 
@@
 
-This set of roots, called elipsoidal coordinates, correspond to the parameters of a point ($x_1,x_2,x_3$) which are under the intersection of three ortogonal surfaces related to the body coordinates.
+This set of roots, called ellipsoidal coordinates, correspond to the parameters of a point ($x_1,x_2,x_3$) which are under the intersection of three ortogonal surfaces related to the body coordinates.
 Their expressions are:
@@
 
-The calculation of the largest root $\lambda$ of the equation \eqref{eq:cubica} is essential, since the magnetic field depends on the spatial derivatives of the equation \ref{eq:elipsoide}, where $s$ admits the value of $\lambda$.
+The calculation of the largest root $\lambda$ of the equation \eqref{eq:cubica} is essential, since the magnetic field depends on the spatial derivatives of the equation \ref{eq:ellipsoide}, where $s$ admits the value of $\lambda$.
 
@@
 
-The desmagnetization factors are given by:
+The demagnetization factors are given by:
 
@@
 
-The Earth's field vector, $F$, and the remanent magnetization ,$d$, also must be converted to the body's coordinates:
+The Earth's field vector, $F$, and the remanent magnetization ,$J_N$, also must be converted to the body's coordinates:
 
 \begin{equation}
-F_h = F(l \, l_h + m \, m_h + n \, n_h)
+\textbf{F}_i = F(l \, l_i + m \, m_i + n \, n_i)
 \end{equation}
@@
 \begin{equation}
-(J_N)_h = J_N (l_N l_h + m_n m_h + n_N n_h)
+(\textbf{J}_N)_i = J_N (l_N l_i + m_n m_i + n_N n_i)
 \end{equation}
 
-Note that $L_r, M_r, N_r$ ($r = 1,2,3$), $l,m,n$ e $l_N, m_N, n_N$ depends on their respective vectors of inclinations and declinations:
+Note that $L_r, M_r, N_r$ ($r = 1,2,3$), $l,m,n$ and $l_N, m_N, n_N$ depends on their respective angles of inclinations and declinations:
 \begin{equation}
@@
 \begin{equation}
-\textbf{J}_R = K\textbf{F} + \textbf{J}_{NRM}
+\textbf{J}_R = \textbf{K}\textbf{F} + \textbf{J}_{NRM}
 \end{equation}
@@
 \begin{equation}
-\textbf{J}_{Rc} = A^{-1} \textbf{J}_R
+\textbf{J}_{Rc} = \textbf{G}^{-1} \textbf{J}_R
 \end{equation}
@@
 \begin{equation}
-A = I + KN = \left[\begin{matrix} 
+\textbf{G} = I + KN = \left[\begin{matrix} 
 1+k_{11}N_1 \quad & k_{12}N_2 \quad & k_{13}N_3 \\\\
@@
 
-This way, the components of the magnetic field produced by a triaxial elipsoid in the body's coordinates outside of it is:
+This way, the components of the magnetic field produced by a triaxial ellipsoid in the body's coordinates outside of it is:
 
 \begin{equation} \label{eq:campo_e}
-\Delta B_1 = f_1 \dfrac{\partial \lambda}{\partial x_1} - 2 \pi abc \, J_1 \, A(\lambda) 
+\Delta \textbf{B}_1 = f_1 \dfrac{\partial \lambda}{\partial x_1} - 2 \pi abc \, J_1 \, A(\lambda) 
 \end{equation}
@@
 \begin{equation}
-\Delta B_2 = f_1 \dfrac{\partial \lambda}{\partial x_2} - 2 \pi abc \, J_2 \, B(\lambda)
+\Delta \textbf{B}_2 = f_1 \dfrac{\partial \lambda}{\partial x_2} - 2 \pi abc \, J_2 \, B(\lambda)
 \end{equation}
@@
 \begin{equation}
-\Delta B_3 = f_1 \dfrac{\partial \lambda}{\partial x_3} - 2 \pi abc \, J_3 \, C(\lambda)
+\Delta \textbf{B}_3 = f_1 \dfrac{\partial \lambda}{\partial x_3} - 2 \pi abc \, J_3 \, C(\lambda)
 \end{equation}
@@
 Both $F(\theta^{'}, k)$ as $E(\theta^{'}, k)$ are again the first and second  noraml Legendre's eliptical integrals.
-While $A(\lambda), B(\lambda), C(\lambda)$ are analytic solutions of the integrals of the potential equation of an elipsoid.
+While $A(\lambda), B(\lambda), C(\lambda)$ are analytic solutions of the integrals of the potential equation of an ellipsoid.
 This problem was solved by Dirichlet in 1839 \citep{clark1986magnetic} for the gravitational potential given by:
@@
 Using the equations from \eqref{eq:campo_e} to \eqref{eq:integralC}, we can rearrange them in a matrix format that will be more computationally efficient.
-Thus, the magnetic field generated by the elipsoid is:
+Thus, the magnetic field generated by the triaxial ellipsoid \eqref{eq:campoGeo} is:
 
-\begin{equation}\label{eq:campoGeo}
-b_i^j = 2\pi a_j b_j c_j \times [M_i^j - D_i^j] \times J^j \quad j=1,...,L
+\begin{equation}
+\textbf{b}_i^j = 2\pi a_j b_j c_j \times [\textbf{M}_i^j - \textbf{D}_i^j] \times \textbf{J}^j \quad j=1,...,L
 \end{equation}
@@
 \begin{equation}
-M_i^j = \dfrac{1}{\sqrt{[(a^2+\lambda)(b^2+\lambda)(c^2+\lambda)]}}
+\textbf{M}_i^j = \dfrac{1}{\sqrt{[(a^2+\lambda)(b^2+\lambda)(c^2+\lambda)]}}
 \left[\begin{matrix} 
@@
 \begin{equation}
-D_i^j =
+\textbf{D}_i^j =
 \left[\begin{matrix} 
@@
 
-For $j = 1,...,L$, the number of elipsoids been modeled and $i = 1,...,N$  for the $i$th element of the calculated field. The total magnetic field then is:
+\subsection{The forward model of a prolate ellipsoid}
 
-\begin{equation}\label{eq:campoGeoNL}
-B_i = \sum_{j=1}^{L} b_i^j, \quad i=1,...,N
-\end{equation}
-
-We must remember that every calculation so far was done using the body's coordinates, however the notation in equation \eqref{eq:campoGeo} the magnetic field is already in geographics coordinates.
-To calculate each component of the magnetic field's vector back:
-
+The same way that the triaxial ellipsoid, the magnetic field generated by a prolate ellipsoid ($a$ > $b$), must be calculated in the body's coordinate.
+In this case the matrix $\textbf{V}$ is composed by the same equations shown for the triaxial, but considering gamma equal to $0^o$ :
 \begin{equation}
-\Delta B_x = \Delta B_1l_1 + \Delta B_2l_2 + \Delta B_3l_3
+\textbf{v}_1 = (l_1,l_2,l_3) = (-\cos\alpha \cos\delta, \cos\alpha \sin\delta, \sin\alpha)
 \end{equation}
@@
 \begin{equation}
-\Delta B_y = \Delta B_1m_1 + \Delta B_2m_2 + \Delta B_3m_3
+\textbf{v}_2 = (m_1,m_2,m_3) = (-\sin\alpha \cos\delta, \sin\alpha \sin\delta, -\cos\alpha)
 \end{equation}
@@
 \begin{equation}
-\Delta B_z = \Delta B_1n_1 + \Delta B_2n_2 + \Delta B_3n_3
+\textbf{v}_3 = (n_1,n_2,n_3) = (-\sin\delta, -\cos\delta, 0)
 \end{equation}
+
+The coordinate transformation is the same as equation \eqref{eq:bodyco}.
+The calculation of $\lambda$ is and its spatial derivatives are:
+\begin{equation}
+\lambda = \dfrac{r^2-a^2-b^2+ \Delta}{2},
+\end{equation}
+
+where:
+\begin{equation}
+r = \sqrt{x^2_1 + x^2_2 + x^2_3},
+\end{equation}
+
+and
+\begin{equation}
+\Delta = \sqrt{r^4 - (a^2-b^2)^2 -2(a^2-b^2)(x^2_1 - x^2_2 - x^2_3)},
+\end{equation}
+
+Hence its spatial derivatives are:
+\begin{equation}
+\dfrac{\partial \lambda}{\partial x_1} = x_1 \left(1 + \dfrac{r^2-a^2+b^2}{\Delta}\right)
+\end{equation}
+
+\begin{equation}
+\dfrac{\partial \lambda}{\partial x_2} = x_2 \left(1 + \dfrac{r^2+a^2-b^2}{\Delta}\right)
+\end{equation}
+
+\begin{equation}
+\dfrac{\partial \lambda}{\partial x_3} = x_3 \left(1 + \dfrac{r^2+a^2-b^2}{\Delta}\right)
+\end{equation}
+
+The demagnetization factor are:
+\begin{equation}
+N_1 = \dfrac{4\pi ab^2}{(a^2-b^2)^{3/2}} \left\{ \log_e \left[\left(\sqrt{\dfrac{a^2}{b^2}-1}\right) + \dfrac{a}{b}\right] - \sqrt{\left(1 - \dfrac{b^2}{a^2}\right)} \right\}
+\end{equation}
+
+\begin{equation}
+N_2 = 2\pi - \dfrac{N_1}{2}
+\end{equation}
+
+The calculations of the susceptibility tensor $k$, Earth's field $\textbf{F}_i$, remanent magnetization vector $(\textbf{J}_N)_i$ and the resultant magnetization vector $\textbf{J}_{Rc}$ are the same as the triaxial ellipsoid.
+
+The magnetic field generated by the prolate ellipsoid \eqref{eq:campoGeo} can also be written in a matrix form as:
+
+\begin{equation}
+\textbf{b}_i^j = 2\pi a_j b_j c_j \times [\textbf{M}_i^j - \textbf{D}_i^j] \times \textbf{J}^j \quad j=1,...,L
+\end{equation}
+
+With:
+
+\begin{equation}
+\textbf{M}_i^j = \dfrac{1}{\sqrt{[(a^2+\lambda)(b^2+\lambda)(c^2+\lambda)]}}
+\left[\begin{matrix} 
+\dfrac{\partial \lambda}{\partial x_1} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_1} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_1} \dfrac{x_3}{c^2+\lambda} \\\\
+\dfrac{\partial \lambda}{\partial x_2} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_2} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_2} \dfrac{x_3}{c^2+\lambda} \\\\
+\dfrac{\partial \lambda}{\partial x_3} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_3} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_3} \dfrac{x_3}{c^2+\lambda}
+\end{matrix}\right]_{3 \times 3}
+\end{equation}
+
+\begin{equation}
+\textbf{D}_i^j =
+\left[\begin{matrix} 
+A(\lambda) & 0 & 0 \\
+0 & B(\lambda) & 0 \\
+0 & 0 & C(\lambda)
+\end{matrix}\right]
+\end{equation}
+
+\subsection{The forward model of a oblate ellipsoid}
 

### 2017-01-11 manuscript/Paper-magnetic-elipsoid_metodologia.tex
Metodologia Triaxial, prolato e oblato

@@
 
-\title{3D MAGNETIC MODELLING FOR ELIPSOIDS}
+\title{3D MAGNETIC MODELLING FOR ELLIPSOIDS}
 
@@
 
+Important to remenber that all this calcuations are in the body's coordinates. In order to transform to the observations points use equation \eqref{eq:7}.
+
 \subsection{The forward model of a prolate ellipsoid}
@@
 \begin{equation}
-\textbf{M}_i^j = \dfrac{1}{\sqrt{[(a^2+\lambda)(b^2+\lambda)(c^2+\lambda)]}}
+\textbf{M}_i^j = \dfrac{1}{(a^2+\lambda)^{1/2}(b^2+\lambda)}
 \left[\begin{matrix} 
-\dfrac{\partial \lambda}{\partial x_1} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_1} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_1} \dfrac{x_3}{c^2+\lambda} \\\\
-\dfrac{\partial \lambda}{\partial x_2} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_2} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_2} \dfrac{x_3}{c^2+\lambda} \\\\
-\dfrac{\partial \lambda}{\partial x_3} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_3} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_3} \dfrac{x_3}{c^2+\lambda}
+\dfrac{\partial \lambda}{\partial x_1} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_1} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_1} \dfrac{x_3}{b^2+\lambda} \\\\
+\dfrac{\partial \lambda}{\partial x_2} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_2} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_2} \dfrac{x_3}{b^2+\lambda} \\\\
+\dfrac{\partial \lambda}{\partial x_3} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_3} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_3} \dfrac{x_3}{b^2+\lambda}
 \end{matrix}\right]_{3 \times 3}
@@
 0 & B(\lambda) & 0 \\
-0 & 0 & C(\lambda)
-\end{matrix}\right]
+0 & 0 & B(\lambda)
+\end{matrix}\right],
 \end{equation}
 
-\subsection{The forward model of a oblate ellipsoid}
+where:
+\begin{equation}
+A(\lambda) = \dfrac{2}{(a^2-b^2)^{3/2}} \left\{\sqrt{\dfrac{a^2-b^2}{a^2+ \lambda}} - \log_e[\dfrac{(a^2-b^2)^{1/2} + (a^2+\lambda)^{1/2}}{(b^2+\lambda)^{1/2}}]  \right\}
+\end{equation}
+
+\begin{equation}
+B(\lambda) = \dfrac{1}{(a^2-b^2)^{3/2}} \left\{\dfrac{\sqrt{(a^2-b^2)(a^2+\lambda)}}{b^2+\lambda} - \log_e[\dfrac{(a^2-b^2)^{1/2} + (a^2+\lambda)^{1/2}}{(b^2+\lambda)^{1/2}}]  \right\}
+\end{equation}
+
+\subsection{The forward model of an oblate ellipsoid}
+
+The magnetic field generated by an oblate ellipsoid ($b$ > $a$), also must be calculated in the body's coordinate.
+The matrix $\textbf{V}$ is composed by the same equations shown for the prolate ellipsoid, but doing the changes due to the major semi-axe being $b$ :
+\begin{equation}
+\textbf{v}_1 = (l_1,l_2,l_3) = (\cos\alpha \sin\delta, -\cos\alpha \cos\delta, -\sin\alpha)
+\end{equation}
+
+\begin{equation}
+\textbf{v}_2 = (m_1,m_2,m_3) = (\sin\alpha \sin\delta, -\sin\alpha \cos\delta, \cos\alpha)
+\end{equation}
+
+\begin{equation}
+\textbf{v}_3 = (n_1,n_2,n_3) = (-\cos\delta, -\sin\delta, 0)
+\end{equation}
+
+The coordinate transformation is the same as equation \eqref{eq:bodyco}.
+The calculation of $\lambda$ is and its spatial derivatives are the same as the prolate case.
+
+The demagnetization factor are:
+\begin{equation}
+N_1 = \dfrac{4\pi ab^2}{(b^2-a^2)^{3/2}} \left[\dfrac{\sqrt{b^2-a^2}}{a} - \tan^{-1} \dfrac{\sqrt{b^2-a^2}}{a}\right]
+\end{equation}
+
+\begin{equation}
+N_2 = 2\pi - \dfrac{N_1}{2}
+\end{equation}
+
+The calculations of the susceptibility tensor $k$, Earth's field $\textbf{F}_i$, remanent magnetization vector $(\textbf{J}_N)_i$ and the resultant magnetization vector $\textbf{J}_{Rc}$ are the same as the triaxial ellipsoid.
+
+The magnetic field generated by the prolate ellipsoid \eqref{eq:campoGeo} can also be written in a matrix form as:
+
+\begin{equation}
+\textbf{b}_i^j = 2\pi a_j b_j c_j \times [\textbf{M}_i^j - \textbf{D}_i^j] \times \textbf{J}^j \quad j=1,...,L
+\end{equation}
+
+With:
+
+\begin{equation}
+\textbf{M}_i^j = \dfrac{1}{(a^2+\lambda)^{1/2}(b^2+\lambda)}
+\left[\begin{matrix} 
+\dfrac{\partial \lambda}{\partial x_1} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_1} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_1} \dfrac{x_3}{b^2+\lambda} \\\\
+\dfrac{\partial \lambda}{\partial x_2} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_2} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_2} \dfrac{x_3}{b^2+\lambda} \\\\
+\dfrac{\partial \lambda}{\partial x_3} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_3} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_3} \dfrac{x_3}{b^2+\lambda}
+\end{matrix}\right]_{3 \times 3}
+\end{equation}
+
+\begin{equation}
+\textbf{D}_i^j =
+\left[\begin{matrix} 
+A(\lambda) & 0 & 0 \\
+0 & B(\lambda) & 0 \\
+0 & 0 & B(\lambda)
+\end{matrix}\right],
+\end{equation}
+
+where:
+\begin{equation}
+A(\lambda) = \dfrac{2}{(b^2-a^2)^{3/2}} \left\{\sqrt{\dfrac{b^2-a^2}{a^2+ \lambda}} - \tan^{-1}\sqrt{\dfrac{b^2-a^2}{a^2+\lambda}}  \right\}
+\end{equation}
+
+\begin{equation}
+B(\lambda) = \dfrac{1}{(b^2-a^2)^{3/2}} \left\{\tan^{-1}\sqrt{\dfrac{b^2-a^2}{a^2+\lambda}} - \dfrac{\sqrt{(b^2-a^2)(a^2+\lambda)}}{b^2+\lambda}  \right\}
+\end{equation}
 

### 2017-01-12 manuscript/manuscript.tex
subsection geometrical aspects of methodology section - preliminay version

--- 2016-12-02 manuscript/Paper-magnetic-elipsoid_metodologia.tex
@@
 \begin{abstract}
-In this work we will present results from a numerical modeling of the magnetic field and total field anomaly, represented by triaxial and prolate elipsoidal sources.
-Such approach provide analytical results for anisotropy of magnetic susceptibility as well as for self-demagnetization effects, which can be easily adapted for distinctive geologic structures - hence being an useful tool for educational (e.g., potential methods and rock magnetism) and applied geophysics (e.g., characterization of high magnetic susceptibility, mineralized bodies) purposes.
-Numerical tests by means of a Python code (currently under development) allowed us to compared the effects of different geometries (ellipsoidal sources, spheres, dipole lines and elliptic cylinders), which were used to validate our computational implementation.
-This code will be freely available to the scientific community by the end of the year.
+
+TEXT
+
 \end{abstract}
@@
 
-In the 19th century, \cite{dirichlet1839nouvelle} manage to solve the problem of the potential of a homogeneous ellipsoid with semi-axes $a \ge b \ge c$ by using the first and second Legendre's normal elliptic integrals.
-Later, \cite{maxwell1881treatise} showed that only bodies of second degree can be uniformly magnetized when placed in a uniform field.
-\cite{thomson1879and} presented the formulas of the potential and demagnetizing field using the standard integrals expressions for the ellispoid of revolution.
-
-The formulas for the demagnetizing factors of the general ellipsoid alongside a table of values for different proportions of semi-axis was published by \cite{osborn1945demagnetizing}.
-In the same year, \cite{stoner1945xcvii} presented a more simple and friendly formulas of the demagnetizing factors for an ellipsoid, with step-by-step deduction.
-This work includes formulas for different parametrizations of the ellipsoid (triaxial, prolate, oblate).
-
-A decade later, \cite{peake1953magnetic} published a paper with the formulas for the external field of ellipsoid of revolution.
-Some years after that, \cite{chang1961fields} showed the formulas for the external field of triaxial, prolate and oblate ellipsoids.
-Both used the Dirichlet solution in terms of elliptical integrals for external fields.
-More recently, \cite{tejedor1995external}, gave the calculations of the external field generated by ellipsoids using a variational method, in contrast to the usual method of Dirichlet.
-
-In the decade of 1970, \cite{farrar1979some} showed in his work the value of the ellipsoidal model in geophysic exploration, where it was used for analysis of magnetic anomalies in Tennant Creeks's gold mine in Australia.
-The ellipsoid was the most correct geometry to model bodies of lenticular pipe shape and the most appropriate to handle self-desmagnetization of bodies of high susceptibilty - magnetic susceptibility higher than 0.1 SI \citep{clark2014methods}.
-\cite{guo1998self}, showed three case studies of the importance of self-demagnetization of high susceptibilties bodies when modelling magnetic sources.
-A magnetic-iron deposit, a volcanic-hosted iron deposit and an ultramafic-hosted nickel and copper deposits.
-The same author years later,\cite{guo2001systematic}, published another paper analysing the errors of what an uncorrected by demagnetization data can affect in anomalies interpretation.
-
-The magnetic field resultant of an ellipsoid was presented the first time in full modeling in the space domain by \cite{emerson1985magnetic}, along a compilation of several others geometric shapes.
-Through a consistent notation this work tapped a hole in the literature that missed the ellipsoidal model.
-This model, however, consists in a division between prolate and oblate ellipsoids, with a few differences in the algorithm.
-A generalized model for triaxials ellipsoids was published by \cite{clark1986magnetic}.
-Both in Emerson et al.
-and Clark et al.
-works, they were the firsts to include the calculations of the magnetic field in a different coordinate system other than with the origin in the center of the ellipsoid (through a matrix of rotation).
-However, the codes presented for HP-41C calculators are outdated and don't have a descrition of the algorithm, difficulting the reproduction by the cientific commnunity.
-This may be the reason why the magnetic field modelling of the ellipsoid, in general, is manly used through commercial softwares.
-
-As shown, the problem of the magnetic field of the ellipsoid is scattered through the literature, wich can difficult the access to many.
-This article come as a junction of previous works, making the problem easier and more understandable.
-Together we present an algorithm in a modern language with a complete descrition of it.
-The code will be available for free usage of the geophysics community.
+TEXT
 
@@
 
-The total-field anomaly can be described as a difference between the total field vector and the induced magnetization of the crust of the Earth, that includes any anomalous distribuition of magnetization that can occur by magnetizied bodies in subsurface.
-This difference can be written as:
-\begin{equation} \label{eq:1}
-\Delta T^0_i = ||T_i|| - ||F_i||,
+\subsection{Geometrical aspects}
+
+Let $(x, y, z)$ be a point referred to a Cartesian coordinate system with axes
+$x$, $y$ and $z$ pointing to, respectively, North, East and down.
+
+Consider an ellipsoidal body with centre at the point $(x_{c}, y_{c}, z_{c})$,
+semi-axes defined by positive constants $a$, $b$, $c$, and orientation defined by
+three angles $\alpha$, $\beta$, and $\gamma$.
+
+The points $(x, y, z)$ located on the surface of this ellipsoidal body
+satisfy the following equation:
+\begin{equation}
+(\mathbf{r} - \mathbf{r}_c)^T \mathbf{A} (\mathbf{r} - \mathbf{r}_c) = 1 \: ,
+\label{eq:ellipsoid_surface}
 \end{equation}
-where $\Delta T^0_i$ is the observed vector of total-field anomaly in the $i$-th position ($x_i$, $y_i$, $z_i$), $i = 1,...N$, $F_i$ is the geomagnetic field and $||.||$ is the Euclidian norm.
-The total-field vector $T_i$ is:
-\begin{equation}\label{eq:2}
-T_i = F_i + B_i,
+where $\mathbf{r} = [\begin{array}{ccc} x & y & z \end{array} ]^{\top}$,
+$\mathbf{r}_{c} = [\begin{array}{ccc} x_{c} & y_{c} & z_{c} \end{array} ]^{\top}$,
+$\mathbf{A}$ is a positive definite matrix given by
+\begin{equation}
+\mathbf{A} = \mathbf{V}
+\left[ \begin{array}{ccc}
+a^{-2} & 0 & 0 \\
+0 & b^{-2} & 0 \\
+0 & 0 & c^{-2} 
+\end{array} \right] \mathbf{V}^{\top} \: ,
+\label{eq:A}
 \end{equation}
-and $B_i$ is the total induced magnetization vector produced by all sources of anomalous susceptibility distribuition.
-Considering $F_i$ a constant vector, $F_0$ for local ou regional scale, and that $||F_0|| \gg ||B_0||$, since, $B_i$ is a small pertubation of the magnetic field $F_i$, we can approximate the euclidian norm of the vector $T_i$ by a Taylor's expansion of first order:
-\begin{equation}\label{eq:3}
-||T_i|| \approx ||F_0 + B_i|| \approx ||F_0|| + F^T B_i
+and $\mathbf{V}$ is an orthogonal matrix whose columns are defined
+by unit vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$, and $\mathbf{v}_{3}$.
+
+The vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$, and $\mathbf{v}_{3}$ 
+have the same direction as the semi-axes $a$, $b$, $c$ of the 
+ellipsoid, depend on the orientation angles 
+$\alpha$, $\beta$, $\gamma$ and are defined 
+according to the ellipsoid type.
+
+For triaxial ellipsoids (i.e., $a > b > c$), the vectors 
+$\mathbf{v}_{1}$, $\mathbf{v}_{2}$, and $\mathbf{v}_{3}$ are given
+by \citep{clark1986magnetic}:
+\begin{equation}
+\mathbf{v}_{1} = \left[\begin{array}{c} 
+                  -\cos\alpha \; \cos\delta \\
+                  -\sin\alpha \; \cos\delta \\
+                  -\sin\delta
+                  \end{array} \right] \: ,
+\label{eq:v1_triaxial_prolate}
 \end{equation}
-where $T$ indicates transposition and
-\begin{equation}\label{eq:4}
-\hat{F} = \dfrac{F_o}{||F_0||}
+\begin{equation}
+\mathbf{v}_{2} = \left[\begin{array}{c} 
+                  \cos\alpha \; \cos\gamma \; \sin\delta + \sin\alpha \; \sin\gamma \\                   
+                  \sin\alpha \; \cos\gamma \; \sin\delta - \cos\alpha \; \sin\gamma \\ 
+                  -\cos\gamma \; \cos\delta
+                  \end{array} \right] \: ,
+\label{eq:v2_triaxial_prolate}
+\end{equation}                   
+\begin{equation}                    
+\mathbf{v}_{3} = \left[\begin{array}{c} 
+                  \sin\alpha \; \cos\gamma - \cos\alpha \; \sin\gamma \; \sin\delta \\                    
+                  -\cos\alpha \; \cos\gamma - \sin\alpha \; \sin\gamma \; \sin\delta \\
+                  \sin\gamma \; \cos\delta
+                  \end{array} \right] \: .
+\label{eq:v3_triaxial_prolate}
 \end{equation}
 
-is a unit vector that represents the gradient of the function $||T_i||$ in relation to the vector's components $T_i$. This way, we can approximate the Eq.(\ref{eq:1}) of total-field anomaly to:
-\begin{equation}\label{eq:5}
-\Delta T \approx \hat{F}^T \bar{B}_i, \quad i=1,...,NF
-\end{equation}
+Similarly, the vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$, and $\mathbf{v}_{3}$
+defining the semi-axes of prolate ellipsoids (i.e., $a > b = c$) are 
+calculated by using equations \ref{eq:v1_triaxial_prolate}, \ref{eq:v2_triaxial_prolate}, 
+and \ref{eq:v3_triaxial_prolate}, but with $\gamma = 0^{\circ}$ \citep{emerson1985magnetic}.
 
-The field now $\bar{B}_i$ is represented this way to show that is in the geographic coordinates.
-One of the main steps to calculate the magnetic field of an ellipsoid is to change this system of coordinates to the body coordinates with origin in the center of it.
-The conversion can be done through a matrix of rotation $\bar{\bar{V}}$ that differs with the geometric type of ellipsoid, so the formulas will be shown later, separately for each one.
-But, in a general way, the conversion is:
-\begin{equation}\label{eq:5}
-\bar{r}_i = \bar{\bar{V}} \tilde{r}_i + \bar{r}_c,
-\end{equation}
+Finally, the vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$, and $\mathbf{v}_{3}$
+defining the semi-axes of oblate ellipsoids (i.e., $a < b = c$) are
 
-The vector $\bar{r}_i$ has the positions $x,y,z$ in the geographic coordinates, $\bar{r}_i$ has the positions $x1,x2,x3$ in the body coordinates and $\bar{r}_c$ is the position of the center of the body in the geographic coordinates.
+PAREI AQUI
 
-The same way the matrix of conversion can be used to change the magnetic field calculate in the body coordinates, back to the geopraphic, where is more useful to us:
-\begin{equation}\label{eq:5}
-\bar{B}_i = \bar{\bar{V}} \tilde{B}_i
-\end{equation}
+%whose eigenvectors define the 
+%axes of the ellipsoid and the eigenvalues of A are the reciprocals of the squares of the semi-axes
 
-The equation of the surface of an ellipsoid can be written in a matrix form as:
-\begin{equation}
-(\bar{\textbf{r}} - \bar{\textbf{r}}_c)^T \bar{\bar{A}} (\bar{\textbf{r}} - \bar{\textbf{r}}_c) = 1,
-\end{equation}
+\subsection{TEXT}
 
-and $\bar{\bar{A}}$ is a 3X3 matrix formed by:
-\begin{equation}
-\bar{\bar{A}} = \bar{\bar{V}} 
-\left[\begin{matrix} 
-\dfrac{1}{a^2+s} & 0 & 0 \\
-0 & \dfrac{1}{b^2+s} & 0 \\
-0 & 0 & \dfrac{1}{c^2+s}
-\end{matrix}\right]
-\bar{\bar{V}}^T,
-\end{equation}
-
-where the columns of $\bar{\bar{V}}$ are the eigenvectors that represents the principal axes of the ellipsoid and the diagonal of the middle matrix the eigenvalues that represents the reciprocals of the square of the semi-axes $a^{-2}$, $b^{-2}$ and $c^{-2}$.
-
-\subsection{The Forward model of a sphere}
-
-\subsection{The Forward model of a triaxial elipsoid}
-The implementation of the forward problem of a triaxial elipsoid's magnetic field (three semi-axis $a > b > c$) is done in a new coordinate system, where its origin is the center of this elipsoidal body.
-
-This new coordinate system ($x_1,x_2,x_3$) is defined by the unit vectors $\hat{v}_h (h=1,2,3)$ with the respect with the geographic axis $x$, $y$ e $z$:
-\begin{equation}
-\textbf{v}_1 = (l_1,m_1,n_1) = (-\cos\alpha \cos\delta, -\sin\alpha \cos\delta, -\sin\delta)
-\end{equation}
-
-\begin{equation}
-\begin{split}
-\textbf{v}_2 = (l_2,m_2,n_2) = (\cos\alpha \cos\gamma \sin\delta + \sin\alpha \sin\gamma,\\ \sin\alpha \cos\gamma \sin\delta - \cos\alpha \sin\gamma, -\cos\gamma \cos\delta)
-\end{split}
-\end{equation}
-
-\begin{equation}
-\begin{split}
-\textbf{v}_3 = (l_3,m_3,n_3) = (\sin\alpha \cos\gamma - \cos\alpha \sin\gamma \sin\delta,\\ -\cos\alpha \cos\gamma - \sin\alpha \sin\gamma \sin\delta, \sin\gamma \cos\delta)
-\end{split}
-\end{equation}
-
-The angles referring to the unit vectors are determined by the orientations of the elipsoid's semi-axis.
-The angle $\alpha$ is the azimuth of semi-major axe ($a$) plus 180$^{\circ}$.
-While $\delta$ is the inclination of semi-major axe ($a$) in relation to the geographic plane.
-Lastly, $\gamma$ is the angle between the semi-mid axe ($b$) and the vertical projection of the elipsoid's center with the geographic plane.
-
-Thus, the coordinates of the body's semi-axis are given by:
-
-\begin{equation}
-x_h = (x-xc)l_h + (y-yc)m_h + (z-zc)n_h \quad (h= 1,2,3)
-\end{equation}
-
-Where $x_c$, $y_c$ e $z_c$ are the coordinates of the elipsoid's center in the geographic system $x$, $y$ e $z$.
-
-For an elipsoid of semi-axis $a > b > c$, the equation that defines your surface is:
-
-\begin{equation} \label{eq:elipsoide}
-\dfrac{x_1^2}{(a^2+s)} + \dfrac{x_2^2}{(b^2+s)} + \dfrac{x_3^2}{(c^2+s)} = 1
-\end{equation}
-
-The parameter $s$ controls the elipsoid form.
-When $s$ gets close to $\infty$ the equation \eqref{eq:elipsoide} tends to the sphere equation of radius $r=\sqrt{\lambda}$.
-When $s = -c^2$, the last term of the elipsoid's equation is less than zero and it becomes the equation of a circle.
-
-There is, however, a set of values for $s (\lambda,\mu,\nu)$, which are roots of the cubic equation:
-
-\begin{equation} \label{eq:cubica}
-s^3 + p_2s^2 + p_1s + p_0 = 0
-\end{equation}
-
-This set of roots, called elipsoidal coordinates, correspond to the parameters of a point ($x_1,x_2,x_3$) which are under the intersection of three ortogonal surfaces related to the body coordinates.
-Their expressions are:
-
-\begin{equation}
-\lambda = 2 \sqrt{\left (\dfrac{-p}{3} \right)} \cos \left(\dfrac{\theta}{3} \right) - \dfrac{p_2}{3}
-\end{equation}
-
-\begin{equation}
-\mu = -2 \sqrt{\left (\dfrac{-p}{3} \right)} \cos \left(\dfrac{\theta}{3} + \dfrac{\pi}{3} \right) - \dfrac{p_2}{3}
-\end{equation}
-
-\begin{equation}
-\mu = -2 \sqrt{\left (\dfrac{-p}{3} \right)} \cos \left(\dfrac{\theta}{3} - \dfrac{\pi}{3} \right) - \dfrac{p_2}{3}
-\end{equation}
-
-Where:
-\begin{equation}
-p_0 = a^2b^2c^2 - b^2c^2x_1^2 - c^2a^2x_2^2 - a^2b^2x_3^2
-\end{equation}
-
-\begin{equation}
-p_1 = a^2b^2 + b^2c^2 + c^2a^2 - (b^2+c^2)x_1^2 - (c^2+a^2)x_2^2 - (a^2+b^2)x_3^2
-\end{equation}
-
-\begin{equation}
-p_2 = a^2 + b^2 + c^2 - x_1^2 - x_2^2 - x_3^2
-\end{equation}
-
-\begin{equation}
-p = p_1 - \dfrac{p_2^2}{3}
-\end{equation}
-
-\begin{equation}
-q = p_0 - \dfrac{p_1p_2}{3} + 2 \left(\dfrac{p_2}{3} \right)^3
-\end{equation}
-
-\begin{equation}
-\theta = \cos^{-1} \left[\dfrac{-q}{2} \sqrt{\left(\dfrac{-p}{3} \right)^3} \right]
-\end{equation}
-
-The calculation of the largest root $\lambda$ of the equation \eqref{eq:cubica} is essential, since the magnetic field depends on the spatial derivatives of the equation \ref{eq:elipsoide}, where $s$ admits the value of $\lambda$.
-
-\begin{equation}
-\dfrac{\partial \lambda}{\partial x_1} = \dfrac{2x_1/(a^2+\lambda)}{\left(\dfrac{x_1}{a^2+\lambda}\right)^2 + \left(\dfrac{x_2}{b^2+\lambda}\right)^2 + \left(\dfrac{x_3}{c^2+\lambda}\right)^2}
-\end{equation}
-
-\begin{equation}
-\dfrac{\partial \lambda}{\partial x_2} = \dfrac{2x_2/(b^2+\lambda)}{\left(\dfrac{x_1}{a^2+\lambda}\right)^2 + \left(\dfrac{x_2}{b^2+\lambda}\right)^2 + \left(\dfrac{x_3}{c^2+\lambda}\right)^2}
-\end{equation}
-
-\begin{equation}
-\dfrac{\partial \lambda}{\partial x_3} = \dfrac{2x_3/(c^2+\lambda)}{\left(\dfrac{x_1}{a^2+\lambda}\right)^2 + \left(\dfrac{x_2}{b^2+\lambda}\right)^2 + \left(\dfrac{x_3}{c^2+\lambda}\right)^2}
-\end{equation}\\
-
-The desmagnetization factors are given by:
-
-\begin{equation}
-N_1 = \dfrac{4 \pi abc}{(a^2-b^2)\sqrt{(a^2-c^2)}} [F(\theta,k) - E(\theta,k)]
-\end{equation}
-
-\begin{equation}
-N_2 = \dfrac{4 \pi abc \sqrt{(a^2-c^2)}}{(a^2-b^2)(b^2-c^2)} \left[E(\theta,k) - \left(\dfrac{b^2-c^2}{a^2-c^2} \right) F(\theta,k) - \dfrac{c(a^2-b^2)}{ab \sqrt{(a^2-c^2)}} \right]
-\end{equation}
-
-\begin{equation}
-N_3 = \dfrac{4 \pi abc}{(b^2-c^2)\sqrt{(a^2-c^2)}} \left[\dfrac{b \sqrt{(a^2-c^2)}}{ac} - E(\theta,k) \right]
-\end{equation}
-
-Where $F(\theta,k)$ e $E(\theta,k)$ are first and second Legendre's normal eliptical integrals, respectively. To calculate $k$ and $\theta$ we have the following expressions:
-
-\begin{equation}
-k = \sqrt{\left(\dfrac{a^2-b^2}{a^2-c^2} \right)}
-\end{equation}
-
-\begin{equation}
-\theta = \cos^{-1}(c/a) \quad (0 \le \theta \le \pi/2)
-\end{equation}
-
-The susceptibility tensor matrix is:
-
-\begin{equation}
-k_{ij} = \sum_r k_r (L_r l_i + M_r m_i + N_r n_i) (L_r l_j + M_r m_j + N_r n_j) \quad (r = 1,2,3)
-\end{equation}
-
-The Earth's field vector, $F$, and the remanent magnetization ,$d$, also must be converted to the body's coordinates:
-
-\begin{equation}
-F_h = F(l \, l_h + m \, m_h + n \, n_h)
-\end{equation}
-
-\begin{equation}
-(J_N)_h = J_N (l_N l_h + m_n m_h + n_N n_h)
-\end{equation}
-
-Note that $L_r, M_r, N_r$ ($r = 1,2,3$), $l,m,n$ e $l_N, m_N, n_N$ depends on their respective vectors of inclinations and declinations:
-\begin{equation}
-L_R,l,l_N = \cos(dec) \, \cos(inc)
-\end{equation}
-
-\begin{equation}
-M_R,m,m_N = \sin(dec) \, \cos(inc)
-\end{equation}
-
-\begin{equation}
-N_R,n,n_N = \sin(inc)
-\end{equation}
-
-In the case that the body has a very low susceptibility ($\chi < 0.1$ SI) the self-demagnatization is negligible and the resultant magnetic vector is given by:
-
-\begin{equation}
-\textbf{J}_R = K\textbf{F} + \textbf{J}_{NRM}
-\end{equation}
-
-For values bigger than 0.1 SI the resultant magnetic vector is:
-
-\begin{equation}
-\textbf{J}_{Rc} = A^{-1} \textbf{J}_R
-\end{equation}
-
-Where:
-
-\begin{equation}
-A = I + KN = \left[\begin{matrix} 
-1+k_{11}N_1 \quad & k_{12}N_2 \quad & k_{13}N_3 \\\\
-k_{21}N_1 \quad & 1+k_{22}N_2 \quad & k_{23}N_3 \\\\
-k_{31}N_1 \quad & k_{23}N_2 \quad & 1+k_{33}N_3
-\end{matrix}\right]
-\end{equation}
-
-This way, the components of the magnetic field produced by a triaxial elipsoid in the body's coordinates outside of it is:
-
-\begin{equation} \label{eq:campo_e}
-\Delta B_1 = f_1 \dfrac{\partial \lambda}{\partial x_1} - 2 \pi abc \, J_1 \, A(\lambda) 
-\end{equation}
-
-\begin{equation}
-\Delta B_2 = f_1 \dfrac{\partial \lambda}{\partial x_2} - 2 \pi abc \, J_2 \, B(\lambda)
-\end{equation}
-
-\begin{equation}
-\Delta B_3 = f_1 \dfrac{\partial \lambda}{\partial x_3} - 2 \pi abc \, J_3 \, C(\lambda)
-\end{equation}
-
-where:
-
-\begin{equation}
-f_1 = \dfrac{2\pi abc}{\sqrt{[(a^2+\lambda)(b^2+\lambda)(c^2+\lambda)]}} \left[\dfrac{J_1x_1}{a^2+\lambda} + \dfrac{J_2x_2}{b^2+\lambda} + \dfrac{J_3x_3}{c^2+\lambda}\right]
-\end{equation}
-
-\begin{equation}
-A(\lambda) = \dfrac{2}{(a^2-b^2) \sqrt{(a^2-c^2)}} [F(\theta^{'},k) - E(\theta^{'},k)]
-\end{equation}
-
-\begin{equation}
-B(\lambda) = \dfrac{2 \sqrt{(a^2-c^2)}}{(a^2-b^2)(b^2-c^2)} \left[ E(\theta^{'},k) - \left(\dfrac{b^2-c^2}{a^2-c^2} \right) F(\theta^{'},k) - \dfrac{k^2\sin\theta^{'}\cos\theta^{'}}{\sqrt{(1-k^2\sin^2\theta^{'})}} \right]
-\end{equation}
-
-\begin{equation} \label{eq:integralC}
-C(\lambda) = \dfrac{2}{(b^2-c^2) \sqrt{(a^2-c^2)}} \left[\dfrac{\sin\theta^{'} \sqrt{(1-k^2\sin^2\theta^{'})}} {\cos\theta^{'}} - E(\theta^{'},k) \right]
-\end{equation}
-
-And:
-
-\begin{equation}
-\theta^{'} = \sin^{-1} \left(\dfrac{a^2-c^2}{a^2+\lambda}\right)^{0.5} \quad (0 \le \theta^{'} \le \pi/2) 
-\end{equation}
-
-Both $F(\theta^{'}, k)$ as $E(\theta^{'}, k)$ are again the first and second  noraml Legendre's eliptical integrals.
-While $A(\lambda), B(\lambda), C(\lambda)$ are analytic solutions of the integrals of the potential equation of an elipsoid.
-This problem was solved by Dirichlet in 1839 \citep{clark1986magnetic} for the gravitational potential given by:
-
-\begin{equation}
-U_i(x_1,x_2,x_3) = \pi abc G \rho \int_{0}^{\infty} \left[1 - \dfrac{x_1^2}{a^2+u} - \dfrac{x_2^2}{b^2+u} - \dfrac{x_3^2}{c^2+u}\right] \dfrac{du}{R(u)}
-\end{equation}
-
-That can be rewritten as:
-\begin{equation}
-U_i(x_1,x_2,x_3) = \pi abc G \rho \int_{0}^{\infty} [D(\lambda) - A(\lambda) - B(\lambda) - C(\lambda)] \dfrac{du}{R(u)}
-\end{equation}
-
-Where $G$ is the gravitational constant and $\rho$ the body's density.
-
-Using the equations from \eqref{eq:campo_e} to \eqref{eq:integralC}, we can rearrange them in a matrix format that will be more computationally efficient.
-Thus, the magnetic field generated by the elipsoid is:
-
-\begin{equation}\label{eq:campoGeo}
-b_i^j = 2\pi a_j b_j c_j \times [M_i^j - D_i^j] \times J^j \quad j=1,...,L
-\end{equation}
-
-With:
-
-\begin{equation}
-M_i^j = \dfrac{1}{\sqrt{[(a^2+\lambda)(b^2+\lambda)(c^2+\lambda)]}}
-\left[\begin{matrix} 
-\dfrac{\partial \lambda}{\partial x_1} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_1} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_1} \dfrac{x_3}{c^2+\lambda} \\\\
-\dfrac{\partial \lambda}{\partial x_2} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_2} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_2} \dfrac{x_3}{c^2+\lambda} \\\\
-\dfrac{\partial \lambda}{\partial x_3} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_3} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_3} \dfrac{x_3}{c^2+\lambda}
-\end{matrix}\right]_{3 \times 3}
-\end{equation}
-
-\begin{equation}
-D_i^j =
-\left[\begin{matrix} 
-A(\lambda) & 0 & 0 \\
-0 & B(\lambda) & 0 \\
-0 & 0 & C(\lambda)
-\end{matrix}\right]
-\end{equation}
-
-For $j = 1,...,L$, the number of elipsoids been modeled and $i = 1,...,N$  for the $i$th element of the calculated field. The total magnetic field then is:
-
-\begin{equation}\label{eq:campoGeoNL}
-B_i = \sum_{j=1}^{L} b_i^j, \quad i=1,...,N
-\end{equation}
-
-We must remember that every calculation so far was done using the body's coordinates, however the notation in equation \eqref{eq:campoGeo} the magnetic field is already in geographics coordinates.
-To calculate each component of the magnetic field's vector back:
-
-\begin{equation}
-\Delta B_x = \Delta B_1l_1 + \Delta B_2l_2 + \Delta B_3l_3
-\end{equation}
-
-\begin{equation}
-\Delta B_y = \Delta B_1m_1 + \Delta B_2m_2 + \Delta B_3m_3
-\end{equation}
-
-\begin{equation}
-\Delta B_z = \Delta B_1n_1 + \Delta B_2n_2 + \Delta B_3n_3
-\end{equation}
-
-\subsubsection{HEADING}
+\subsubsection{TEXT}
 TEXT
@@
 %%
-%% \bibliographystyle{copernicus}
-%% \bibliography{example.bib}
+\bibliographystyle{copernicus}
+\bibliography{references.bib}
 %%

### 2017-01-13 manuscript/manuscript.tex
methodology - geometrical aspects defining ellipsoids

@@
 
-\title{3D MAGNETIC MODELLING FOR ELLIPSOIDS}
+\title{3D Magnetic modelling of ellipsoidal bodies}
 
@@
 
-\affil[1]{Department of Geophysics, Observatorio Nacional, Rio de Janeiro, Brazil}
+\affil[1]{Department of Geophysics, Observat\'{o}rio Nacional, Rio de Janeiro, Brazil}
 %\affil[]{}
@@
 
-\correspondence{DIEGO TAKAHASHI TOMAZELLA (diego.takahashi@gmail.com)}
+\correspondence{Diego Takahashi Tomazella (diego.takahashi@gmail.com)}
 
@@
 
-\subsection{Geometrical aspects}
+\subsection{Geometrical parameters defining ellipsoids}
 
@@
 $x$, $y$ and $z$ pointing to, respectively, North, East and down.
-
-Consider an ellipsoidal body with centre at the point $(x_{c}, y_{c}, z_{c})$,
-semi-axes defined by positive constants $a$, $b$, $c$, and orientation defined by
+For convenience, we denominate this coordinate system as 
+\textit{main coordinate system}.
+Let us consider an ellipsoidal body with centre at the point $(x_{c}, y_{c}, z_{c})$,
+semi-axes defined by positive constants $a$, $b$, $c$, 
+where $a > b > c$, and orientation defined by
 three angles $\alpha$, $\beta$, and $\gamma$.
-
 The points $(x, y, z)$ located on the surface of this ellipsoidal body
@@
 The vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$, and $\mathbf{v}_{3}$ 
-have the same direction as the semi-axes $a$, $b$, $c$ of the 
-ellipsoid, depend on the orientation angles 
+depend on the orientation angles 
 $\alpha$, $\beta$, $\gamma$ and are defined 
-according to the ellipsoid type.
-
-For triaxial ellipsoids (i.e., $a > b > c$), the vectors 
-$\mathbf{v}_{1}$, $\mathbf{v}_{2}$, and $\mathbf{v}_{3}$ are given
-by \citep{clark1986magnetic}:
+as follows \citep{clark1986magnetic}:
 \begin{equation}
@@
 \end{equation}
+For triaxial ellipsoids (i.e., $a > b > c$), the orthogonal matrix
+$\mathbf{V}$ (equation \ref{eq:A}) is calculated by using equations
+\ref{eq:v1_triaxial_prolate}, \ref{eq:v2_triaxial_prolate}, and
+\ref{eq:v3_triaxial_prolate} as follows:
+\begin{equation}
+\mathbf{V} = \left[ \begin{array}{ccc}
+\mathbf{v}_{1} & \mathbf{v}_{2} & \mathbf{v}_{3}
+\end{array} \right] \: .
+\label{eq:V_triaxial_prolate}
+\end{equation}
+Similarly, the matrix $\mathbf{V}$ (equation \ref{eq:A}) for
+prolate ellipsoids (i.e., $a > b = c$) is calculated according
+to equation \ref{eq:V_triaxial_prolate} by using equations
+\ref{eq:v1_triaxial_prolate}, \ref{eq:v2_triaxial_prolate}, and
+\ref{eq:v3_triaxial_prolate}, but with $\gamma = 0^{\circ}$ 
+\citep{emerson1985magnetic}.
+Finally, the matrix $\mathbf{V}$ (equation \ref{eq:A}) for
+oblate ellipsoids (i.e., $a < b = c$) is calculated by 
+using equations \ref{eq:v1_triaxial_prolate}, \ref{eq:v2_triaxial_prolate}, and
+\ref{eq:v3_triaxial_prolate}, with $\gamma = 0^{\circ}$, as follows
+\citep{emerson1985magnetic}:
+\begin{equation}
+\mathbf{V} = \left[ \begin{array}{ccc}
+\mathbf{v}_{2} & \mathbf{v}_{1} & -\mathbf{v}_{3}
+\end{array} \right] \: .
+\label{eq:V_oblate}
+\end{equation}
+The orientation of the semi-axes $a$, $b$, and $c$ are defined 
+by the first, second, and third columns of the matrix 
+$\mathbf{V}$ given by equation \ref{eq:V_triaxial_prolate},
+in the case of a triaxial or prolate ellipsoid, or the
+matrix $\mathbf{V}$ given by equation \ref{eq:V_oblate},
+in the case of an oblate ellipsoid.
 
-Similarly, the vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$, and $\mathbf{v}_{3}$
-defining the semi-axes of prolate ellipsoids (i.e., $a > b = c$) are 
-calculated by using equations \ref{eq:v1_triaxial_prolate}, \ref{eq:v2_triaxial_prolate}, 
-and \ref{eq:v3_triaxial_prolate}, but with $\gamma = 0^{\circ}$ \citep{emerson1985magnetic}.
+The magnetic modelling of an ellipsoidal body is commonly performed
+in a particular Cartesian coordinate system that is aligned 
+with the body semi-axes
+and has the origin coincident with the body centre.
+For convenience, we denominate this particular coordinate 
+system as \textit{local coordinate system}.
+The relationship between the Cartesian coordinates 
+$(\tilde{x}, \tilde{y}, \tilde{z})$ of a point in 
+a local coordinate system and the Cartesian 
+coordinates $(x, y, z)$ of the same point in the main
+system is given by:
+\begin{equation}
+\tilde{\mathbf{r}} = \mathbf{V}^{\top} \left( \mathbf{r} - \mathbf{r}_{c} \right) \: ,
+\label{eq:coord_transformation}
+\end{equation}
+where 
+$\tilde{\mathbf{r}} = [\begin{array}{ccc} \tilde{x} & 
+                                          \tilde{y} & 
+                                          \tilde{z} \end{array} ]^{\top}$,
+$\mathbf{r}$ and $\mathbf{r}_{c}$
+are defined in equation \ref{eq:ellipsoid_surface} and the matrix $\mathbf{V}$
+is defined according to equations \ref{eq:V_triaxial_prolate} or
+\ref{eq:V_oblate}, depending on the ellipsoid type.
 
-Finally, the vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$, and $\mathbf{v}_{3}$
-defining the semi-axes of oblate ellipsoids (i.e., $a < b = c$) are
+A last but not least set of parameters defining the geometry of
+an ellipsoid are their focal points.
+The focal points are defined on the axes of the local coordinate 
+system as follows:
+\begin{equation}
+\left(\tilde{x}, \tilde{y}, \tilde{z} \right) = 
+\begin{cases}
+\left( \pm \sqrt{a^{2} - b^{2}}, 0, 0 \right) \\
+\left( \pm \sqrt{a^{2} - c^{2}}, 0, 0 \right) \\
+\left( 0, \pm \sqrt{b^{2} - c^{2}}, 0 \right)
+\end{cases} \: .
+\label{eq:focal-points}
+\end{equation}
+All ellipsoids sharing a common set of focal points form a family of confocal ellipsoids.
 
-PAREI AQUI
+\subsection{Auxiliary variable $\lambda$}
 
-%whose eigenvectors define the 
-%axes of the ellipsoid and the eigenvalues of A are the reciprocals of the squares of the semi-axes
+The methods commonly applied in the magnetic modelling of
+ellipsoidal bodies make use of an auxiliary variable $\lambda$,
+which is a real number.
+
+\subsection{Magnetic induction}
 

### 2017-01-17 manuscript/manuscript.tex
problema na matriz de suscetibilidade

@@
 
-TEXT
+\citep{dubois1896}: The magnetisation induced in a uniform field is not necessarily 
+also uniform.
+A vector is said to be distributed uniformly when at
+every point throughout the region considered it has the same
+direction and the same value.
+It maybe mathematically proved that such
+uniformity only holds for bodies of an ellipsoidal shape.
+If one axis coincides with the direction of the field, 
+the magnetisation is in the same direction as that axis.
+The demagnetising intensity for unit magnetisation we 
+shall again speak of as the demagnetising
+factor for the axial direction in question.
 
@@
 
-A last but not least set of parameters defining the geometry of
-an ellipsoid are their focal points.
-The focal points are defined on the axes of the local coordinate 
-system as follows:
-\begin{equation}
-\left(\tilde{x}, \tilde{y}, \tilde{z} \right) = 
-\begin{cases}
-\left( \pm \sqrt{a^{2} - b^{2}}, 0, 0 \right) \\
-\left( \pm \sqrt{a^{2} - c^{2}}, 0, 0 \right) \\
-\left( 0, \pm \sqrt{b^{2} - c^{2}}, 0 \right)
-\end{cases} \: .
-\label{eq:focal-points}
-\end{equation}
-All ellipsoids sharing a common set of focal points form a family of confocal ellipsoids.
+%A last but not least set of parameters defining the geometry of
+%an ellipsoid are their focal points.
+%The focal points are defined on the axes of the local coordinate 
+%system as follows:
+%\begin{equation}
+%\left(\tilde{x}, \tilde{y}, \tilde{z} \right) = 
+%\begin{cases}
+%\left( \pm \sqrt{a^{2} - b^{2}}, 0, 0 \right) \\
+%\left( \pm \sqrt{a^{2} - c^{2}}, 0, 0 \right) \\
+%\left( 0, \pm \sqrt{b^{2} - c^{2}}, 0 \right)
+%\end{cases} \: .
+%\label{eq:focal-points}
+%\end{equation}
+%All ellipsoids sharing a common set of focal points form a family of confocal ellipsoids.
 
-\subsection{Auxiliary variable $\lambda$}
+\subsection{Magnetic scalar potential }
 
@@
 
-\bibliographystyle{copernicus}
-\bibliography{references}
-
 %% Since the Copernicus LaTeX package includes the BibTeX style file copernicus.bst,
@@
 \bibliographystyle{copernicus}
-\bibliography{references.bib}
+\bibliography{references}
 %%

### 2017-01-18 manuscript/manuscript.tex
demagnetizing field within ellipsoids

@@
 
-\citep{dubois1896}: The magnetisation induced in a uniform field is not necessarily 
-also uniform.
-A vector is said to be distributed uniformly when at
-every point throughout the region considered it has the same
-direction and the same value.
-It maybe mathematically proved that such
-uniformity only holds for bodies of an ellipsoidal shape.
-If one axis coincides with the direction of the field, 
-the magnetisation is in the same direction as that axis.
-The demagnetising intensity for unit magnetisation we 
-shall again speak of as the demagnetising
-factor for the axial direction in question.
+TEXT
 
@@
 
-\subsection{Geometrical parameters defining ellipsoids}
+\subsection{Geometrical parameters and coordinate systems}
 
@@
 \ref{eq:V_oblate}, depending on the ellipsoid type.
+Afterwards, we use the superscript "$\sim$" to implicitly
+define quantities referred to a local coordinate system.
 
@@
 
-\subsection{Magnetic scalar potential }
+\subsection{Demagnetizing field within ellipsoids}
 
-The methods commonly applied in the magnetic modelling of
-ellipsoidal bodies make use of an auxiliary variable $\lambda$,
-which is a real number.
+Consider a magnetized ellipsoid immersed in
+a uniform magnetic field $\mathbf{H}_{0}$ (in $\unit{Am^{-1}}$).
+The total magnetic intensity field $\mathbf{H}(\mathbf{r})$
+at the position $\mathbf{r}$ (equations \ref{eq:A} and \ref{eq:coord_transformation}) 
+of a point referred to the main coordinate system is defined
+as follows
+\begin{equation}
+\mathbf{H}(\mathbf{r}) = \mathbf{H}_{0} - \nabla \phi(\mathbf{r}) \: ,
+\label{eq:total-H-field}
+\end{equation}
+where the second term, representing the induced magnetic field,
+is the negative gradient of the magnetic scalar potential 
+$\phi(\mathbf{r})$ given by
+\begin{equation}
+\phi(\mathbf{r}) = \frac{1}{4\pi} \iiint_{V} 
+\mathbf{J}(\mathbf{r}^{\prime})^{\top} \left(
+\frac{\mathbf{r} - \mathbf{r}^{\prime}}{\| \mathbf{r} - \mathbf{r}^{\prime} \|^{3}}
+\right) \, dx^{\prime}dy^{\prime}dz^{\prime} \: .
+\label{eq:phi-potential}
+\end{equation}
+In this equation, $\mathbf{r}^{\prime} = [\begin{array}{ccc} 
+x^{\prime} & y^{\prime} & z^{\prime} \end{array} ]^{\top}$
+is the position vector of a point located within the volume $V$, 
+the integral is conducted over the variables 
+$x^{\prime}$, $y^{\prime}$ and, $z^{\prime}$ representing
+the coordinates of a point located within the volume $V$
+of the ellipsoid, $\| \cdot \|$ denotes the Euclidean norm and 
+$\mathbf{J}(\mathbf{r}^{\prime})$ is the magnetization vector
+(in $\unit{Am^{-1}}$).
+Equation \ref{eq:total-H-field} is valid anywhere, 
+independently if the position vector $\mathbf{r}$ represents
+a point located inside or outside the magnetized body.
+
+According to \citet{maxwell1873}, the only finite bodies that 
+can be uniformly magnetized in the presence of a uniform and static 
+magnetic field are the ones bounded by surfaces of second degree, which
+are ellipsoids.
+
+This property comes from the fact that the gravitational potential
+within an ellipsoid with uniform density is a quadratic function
+of the spatial coordinates.
+
+Based on this, the magnetization vector 
+$\mathbf{J}(\mathbf{r}^{\prime})$ (equation \ref{eq:phi-potential})
+can be moved outside the integral, resulting that
+%\begin{equation}
+%
+%\label{eq:total-H-field-matrix}
+%\end{equation}
 

### 2017-01-18 code/ellipsoid_triaxial_func.py

@@ -1,0 +1,511 @@
+import numpy as np
+from scipy import linalg
+from matplotlib import pyplot as plt
+
+from fatiando import mesher, gridder, utils
+
+import scipy.special
+
+def ellipsoid (xp,yp,zp,xc,yc,zc,a,b,c,azimuth,delta,gamma,declirem,inclirem,intensity,decT,incT,intT,k):
+    '''
+    Calculates the three componentes of magnetic field generated by an ellipsoid.
+    
+    input:
+    xp,yp - Origin of the ellipsoid in the geographic coordinate.
+    zp - Depth of the the ellipsoid.
+    a,b - Minor and major axis, respectively.
+    azimuth - angle in relation to the major-axe and the geographic north (0<=alpha<=360, radians).
+    delta - Inclination between the major-axe and the horizontal plane (0<=delta<=90, radians).
+    gamma - Angle between the intermediate-axe and the vertical projection of the horizontal plane to the
+    center of the ellipsoid(radians).
+    xc,yc,zc - point in the grid that has the center of the ellipsoid.
+    declirem - declination of the remanent vector.
+    inclirem - inclination of the remanent vector.
+    intensity - intensity of the remanent vector.
+    intT - Intensity of the Earth's magnetic field.
+    incT - Inclination of the Earth's magnetic field.
+    decT - Declination of the Earth's magnetic field.
+    k - 3x3 matrix where each line has the intensity, declination and inclination of the three susceptibilities vectors.
+    Bx_T, By_T, Bz_T, Tf_T - componentes of magnetic field generated by an ellipsoid and the total-field anomaly.
+    '''
+    
+    center = np.array([xc,yc,zc])
+    axis = np.array([a,b,c])
+    
+    azimuth = np.deg2rad(azimuth)
+    delta = np.deg2rad(delta)
+    angles = np.array([azimuth+np.pi,delta,gamma])
+    
+    mcon, mconT = m_convT(angles)
+    
+    declirem = np.deg2rad(declirem)
+    inclirem = np.deg2rad(inclirem)
[…]

### 2017-01-19 manuscript/manuscript.tex
start the magnetic field produced by ellipsoid

--- 2017-01-17 manuscript/manuscript.tex
@@
 \ref{eq:V_oblate}, depending on the ellipsoid type.
+Similarly, the transformation of a generic 
+linear system $\mathbf{M} \mathbf{p} = \mathbf{d}$
+referred to the main coordinate system into a new
+linear system 
+$\tilde{\mathbf{M}} \tilde{\mathbf{p}} = \tilde{\mathbf{d}}$
+referred to a local coordinate system is given by
+\begin{equation}
+\tilde{\mathbf{M}} = \mathbf{V}^{\top} \mathbf{M} \mathbf{V} \: , 
+\quad \tilde{\mathbf{p}} = \mathbf{V}^{\top} \mathbf{p} \: ,
+\quad \tilde{\mathbf{d}} = \mathbf{V}^{\top} \mathbf{d} \: .
+\label{eq:matrix_transformation}
+\end{equation}
 
@@
 
-\subsection{Magnetic scalar potential }
+\subsection{Magnetic field produced by ellipsoids}
 
-The methods commonly applied in the magnetic modelling of
-ellipsoidal bodies make use of an auxiliary variable $\lambda$,
-which is a real number.
+Based on the mathematical theory of the magnetic 
+induction developed by \citet{poisson1824}, 
+\citet{maxwell1873} affirmed that, if $V$ is the 
+gravitational potential produced by any body 
+with uniform density $\rho$ and arbitrary shape at 
+a point $(x, y, z)$, then $-\frac{\partial V}{\partial x}$
+is the magnetic scalar potential produced 
+at the same point by the same body 
+if it has a uniform magnetization oriented along $x$ 
+with intensity $\rho$.
+\citet{maxwell1873} generalized this idea as a way
+of determining the magnetic scalar potential produced
+by any body uniformly magnetized in a given direction.
+By presuming that this uniform magnetization is due to
+induction, he postulated that the resulting magnetic
+field intensity at all points within the body must
+also be uniform and parallel the magnetization, which
+results that the gravitational potential $V$ at points
+within the body must be a quadratic function of the
+spatial coordinates.
+Apparently, \citet{maxwell1873} was the first one to
+affirm that the only finite bodies having a gravitational
+potential with this property and that, as a consequence,
+can be uniformly magnetized in the presence of a uniform and 
+static magnetic field are the ones bounded by surfaces 
+of second degree, which are ellipsoids.
+
+Let us start our description of the magnetic field produced
+by ellipsoids by considering a magnetized ellipsoid immersed in
+a uniform magnetic field $\mathbf{H}_{0}$ (in $\unit{Am^{-1}}$).
+The total magnetic intensity field $\mathbf{H}(\mathbf{r})$
+at the position $\mathbf{r}$ (equations \ref{eq:A} and 
+\ref{eq:coord_transformation}) of a point referred to the main 
+coordinate system is defined as follows
+\begin{equation}
+\mathbf{H}(\mathbf{r}) = \mathbf{H}_{0} - \nabla \phi(\mathbf{r}) \: ,
+\label{eq:total-H-field}
+\end{equation}
+where the second term is the negative gradient of 
+the magnetic scalar potential $\phi(\mathbf{r})$ given by
+\begin{equation}
+\phi(\mathbf{r}) = \frac{1}{4\pi} \iiint_{V} 
+\mathbf{M}(\mathbf{r}^{\prime})^{\top} \left(
+\frac{\mathbf{r} - \mathbf{r}^{\prime}}{\| \mathbf{r} - \mathbf{r}^{\prime} \|^{3}}
+\right) \, dx^{\prime}dy^{\prime}dz^{\prime} \: .
+\label{eq:phi-potential}
+\end{equation}
+In this equation, $\mathbf{r}^{\prime} = [\begin{array}{ccc} 
+x^{\prime} & y^{\prime} & z^{\prime} \end{array} ]^{\top}$
+is the position vector of a point located within the volume $V$, 
+the integral is conducted over the variables 
+$x^{\prime}$, $y^{\prime}$ and, $z^{\prime}$ representing
+the coordinates of a point located within the volume $V$
+of the ellipsoid, $\| \cdot \|$ denotes the Euclidean norm and 
+$\mathbf{M}(\mathbf{r}^{\prime})$ is the magnetization vector
+(in $\unit{Am^{-1}}$).
+Equation \ref{eq:total-H-field} is valid anywhere, 
+independently if the position vector $\mathbf{r}$ represents
+a point located inside or outside the magnetized body.
+
+Based on \citeauthor{maxwell1873}'s postulate, let us
+assume that the body has a uniform magnetization given by
+\begin{equation}
+\mathbf{M} = \mathbf{K} \, \mathbf{H}_{i} \: ,
+\label{eq:M-KH}
+\end{equation}
+where $\mathbf{H}_{i}$ is the resultant uniform magnetic field 
+intensity at any point within the body and $\mathbf{K}$ is a 
+constant and symmetrical 2nd-order tensor representing the 
+magnetic susceptibility of the body. In this case, equation 
+\ref{eq:total-H-field} can be rewritten as follows:
+\begin{equation}
+\mathbf{H}(\mathbf{r}) = \mathbf{H}_{0} 
+- \mathbf{N}(\mathbf{r}) \, \mathbf{K} \, \mathbf{H}_{i} \: ,
+\label{eq:total-H-field-M-uniform}
+\end{equation}
+where $\mathbf{N}(\mathbf{r})$ is a $3 \times 3$ matrix whose
+$\alpha \beta$-element $n_{\alpha \beta}(\mathbf{r})$ is given by
+\begin{equation}
+n_{\alpha \beta}(\mathbf{r}) = - 
+\frac{1}{4\pi} \frac{\partial^{2}}{\partial \alpha \, \partial \beta}
+\iiint_{V} 
+\frac{1}{\| \mathbf{r} - \mathbf{r}^{\prime} \|}
+\, dx^{\prime}dy^{\prime}dz^{\prime} \: , \quad \alpha = x, y, z \: , 
+\quad \beta = x, y, z \: .
+\label{eq:n-alpha-beta}
+\end{equation}
+
+%
+%This property comes from the fact that the gravitational potential
+%within an ellipsoid with uniform density is a quadratic function
+%of the spatial coordinates.
+%
+%Based on this, the magnetization vector
 

### 2017-01-20 manuscript/manuscript.tex
define the depolarization tensor

@@
 $\alpha$, $\beta$, $\gamma$ and are defined 
-as follows \citep{clark1986magnetic}:
+as follows \citep{clark1986}:
 \begin{equation}
@@
 \ref{eq:v3_triaxial_prolate}, but with $\gamma = 0^{\circ}$ 
-\citep{emerson1985magnetic}.
+\citep{emerson1985}.
 Finally, the matrix $\mathbf{V}$ (equation \ref{eq:A}) for
@@
 \ref{eq:v3_triaxial_prolate}, with $\gamma = 0^{\circ}$, as follows
-\citep{emerson1985magnetic}:
+\citep{emerson1985}:
 \begin{equation}
@@
 induction, he postulated that the resulting magnetic
-field intensity at all points within the body must
+field (intensity) at all points within the body must
 also be uniform and parallel the magnetization, which
@@
 
-Let us start our description of the magnetic field produced
-by ellipsoids by considering a magnetized ellipsoid immersed in
+Consider a magnetized ellipsoid immersed in
 a uniform magnetic field $\mathbf{H}_{0}$ (in $\unit{Am^{-1}}$).
-The total magnetic intensity field $\mathbf{H}(\mathbf{r})$
+In the absence of conduction currents, 
+the total magnetic field $\mathbf{H}(\mathbf{r})$
 at the position $\mathbf{r}$ (equations \ref{eq:A} and 
 \ref{eq:coord_transformation}) of a point referred to the main 
-coordinate system is defined as follows
+coordinate system is defined as follows \citep{sttraton2007}:
 \begin{equation}
@@
 where the second term is the negative gradient of 
-the magnetic scalar potential $\phi(\mathbf{r})$ given by
+the magnetic scalar potential $\phi(\mathbf{r})$ given by:
 \begin{equation}
-\phi(\mathbf{r}) = \frac{1}{4\pi} \iiint_{V} 
-\mathbf{M}(\mathbf{r}^{\prime})^{\top} \left(
-\frac{\mathbf{r} - \mathbf{r}^{\prime}}{\| \mathbf{r} - \mathbf{r}^{\prime} \|^{3}}
+\phi(\mathbf{r}) = -\frac{1}{4\pi} \iiint_{V} 
+\mathbf{M}(\mathbf{r}^{\prime})^{\top} 
+\nabla \left(
+\frac{1}{\| \mathbf{r} - \mathbf{r}^{\prime} \|}
 \right) \, dx^{\prime}dy^{\prime}dz^{\prime} \: .
@@
 (in $\unit{Am^{-1}}$).
-Equation \ref{eq:total-H-field} is valid anywhere, 
+Equation \ref{eq:phi-potential} is valid anywhere, 
 independently if the position vector $\mathbf{r}$ represents
-a point located inside or outside the magnetized body.
+a point located inside or outside the magnetized body
+\citep{dubois1896}.
 
@@
 where $\mathbf{H}_{i}$ is the resultant uniform magnetic field 
-intensity at any point within the body and $\mathbf{K}$ is a 
+at any point within the body and $\mathbf{K}$ is a 
 constant and symmetrical 2nd-order tensor representing the 
@@
 \end{equation}
+It can be shown that the elements $n_{\alpha \beta}(\mathbf{r})$ are
+finite whether $\mathbf{r}$ is a point within or without
+the volume $V$ \citep{peirce1902, webster1904}.
+The matrix $\mathbf{N}(\mathbf{r})$ (equation \ref{eq:total-H-field-M-uniform})
+is called \textit{depolarization tensor} \citep{soliverez1981, soliverez2008}.
 
-%
-%This property comes from the fact that the gravitational potential
-%within an ellipsoid with uniform density is a quadratic function
-%of the spatial coordinates.
-%
-%Based on this, the magnetization vector
+\subsubsection{Internal magnetic field and magnetization}
 
-\subsection{Magnetic induction}
+\subsubsection{External magnetic induction}
 

### 2017-01-23 manuscript/manuscript.tex
appendix A and transformed depolarization tensor

@@
 \ref{eq:V_oblate}, depending on the ellipsoid type.
-Similarly, the transformation of a generic 
-linear system $\mathbf{M} \mathbf{p} = \mathbf{d}$
-referred to the main coordinate system into a new
-linear system 
-$\tilde{\mathbf{M}} \tilde{\mathbf{p}} = \tilde{\mathbf{d}}$
-referred to a local coordinate system is given by
-\begin{equation}
-\tilde{\mathbf{M}} = \mathbf{V}^{\top} \mathbf{M} \mathbf{V} \: , 
-\quad \tilde{\mathbf{p}} = \mathbf{V}^{\top} \mathbf{p} \: ,
-\quad \tilde{\mathbf{d}} = \mathbf{V}^{\top} \mathbf{d} \: .
-\label{eq:matrix_transformation}
-\end{equation}
-
-%A last but not least set of parameters defining the geometry of
-%an ellipsoid are their focal points.
-%The focal points are defined on the axes of the local coordinate 
-%system as follows:
+%Similarly, we may properly use the orthogonality of 
+%matrix $\mathbf{V}$ to transform a generic 
+%linear system $\mathbf{M} \mathbf{p} = \mathbf{d}$,
+%referred to the main coordinate system, into a new
+%linear system 
+%$\tilde{\mathbf{M}} \, \tilde{\mathbf{p}} = \tilde{\mathbf{d}}$,
+%referred to a local coordinate system, 
+%as follows:
 %\begin{equation}
-%\left(\tilde{x}, \tilde{y}, \tilde{z} \right) = 
-%\begin{cases}
-%\left( \pm \sqrt{a^{2} - b^{2}}, 0, 0 \right) \\
-%\left( \pm \sqrt{a^{2} - c^{2}}, 0, 0 \right) \\
-%\left( 0, \pm \sqrt{b^{2} - c^{2}}, 0 \right)
-%\end{cases} \: .
-%\label{eq:focal-points}
+%\underbrace{\mathbf{V}^{\top} \mathbf{M} \mathbf{V}}_{\tilde{\mathbf{M}}} \, 
+%\underbrace{\mathbf{V}^{\top} \mathbf{p}}_{\tilde{\mathbf{p}}} = 
+%\underbrace{\mathbf{V}^{\top} \mathbf{d}}_{\tilde{\mathbf{d}}} \: .
+%\label{eq:matrix-transformation}
 %\end{equation}
-%All ellipsoids sharing a common set of focal points form a family of confocal ellipsoids.
 
@@
 \end{equation}
-where $\mathbf{N}(\mathbf{r})$ is a $3 \times 3$ matrix whose
-$\alpha \beta$-element $n_{\alpha \beta}(\mathbf{r})$ is given by
+where $\mathbf{N}(\mathbf{r})$ is a symmetrical matrix whose
+$ij$-element $n_{ij}(\mathbf{r})$ is given by
 \begin{equation}
-n_{\alpha \beta}(\mathbf{r}) = - 
-\frac{1}{4\pi} \frac{\partial^{2}}{\partial \alpha \, \partial \beta}
-\iiint_{V} 
+n_{ij}(\mathbf{r}) = - 
+\frac{1}{4\pi} \frac{\partial^{2} \, f(\mathbf{r})}
+{\partial r_{i} \, \partial r_{j}} 
+\: , \quad i = 1, 2, 3 \: , 
+\quad j = 1, 2, 3 \: ,
+\label{eq:nij}
+\end{equation}
+$r_{1} = x$, $r_{2} = y$, $r_{3} = z$ are the elements of 
+the position vector $\mathbf{r}$ (equation \ref{eq:ellipsoid_surface}), 
+and
+\begin{equation}
+f(\mathbf{r}) = \iiint_{V} 
 \frac{1}{\| \mathbf{r} - \mathbf{r}^{\prime} \|}
-\, dx^{\prime}dy^{\prime}dz^{\prime} \: , \quad \alpha = x, y, z \: , 
-\quad \beta = x, y, z \: .
-\label{eq:n-alpha-beta}
+\, dx^{\prime}dy^{\prime}dz^{\prime} \: .
+\label{eq:f}
 \end{equation}
-It can be shown that the elements $n_{\alpha \beta}(\mathbf{r})$ are
+Notice that the scalar function $f(\mathbf{r})$ 
+(equation \ref{eq:f}) is proportional
+to the gravitational potential that would be produced by the 
+ellipsoidal body with volume $V$ if it had a uniform density 
+equal to the inverse of the gravitational constant.
+It can be shown that the elements $n_{ij}(\mathbf{r})$ are
 finite whether $\mathbf{r}$ is a point within or without
@@
 
+The following part of this paper moves on to describe 
+the magnetic field $\mathbf{H}(\mathbf{r})$ 
+(equation \ref{eq:total-H-field-M-uniform}) at points located
+both within and without the volume $V$ of the ellipsoidal
+body. However, the mathematical developments are conveniently 
+done in the local coordinate system related to the
+respective ellipsoidal body.
+
+Let $\tilde{f}(\tilde{\mathbf{r}})$ be the scalar function
+obtained by transforming $f(\mathbf{r})$ (equation \ref{eq:f})
+from the main coordinate system to a local coordinate system.
+Apparently, the function $\tilde{f}(\tilde{\mathbf{r}})$ was first 
+presented by Dirichlet in 1839 as a result of his study about
+the gravitational potential produced by homogeneous ellipsoids.
+Posteriorly, several authors also deduced and used this function
+for describing the magnetic and gravitational fields produced
+by ellipsoids \citep{maxwell1873, thomson1879, dubois1896, 
+peirce1902, webster1904, kellogg1929, stoner1945, osborn1945, sttraton2007}.
+
+INTRODUZIR A FUNCAO $\tilde{f}(\tilde{\mathbf{r}})$ E ADAPTAR 
+O TEXTO ABAIXO
+
+By properly using the orthogonality of matrix $\mathbf{V}$ 
+(equations \ref{eq:V_triaxial_prolate} and \ref{eq:V_oblate}),
+the magnetic field $\mathbf{H}(\mathbf{r})$ 
+(equation \ref{eq:total-H-field-M-uniform}) can be transformed
+from the main coordinate system to a local coordinate system
+as follows:
+\begin{equation}
+\underbrace{\mathbf{V}^{\top} \mathbf{H}(\mathbf{r})}_{\tilde{\mathbf{H}}(\tilde{\mathbf{r}})} = 
+\underbrace{\mathbf{V}^{\top} \mathbf{H}_{0}}_{\tilde{\mathbf{H}}_{0}}
+- \underbrace{\mathbf{V}^{\top} \mathbf{N}(\mathbf{r}) \mathbf{V}}
+_{\tilde{\mathbf{N}}(\tilde{\mathbf{r}})} \;
+\underbrace{\mathbf{V}^{\top} \mathbf{K} \mathbf{V}}
+_{\tilde{\mathbf{K}}} \; 
+\underbrace{\mathbf{V}^{\top} \mathbf{H}_{i}}
+_{\tilde{\mathbf{H}}_{i}} \: ,
+\label{eq:total-H-field-local-system}
+\end{equation}
+where the superscript "$\sim$" denotes quantities
+referred to the respective local coordinate system.
+
+In equation \ref{eq:total-H-field-local-system}, the transformed
+depolarization tensor $\tilde{\mathbf{N}}(\tilde{\mathbf{r}})$
+is calculated as a function of the original depolarization
+tensor $\mathbf{N}(\mathbf{r})$ (equation \ref{eq:total-H-field-M-uniform}).
+In this case, the elements of $\tilde{\mathbf{N}}(\tilde{\mathbf{r}})$
+are calculated as a function of the second derivatives of the
+function $f(\mathbf{r})$ (equation \ref{eq:f}),
+which is defined in the main coordinate system.
+It can be shown (Appendix A), however, that the
+elements $\tilde{n}_{ij}(\tilde{\mathbf{r}})$ of
+$\tilde{\mathbf{N}}(\tilde{\mathbf{r}})$ can also be calculated
+as follows:
+\begin{equation}
+\tilde{n}_{ij}(\tilde{\mathbf{r}}) = - 
+\frac{1}{4\pi} \frac{\partial^{2} \, \tilde{f}(\tilde{\mathbf{r}})}
+{\partial \tilde{r}_{i} \, \partial \tilde{r}_{j}} 
+\: , \quad i = 1, 2, 3 \: , \quad j = 1, 2, 3 \: ,
+\label{eq:nij-tilde}
+\end{equation}
+where $\tilde{r}_{1} = \tilde{x}$, $\tilde{r}_{2} = \tilde{y}$, 
+and $\tilde{r}_{3} = \tilde{z}$ are the elements of the
+transformed vector $\tilde{\mathbf{r}}$ (equation \ref{eq:coord_transformation})
+and $\tilde{f}(\tilde{\mathbf{r}})$ is a scalar function
+obtained by transforming $f(\mathbf{r})$ (equation \ref{eq:f})
+from the main coordinate system to the respective local
+coordinate system.
+
 \subsubsection{Internal magnetic field and magnetization}
 
+By considering $\mathbf{r}$ as a point internal to the
+volume $V$ of the ellipsoid and using the Maxwell's postulate 
+about the uniformity of the magnetic field $\mathbf{H}(\mathbf{r})$ 
+inside ellipsoidal bodies, we can rewrite equation \ref{eq:total-H-field-local-system}
+as follows:
+%\begin{equation}
+%
+%\label{eq:total-Hi-local-system}
+%\end{equation}
+
 \subsubsection{External magnetic induction}
-
-\subsection{TEXT}
-
-\subsubsection{TEXT}
-TEXT
 
@@
 \appendix
-\section{}    %% Appendix A
+\section{Relationship between the derivatives of the functions 
+$f(\mathbf{r})$ and $\tilde{f}(\tilde{\mathbf{r}})$}    %% Appendix A
 
-\subsection{}                               %% Appendix A1, A2, etc.
+Let $\tilde{f}(\tilde{\mathbf{r}})$ the scalar
+function obtained by transforming $f(\mathbf{r})$ 
+(equation \ref{eq:f}) from the
+main coordinate system to a local coordinate system.
+
+For convenience, let us rewrite equation 
+\ref{eq:coord_transformation} as follows:
+\begin{equation}
+\tilde{r}_{k} = v_{k1} \, r_{1} + v_{k2} \, r_{2} + v_{k3} \, r_{3} + c_{k} \: ,
+\label{eq:r-tilde-k}
+\end{equation}
+where $r_{j}$, $j = 1, 2, 3$, are the elements of the position vector
+$\mathbf{r}$ (equation \ref{eq:ellipsoid_surface}),
+$v_{kj}$, $j = 1, 2, 3$, are the elements of the matrix
+$\mathbf{V}$ (equation \ref{eq:V_triaxial_prolate} or \ref{eq:V_oblate}),
+and $c_{k}$ is a constant defined by the coordinates
+$x_{c}$, $y_{c}$, and $z_{c}$ of the centre of the ellipsoid body.
+
+By considering the functions $f(\mathbf{r})$ 
+(equation \ref{eq:f}) and $\tilde{f}(\tilde{\mathbf{r}})$
+evaluated at the same point, but on different coordinate
+systems, we have:
+\begin{equation*}
+\frac{\partial f(\mathbf{r})}{\partial r_{j}} = 
+\frac{\partial \tilde{f}(\tilde{\mathbf{r}})}{\partial \tilde{r}_{1}} \,
+\frac{\partial \tilde{r}_{1}}{\partial r_{j}} +
+\frac{\partial \tilde{f}(\tilde{\mathbf{r}})}{\partial \tilde{r}_{2}} \,
+\frac{\partial \tilde{r}_{2}}{\partial r_{j}} +
+\frac{\partial \tilde{f}(\tilde{\mathbf{r}})}{\partial \tilde{r}_{3}} \,
+\frac{\partial \tilde{r}_{3}}{\partial r_{j}} \: ,
+\quad j = 1, 2, 3 \: ,
+\end{equation*}
+which, from equation \ref{eq:r-tilde-k}, can be given by
+\begin{equation}
+\frac{\partial f(\mathbf{r})}{\partial r_{j}} = 
+v_{j1} \, \frac{\partial \tilde{f}(\tilde{\mathbf{r}})}{\partial \tilde{r}_{1}} +
+v_{j2} \, \frac{\partial \tilde{f}(\tilde{\mathbf{r}})}{\partial \tilde{r}_{2}} +
+v_{j3} \, \frac{\partial \tilde{f}(\tilde{\mathbf{r}})}{\partial \tilde{r}_{3}} \: ,
+\quad j = 1, 2, 3 \: .
+\label{eq:df_drj}
+\end{equation}
+
+Now, by deriving $\frac{\partial f(\mathbf{r})}{\partial r_{j}}$
+(equation \ref{eq:df_drj}) with respect to the $i$th element 
+$r_{i}$ of the position vector $\mathbf{r}$ (equation \ref{eq:ellipsoid_surface}),
+we obtain:
+\begin{equation}
+\begin{split}
+\frac{\partial^{2} f(\mathbf{r})}{\partial r_{i} \, \partial r_{j}} &=
+v_{j1} \, \frac{\partial}{\partial r_{i}} 
+\left( \frac{\partial \tilde{f}(\tilde{\mathbf{r}})}{\partial \tilde{r}_{1}} \right) +
+v_{j2} \, \frac{\partial}{\partial r_{i}} 
+\left( \frac{\partial \tilde{f}(\tilde{\mathbf{r}})}{\partial \tilde{r}_{2}} \right) +
+v_{j3} \, \frac{\partial}{\partial r_{i}} 
+\left( \frac{\partial \tilde{f}(\tilde{\mathbf{r}})}{\partial \tilde{r}_{3}} \right) \\
+&= v_{j1} \, \left( 
+\frac{\partial^{2} \tilde{f}(\tilde{\mathbf{r}})}
+{\partial \tilde{r}_{1} \, \partial \tilde{r}_{1}} \, v_{i1} + 
+\frac{\partial^{2} \tilde{f}(\tilde{\mathbf{r}})}
+{\partial \tilde{r}_{2} \, \partial \tilde{r}_{1}} \, v_{i2} + 
+\frac{\partial^{2} \tilde{f}(\tilde{\mathbf{r}})}
+{\partial \tilde{r}_{3} \, \partial \tilde{r}_{1}} \, v_{i3} 
+\right) + \\
+&+ v_{j2} \, \left( 
+\frac{\partial^{2} \tilde{f}(\tilde{\mathbf{r}})}
+{\partial \tilde{r}_{1} \, \partial \tilde{r}_{2}} \, v_{i1} + 
+\frac{\partial^{2} \tilde{f}(\tilde{\mathbf{r}})}
+{\partial \tilde{r}_{2} \, \partial \tilde{r}_{2}} \, v_{i2} + 
+\frac{\partial^{2} \tilde{f}(\tilde{\mathbf{r}})}
+{\partial \tilde{r}_{3} \, \partial \tilde{r}_{2}} \, v_{i3} 
+\right) + \\
+&+ v_{j3} \, \left( 
+\frac{\partial^{2} \tilde{f}(\tilde{\mathbf{r}})}
+{\partial \tilde{r}_{1} \, \partial \tilde{r}_{3}} \, v_{i1} + 
+\frac{\partial^{2} \tilde{f}(\tilde{\mathbf{r}})}
+{\partial \tilde{r}_{2} \, \partial \tilde{r}_{3}} \, v_{i2} + 
+\frac{\partial^{2} \tilde{f}(\tilde{\mathbf{r}})}
+{\partial \tilde{r}_{3} \, \partial \tilde{r}_{3}} \, v_{i3} 
+\right) \\
+&= \left[ \begin{array}{ccc}
+v_{j1} & v_{j2} & v_{j3}
+\end{array} \right] \tilde{\mathbf{F}}(\tilde{\mathbf{r}})
+\left[ \begin{array}{c}
+v_{i1} \\ v_{i2} \\ v_{i3}
+\end{array} \right]
+\end{split} \: ,
+\label{eq:d2f-dridrj}
+\end{equation}
+where $\tilde{\mathbf{F}}(\tilde{\mathbf{r}})$ is a $3 \times 3$
+matrix whose $ij$-th element is 
+$\frac{\partial^{2} \tilde{f}(\tilde{\mathbf{r}})}
+{\partial \tilde{r}_{i} \, \partial \tilde{r}_{j}}$.
+From equation \ref{eq:d2f-dridrj}, we obtain
+\begin{equation}
+\mathbf{F}(\mathbf{r}) = \mathbf{V} \, 
+\tilde{\mathbf{F}}(\tilde{\mathbf{r}}) \, \mathbf{V}^{\top} \: ,
+\label{eq:F-V-F-tilde-VT}
+\end{equation}
+where $\mathbf{F}(\mathbf{r})$ is a $3 \times 3$
+matrix whose $ij$-th element is 
+$\frac{\partial^{2} f(\mathbf{r})}
+{\partial r_{i} \, \partial r_{j}}$ and
+$\mathbf{V}$ is defined by equations 
+\ref{eq:V_triaxial_prolate} or
+\ref{eq:V_oblate}, depending on the ellipsoid
+type. As one may noticed, the matrices $\mathbf{F}(\mathbf{r})$ and
+$\tilde{\mathbf{F}}(\tilde{\mathbf{r}})$ represent the Hessians
+of the functions $f(\mathbf{r})$ (equation \ref{eq:f})
+and $\tilde{f}(\tilde{\mathbf{r}})$, respectively.
+Besides, the depolarization tensor $\mathbf{N}(\mathbf{r})$
+(equation \ref{eq:total-H-field-M-uniform}) can be 
+rewritten by using the matrix $\mathbf{F}(\mathbf{r})$
+as follows
+\begin{equation}
+\mathbf{N}(\mathbf{r}) = - \frac{1}{4 \pi} \mathbf{F}(\mathbf{r}) \: .
+\label{eq:N-F}
+\end{equation}
+By properly using the orthogonality of the matrix
+$\mathbf{V}$, we may rewrite equation \ref{eq:F-V-F-tilde-VT}
+as follows:
+\begin{equation}
+\tilde{\mathbf{F}}(\tilde{\mathbf{r}}) = \mathbf{V}^{\top} \, 
+\mathbf{F}(\mathbf{r}) \, \mathbf{V} \: .
+\label{eq:F-tilde-VT-F-V}
+\end{equation}
+Finally, by multiplying both sides of equation \ref{eq:F-tilde-VT-F-V}
+by $-\frac{1}{4 \pi}$ and using equations \ref{eq:N-F}
+and \ref{eq:total-H-field-local-system}, we conclude that 
+\begin{equation}
+\tilde{\mathbf{N}}(\tilde{\mathbf{r}}) = 
+- \frac{1}{4 \pi} 
+\tilde{\mathbf{F}}(\tilde{\mathbf{r}}) \: .
+\label{eq:N-tilde-F-tilde}
+\end{equation}
+
+%\subsection{}                               %% Appendix A1, A2, etc.
 

### 2017-01-23 manuscript/manuscript.tex
appendix B

@@
 
-\subsection{Magnetic field produced by ellipsoids}
+\subsection{Theoretical background}
 
@@
 
+\subsection{Coordinate transformation}
+
 Let $\tilde{f}(\tilde{\mathbf{r}})$ be the scalar function
@@
 from the main coordinate system to a local coordinate system.
-Apparently, the function $\tilde{f}(\tilde{\mathbf{r}})$ was first 
-presented by Dirichlet in 1839 as a result of his study about
-the gravitational potential produced by homogeneous ellipsoids.
+The function $\tilde{f}(\tilde{\mathbf{r}})$ was first 
+presented by \citet{dirichlet1839} to describe the gravitational potential
+produced by homogeneous ellipsoids.
 Posteriorly, several authors also deduced and used this function
 for describing the magnetic and gravitational fields produced
-by ellipsoids \citep{maxwell1873, thomson1879, dubois1896, 
-peirce1902, webster1904, kellogg1929, stoner1945, osborn1945, sttraton2007}.
+by triaxial, prolate, and/or oblate ellipsoids  
+\citep{maxwell1873, thomson1879, dubois1896, 
+peirce1902, webster1904, kellogg1929, stoner1945, osborn1945,
+lowes1974,  peake1953, chang1961, clark1986, tejedor1995, sttraton2007}.
+It is convenient to use $\tilde{f}_{i}(\tilde{\mathbf{r}})$
+and $\tilde{f}_{e}(\tilde{\mathbf{r}})$ to define 
+the function $\tilde{f}(\tilde{\mathbf{r}})$ evaluated, 
+respectively, at points 
+$\tilde{\mathbf{r}}$ inside and outside the volume $V$ of the
+ellipsoidal body.
 
-INTRODUZIR A FUNCAO $\tilde{f}(\tilde{\mathbf{r}})$ E ADAPTAR 
-O TEXTO ABAIXO
+By following \citet{webster1904}, $\tilde{f}_{i}(\tilde{\mathbf{r}})$
+is given by
+\begin{equation}
+\tilde{f}_{i}(\tilde{\mathbf{r}}) = \pi \, abc \, 
+\int_{0}^{\infty} \left( 1 
+- \frac{\tilde{x}^{2}}{a^{2} + u} 
+- \frac{\tilde{y}^{2}}{b^{2} + u}
+- \frac{\tilde{z}^{2}}{c^{2} + u} \right)
+\frac{1}{R(u)} \, du \: , \quad \tilde{\mathbf{r}} \in V \: ,
+\label{eq:fi-tilde}
+\end{equation}
+where
+\begin{equation}
+R(u) = \sqrt{\left( a^{2} + u \right)\left( b^{2} + u \right)\left( c^{2} + u \right)} \: .
+\label{eq:R}
+\end{equation}
+This function represents the gravitational potential
+that would be produced by the ellipsoidal body at
+points located within its volume $V$ if it
+had a uniform density equal to the inverse of the
+gravitational constant.
+Notice that, in this case, the gravitational potential
+is a quadratic function of the spatial coordinates
+$\tilde{x}$, $\tilde{y}$, and $\tilde{z}$, which
+supported the \citeauthor{maxwell1873}'s (\citeyear{maxwell1873})
+postulate about uniformly magnetized ellipsoids.
+
+In a similar way, the function $\tilde{f}_{e}(\tilde{\mathbf{r}})$
+is given by \citep{webster1904}
+\begin{equation}
+\tilde{f}_{e}(\tilde{\mathbf{r}}) = \pi \, abc \, 
+\int_{\lambda}^{\infty} \left( 1 
+- \frac{\tilde{x}^{2}}{a^{2} + u} 
+- \frac{\tilde{y}^{2}}{b^{2} + u}
+- \frac{\tilde{z}^{2}}{c^{2} + u} \right)
+\frac{1}{R(u)} \, du \: , \quad \tilde{\mathbf{r}} \not\in V \: ,
+\label{eq:fe-tilde}
+\end{equation}
+where $R(u)$ is defined by equation \ref{eq:R} and the
+parameter $\lambda$ is a constant defining the integral 
+lower limit.
+
+The parameter $\lambda$ is defined according to the
+ellipsoid type. Details about the mathematical meaning
+of this parameter are given in Appendix B.
+
+PAREI AQUI
 
@@
 
-\subsubsection{Internal magnetic field and magnetization}
+\subsubsection{Internal magnetic field and demagnetization}
 
@@
 \appendix
-\section{Relationship between the derivatives of the functions 
-$f(\mathbf{r})$ and $\tilde{f}(\tilde{\mathbf{r}})$}    %% Appendix A
+\section{Relationship between the derivatives of the functions $f(\mathbf{r})$ and $\tilde{f}(\tilde{\mathbf{r}})$}    %% Appendix A
 
@@
 
-%\subsection{}                               %% Appendix A1, A2, etc.
+\section{Parameter $\lambda$ and its spatial derivatives}    %% Appendix B
+
+Here, we follow the reasoning presented by \citet{webster1904}
+for analysing the parameter $\lambda$ describing triaxial, prolate
+and oblate ellipsoids.
+
+\subsection{Parameter $\lambda$ defining triaxial ellipsoids} %% Appendix A1, A2, etc.
+
+Let us consider an ellipsoid with semi-axes $a$, $b$, $c$ oriented along 
+the $\tilde{x}$-, $\tilde{y}$-, and $\tilde{z}$-axis, respectively, 
+of its local coordinate system, where $a > b > c > 0$. 
+This ellipsoid is defined by the following equation:
+\begin{equation}
+\frac{\tilde{x}^{2}}{a^{2}} + \frac{\tilde{y}^{2}}{b^{2}} + \frac{\tilde{z}^{2}}{c^{2}} = 1 \: .
+\label{eq:reference-triaxial-ell}
+\end{equation}
+A quadric surface which is confocal with the ellipsoid defined in 
+equation \ref{eq:reference-triaxial-ell} can be described as 
+follows:
+\begin{equation}
+\frac{\tilde{x}^{2}}{a^{2} + u} + \frac{\tilde{y}^{2}}{b^{2} + u} + \frac{\tilde{z}^{2}}{c^{2} + u} = 1 \: ,
+\label{eq:quadric-confocal-triaxial-ell}
+\end{equation}
+where $u$ is a real number. We know that \ref{eq:quadric-confocal-triaxial-ell} 
+represents an ellipsoid for $u$ satisfying the condition
+\begin{equation}
+u + c^{2} > 0 \: .
+\label{eq:condition-triaxial-ell}
+\end{equation}
+
+Given $a$, $b$, $c$, and a $u$ satisfying \ref{eq:condition-triaxial-ell}, 
+we may use \ref{eq:quadric-confocal-triaxial-ell} for determining a set of 
+points $(x, y, z)$ lying on the surface of an ellipsoid which is confocal 
+with that one defined in equation \ref{eq:reference-triaxial-ell}. 
+Now, consider the problem of determining the ellipsoid which is confocal 
+with that one defined in \ref{eq:reference-triaxial-ell} and pass through 
+a particular point $(\tilde{x}, \tilde{y}, \tilde{z})$. 
+This problem consists in determining the real number $u$ that, 
+given $a$, $b$, $c$, $\tilde{x}$, $\tilde{y}$, and $\tilde{z}$, 
+satisfies the condition expressed by equation \ref{eq:condition-triaxial-ell}.
+By rearranging equation \ref{eq:quadric-confocal-triaxial-ell}, 
+we obtain the following cubic equation for $u$:
+\begin{equation}
+p(u) = (a^{2} + u)(b^{2} + u)(c^{2} + u) - (b^{2} + u)(c^{2} + u) \, \tilde{x}^{2}
+- (a^{2} + u)(c^{2} + u) \, \tilde{y}^{2} - (a^{2} + u)(b^{2} + u) \, \tilde{z}^{2} \: .
+\label{eq:cubic-equation-triaxial-ell}
+\end{equation}
+By analysing the signals of this cubic equation we conclude that:
+\begin{equation}
+u = \begin{cases}
+d \to \infty \: &, \quad p(u) > 0 \\
+-c^{2} \: &, \quad p(u) < 0 \\
+-b^{2} \: &, \quad p(u) > 0 \\
+-a^{2} \: &, \quad p(u) < 0
+\end{cases} \: .
+\label{eq:cubic-equation-signals-triaxial-ell}
+\end{equation}
+Notice that, according to \ref{eq:cubic-equation-signals-triaxial-ell},
+the smaller, intermediate and largest roots of the cubic 
+equation $p(u)$ (equation \ref{eq:cubic-equation-triaxial-ell}) are 
+located, respectively, in the intervals $[ -a^{2} \, , -b^{2} ]$,
+$[ -b^{2} \, , -c^{2} ]$ and $[ -c^{2} \, , \infty [$.
+Remember that we are interested in a $u$ satisfying 
+the condition expressed by equation \ref{eq:condition-triaxial-ell}. 
+Consequently, according to the signal analysis shown in equation
+\ref{eq:cubic-equation-signals-triaxial-ell}, we are interested in 
+the largest root $\lambda$ of the cubic equation $p(u)$ (equation
+\ref{eq:cubic-equation-triaxial-ell}).
+
+From equation \ref{eq:cubic-equation-triaxial-ell}, we obtain a
+simpler one given by
+\begin{equation}
+p(u) =  u^{u} + p_{2} \, u^{2} + p_{1} \, u + p_{0} \: ,
+\label{eq:cubic-equation-triaxial-ell-simpler}
+\end{equation}
+where
+\begin{equation}
+p_{2} = a^{2} + b^{2} + c^{2} - \tilde{x}^{2} - \tilde{y}^{2} - \tilde{z}^{2} \: ,
+\label{eq:p2-triaxial-ell}
+\end{equation}
+\begin{equation}
+p_{1} = p_{1} =  ^{2} \, c^{2} + a^{2} \, c^{2} + a^{2} \, b^{2} 
+- (b^{2} + c^{2}) \, \tilde{x}^{2}
+- (a^{2} + c^{2}) \, \tilde{y}^{2} 
+- (a^{2} + b^{2}) \, \tilde{z}^{2}
+\label{eq:p1-triaxial-ell}
+\end{equation}
+and
+\begin{equation}
+p_{0} =  a^{2} \, b^{2} \, c^{2} - b^{2} \, c^{2} \, 
+\tilde{x}^{2} - a^{2} \, c^{2} \, \tilde{y}^{2} - a^{2} \, 
+b^{2} \, \tilde{z}^{2} \: .
+\label{eq:p0-triaxial-ell}
+\end{equation}
+Finally, from equations \ref{eq:p2-triaxial-ell}, 
+\ref{eq:p1-triaxial-ell} and \ref{eq:p0-triaxial-ell},
+the largest root $\lambda$ of $p(u)$ 
+(equation \ref{eq:cubic-equation-triaxial-ell}) can be 
+calculated as follows \citep{weisstein2017}:
+\begin{equation}
+\lambda = 2 \, \sqrt{-Q} \, \cos \left( \frac{\theta}{3}\right) - \frac{p_{2}}{3} \: ,
+\label{eq:lambda-triaxial-ell}
+\end{equation}
+where
+\begin{equation}
+\theta = \cos^{-1} \left( \frac{R}{\sqrt{Q^{3}}} \right) \: ,
+\label{eq:theta-triaxial-ell}
+\end{equation}
+\begin{equation}
+Q = \frac{3 \, p_{1} - p_{2}^{2}}{9}
+\label{eq:Q-triaxial-ell}
+\end{equation}
+and
+\begin{equation}
+R = \frac{9 \, p_{1} \, p_{2} - 27 \, p_{0} - 2 \, p_{2}^{3}}{54} \: .
+\label{eq:R-triaxial-ell}
+\end{equation}
+
+\subsection{Parameter $\lambda$ defining prolate and oblate ellipsoids} %% Appendix A1, A2, etc.
+
+Let us now consider a prolate ellipsoid with semi-axes $a$, $b$, 
+$c$ oriented along the $\tilde{x}$-, $\tilde{y}$-, and 
+$\tilde{z}$-axis, respectively, of its local coordinate system, 
+where $a > b = c > 0$.
+
+In this case,
 

### 2017-01-23 manuscript/manuscript.tex
finish appendix B

@@
 Finally, by multiplying both sides of equation \ref{eq:F-tilde-VT-F-V}
-by $-\frac{1}{4 \pi}$ and using equations \ref{eq:N-F}
-and \ref{eq:total-H-field-local-system}, we conclude that 
+by $-\frac{1}{4 \pi}$ and using equation \ref{eq:N-F},
+we conclude that 
 \begin{equation}
 \tilde{\mathbf{N}}(\tilde{\mathbf{r}}) = 
-- \frac{1}{4 \pi} 
-\tilde{\mathbf{F}}(\tilde{\mathbf{r}}) \: .
-\label{eq:N-tilde-F-tilde}
+\mathbf{V}^{\top} \, \mathbf{N}(\mathbf{r}) \, \mathbf{V} \: .
+\label{eq:N-tilde-VT-N-V}
 \end{equation}
@@
 Here, we follow the reasoning presented by \citet{webster1904}
-for analysing the parameter $\lambda$ describing triaxial, prolate
+for analysing the parameter $\lambda$ which defines triaxial, prolate
 and oblate ellipsoids.
@@
 \end{equation}
-A quadric surface which is confocal with the ellipsoid defined in 
-equation \ref{eq:reference-triaxial-ell} can be described as 
-follows:
+A quadric surface (e.g., ellipsoid, hyperboloid of one sheet or
+hyperboloid of two sheets) which is confocal with the ellipsoid 
+defined in equation \ref{eq:reference-triaxial-ell} can be 
+described as follows:
 \begin{equation}
@@
 \end{equation}
-where $u$ is a real number. We know that \ref{eq:quadric-confocal-triaxial-ell} 
+where $u$ is a real number. Equation \ref{eq:quadric-confocal-triaxial-ell} 
 represents an ellipsoid for $u$ satisfying the condition
@@
 given $a$, $b$, $c$, $\tilde{x}$, $\tilde{y}$, and $\tilde{z}$, 
-satisfies the condition expressed by equation \ref{eq:condition-triaxial-ell}.
+satisfies equation \ref{eq:quadric-confocal-triaxial-ell} and
+the condition expressed by equation \ref{eq:condition-triaxial-ell}.
 By rearranging equation \ref{eq:quadric-confocal-triaxial-ell}, 
@@
 \end{equation}
-By analysing the signals of this cubic equation we conclude that:
+This cubic equation shows that:
 \begin{equation}
@@
 \begin{equation}
-p_{1} = p_{1} =  ^{2} \, c^{2} + a^{2} \, c^{2} + a^{2} \, b^{2} 
+p_{1} = b^{2} \, c^{2} + a^{2} \, c^{2} + a^{2} \, b^{2} 
 - (b^{2} + c^{2}) \, \tilde{x}^{2}
@@
 the largest root $\lambda$ of $p(u)$ 
-(equation \ref{eq:cubic-equation-triaxial-ell}) can be 
+(equation \ref{eq:cubic-equation-triaxial-ell-simpler}) can be 
 calculated as follows \citep{weisstein2017}:
@@
 where $a > b = c > 0$. 
+In this case, the equation defining the surface of the ellipsoid
+is obtained by substituting $c = b$ in equation \ref{eq:reference-triaxial-ell}.
+Consequently, the equation defining the respective confocal quadric
+surface is given by
+\begin{equation}
+\frac{\tilde{x}^{2}}{a^{2} + u} + \frac{\tilde{y}^{2} + \tilde{z}^{2}}{b^{2} + u} = 1
+\label{eq:quadric-confocal-prolate-ell}
+\end{equation}
+and the new condition that must be fulfilled by the variable
+$u$ so that equation \ref{eq:quadric-confocal-prolate-ell}
+represent an ellipsoid is
+\begin{equation}
+u + b^{2} > 0 \: .
+\label{eq:condition-prolate-ell}
+\end{equation}
 
-In this case,
+Similarly to the case of a triaxial ellipsoid presented
+in the previous subsection, we are interested in
+determining the real number $u$ that, 
+given $a$, $b$, $\tilde{x}$, $\tilde{y}$, and $\tilde{z}$, 
+satisfies equation \ref{eq:quadric-confocal-prolate-ell} and
+the condition expressed by equation \ref{eq:condition-prolate-ell}.
+From equation \ref{eq:quadric-confocal-prolate-ell}, 
+we obtain the following quadratic equation for $u$:
+\begin{equation}
+p(u) = (a^{2} + u)(b^{2} + u) - (b^{2} + u) \, \tilde{x}^{2}
+- (a^{2} + u) \, (\tilde{y}^{2} + \tilde{z}^{2}) \: .
+\label{eq:quadratic-equation-prolate-ell}
+\end{equation}
+This equation shows that
+\begin{equation}
+u = \begin{cases}
+d \to \infty \: &, \quad f(\rho) > 0 \\
+-b^{2} \: &, \quad f(\rho) < 0 \\
+-a^{2} \: &, \quad f(\rho) > 0
+\end{cases}
+\label{eq:quadratic-equation-signals-prolate-ell}
+\end{equation}
+and, consequently, that its two roots lie in the intervals
+$[ -a^{2} \, , -b^{2} ]$ and $[ -b^{2} \, , \infty [$.
+Therefore, according to the condition established by
+equation \ref{eq:condition-prolate-ell} and the signal analysis 
+shown in equation \ref{eq:quadratic-equation-signals-prolate-ell}, 
+we are interested in the largest root $\lambda$ of the quadratic 
+equation $p(u)$ (equation \ref{eq:quadratic-equation-prolate-ell}).
+
+By properly manipulating equation \ref{eq:quadratic-equation-prolate-ell},
+we obtain a simpler one given by
+\begin{equation}
+p(u) =  u^{2} + p_{1} \, u + p_{0} \: ,
+\label{eq:quadratic-equation-prolate-ell-simpler}
+\end{equation}
+where
+\begin{equation}
+p_{1} = a^{2} + b^{2} - \tilde{x}^{2} - \tilde{y}^{2} - \tilde{z}^{2}
+\label{eq:p1-prolate-ell}
+\end{equation}
+and
+\begin{equation}
+p_{0} =  a^{2} \, b^{2} 
+- b^{2} \, \tilde{x}^{2} 
+- a^{2} \left( \tilde{y}^{2} + \tilde{z}^{2} \right) \: .
+\label{eq:p0-prolate-ell}
+\end{equation}
+Finally, by using equations \ref{eq:p1-prolate-ell} and
+\ref{eq:p0-prolate-ell}, the largest root $\lambda$ of $p(u)$ 
+(equation \ref{eq:quadratic-equation-prolate-ell-simpler}) can be 
+easily calculated as follows:
+\begin{equation}
+\lambda = \frac{-p_{1} + \sqrt{p_{1}^{2} - 4 \, p_{0}}}{2} \: .
+\label{eq:lambda-prolate-ell}
+\end{equation}
+
+In the case of oblate ellipsoids, the procedure for determining
+the parameter $\lambda$ is very similar to that one for prolate
+ellipsoids.
+The semi-axes $a$, $b$, $c$ of oblate 
+ellipsoids are defined so that $b = c > a > 0$
+and the condition that must be fulfilled by 
+the variable $u$ is $u + a^{2} > 0$.
+In this case, the two roots of the resulting quadratic equation 
+lie in the intervals $[ -b^{2} \, , -a^{2} ]$ and $[ -a^{2} \, , \infty [$.
+Consequently, we are still interested in the largest root of
+the quadratic equation for the variable $u$, which is also 
+calculated by using equation \ref{eq:lambda-prolate-ell}.
+
+\subsection{Spatial derivative of the parameter $\lambda$}
+
+The magnetic modelling of triaxial, prolate or oblate ellipsoids 
+requires not only the parameter lambda defined by equations
+\ref{eq:lambda-triaxial-ell} and \ref{eq:lambda-prolate-ell},
+but also its derivatives with respect to the spatial coordinates
+$\tilde{x}$, $\tilde{y}$, and $\tilde{z}$.
+Fortunately, the spatial derivatives of the parameter $\lambda$ 
+can be calculated in a very similar way for all ellipsoid types.
+
+Let us first consider a triaxial ellipsoid. In this case,
+the spatial derivatives of $\lambda$ are given by
+\begin{equation}
+\frac{\partial \lambda}{\partial \tilde{r}_{j}} =
+\frac{\frac{2 \, \tilde{r}_{j}}{\left( e_{j}^{2} + \lambda \right)}}{
+\left( \frac{\tilde{x}}{a^{2} + \lambda}\right)^{2} +
+\left( \frac{\tilde{y}}{b^{2} + \lambda}\right)^{2} + 
+\left( \frac{\tilde{z}}{c^{2} + \lambda}\right)^{2}} \: , \quad j = 1, 2, 3 \: ,
+\label{eq:dlambda}
+\end{equation}
+where 
+$\tilde{r}_{1} = \tilde{x}$, $\tilde{r}_{2} = \tilde{y}$, $\tilde{r}_{3} = \tilde{z}$,
+$e_{1} = a$, $e_{2} = b$, and $e_{3} = c$.
+This equation can be determined directly from equation
+\ref{eq:quadric-confocal-triaxial-ell}. 
+The spatial derivatives of $\lambda$ in the case of
+prolate or oblate ellipsoids can also be calculated by using
+equation \ref{eq:dlambda}, but with semi-axes $a > b = c$
+or $b = c > a$, respectively.
 

### 2017-01-24 manuscript/manuscript.tex
internal magnetic field, magnetization, external magnatic field and total-field anomaly

@@
 For triaxial ellipsoids (i.e., $a > b > c$), the orthogonal matrix
-$\mathbf{V}$ (equation \ref{eq:A}) is calculated by using equations
+$\mathbf{V}$ (Eq. \ref{eq:A}) is calculated by using Eqs.
 \ref{eq:v1_triaxial_prolate}, \ref{eq:v2_triaxial_prolate}, and
@@
 \end{equation}
-Similarly, the matrix $\mathbf{V}$ (equation \ref{eq:A}) for
+Similarly, the matrix $\mathbf{V}$ (Eq. \ref{eq:A}) for
 prolate ellipsoids (i.e., $a > b = c$) is calculated according
-to equation \ref{eq:V_triaxial_prolate} by using equations
+to Equation \ref{eq:V_triaxial_prolate} by using Equations
 \ref{eq:v1_triaxial_prolate}, \ref{eq:v2_triaxial_prolate}, and
@@
 \citep{emerson1985}.
-Finally, the matrix $\mathbf{V}$ (equation \ref{eq:A}) for
+Finally, the matrix $\mathbf{V}$ (Eq. \ref{eq:A}) for
 oblate ellipsoids (i.e., $a < b = c$) is calculated by 
-using equations \ref{eq:v1_triaxial_prolate}, \ref{eq:v2_triaxial_prolate}, and
+using Eqs. \ref{eq:v1_triaxial_prolate}, \ref{eq:v2_triaxial_prolate}, and
 \ref{eq:v3_triaxial_prolate}, with $\gamma = 0^{\circ}$, as follows
@@
 by the first, second, and third columns of the matrix 
-$\mathbf{V}$ given by equation \ref{eq:V_triaxial_prolate},
+$\mathbf{V}$ given by Equation \ref{eq:V_triaxial_prolate},
 in the case of a triaxial or prolate ellipsoid, or the
-matrix $\mathbf{V}$ given by equation \ref{eq:V_oblate},
+matrix $\mathbf{V}$ given by Equation \ref{eq:V_oblate},
 in the case of an oblate ellipsoid.
@@
 $\mathbf{r}$ and $\mathbf{r}_{c}$
-are defined in equation \ref{eq:ellipsoid_surface} and the matrix $\mathbf{V}$
-is defined according to equations \ref{eq:V_triaxial_prolate} or
+are defined in Equation \ref{eq:ellipsoid_surface} and the matrix $\mathbf{V}$
+is defined according to Eqs. \ref{eq:V_triaxial_prolate} or
 \ref{eq:V_oblate}, depending on the ellipsoid type.
@@
 a uniform magnetic field $\mathbf{H}_{0}$ (in $\unit{Am^{-1}}$).
+This uniform field can be, for example, the main component of the
+Earth's magnetic field, which is usually assumed to be generated
+by the Earth's liquid core.
 In the absence of conduction currents, 
 the total magnetic field $\mathbf{H}(\mathbf{r})$
-at the position $\mathbf{r}$ (equations \ref{eq:A} and 
+at the position $\mathbf{r}$ (Eqs. \ref{eq:A} and 
 \ref{eq:coord_transformation}) of a point referred to the main 
@@
 \mathbf{H}(\mathbf{r}) = \mathbf{H}_{0} - \nabla \phi(\mathbf{r}) \: ,
-\label{eq:total-H-field}
+\label{eq:H}
 \end{equation}
@@
 \begin{equation}
-\mathbf{M} = \mathbf{K} \, \mathbf{H}_{i} \: ,
+\mathbf{M} = \mathbf{K} \, \mathbf{H}_{I} \: ,
 \label{eq:M-KH}
 \end{equation}
-where $\mathbf{H}_{i}$ is the resultant uniform magnetic field 
+where $\mathbf{H}_{I}$ is the resultant uniform magnetic field 
 at any point within the body and $\mathbf{K}$ is a 
 constant and symmetrical 2nd-order tensor representing the 
-magnetic susceptibility of the body. In this case, equation 
-\ref{eq:total-H-field} can be rewritten as follows:
+magnetic susceptibility of the body. In this case, Equation 
+\ref{eq:H} can be rewritten as follows:
 \begin{equation}
 \mathbf{H}(\mathbf{r}) = \mathbf{H}_{0} 
-- \mathbf{N}(\mathbf{r}) \, \mathbf{K} \, \mathbf{H}_{i} \: ,
-\label{eq:total-H-field-M-uniform}
+- \mathbf{N}(\mathbf{r}) \, \mathbf{K} \, \mathbf{H}_{I} \: ,
+\label{eq:H-M-uniform}
 \end{equation}
@@
 $r_{1} = x$, $r_{2} = y$, $r_{3} = z$ are the elements of 
-the position vector $\mathbf{r}$ (equation \ref{eq:ellipsoid_surface}), 
+the position vector $\mathbf{r}$ (Eq. \ref{eq:ellipsoid_surface}), 
 and
@@
 Notice that the scalar function $f(\mathbf{r})$ 
-(equation \ref{eq:f}) is proportional
+(Eq. \ref{eq:f}) is proportional
 to the gravitational potential that would be produced by the 
@@
 the volume $V$ \citep{peirce1902, webster1904}.
-The matrix $\mathbf{N}(\mathbf{r})$ (equation \ref{eq:total-H-field-M-uniform})
+The matrix $\mathbf{N}(\mathbf{r})$ (Eq. \ref{eq:H-M-uniform})
 is called \textit{depolarization tensor} \citep{soliverez1981, soliverez2008}.
@@
 the magnetic field $\mathbf{H}(\mathbf{r})$ 
-(equation \ref{eq:total-H-field-M-uniform}) at points located
+(Eq. \ref{eq:H-M-uniform}) at points located
 both within and without the volume $V$ of the ellipsoidal
 body. However, the mathematical developments are conveniently 
-done in the local coordinate system related to the
+performed in the local coordinate system related to the
 respective ellipsoidal body.
@@
 
-Let $\tilde{f}(\tilde{\mathbf{r}})$ be the scalar function
-obtained by transforming $f(\mathbf{r})$ (equation \ref{eq:f})
-from the main coordinate system to a local coordinate system.
+To continue our description of the magnetic modelling of 
+ellipsoidal bodies, it is convenient to perform two 
+important coordinate transformations. 
+The first one transforms the scalar function 
+$f(\mathbf{r})$ (Eq. \ref{eq:f}) from the 
+main coordinate system into a new scalar function 
+$\tilde{f}(\tilde{\mathbf{r}})$ referred to the
+local coordinate system.
 The function $\tilde{f}(\tilde{\mathbf{r}})$ was first 
@@
 for describing the magnetic and gravitational fields produced
-by triaxial, prolate, and/or oblate ellipsoids  
+by triaxial, prolate, and oblate ellipsoids  
 \citep{maxwell1873, thomson1879, dubois1896, 
@@
 lowes1974,  peake1953, chang1961, clark1986, tejedor1995, sttraton2007}.
-It is convenient to use $\tilde{f}_{i}(\tilde{\mathbf{r}})$
-and $\tilde{f}_{e}(\tilde{\mathbf{r}})$ to define 
+It is convenient to use $\tilde{f}_{I}(\tilde{\mathbf{r}})$
+and $\tilde{f}_{E}(\tilde{\mathbf{r}})$ to define 
 the function $\tilde{f}(\tilde{\mathbf{r}})$ evaluated, 
@@
 
-By following \citet{webster1904}, $\tilde{f}_{i}(\tilde{\mathbf{r}})$
+The scalar function $\tilde{f}_{I}(\tilde{\mathbf{r}})$
 is given by
 \begin{equation}
-\tilde{f}_{i}(\tilde{\mathbf{r}}) = \pi \, abc \, 
+\tilde{f}_{I}(\tilde{\mathbf{r}}) = \pi \, abc \, 
 \int_{0}^{\infty} \left( 1 
@@
 postulate about uniformly magnetized ellipsoids.
-
-In a similar way, the function $\tilde{f}_{e}(\tilde{\mathbf{r}})$
-is given by \citep{webster1904}
-\begin{equation}
-\tilde{f}_{e}(\tilde{\mathbf{r}}) = \pi \, abc \, 
+In a similar way, the function $\tilde{f}_{E}(\tilde{\mathbf{r}})$
+is given by
+\begin{equation}
+\tilde{f}_{E}(\tilde{\mathbf{r}}) = \pi \, abc \, 
 \int_{\lambda}^{\infty} \left( 1 
@@
 \end{equation}
-where $R(u)$ is defined by equation \ref{eq:R} and the
-parameter $\lambda$ is a constant defining the integral 
-lower limit.
-
-The parameter $\lambda$ is defined according to the
-ellipsoid type. Details about the mathematical meaning
-of this parameter are given in Appendix B.
-
-PAREI AQUI
-
+where $R(u)$ is defined by Equation \ref{eq:R} and the
+parameter $\lambda$ is defined according to the
+ellipsoid type as a function of the spatial coordinates
+ $\tilde{x}$, $\tilde{y}$, and $\tilde{z}$ (see Appendix B). 
+For readers interested in additional information about the 
+parameter $\lambda$, we recommend \citet[p.~234]{webster1904},
+\citet[p.~184]{kellogg1929} and \citet{clark1986}.
+
+The second important coordinate transformation is defined
+with respect to Equation \ref{eq:H-M-uniform}.
 By properly using the orthogonality of matrix $\mathbf{V}$ 
-(equations \ref{eq:V_triaxial_prolate} and \ref{eq:V_oblate}),
+(Eqs. \ref{eq:V_triaxial_prolate} and \ref{eq:V_oblate}),
 the magnetic field $\mathbf{H}(\mathbf{r})$ 
-(equation \ref{eq:total-H-field-M-uniform}) can be transformed
+(Eq. \ref{eq:H-M-uniform}) can be transformed
 from the main coordinate system to a local coordinate system
@@
 _{\tilde{\mathbf{K}}} \; 
-\underbrace{\mathbf{V}^{\top} \mathbf{H}_{i}}
-_{\tilde{\mathbf{H}}_{i}} \: ,
-\label{eq:total-H-field-local-system}
+\underbrace{\mathbf{V}^{\top} \mathbf{H}_{I}}
+_{\tilde{\mathbf{H}}_{I}} \: ,
+\label{eq:H-tilde}
 \end{equation}
@@
 
-In equation \ref{eq:total-H-field-local-system}, the transformed
+In Equation \ref{eq:H-tilde}, the transformed
 depolarization tensor $\tilde{\mathbf{N}}(\tilde{\mathbf{r}})$
 is calculated as a function of the original depolarization
-tensor $\mathbf{N}(\mathbf{r})$ (equation \ref{eq:total-H-field-M-uniform}).
+tensor $\mathbf{N}(\mathbf{r})$ (Eq. \ref{eq:H-M-uniform}).
 In this case, the elements of $\tilde{\mathbf{N}}(\tilde{\mathbf{r}})$
 are calculated as a function of the second derivatives of the
-function $f(\mathbf{r})$ (equation \ref{eq:f}),
+function $f(\mathbf{r})$ (Eq. \ref{eq:f}),
 which is defined in the main coordinate system.
@@
 and $\tilde{r}_{3} = \tilde{z}$ are the elements of the
-transformed vector $\tilde{\mathbf{r}}$ (equation \ref{eq:coord_transformation})
-and $\tilde{f}(\tilde{\mathbf{r}})$ is a scalar function
-obtained by transforming $f(\mathbf{r})$ (equation \ref{eq:f})
-from the main coordinate system to the respective local
-coordinate system.
-
-\subsubsection{Internal magnetic field and demagnetization}
-
-By considering $\mathbf{r}$ as a point internal to the
+transformed vector $\tilde{\mathbf{r}}$ (Eq. \ref{eq:coord_transformation})
+and $\tilde{f}(\tilde{\mathbf{r}})$ is given by Equation \ref{eq:fi-tilde}
+or \ref{eq:fe-tilde}, depending if $\tilde{\mathbf{r}}$ represents a
+point located within or without the volume $V$ of the
+ellipsoidal body.
+
+\subsection{Internal magnetic field and magnetization}
+
+By considering $\tilde{\mathbf{r}}$ as a point within the
 volume $V$ of the ellipsoid and using the Maxwell's postulate 
 about the uniformity of the magnetic field $\mathbf{H}(\mathbf{r})$ 
-inside ellipsoidal bodies, we can rewrite equation \ref{eq:total-H-field-local-system}
-as follows:
-%\begin{equation}
-%
-%\label{eq:total-Hi-local-system}
-%\end{equation}
-
-\subsubsection{External magnetic induction}
+inside ellipsoidal bodies, we can use Equation \ref{eq:H-tilde}
+for defining the resultant uniform magnetic field $\tilde{\mathbf{H}}_{I}$
+inside the ellipsoidal body as follows:
+\begin{equation}
+\tilde{\mathbf{H}}_{I} = 
+\left( \mathbf{I} - \tilde{\mathbf{N}}_{I} \, \tilde{\mathbf{K}} \right)^{-1}
+\tilde{\mathbf{H}}_{0} \: ,
+\label{eq:Hi-tilde}
+\end{equation}
+where $\mathbf{I}$ is the identity matrix and 
+$\tilde{\mathbf{N}}_{I}$ represents the
+transformed depolarization tensor evaluated within 
+the volume $V$ of the ellipsoidal body. The elements
+of $\tilde{\mathbf{N}}_{I}$ will be presented in a 
+later section.
+
+Let us pre-multiply the uniform internal field $\tilde{\mathbf{H}}_{I}$
+(Eq. \ref{eq:Hi-tilde}) by the transformed 
+susceptibility tensor $\tilde{\mathbf{K}}$ 
+(Eq. \ref{eq:H-tilde}) to obtain
+\begin{equation}
+\begin{split}
+\tilde{\mathbf{M}} 
+&= \tilde{\mathbf{K}} 
+\left( \mathbf{I} - \tilde{\mathbf{N}}_{I} \, \tilde{\mathbf{K}} \right)^{-1}
+\tilde{\mathbf{H}}_{0} \\
+&=  
+\left( \mathbf{I} - \tilde{\mathbf{K}} \, \tilde{\mathbf{N}}_{I} \right)^{-1}
+\tilde{\mathbf{K}} \, \tilde{\mathbf{H}}_{0}
+\end{split} \: ,
+\label{eq:M-tilde}
+\end{equation}
+where $\tilde{\mathbf{M}}$
+represents the transformed magnetization, as can be easily
+verified by using Eqs. \ref{eq:M-KH} and \ref{eq:H-tilde}.
+The matrix identity used for obtaining the second line of Equation 
+\ref{eq:M-tilde} is given by \citet[p. ~151]{searle1982}.
+
+Equation \ref{eq:M-tilde} can be easily generalized for the case in 
+which the ellipsoid has also a uniform remanent magnetization
+$\tilde{\mathbf{M}}_{R}$. Let us first consider that
+the uniform remanent magnetization satisfies the condition
+$\tilde{\mathbf{H}}_{A} = \tilde{\mathbf{K}}^{-1} \tilde{\mathbf{M}}_{R}$,
+where $\tilde{\mathbf{H}}_{A}$ represents a hypothetical 
+uniform ancient field. Then, if we assume that $\tilde{\mathbf{H}}_{0}$,
+in Eqs. \ref{eq:Hi-tilde} and \ref{eq:M-tilde},
+is in fact the sum of the uniform magnetic field $\tilde{\mathbf{H}}_{0}$ 
+and the hypothetical ancient field $\tilde{\mathbf{H}}_{A}$, we obtain the 
+following generalized equation
+\begin{equation}
+\tilde{\mathbf{M}} =  
+\left( \mathbf{I} - \tilde{\mathbf{K}} \, \tilde{\mathbf{N}}_{I} \right)^{-1}
+\left( \tilde{\mathbf{K}} \, \tilde{\mathbf{H}}_{0} + \tilde{\mathbf{M}}_{R} \right) \: .
+\label{eq:M-tilde-remanence}
+\end{equation}
+Equation \ref{eq:M-tilde-remanence} is consistent with that given by
+\citet[Eq. ~38]{clark1986}.
+
+\subsection{External magnetic field and total-field anomaly}
+
+The magnetic field $\Delta \tilde{\mathbf{H}}(\tilde{\mathbf{r}})$ 
+produced by an ellipsoid at external points is calculated from 
+Eqs. \ref{eq:H-tilde} and \ref{eq:M-tilde-remanence} as the difference
+between the resultant field $\tilde{\mathbf{H}}(\tilde{\mathbf{r}})$ 
+and the uniform field $\tilde{\mathbf{H}}_{0}$:
+\begin{equation}
+\Delta \tilde{\mathbf{H}}(\tilde{\mathbf{r}}) = 
+- \tilde{\mathbf{N}}(\tilde{\mathbf{r}}) \, \tilde{\mathbf{M}} \: .
+\label{eq:delta-H-tilde}
+\end{equation}
+The elements of the transformed depolarization tensor 
+$\tilde{\mathbf{N}}(\tilde{\mathbf{r}})$ used in 
+Equation \ref{eq:delta-H-tilde} will be presented in
+the later following section.
+
+The $\Delta \tilde{\mathbf{H}}(\tilde{\mathbf{r}})$ 
+can be interpreted as a uniformly magnetized body located in the
+crust while the uniform field $\tilde{\mathbf{H}}_{0}$ can
+be interpreted as the main component of the geomagnetic field
+on the study area, which is commonly assumed to be
+generated at the liquid part of the Earth's core.
+Equation \ref{eq:delta-H-tilde} gives the magnetic field
+(in \unit{A \, m^{-1}}) produced by an ellipsoid. However,
+in geophysics, the most widely used field is the magnetic 
+induction (in \unit{nT}). Fortunately, this conversion can
+be easily done by multiplying Equation \ref{eq:delta-H-tilde}
+by $k_{m}~=~10^{9}~\mu_{0}$, where $\mu_{0}$ represents the
+magnetic constant (in \unit{H \, m^{-1}}).
+
+For geophysical applications, it is preferable to
+calculate the total-field anomaly produced by the
+magnetic sources. This scalar quantity is defined 
+as follows \citep{blakely1996}:
+\begin{equation}
+\Delta \tilde{T}(\tilde{\mathbf{r}}) = \| 
+\tilde{\mathbf{B}}_{0} + \Delta \tilde{\mathbf{B}}(\tilde{\mathbf{r}}) \|
+- \| \tilde{\mathbf{B}}_{0} \| \: ,
+\label{eq:delta-T-tilde}
+\end{equation}
+where $\tilde{\mathbf{B}}_{0} = k_{m} \, \tilde{\mathbf{H}}_{0}$
+and $\Delta \tilde{\mathbf{B}}(\tilde{\mathbf{r}}) = 
+k_{m} \, \Delta \tilde{\mathbf{H}}(\tilde{\mathbf{r}})$
+(Eq. \ref{eq:delta-H-tilde}).
+In practical situations, however, 
+$\| \tilde{\mathbf{B}}_{0} \| >> \| \Delta \tilde{\mathbf{B}}(\tilde{\mathbf{r}}) \|$
+and, consequently, the following approximation is valid \citep{blakely1996}:
+\begin{equation}
+\Delta \tilde{T}(\tilde{\mathbf{r}}) \approx  
+\frac{\tilde{\mathbf{B}}_{0}^{\top} \Delta \tilde{\mathbf{B}}(\tilde{\mathbf{r}})}{\| \tilde{\mathbf{B}}_{0} \|} \: .
+\label{eq:delta-T-tilde-approx}
+\end{equation}
+
+\subsection{Transformed depolarization tensor $\tilde{\mathbf{N}}(\tilde{\mathbf{r}})$}
 
@@
 
-Let $\tilde{f}(\tilde{\mathbf{r}})$ the scalar
+Let $\tilde{f}(\tilde{\mathbf{r}})$ be the scalar
 function obtained by transforming $f(\mathbf{r})$ 
-(equation \ref{eq:f}) from the
+(Eq. \ref{eq:f}) from the
 main coordinate system to a local coordinate system.
 
-For convenience, let us rewrite equation 
+For convenience, let us rewrite Equation 
 \ref{eq:coord_transformation} as follows:
@@
 \end{equation}
-where $r_{j}$, $j = 1, 2, 3$, are the elements of the position vector
-$\mathbf{r}$ (equation \ref{eq:ellipsoid_surface}),
+where $\tilde{r}_{k}$, $k = 1, 2, 3$, are the elements of the transformed
+position vector $\tilde{\mathbf{r}}$ (Eq. \ref{eq:coord_transformation}),
+$r_{j}$, $j = 1, 2, 3$, are the elements of the position vector
+$\mathbf{r}$ (Eq. \ref{eq:ellipsoid_surface}),
 $v_{kj}$, $j = 1, 2, 3$, are the elements of the matrix
-$\mathbf{V}$ (equation \ref{eq:V_triaxial_prolate} or \ref{eq:V_oblate}),
+$\mathbf{V}$ (Eq. \ref{eq:V_triaxial_prolate} or \ref{eq:V_oblate}),
 and $c_{k}$ is a constant defined by the coordinates
-$x_{c}$, $y_{c}$, and $z_{c}$ of the centre of the ellipsoid body.
+$x_{c}$, $y_{c}$, and $z_{c}$ of the centre of the ellipsoidal body.
 
 By considering the functions $f(\mathbf{r})$ 
-(equation \ref{eq:f}) and $\tilde{f}(\tilde{\mathbf{r}})$
+(Eq. \ref{eq:f}) and $\tilde{f}(\tilde{\mathbf{r}})$
 evaluated at the same point, but on different coordinate
@@
 \end{equation*}
-which, from equation \ref{eq:r-tilde-k}, can be given by
+which, from Equation \ref{eq:r-tilde-k}, can be given by
 \begin{equation}
@@
 Now, by deriving $\frac{\partial f(\mathbf{r})}{\partial r_{j}}$
-(equation \ref{eq:df_drj}) with respect to the $i$th element 
-$r_{i}$ of the position vector $\mathbf{r}$ (equation \ref{eq:ellipsoid_surface}),
+(Eq. \ref{eq:df_drj}) with respect to the $i$th element 
+$r_{i}$ of the position vector $\mathbf{r}$ (Eq. \ref{eq:ellipsoid_surface}),
 we obtain:
@@
 {\partial \tilde{r}_{i} \, \partial \tilde{r}_{j}}$.
-From equation \ref{eq:d2f-dridrj}, we obtain
+From Equation \ref{eq:d2f-dridrj}, we obtain
 \begin{equation}
@@
 {\partial r_{i} \, \partial r_{j}}$ and
-$\mathbf{V}$ is defined by equations 
+$\mathbf{V}$ is defined by Eqs. 
 \ref{eq:V_triaxial_prolate} or
@@
 $\tilde{\mathbf{F}}(\tilde{\mathbf{r}})$ represent the Hessians
-of the functions $f(\mathbf{r})$ (equation \ref{eq:f})
+of the functions $f(\mathbf{r})$ (Eq. \ref{eq:f})
 and $\tilde{f}(\tilde{\mathbf{r}})$, respectively.
 Besides, the depolarization tensor $\mathbf{N}(\mathbf{r})$
-(equation \ref{eq:total-H-field-M-uniform}) can be 
+(Eq. \ref{eq:H-M-uniform}) can be 
 rewritten by using the matrix $\mathbf{F}(\mathbf{r})$
@@
 By properly using the orthogonality of the matrix
-$\mathbf{V}$, we may rewrite equation \ref{eq:F-V-F-tilde-VT}
+$\mathbf{V}$, we may rewrite Equation \ref{eq:F-V-F-tilde-VT}
 as follows:
@@
 \end{equation}
-Finally, by multiplying both sides of equation \ref{eq:F-tilde-VT-F-V}
-by $-\frac{1}{4 \pi}$ and using equation \ref{eq:N-F},
+Finally, by multiplying both sides of Equation \ref{eq:F-tilde-VT-F-V}
+by $-\frac{1}{4 \pi}$ and using Equation \ref{eq:N-F},
 we conclude that 
@@
 hyperboloid of two sheets) which is confocal with the ellipsoid 
-defined in equation \ref{eq:reference-triaxial-ell} can be 
+defined in Equation \ref{eq:reference-triaxial-ell} can be 
 described as follows:
@@
 points $(x, y, z)$ lying on the surface of an ellipsoid which is confocal 
-with that one defined in equation \ref{eq:reference-triaxial-ell}. 
+with that one defined in Equation \ref{eq:reference-triaxial-ell}. 
 Now, consider the problem of determining the ellipsoid which is confocal 
@@
 given $a$, $b$, $c$, $\tilde{x}$, $\tilde{y}$, and $\tilde{z}$, 
-satisfies equation \ref{eq:quadric-confocal-triaxial-ell} and
-the condition expressed by equation \ref{eq:condition-triaxial-ell}.
-By rearranging equation \ref{eq:quadric-confocal-triaxial-ell}, 
+satisfies Equation \ref{eq:quadric-confocal-triaxial-ell} and
+the condition expressed by Equation \ref{eq:condition-triaxial-ell}.
+By rearranging Equation \ref{eq:quadric-confocal-triaxial-ell}, 
 we obtain the following cubic equation for $u$:
@@
 the smaller, intermediate and largest roots of the cubic 
-equation $p(u)$ (equation \ref{eq:cubic-equation-triaxial-ell}) are 
+equation $p(u)$ (Eq. \ref{eq:cubic-equation-triaxial-ell}) are 
 located, respectively, in the intervals $[ -a^{2} \, , -b^{2} ]$,
@@
 Remember that we are interested in a $u$ satisfying 
-the condition expressed by equation \ref{eq:condition-triaxial-ell}. 
-Consequently, according to the signal analysis shown in equation
+the condition expressed by Equation \ref{eq:condition-triaxial-ell}. 
+Consequently, according to the signal analysis shown in Equation
 \ref{eq:cubic-equation-signals-triaxial-ell}, we are interested in 
-the largest root $\lambda$ of the cubic equation $p(u)$ (equation
+the largest root $\lambda$ of the cubic equation $p(u)$ (Eq.
 \ref{eq:cubic-equation-triaxial-ell}).
 
-From equation \ref{eq:cubic-equation-triaxial-ell}, we obtain a
+From Equation \ref{eq:cubic-equation-triaxial-ell}, we obtain a
 simpler one given by
@@
 \end{equation}
-Finally, from equations \ref{eq:p2-triaxial-ell}, 
+Finally, from Eqs. \ref{eq:p2-triaxial-ell}, 
 \ref{eq:p1-triaxial-ell} and \ref{eq:p0-triaxial-ell},
 the largest root $\lambda$ of $p(u)$ 
-(equation \ref{eq:cubic-equation-triaxial-ell-simpler}) can be 
+(Eq. \ref{eq:cubic-equation-triaxial-ell-simpler}) can be 
 calculated as follows \citep{weisstein2017}:
@@
 where $a > b = c > 0$. 
-In this case, the equation defining the surface of the ellipsoid
-is obtained by substituting $c = b$ in equation \ref{eq:reference-triaxial-ell}.
+In this case, the Equation defining the surface of the ellipsoid
+is obtained by substituting $c = b$ in Equation \ref{eq:reference-triaxial-ell}.
 Consequently, the equation defining the respective confocal quadric
@@
 and the new condition that must be fulfilled by the variable
-$u$ so that equation \ref{eq:quadric-confocal-prolate-ell}
+$u$ so that Equation \ref{eq:quadric-confocal-prolate-ell}
 represent an ellipsoid is
@@
 given $a$, $b$, $\tilde{x}$, $\tilde{y}$, and $\tilde{z}$, 
-satisfies equation \ref{eq:quadric-confocal-prolate-ell} and
-the condition expressed by equation \ref{eq:condition-prolate-ell}.
-From equation \ref{eq:quadric-confocal-prolate-ell}, 
+satisfies Equation \ref{eq:quadric-confocal-prolate-ell} and
+the condition expressed by Equation \ref{eq:condition-prolate-ell}.
+From Equation \ref{eq:quadric-confocal-prolate-ell}, 
 we obtain the following quadratic equation for $u$:
@@
 Therefore, according to the condition established by
-equation \ref{eq:condition-prolate-ell} and the signal analysis 
-shown in equation \ref{eq:quadratic-equation-signals-prolate-ell}, 
+Equation \ref{eq:condition-prolate-ell} and the signal analysis 
+shown in Equation \ref{eq:quadratic-equation-signals-prolate-ell}, 
 we are interested in the largest root $\lambda$ of the quadratic 
-equation $p(u)$ (equation \ref{eq:quadratic-equation-prolate-ell}).
-
-By properly manipulating equation \ref{eq:quadratic-equation-prolate-ell},
+equation $p(u)$ (Eq. \ref{eq:quadratic-equation-prolate-ell}).
+
+By properly manipulating Equation \ref{eq:quadratic-equation-prolate-ell},
 we obtain a simpler one given by
@@
 \end{equation}
-Finally, by using equations \ref{eq:p1-prolate-ell} and
+Finally, by using Eqs. \ref{eq:p1-prolate-ell} and
 \ref{eq:p0-prolate-ell}, the largest root $\lambda$ of $p(u)$ 
-(equation \ref{eq:quadratic-equation-prolate-ell-simpler}) can be 
+(Eq. \ref{eq:quadratic-equation-prolate-ell-simpler}) can be 
 easily calculated as follows:
@@
 the quadratic equation for the variable $u$, which is also 
-calculated by using equation \ref{eq:lambda-prolate-ell}.
+calculated by using Equation \ref{eq:lambda-prolate-ell}.
 
@@
 The magnetic modelling of triaxial, prolate or oblate ellipsoids 
-requires not only the parameter lambda defined by equations
+requires not only the parameter lambda defined by Eqs.
 \ref{eq:lambda-triaxial-ell} and \ref{eq:lambda-prolate-ell},
@@
 prolate or oblate ellipsoids can also be calculated by using
-equation \ref{eq:dlambda}, but with semi-axes $a > b = c$
+Equation \ref{eq:dlambda}, but with semi-axes $a > b = c$
 or $b = c > a$, respectively.

### 2017-01-25 manuscript/manuscript.tex
depolarization tensor N ast

@@
 \begin{equation}
-\mathbf{M} = \mathbf{K} \, \mathbf{H}_{I} \: ,
+\mathbf{M} = \mathbf{K} \, \mathbf{H}^{\ast} \: ,
 \label{eq:M-KH}
 \end{equation}
-where $\mathbf{H}_{I}$ is the resultant uniform magnetic field 
+where $\mathbf{H}^{\ast}$ is the resultant uniform magnetic field 
 at any point within the body and $\mathbf{K}$ is a 
@@
 \mathbf{H}(\mathbf{r}) = \mathbf{H}_{0} 
-- \mathbf{N}(\mathbf{r}) \, \mathbf{K} \, \mathbf{H}_{I} \: ,
+- \mathbf{N}(\mathbf{r}) \, \mathbf{K} \, \mathbf{H}^{\ast} \: ,
 \label{eq:H-M-uniform}
@@
 lowes1974,  peake1953, chang1961, clark1986, tejedor1995, sttraton2007}.
-It is convenient to use $\tilde{f}_{I}(\tilde{\mathbf{r}})$
-and $\tilde{f}_{E}(\tilde{\mathbf{r}})$ to define 
+It is convenient to use $\tilde{f}^{\ast}(\tilde{\mathbf{r}})$
+and $\tilde{f}^{\dagger}(\tilde{\mathbf{r}})$ to define 
 the function $\tilde{f}(\tilde{\mathbf{r}})$ evaluated, 
@@
 
-The scalar function $\tilde{f}_{I}(\tilde{\mathbf{r}})$
+The scalar function $\tilde{f}^{\ast}(\tilde{\mathbf{r}})$
 is given by
 \begin{equation}
-\tilde{f}_{I}(\tilde{\mathbf{r}}) = \pi \, abc \, 
+\tilde{f}^{\ast}(\tilde{\mathbf{r}}) = \pi \, abc \, 
 \int_{0}^{\infty} \left( 1 
@@
 postulate about uniformly magnetized ellipsoids.
-In a similar way, the function $\tilde{f}_{E}(\tilde{\mathbf{r}})$
+In a similar way, the function $\tilde{f}^{\dagger}(\tilde{\mathbf{r}})$
 is given by
 \begin{equation}
-\tilde{f}_{E}(\tilde{\mathbf{r}}) = \pi \, abc \, 
+\tilde{f}^{\dagger}(\tilde{\mathbf{r}}) = \pi \, abc \, 
 \int_{\lambda}^{\infty} \left( 1 
@@
 _{\tilde{\mathbf{K}}} \; 
-\underbrace{\mathbf{V}^{\top} \mathbf{H}_{I}}
-_{\tilde{\mathbf{H}}_{I}} \: ,
+\underbrace{\mathbf{V}^{\top} \mathbf{H}^{\ast}}
+_{\tilde{\mathbf{H}}^{\ast}} \: ,
 \label{eq:H-tilde}
@@
 inside ellipsoidal bodies, we can use Equation \ref{eq:H-tilde}
-for defining the resultant uniform magnetic field $\tilde{\mathbf{H}}_{I}$
+for defining the resultant uniform magnetic field $\tilde{\mathbf{H}}^{\ast}$
 inside the ellipsoidal body as follows:
 \begin{equation}
-\tilde{\mathbf{H}}_{I} = 
-\left( \mathbf{I} - \tilde{\mathbf{N}}_{I} \, \tilde{\mathbf{K}} \right)^{-1}
+\tilde{\mathbf{H}}^{\ast} = 
+\left( \mathbf{I} - \tilde{\mathbf{N}}^{\ast} \, \tilde{\mathbf{K}} \right)^{-1}
 \tilde{\mathbf{H}}_{0} \: ,
@@
 where $\mathbf{I}$ is the identity matrix and 
-$\tilde{\mathbf{N}}_{I}$ represents the
+$\tilde{\mathbf{N}}^{\ast}$ represents the
 transformed depolarization tensor evaluated within 
 the volume $V$ of the ellipsoidal body. The elements
-of $\tilde{\mathbf{N}}_{I}$ will be presented in a 
-later section.
-
-Let us pre-multiply the uniform internal field $\tilde{\mathbf{H}}_{I}$
+of $\tilde{\mathbf{N}}^{\ast}$ will be presented in a 
+latter section.
+
+Let us pre-multiply the uniform internal field $\tilde{\mathbf{H}}^{\ast}$
 (Eq. \ref{eq:Hi-tilde}) by the transformed 
@@
 &= \tilde{\mathbf{K}} 
-\left( \mathbf{I} - \tilde{\mathbf{N}}_{I} \, \tilde{\mathbf{K}} \right)^{-1}
+\left( \mathbf{I} - \tilde{\mathbf{N}}^{\ast} \, \tilde{\mathbf{K}} \right)^{-1}
 \tilde{\mathbf{H}}_{0} \\
 &=  
-\left( \mathbf{I} - \tilde{\mathbf{K}} \, \tilde{\mathbf{N}}_{I} \right)^{-1}
+\left( \mathbf{I} - \tilde{\mathbf{K}} \, \tilde{\mathbf{N}}^{\ast} \right)^{-1}
 \tilde{\mathbf{K}} \, \tilde{\mathbf{H}}_{0}
@@
 \tilde{\mathbf{M}} =  
-\left( \mathbf{I} - \tilde{\mathbf{K}} \, \tilde{\mathbf{N}}_{I} \right)^{-1}
+\left( \mathbf{I} - \tilde{\mathbf{K}} \, \tilde{\mathbf{N}}^{\ast} \right)^{-1}
 \left( \tilde{\mathbf{K}} \, \tilde{\mathbf{H}}_{0} + \tilde{\mathbf{M}}_{R} \right) \: .
@@
 \Delta \tilde{\mathbf{H}}(\tilde{\mathbf{r}}) = 
-- \tilde{\mathbf{N}}(\tilde{\mathbf{r}}) \, \tilde{\mathbf{M}} \: .
+- \tilde{\mathbf{N}}^{\dagger}(\tilde{\mathbf{r}}) \, \tilde{\mathbf{M}} \: .
 \label{eq:delta-H-tilde}
@@
 The elements of the transformed depolarization tensor 
-$\tilde{\mathbf{N}}(\tilde{\mathbf{r}})$ used in 
+$\tilde{\mathbf{N}}^{\dagger}(\tilde{\mathbf{r}})$ used in 
 Equation \ref{eq:delta-H-tilde} will be presented in
-the later following section.
+the following section.
 
@@
 
-\subsection{Transformed depolarization tensor $\tilde{\mathbf{N}}(\tilde{\mathbf{r}})$}
+\subsection{Transformed depolarization tensors $\tilde{\mathbf{N}}(\tilde{\mathbf{r}})$}
+
+\subsubsection{Depolarization tensor $\tilde{\mathbf{N}}^{\ast}$}
+
+The elements of the transformed depolarization tensor 
+$\tilde{\mathbf{N}}^{\ast}$ used to compute the 
+uniform magnetic field $\tilde{\mathbf{H}}^{\ast}$
+(Eq. \ref{eq:Hi-tilde}) and the magnetization $\tilde{\mathbf{M}}$ 
+(Eqs. \ref{eq:M-tilde} and \ref{eq:M-tilde-remanence})
+are calculated according to Equation \ref{eq:nij-tilde}, with 
+$\tilde{f}(\tilde{\mathbf{r}})$ given by 
+$\tilde{f}^{\ast}(\tilde{\mathbf{r}})$ (Eq. \ref{eq:fi-tilde}).
+As we have already pointed out, the  
+$\tilde{f}^{\ast}(\tilde{\mathbf{r}})$ (Eq. \ref{eq:fi-tilde}) is a
+quadratic function of the spatial coordinates $\tilde{x}$,
+$\tilde{y}$ and $\tilde{z}$. Consequently, the off-diagonal
+elements $\tilde{n}^{\ast}_{ij}(\tilde{\mathbf{r}})$, $i = 1, 2, 3$, 
+$j = 1, 2, 3$, $i \ne j$, are equal to zero. The remaining
+diagonal elements are given by \citep{stoner1945}:
+\begin{equation}
+\tilde{n}^{\ast}_{ii}(\tilde{\mathbf{r}}) = \frac{abc}{2}
+\int_{0}^{\infty} \frac{1}{\left( e_{i}^{2} 
++ u \right) R(u)} \, du \: , \quad i = 1, 2, 3 \: ,
+\label{eq:n-tilde-ast-ii}
+\end{equation}
+where $R(u)$ is defined by Equation \ref{eq:R} and
+$e_{1} = a$, $e_{2} = b$, and $e_{3} = c$. These elements
+are commonly known as \textit{demagnetizing factors}.
+Notice that, according to Equations \ref{eq:H-tilde} 
+and \ref{eq:N-tilde-VT-N-V},
+\begin{equation}
+\mathbf{N}(\mathbf{r}) = 
+\mathbf{V} \, \tilde{\mathbf{N}}^{\ast} \, 
+\mathbf{V}^{\top} \: ,
+\label{eq:N-V-N-ast-VT}
+\end{equation}
+where $\tilde{\mathbf{N}}^{\ast}$ (Eqs. \ref{eq:Hi-tilde}, 
+\ref{eq:M-tilde} and \ref{eq:M-tilde-remanence}) is a diagonal 
+matrix and $\mathbf{V}$ (Eqs. \ref{eq:V_triaxial_prolate} and
+\ref{eq:V_oblate}) is an orthogonal matrix.
+This equation shows that, for the particular case 
+in which $\mathbf{r}$ and consequently $\tilde{\mathbf{r}}$
+represent a point inside the
+volume $V$ of the ellipsoid, the elements 
+$\tilde{n}^{\ast}_{ii}(\tilde{\mathbf{r}})$ (Eq. \ref{eq:n-tilde-ast-ii})
+of $\tilde{\mathbf{N}}^{\ast}$ represent the eigenvalues while the 
+columns of $\mathbf{V}$ represent the eigenvectors of the 
+original depolarization tensor $\mathbf{N}(\mathbf{r})$.
+
+INTRODUZIR OS ELEMENTOS $\tilde{n}^{\ast}_{ii}(\tilde{\mathbf{r}})$
+PARA OS TRES TIPOS DE ELIPSOIDE
+
+\subsubsection{Depolarization tensor $\tilde{\mathbf{N}}^{\dagger}(\tilde{\mathbf{r}})$}
+
+The elements of the transformed depolarization tensor 
+$\tilde{\mathbf{N}}^{\dagger}(\tilde{\mathbf{r}})$ used to compute
+the magnetic field $\Delta \tilde{\mathbf{H}}(\tilde{\mathbf{r}})$ 
+produced by the ellipsoid (Eq. \ref{eq:delta-H-tilde}) and
+the total-field anomaly $\Delta \tilde{T}(\tilde{\mathbf{r}})$
+(Eqs. \ref{eq:delta-T-tilde} and \ref{eq:delta-T-tilde-approx}) 
+are calculated according to Equation \ref{eq:nij-tilde}, with 
+$\tilde{f}(\tilde{\mathbf{r}})$ given by $\tilde{f}^{\dagger}(\tilde{\mathbf{r}})$
+(Eq. \ref{eq:fe-tilde}).
 
@@
 main coordinate system to a local coordinate system.
-
 For convenience, let us rewrite Equation 

### 2017-01-25 code/ellipsoid_oblate_matrix.py
new codes

@@ -34,40 +34,37 @@ def ellipsoid (xp,yp,zp,xc,yc,zc,a,b,azimuth,delta,declirem,inclirem,intensity,d
     
     azimuth = np.deg2rad(azimuth)
     delta = np.deg2rad(delta)
-    angles = np.array([azimuth,delta,(np.pi/2)])
+    angles = np.array([azimuth,delta,0.])
     
-    mcon, mconT = m_convO(angles)
-    
-    declirem = np.deg2rad(declirem)
-    inclirem = np.deg2rad(inclirem)
-    
-    ln,mn,nn = lmnn_v (declirem, inclirem)
-    
-    decT = np.deg2rad(decT)
-    incT = np.deg2rad(incT)
-    
-    lt,mt,nt = lmnn_v (decT, incT)
+    V = V_e(angles)
 
-    k_int = np.array([k[0][0],k[1][0],k[2][0]])
-    k_inc = np.array([k[0][1],k[1][1],k[2][1]])
-    k_dec = np.array([k[0][2],k[1][2],k[2][2]])
+    ln, mn, nn = utils.dircos(inclirem, declirem)
     
+    lt,mt,nt = utils.dircos(incT, decT)
+
+    k_int = np.array([k[0],k[1],k[2]])
+    k_angles = np.deg2rad(np.array([k[3],k[4],k[5]]))
+
+    #isotropic case
     if k_int[0] == (k_int[1] and k_int[2]):
-        km = k_matrix(k_int,mcon)
+        km = np.diag(k_int)
+    #anisotropic case
     else:
-        km = k_matrix2(k_int,mcon)
+        k_angles[0] = k_angles[0] + np.pi
+        U = U_e(k_angles)
+        km = k_matrix(U,V,np.diag(k_int))
 
     # Earth's field and total body magnetization (including demagnetization) in the body's coordinate
-    F = F_e (intT,lt,mt,nt,mcon)
-    JN = JN_e (intensity,ln,mn,nn,mcon)
+    F = F_e (intT,lt,mt,nt,V)
+    JN = JN_e (intensity,ln,mn,nn,V)
     N1,N2 = N_desmag (axis[0],axis[1])
     JR = JR_e (km,JN,F)
     JRD = JRD_e (km,N1,N2,JR)
-    JRD_carte = (mconT).dot(JRD)
+    JRD_carte = (V).dot(JRD)
     JRD_ang = utils.vec2ang(JRD_carte)
     
     # Ellipsoid cartesian body coordinates
[…]

### 2017-01-25 code/ellipsoid_prolate_matrix.py

@@ -34,40 +34,37 @@ def ellipsoid (xp,yp,zp,xc,yc,zc,a,b,azimuth,delta,declirem,inclirem,intensity,d
     
     azimuth = np.deg2rad(azimuth)
     delta = np.deg2rad(delta)
-    angles = np.array([azimuth+np.pi,delta,(np.pi/2)])
+    angles = np.array([azimuth+np.pi,delta,0.])
     
-    mcon, mconT = m_convP(angles)
-    
-    declirem = np.deg2rad(declirem)
-    inclirem = np.deg2rad(inclirem)
-    
-    ln,mn,nn = lmnn_v (declirem, inclirem)
-    
-    decT = np.deg2rad(decT)
-    incT = np.deg2rad(incT)
-    
-    lt,mt,nt = lmnn_v (decT, incT)
+    V = V_e(angles)
 
-    k_int = np.array([k[0][0],k[1][0],k[2][0]])
-    k_inc = np.array([k[0][1],k[1][1],k[2][1]])
-    k_dec = np.array([k[0][2],k[1][2],k[2][2]])
+    ln, mn, nn = utils.dircos(inclirem, declirem)
     
+    lt,mt,nt = utils.dircos(incT, decT)
+
+    k_int = np.array([k[0],k[1],k[2]])
+    k_angles = np.deg2rad(np.array([k[3],k[4],k[5]]))
+
+    #isotropic case
     if k_int[0] == (k_int[1] and k_int[2]):
-        km = k_matrix(k_int,mcon)
+        km = np.diag(k_int)
+    #anisotropic case
     else:
-        km = k_matrix2(k_int,mcon)
+        k_angles[0] = k_angles[0]+np.pi
+        U = V_e(k_angles)
+        km = k_matrix(U,V,np.diag(k_int))
 
     # Earth's field and total body magnetization (including demagnetization) in the body's coordinate
-    F = F_e (intT,lt,mt,nt,mcon)
-    JN = JN_e (intensity,ln,mn,nn,mcon)
+    F = F_e (intT,lt,mt,nt,V)
+    JN = JN_e (intensity,ln,mn,nn,V)
     N1,N2 = N_desmag (axis[0],axis[1])
     JR = JR_e (km,JN,F)
     JRD = JRD_e (km,N1,N2,JR)
-    JRD_carte = (mconT).dot(JRD)
+    JRD_carte = (V).dot(JRD)
     JRD_ang = utils.vec2ang(JRD_carte)
     
[…]

### 2017-01-25 code/ellipsoid_triaxial_func.py

@@ -36,30 +36,26 @@ def ellipsoid (xp,yp,zp,xc,yc,zc,a,b,c,azimuth,delta,gamma,declirem,inclirem,int
     delta = np.deg2rad(delta)
     angles = np.array([azimuth+np.pi,delta,gamma])
     
-    mcon, mconT = m_convT(angles)
-    
-    declirem = np.deg2rad(declirem)
-    inclirem = np.deg2rad(inclirem)
-    
-    ln,mn,nn = lmnn_v (declirem, inclirem)
-    
-    decT = np.deg2rad(decT)
-    incT = np.deg2rad(incT)
-    
-    lt,mt,nt = lmnn_v (decT, incT)
+    V = V_e(angles)
 
-    k_int = np.array([k[0][0],k[1][0],k[2][0]])
-    k_inc = np.deg2rad(np.array([k[0][1],k[1][1],k[2][1]]))
-    k_dec = np.deg2rad(np.array([k[0][2],k[1][2],k[2][2]]))
+    ln, mn, nn = utils.dircos(inclirem, declirem)
     
+    lt,mt,nt = utils.dircos(incT, decT)
+
+    k_int = np.array([k[0],k[1],k[2]])
+    k_angles = np.deg2rad(np.array([k[3],k[4],k[5]]))
+
+    #isotropic case
     if k_int[0] == (k_int[1] and k_int[2]):
-        km = k_matrix(k_int,mcon)
+        km = np.diag(k_int)
+    #anisotropic case
     else:
-        km = k_matrix2(k_int,k_dec,k_inc,mcon)
+        k_angles[0] = k_angles[0]+np.pi
+        U = V_e(k_angles)
+        km = k_matrix(U,V,np.diag(k_int))
     
-    print km
     # Ellipsoid cartesian body coordinates
-    x1,x2,x3 = x_e (xp,yp,zp,center,mcon)
+    x1,x2,x3 = x_e (xp,yp,zp,center,V)
     
     # Largest real root of the cubic equation (Lambda)
     lamb,teta,q,p,p2,p1,p0 = lamb_T(axis,x1,x2,x3)
@@ -74,31 +70,30 @@ def ellipsoid (xp,yp,zp,xc,yc,zc,a,b,c,azimuth,delta,gamma,declirem,inclirem,int
     A, B, C = potential_integrals(axis,k,theta_l,F,E)
     
     # Earth's field and total body magnetization (including demagnetization) in the body's coordinate
[…]

### 2017-01-26 manuscript/manuscript.tex
new codes
demagnetizing factors for all ellipsoids

--- 2017-01-24 manuscript/manuscript.tex
@@
 induction developed by \citet{poisson1824}, 
-\citet{maxwell1873} affirmed that, if $V$ is the 
+\citet{maxwell1873} affirmed that, if $U$ is the 
 gravitational potential produced by any body 
 with uniform density $\rho$ and arbitrary shape at 
-a point $(x, y, z)$, then $-\frac{\partial V}{\partial x}$
+a point $(x, y, z)$, then $-\frac{\partial U}{\partial x}$
 is the magnetic scalar potential produced 
@@
 also be uniform and parallel the magnetization, which
-results that the gravitational potential $V$ at points
+results that the gravitational potential $U$ at points
 within the body must be a quadratic function of the
@@
 \ref{eq:coord_transformation}) of a point referred to the main 
-coordinate system is defined as follows \citep{sttraton2007}:
-\begin{equation}
-\mathbf{H}(\mathbf{r}) = \mathbf{H}_{0} - \nabla \phi(\mathbf{r}) \: ,
+coordinate system is defined as follows \citep{sharma1966, 
+eskola1980, reitz1992, sttraton2007}:
+\begin{equation}
+\mathbf{H}(\mathbf{r}) = \mathbf{H}_{0} - \nabla V(\mathbf{r}) \: ,
 \label{eq:H}
@@
 where the second term is the negative gradient of 
-the magnetic scalar potential $\phi(\mathbf{r})$ given by:
-\begin{equation}
-\phi(\mathbf{r}) = -\frac{1}{4\pi} \iiint_{V} 
+the magnetic scalar potential $V(\mathbf{r})$ given by:
+\begin{equation}
+V(\mathbf{r}) = -\frac{1}{4\pi} \iiint_{\vartheta} 
 \mathbf{M}(\mathbf{r}^{\prime})^{\top} 
@@
 x^{\prime} & y^{\prime} & z^{\prime} \end{array} ]^{\top}$
-is the position vector of a point located within the volume $V$, 
+is the position vector of a point located within the volume $\vartheta$, 
 the integral is conducted over the variables 
 $x^{\prime}$, $y^{\prime}$ and, $z^{\prime}$ representing
-the coordinates of a point located within the volume $V$
+the coordinates of a point located within the volume $\vartheta$
 of the ellipsoid, $\| \cdot \|$ denotes the Euclidean norm and 
@@
 \begin{equation}
-\mathbf{M} = \mathbf{K} \, \mathbf{H}_{I} \: ,
+\mathbf{M} = \mathbf{K} \, \mathbf{H}^{\dagger} \: ,
 \label{eq:M-KH}
 \end{equation}
-where $\mathbf{H}_{I}$ is the resultant uniform magnetic field 
+where $\mathbf{H}^{\dagger}$ is the resultant uniform magnetic field 
 at any point within the body and $\mathbf{K}$ is a 
@@
 \mathbf{H}(\mathbf{r}) = \mathbf{H}_{0} 
-- \mathbf{N}(\mathbf{r}) \, \mathbf{K} \, \mathbf{H}_{I} \: ,
+- \mathbf{N}(\mathbf{r}) \, \mathbf{K} \, \mathbf{H}^{\dagger} \: ,
 \label{eq:H-M-uniform}
@@
 \begin{equation}
-f(\mathbf{r}) = \iiint_{V} 
+f(\mathbf{r}) = \iiint_{\vartheta} 
 \frac{1}{\| \mathbf{r} - \mathbf{r}^{\prime} \|}
@@
 to the gravitational potential that would be produced by the 
-ellipsoidal body with volume $V$ if it had a uniform density 
+ellipsoidal body with volume $\vartheta$ if it had a uniform density 
 equal to the inverse of the gravitational constant.
@@
 finite whether $\mathbf{r}$ is a point within or without
-the volume $V$ \citep{peirce1902, webster1904}.
+the volume $\vartheta$ \citep{peirce1902, webster1904}.
 The matrix $\mathbf{N}(\mathbf{r})$ (Eq. \ref{eq:H-M-uniform})
@@
 (Eq. \ref{eq:H-M-uniform}) at points located
-both within and without the volume $V$ of the ellipsoidal
+both within and without the volume $\vartheta$ of the ellipsoidal
 body. However, the mathematical developments are conveniently 
@@
 lowes1974,  peake1953, chang1961, clark1986, tejedor1995, sttraton2007}.
-It is convenient to use $\tilde{f}_{I}(\tilde{\mathbf{r}})$
-and $\tilde{f}_{E}(\tilde{\mathbf{r}})$ to define 
+It is convenient to use $\tilde{f}^{\dagger}(\tilde{\mathbf{r}})$
+and $\tilde{f}^{\ddagger}(\tilde{\mathbf{r}})$ to define 
 the function $\tilde{f}(\tilde{\mathbf{r}})$ evaluated, 
 respectively, at points 
-$\tilde{\mathbf{r}}$ inside and outside the volume $V$ of the
+$\tilde{\mathbf{r}}$ inside and outside the volume $\vartheta$ of the
 ellipsoidal body.
 
-The scalar function $\tilde{f}_{I}(\tilde{\mathbf{r}})$
+The scalar function $\tilde{f}^{\dagger}(\tilde{\mathbf{r}})$
 is given by
 \begin{equation}
-\tilde{f}_{I}(\tilde{\mathbf{r}}) = \pi \, abc \, 
+\tilde{f}^{\dagger}(\tilde{\mathbf{r}}) = \pi \, abc \, 
 \int_{0}^{\infty} \left( 1 
@@
 that would be produced by the ellipsoidal body at
-points located within its volume $V$ if it
+points located within its volume $\vartheta$ if it
 had a uniform density equal to the inverse of the
@@
 postulate about uniformly magnetized ellipsoids.
-In a similar way, the function $\tilde{f}_{E}(\tilde{\mathbf{r}})$
+In a similar way, the function $\tilde{f}^{\ddagger}(\tilde{\mathbf{r}})$
 is given by
 \begin{equation}
-\tilde{f}_{E}(\tilde{\mathbf{r}}) = \pi \, abc \, 
+\tilde{f}^{\ddagger}(\tilde{\mathbf{r}}) = \pi \, abc \, 
 \int_{\lambda}^{\infty} \left( 1 
@@
 _{\tilde{\mathbf{K}}} \; 
-\underbrace{\mathbf{V}^{\top} \mathbf{H}_{I}}
-_{\tilde{\mathbf{H}}_{I}} \: ,
+\underbrace{\mathbf{V}^{\top} \mathbf{H}^{\dagger}}
+_{\tilde{\mathbf{H}}^{\dagger}} \: ,
 \label{eq:H-tilde}
@@
 or \ref{eq:fe-tilde}, depending if $\tilde{\mathbf{r}}$ represents a
-point located within or without the volume $V$ of the
+point located within or without the volume $\vartheta$ of the
 ellipsoidal body.
@@
 By considering $\tilde{\mathbf{r}}$ as a point within the
-volume $V$ of the ellipsoid and using the Maxwell's postulate 
+volume $\vartheta$ of the ellipsoid and using the Maxwell's postulate 
 about the uniformity of the magnetic field $\mathbf{H}(\mathbf{r})$ 
 inside ellipsoidal bodies, we can use Equation \ref{eq:H-tilde}
-for defining the resultant uniform magnetic field $\tilde{\mathbf{H}}_{I}$
+for defining the resultant uniform magnetic field $\tilde{\mathbf{H}}^{\dagger}$
 inside the ellipsoidal body as follows:
 \begin{equation}
-\tilde{\mathbf{H}}_{I} = 
-\left( \mathbf{I} - \tilde{\mathbf{N}}_{I} \, \tilde{\mathbf{K}} \right)^{-1}
+\tilde{\mathbf{H}}^{\dagger} = 
+\left( \mathbf{I} - \tilde{\mathbf{N}}^{\dagger} \, \tilde{\mathbf{K}} \right)^{-1}
 \tilde{\mathbf{H}}_{0} \: ,
@@
 where $\mathbf{I}$ is the identity matrix and 
-$\tilde{\mathbf{N}}_{I}$ represents the
+$\tilde{\mathbf{N}}^{\dagger}$ represents the
 transformed depolarization tensor evaluated within 
-the volume $V$ of the ellipsoidal body. The elements
-of $\tilde{\mathbf{N}}_{I}$ will be presented in a 
-later section.
-
-Let us pre-multiply the uniform internal field $\tilde{\mathbf{H}}_{I}$
+the volume $\vartheta$ of the ellipsoidal body. The elements
+of $\tilde{\mathbf{N}}^{\dagger}$ will be presented in a 
+latter section.
+
+Let us pre-multiply the uniform internal field $\tilde{\mathbf{H}}^{\dagger}$
 (Eq. \ref{eq:Hi-tilde}) by the transformed 
@@
 &= \tilde{\mathbf{K}} 
-\left( \mathbf{I} - \tilde{\mathbf{N}}_{I} \, \tilde{\mathbf{K}} \right)^{-1}
+\left( \mathbf{I} - \tilde{\mathbf{N}}^{\dagger} \, \tilde{\mathbf{K}} \right)^{-1}
 \tilde{\mathbf{H}}_{0} \\
 &=  
-\left( \mathbf{I} - \tilde{\mathbf{K}} \, \tilde{\mathbf{N}}_{I} \right)^{-1}
+\left( \mathbf{I} - \tilde{\mathbf{K}} \, \tilde{\mathbf{N}}^{\dagger} \right)^{-1}
 \tilde{\mathbf{K}} \, \tilde{\mathbf{H}}_{0}
@@
 \tilde{\mathbf{M}} =  
-\left( \mathbf{I} - \tilde{\mathbf{K}} \, \tilde{\mathbf{N}}_{I} \right)^{-1}
+\left( \mathbf{I} - \tilde{\mathbf{K}} \, \tilde{\mathbf{N}}^{\dagger} \right)^{-1}
 \left( \tilde{\mathbf{K}} \, \tilde{\mathbf{H}}_{0} + \tilde{\mathbf{M}}_{R} \right) \: .
@@
 \Delta \tilde{\mathbf{H}}(\tilde{\mathbf{r}}) = 
-- \tilde{\mathbf{N}}(\tilde{\mathbf{r}}) \, \tilde{\mathbf{M}} \: .
+- \tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}}) \, \tilde{\mathbf{M}} \: .
 \label{eq:delta-H-tilde}
@@
 The elements of the transformed depolarization tensor 
-$\tilde{\mathbf{N}}(\tilde{\mathbf{r}})$ used in 
+$\tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}})$ used in 
 Equation \ref{eq:delta-H-tilde} will be presented in
-the later following section.
+the following section.
 
@@
 
-\subsection{Transformed depolarization tensor $\tilde{\mathbf{N}}(\tilde{\mathbf{r}})$}
+\subsection{Transformed depolarization tensors $\tilde{\mathbf{N}}(\tilde{\mathbf{r}})$}
+
+\subsubsection{Depolarization tensor $\tilde{\mathbf{N}}^{\dagger}$}
+
+The elements of the transformed depolarization tensor 
+$\tilde{\mathbf{N}}^{\dagger}$ used to compute the 
+uniform magnetic field $\tilde{\mathbf{H}}^{\dagger}$
+(Eq. \ref{eq:Hi-tilde}) and the magnetization $\tilde{\mathbf{M}}$ 
+(Eqs. \ref{eq:M-tilde} and \ref{eq:M-tilde-remanence})
+are calculated according to Equation \ref{eq:nij-tilde}, with 
+$\tilde{f}(\tilde{\mathbf{r}})$ given by 
+$\tilde{f}^{\dagger}(\tilde{\mathbf{r}})$ (Eq. \ref{eq:fi-tilde}).
+As we have already pointed out, the  
+$\tilde{f}^{\dagger}(\tilde{\mathbf{r}})$ (Eq. \ref{eq:fi-tilde}) is a
+quadratic function of the spatial coordinates $\tilde{x}$,
+$\tilde{y}$ and $\tilde{z}$. Consequently, the 
+elements $\tilde{n}^{\dagger}_{ij}$, $i = 1, 2, 3$, 
+$j = 1, 2, 3$, of $\tilde{\mathbf{N}}^{\dagger}$ 
+do not depend on the transformed position
+vector $\tilde{\mathbf{r}}$ (equation \ref{eq:coord_transformation}). 
+Besides, the off-diagonal elements, $i \ne j$, are zero and
+the diagonal elements are given by \citep{stoner1945}:
+\begin{equation}
+\tilde{n}^{\dagger}_{ii} = \frac{abc}{2}
+\int_{0}^{\infty} \frac{1}{\left( e_{i}^{2} 
++ u \right) R(u)} \, du \: , \quad i = 1, 2, 3 \: ,
+\label{eq:n-tilde-dagger-ii}
+\end{equation}
+where $R(u)$ is defined by Equation \ref{eq:R} and
+$e_{1} = a$, $e_{2} = b$, and $e_{3} = c$. These elements 
+are commonly known as \textit{demagnetizing factors}
+and are defined according to the ellipsoid type.
+Notice that, according to Equations \ref{eq:H-tilde} 
+and \ref{eq:N-tilde-VT-N-V},
+\begin{equation}
+\mathbf{N}(\mathbf{r}) = 
+\mathbf{V} \, \tilde{\mathbf{N}}^{\dagger} \, 
+\mathbf{V}^{\top} \: ,
+\label{eq:N-V-N-dagger-VT}
+\end{equation}
+where $\tilde{\mathbf{N}}^{\dagger}$ (Eqs. \ref{eq:Hi-tilde}, 
+\ref{eq:M-tilde} and \ref{eq:M-tilde-remanence}) is a diagonal 
+matrix and $\mathbf{V}$ (Eqs. \ref{eq:V_triaxial_prolate} and
+\ref{eq:V_oblate}) is an orthogonal matrix.
+This equation shows that, for the particular case 
+in which $\mathbf{r}$ and consequently $\tilde{\mathbf{r}}$
+represent a point inside the
+volume $\vartheta$ of the ellipsoid, the elements 
+$\tilde{n}^{\dagger}_{ii}$ (Eq. \ref{eq:n-tilde-dagger-ii})
+of $\tilde{\mathbf{N}}^{\dagger}$ represent the eigenvalues while the 
+columns of $\mathbf{V}$ represent the eigenvectors of the 
+original depolarization tensor $\mathbf{N}(\mathbf{r})$.
+
+\subparagraph*{Triaxial ellipsoids}
+
+For triaxial ellipsoids (e.g., $a > b > c$), the demagnetization
+factors are given by:
+\begin{equation}
+\tilde{n}^{\dagger}_{11} = \frac{abc}
+{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
+\left( a^{2} - b^{2} \right)} 
+\left[ F(\kappa, \phi) - E(\kappa, \phi) \right] \: ,
+\label{eq:n-tilde-dagger-11-triaxial}
+\end{equation}
+\begin{equation}
+\tilde{n}^{\dagger}_{22} = 
+-\frac{abc}
+{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
+\left( a^{2} - b^{2} \right)} 
+\left[ F(\kappa, \phi) - E(\kappa, \phi) \right] + 
+\frac{abc}
+{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
+\left( b^{2} - c^{2} \right)} E(\kappa, \phi)
+- \frac{c^{2}}{b^{2} - c^{2}}
+\label{eq:n-tilde-dagger-22-triaxial}
+\end{equation}
+and
+\begin{equation}
+\tilde{n}^{\dagger}_{33} = 
+-\frac{abc}
+{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
+\left( b^{2} - c^{2} \right)} E(\kappa, \phi) +
+\frac{b^{2}}{b^{2} - c^{2}} \: ,
+\label{eq:n-tilde-dagger-33-triaxial}
+\end{equation}
+where $\kappa = \left[ \left( a^{2} - b^{2} \right) / 
+\left( a^{2} - c^{2} \right) \right]^{\frac{1}{2}}$,
+$\cos \phi = c/a$,
+\begin{equation}
+F(\kappa, \phi) = 
+\int^{\phi}_{0} 
+\frac{1}{\left( 1 - \kappa^{2} \sin^{2} \psi \right)^{\frac{1}{2}}}
+d\psi \: ,
+\label{eq:F-kappa-phi}
+\end{equation}
+and
+\begin{equation}
+E(\kappa, \phi) = 
+\int^{\phi}_{0} 
+\left( 1 - \kappa^{2} \sin^{2} \psi \right)^{\frac{1}{2}}
+d\psi \: .
+\label{eq:E-kappa-phi}
+\end{equation}
+The functions $F(\kappa, \phi)$ (Eq. \ref{eq:F-kappa-phi}) and 
+$E(\kappa, \phi)$ (Eq. \ref{eq:E-kappa-phi}) are
+called Legendre's normal elliptic integrals of the first and 
+second kind, respectivelly. \citet{stoner1945} presented a 
+detailed deduction of the demagnetization factors $\tilde{n}^{\dagger}_{11}$
+(Eq. \ref{eq:n-tilde-dagger-11-triaxial}), $\tilde{n}^{\dagger}_{22}$
+(Eq. \ref{eq:n-tilde-dagger-22-triaxial}) and $\tilde{n}^{\dagger}_{33}$
+(Eq. \ref{eq:n-tilde-dagger-33-triaxial}). \citet{clark1986} presented similar
+formulas, but without any proof.
+
+\subparagraph*{Prolate ellipsoids}
+
+For prolate ellipsoids (e.g., $a > b = c$), the demagnetization
+factors are given by
+\begin{equation}
+\tilde{n}^{\dagger}_{11} = \frac{1}{m^{2} - 1}
+\left\lbrace \frac{m}{\left( m^{2} - 1 \right)^{\frac{1}{2}}}
+\ln \left[ m + \left( m^{2} - 1 \right)^{\frac{1}{2}} \right]
+- 1 \right\rbrace
+\label{eq:n-tilde-dagger-11-prolate}
+\end{equation}
+and
+\begin{equation}
+\tilde{n}^{\dagger}_{22} = \frac{1}{2} \left(1 - \tilde{n}^{\dagger}_{11} \right) \: ,
+\label{eq:n-tilde-dagger-22-prolate}
+\end{equation}
+where $\tilde{n}^{\dagger}_{33} = \tilde{n}^{\dagger}_{22}$, 
+which uses the $\tilde{n}^{\dagger}_{11}$ defined in 
+Equation \ref{eq:n-tilde-dagger-11-prolate}, and $m = a/b$.
+The detailed deduction of the demagnetization factors 
+$\tilde{n}^{\dagger}_{11}$ (Eq. \ref{eq:n-tilde-dagger-11-prolate}) 
+and $\tilde{n}^{\dagger}_{22}$ (Eq. \ref{eq:n-tilde-dagger-22-prolate})
+can be found in \citet{stoner1945}. These formulas were posteriorly 
+presented by \citet{emerson1985}, but without any mathematical proof.
+
+\subparagraph*{Oblate ellipsoids}
+
+For oblate ellipsoids (e.g., $a < b = c$), the demagnetization
+factors are given by
+\begin{equation}
+\tilde{n}^{\dagger}_{11} = 
+\frac{1}{1 - m^{2}} \left[
+1 - \frac{m}{\left( 1 - m^{2} \right)^{\frac{1}{2}}} \cos^{-1}m
+\right] \: ,
+\label{eq:n-tilde-dagger-11-oblate}
+\end{equation}
+where $\tilde{n}^{\dagger}_{22}$ and $\tilde{n}^{\dagger}_{33}$ 
+are calculated according to
+\ref{eq:n-tilde-dagger-22-prolate}, but with $\tilde{n}^{\dagger}_{11}$ 
+defined in Equation \ref{eq:n-tilde-dagger-11-oblate}), 
+and $m = a/b$.
+The detailed deduction of these demagnetization factors 
+can be found in \citet{stoner1945}. These formulas can also be found
+in \citet{emerson1985}, but without any mathematical proof.
+The only difference, however, is that \citet{emerson1985} replaced
+the term $\cos^{-1}$ by a term $\tan^{-1}$, according to 
+the trigonometric identity 
+$\tan^{-1}x = \cos^{-1}(1/\sqrt{x^{2} + 1})$, $x > 0$.
+
+\subsubsection{Depolarization tensor $\tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}})$}
+
+The elements of the transformed depolarization tensor 
+$\tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}})$ used to compute
+the magnetic field $\Delta \tilde{\mathbf{H}}(\tilde{\mathbf{r}})$ 
+produced by the ellipsoid (Eq. \ref{eq:delta-H-tilde}) and
+the total-field anomaly $\Delta \tilde{T}(\tilde{\mathbf{r}})$
+(Eqs. \ref{eq:delta-T-tilde} and \ref{eq:delta-T-tilde-approx}) 
+are calculated according to Equation \ref{eq:nij-tilde}, with 
+$\tilde{f}(\tilde{\mathbf{r}})$ given by $\tilde{f}^{\ddagger}(\tilde{\mathbf{r}})$
+(Eq. \ref{eq:fe-tilde}).
 

### 2017-01-26 manuscript/manuscript.tex
depolarization tensor N dagger for all ellipsoids

@@
 For triaxial ellipsoids (e.g., $a > b > c$), the demagnetization
-factors are given by:
+factors obtained by solving Equation \ref{eq:n-tilde-dagger-ii} 
+are given by:
 \begin{equation}
@@
 For prolate ellipsoids (e.g., $a > b = c$), the demagnetization
-factors are given by
+factors obtained by solving Equation \ref{eq:n-tilde-dagger-ii} 
+are given by:
 \begin{equation}
@@
 and $\tilde{n}^{\dagger}_{22}$ (Eq. \ref{eq:n-tilde-dagger-22-prolate})
-can be found in \citet{stoner1945}. These formulas were posteriorly 
+can be found, for example, in \citet{stoner1945}. 
+These formulas were posteriorly 
 presented by \citet{emerson1985}, but without any mathematical proof.
@@
 For oblate ellipsoids (e.g., $a < b = c$), the demagnetization
-factors are given by
+factors obtained by solving Equation \ref{eq:n-tilde-dagger-ii} 
+are given by:
 \begin{equation}
@@
 where $\tilde{n}^{\dagger}_{22}$ and $\tilde{n}^{\dagger}_{33}$ 
-are calculated according to
+are calculated according to Equation
 \ref{eq:n-tilde-dagger-22-prolate}, but with $\tilde{n}^{\dagger}_{11}$ 
-defined in Equation \ref{eq:n-tilde-dagger-11-oblate}), 
+defined in Equation \ref{eq:n-tilde-dagger-11-oblate}, 
 and $m = a/b$.
 The detailed deduction of these demagnetization factors 
-can be found in \citet{stoner1945}. These formulas can also be found
+can be found, for example, in \citet{stoner1945}. These formulas can also be found
 in \citet{emerson1985}, but without any mathematical proof.
@@
 
-The elements of the transformed depolarization tensor 
+The elements $\tilde{n}^{\ddagger}_{ij}(\tilde{\mathbf{r}})$,
+$i = 1, 2, 3$, $j = 1, 2, 3$, of the transformed depolarization tensor 
 $\tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}})$ used to compute
 the magnetic field $\Delta \tilde{\mathbf{H}}(\tilde{\mathbf{r}})$ 
-produced by the ellipsoid (Eq. \ref{eq:delta-H-tilde}) and
+(Eq. \ref{eq:delta-H-tilde}) and
 the total-field anomaly $\Delta \tilde{T}(\tilde{\mathbf{r}})$
@@
 In the case of oblate ellipsoids, the procedure for determining
-the parameter $\lambda$ is very similar to that one for prolate
+the parameter $\lambda$ is very similar to this one for prolate
 ellipsoids.
@@
 prolate or oblate ellipsoids can also be calculated by using
-Equation \ref{eq:dlambda}, but with semi-axes $a > b = c$
-or $b = c > a$, respectively.
+Equation \ref{eq:dlambda} for the particular case in
+with $b = c$.
 

### 2017-01-27 manuscript/manuscript.tex
elements of the N ddagger depolarizatin tensor
preliminary version of introduction

@@
 
-TEXT
+Based on the mathematical theory of the magnetic 
+induction developed by \citet{poisson1824}, 
+\citet{maxwell1873} affirmed that, if $U$ is the 
+gravitational potential produced by any body 
+with uniform density $\rho$ and arbitrary shape at 
+a point $(x, y, z)$, then $-\frac{\partial U}{\partial x}$
+is the magnetic scalar potential produced 
+at the same point by the same body 
+if it has a uniform magnetization oriented along $x$ 
+with intensity $\rho$.
+\citet{maxwell1873} generalized this idea as a way
+of determining the magnetic scalar potential produced
+by any body uniformly magnetized in a given direction.
+By presuming that this uniform magnetization is due to
+induction, he postulated that the resulting magnetic
+field (intensity) at all points within the body must
+also be uniform and parallel to the magnetization.
+As a consequence, the gravitational potential 
+$U$ at points within the body must be a quadratic 
+function of the spatial coordinates.
+Apparently, \citet{maxwell1873} was the first one to
+postulate that ellipsoids are the only finite bodies 
+having a gravitational potential which satisfies this 
+property and hence can be uniformly magnetized 
+in the presence of a uniform magnetic field.
+
+This property can be extended to other bodies
+whose shape derives from an ellipsoid 
+(e.g., spheres, elliptic cylinders), however all the
+remaining non-ellipsoidal bodies cannot be
+uniformly magnetized in the presence of a uniform
+inducing field \citep{jahren1963, schlomann1965, clark1999}.
+
+Self-demagnetization demagnetization gives rise to shape 
+anisotropy.
+
+Self-demagnetization is a function of the shape of 
+the body.
+
+The self-demagnetization contributes to decrease the
+magnitude of the magnetization along the shortest 
+dimensions of a body.
+
+Ellipsoids are the only bodies which enable an
+analytical computation of its self-demagnetization.
+
+Ellipsoids can assume a wide range of shapes and
+therefore can be used to represent different geological
+bodies.
+
+It is well-known by that the self-demagnetization can 
+be neglected if the body has a susceptibility lower 
+than 0.1 SI \citep{austin2014, clark2014, clark1986, 
+emerson1985, eskola1980, guo1998, guo2001, purss2005,
+hillan2013}.
+
+However, neglecting the self-demagnetization in
+geological bodies with high susceptibilities (> 0.1 SI) 
+may strongly mislead the results obtained from
+magnetic methods.
+
+\citet{farrar1979} demonstrated the importance of the
+ellipsoidal model in taking into account the 
+self-demagnetization and determining reliable 
+drilling directions on the Tennant Creek field, 
+Australia.
+
+Posteriorly, \citet{hoschke1991} also showed how the
+ellipsoidal model proved to be highly successful in
+locating and defining ironstone bodies in the
+Tennant Creek field.
+
+\citet{clark2000} provides a good discussion about the
+influence of the self-demagnetization in magnetic
+interpretation of the Osborne copper-gold deposit, 
+Australia. This deposit is hosted by ironstone 
+bodies that have very high susceptibility.
+According to \citet{clark2000}, neglecting the effects 
+of self-demagnetisation led errors of $\approx 55^{\circ}$
+in the interpreted dip.
+
+Based on magnetic modelling and rock property 
+measurements, \citet{austin2014} showed that,
+contrary to previous interpretations, the magnetization
+of the Candelaria iron oxide copper-gold deposit, 
+Chile, is not dominated by the induced component.
+Rather, the deposit has a relatively weak remanent 
+magnetization and is strongly affected by 
+self-demagnetization.
+
+These examples show the practical importance of
+self-demagnetization for the correct interpretation
+of magnetic data produced by geological bodies having
+high susceptibilities.
+
+These examples also show the importance of the ellipsoidal
+model in producing trustworthy geological models of orebodies,
+which may save significant cost associated with drilling.
+
+%The ellipsoidal model ability in analytically
+%incorporating the self-demagnetization...
+%FALAR DA APLICACAO DIDATICA
+
+%Apesar da grande aplicabilidade do modelo elipsoidal 
+%na geofísica, apenas alguns softwares proprietários 
+%possuem sua implementação. Neste sentido, este trabalho 
+%tem a finalidade de disponibilizar uma ferramenta de 
+%código aberto, que poderá ser utilizada livremente 
+%por toda a comunidade geofísica. 
+%VER COMO AQUELE CARA DA ISOSTASIA ESCREVEU
 
@@
 prolate ellipsoids (i.e., $a > b = c$) is calculated according
-to Equation \ref{eq:V_triaxial_prolate} by using Equations
+to Eq. \ref{eq:V_triaxial_prolate} by using Eqs.
 \ref{eq:v1_triaxial_prolate}, \ref{eq:v2_triaxial_prolate}, and
@@
 by the first, second, and third columns of the matrix 
-$\mathbf{V}$ given by Equation \ref{eq:V_triaxial_prolate},
+$\mathbf{V}$ given by Eq. \ref{eq:V_triaxial_prolate},
 in the case of a triaxial or prolate ellipsoid, or the
-matrix $\mathbf{V}$ given by Equation \ref{eq:V_oblate},
+matrix $\mathbf{V}$ given by Eq. \ref{eq:V_oblate},
 in the case of an oblate ellipsoid.
@@
 $\mathbf{r}$ and $\mathbf{r}_{c}$
-are defined in Equation \ref{eq:ellipsoid_surface} and the matrix $\mathbf{V}$
+are defined in Eq. \ref{eq:ellipsoid_surface} and the matrix $\mathbf{V}$
 is defined according to Eqs. \ref{eq:V_triaxial_prolate} or
@@
 
-Based on the mathematical theory of the magnetic 
-induction developed by \citet{poisson1824}, 
-\citet{maxwell1873} affirmed that, if $U$ is the 
-gravitational potential produced by any body 
-with uniform density $\rho$ and arbitrary shape at 
-a point $(x, y, z)$, then $-\frac{\partial U}{\partial x}$
-is the magnetic scalar potential produced 
-at the same point by the same body 
-if it has a uniform magnetization oriented along $x$ 
-with intensity $\rho$.
-\citet{maxwell1873} generalized this idea as a way
-of determining the magnetic scalar potential produced
-by any body uniformly magnetized in a given direction.
-By presuming that this uniform magnetization is due to
-induction, he postulated that the resulting magnetic
-field (intensity) at all points within the body must
-also be uniform and parallel the magnetization, which
-results that the gravitational potential $U$ at points
-within the body must be a quadratic function of the
-spatial coordinates.
-Apparently, \citet{maxwell1873} was the first one to
-affirm that the only finite bodies having a gravitational
-potential with this property and that, as a consequence,
-can be uniformly magnetized in the presence of a uniform and 
-static magnetic field are the ones bounded by surfaces 
-of second degree, which are ellipsoids.
-
 Consider a magnetized ellipsoid immersed in
@@
 (in $\unit{Am^{-1}}$).
-Equation \ref{eq:phi-potential} is valid anywhere, 
+Eq. \ref{eq:phi-potential} is valid anywhere, 
 independently if the position vector $\mathbf{r}$ represents
@@
 \end{equation}
-where $R(u)$ is defined by Equation \ref{eq:R} and the
+where $R(u)$ is defined by Eq. \ref{eq:R} and the
 parameter $\lambda$ is defined according to the
@@
 The second important coordinate transformation is defined
-with respect to Equation \ref{eq:H-M-uniform}.
+with respect to Eq. \ref{eq:H-M-uniform}.
 By properly using the orthogonality of matrix $\mathbf{V}$ 
@@
 
-In Equation \ref{eq:H-tilde}, the transformed
+In Eq. \ref{eq:H-tilde}, the transformed
 depolarization tensor $\tilde{\mathbf{N}}(\tilde{\mathbf{r}})$
@@
 transformed vector $\tilde{\mathbf{r}}$ (Eq. \ref{eq:coord_transformation})
-and $\tilde{f}(\tilde{\mathbf{r}})$ is given by Equation \ref{eq:fi-tilde}
+and $\tilde{f}(\tilde{\mathbf{r}})$ is given by Eq. \ref{eq:fi-tilde}
 or \ref{eq:fe-tilde}, depending if $\tilde{\mathbf{r}}$ represents a
@@
 about the uniformity of the magnetic field $\mathbf{H}(\mathbf{r})$ 
-inside ellipsoidal bodies, we can use Equation \ref{eq:H-tilde}
+inside ellipsoidal bodies, we can use Eq. \ref{eq:H-tilde}
 for defining the resultant uniform magnetic field $\tilde{\mathbf{H}}^{\dagger}$
@@
 verified by using Eqs. \ref{eq:M-KH} and \ref{eq:H-tilde}.
-The matrix identity used for obtaining the second line of Equation 
+The matrix identity used for obtaining the second line of Eq. 
 \ref{eq:M-tilde} is given by \citet[p. ~151]{searle1982}.
@@
 $\tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}})$ used in 
-Equation \ref{eq:delta-H-tilde} will be presented in
+Eq. \ref{eq:delta-H-tilde} will be presented in
 the following section.
@@
 induction (in \unit{nT}). Fortunately, this conversion can
-be easily done by multiplying Equation \ref{eq:delta-H-tilde}
+be easily done by multiplying Eq. \ref{eq:delta-H-tilde}
 by $k_{m}~=~10^{9}~\mu_{0}$, where $\mu_{0}$ represents the
@@
 (Eqs. \ref{eq:M-tilde} and \ref{eq:M-tilde-remanence})
-are calculated according to Equation \ref{eq:nij-tilde}, with 
+are calculated according to Eq. \ref{eq:nij-tilde}, with 
 $\tilde{f}(\tilde{\mathbf{r}})$ given by 
@@
 vector $\tilde{\mathbf{r}}$ (equation \ref{eq:coord_transformation}). 
-Besides, the off-diagonal elements, $i \ne j$, are zero and
+Besides, the off-diagonal elements are zero and
 the diagonal elements are given by \citep{stoner1945}:
@@
 \end{equation}
-where $R(u)$ is defined by Equation \ref{eq:R} and
+where $R(u)$ is defined by Eq. \ref{eq:R} and
 $e_{1} = a$, $e_{2} = b$, and $e_{3} = c$. These elements 
@@
 and are defined according to the ellipsoid type.
-Notice that, according to Equations \ref{eq:H-tilde} 
+Notice that, according to Eqs. \ref{eq:H-tilde} 
 and \ref{eq:N-tilde-VT-N-V},
@@
 For triaxial ellipsoids (e.g., $a > b > c$), the demagnetization
-factors obtained by solving Equation \ref{eq:n-tilde-dagger-ii} 
+factors obtained by solving Eq. \ref{eq:n-tilde-dagger-ii} 
 are given by:
@@
 For prolate ellipsoids (e.g., $a > b = c$), the demagnetization
-factors obtained by solving Equation \ref{eq:n-tilde-dagger-ii} 
+factors obtained by solving Eq. \ref{eq:n-tilde-dagger-ii} 
 are given by:
@@
 which uses the $\tilde{n}^{\dagger}_{11}$ defined in 
-Equation \ref{eq:n-tilde-dagger-11-prolate}, and $m = a/b$.
+Eq. \ref{eq:n-tilde-dagger-11-prolate}, and $m = a/b$.
 The detailed deduction of the demagnetization factors 
@@
 For oblate ellipsoids (e.g., $a < b = c$), the demagnetization
-factors obtained by solving Equation \ref{eq:n-tilde-dagger-ii} 
+factors obtained by solving Eq. \ref{eq:n-tilde-dagger-ii} 
 are given by:
@@
 where $\tilde{n}^{\dagger}_{22}$ and $\tilde{n}^{\dagger}_{33}$ 
-are calculated according to Equation
+are calculated according to Eq.
 \ref{eq:n-tilde-dagger-22-prolate}, but with $\tilde{n}^{\dagger}_{11}$ 
@@
 (Eqs. \ref{eq:delta-T-tilde} and \ref{eq:delta-T-tilde-approx}) 
-are calculated according to Equation \ref{eq:nij-tilde}, with 
+are calculated according to Eq. \ref{eq:nij-tilde}, with 
 $\tilde{f}(\tilde{\mathbf{r}})$ given by $\tilde{f}^{\ddagger}(\tilde{\mathbf{r}})$
 (Eq. \ref{eq:fe-tilde}).
+
+\begin{equation}
+\tilde{n}^{\ddagger}_{ii}(\tilde{\mathbf{r}}) =
+\frac{abc}{2}
+\left( \frac{\partial \lambda}{\partial \tilde{r}_{i}} \, h_{i} \, \tilde{r}_{i}
+- g_{i} \right)
+\label{eq:n-tilde-dagger-ii}
+\end{equation}
+
+\begin{equation}
+\tilde{n}^{\ddagger}_{ij}(\tilde{\mathbf{r}}) =
+\frac{abc}{2} \left(
+\frac{\partial \lambda}{\partial \tilde{r}_{i}} \, h_{j} \, \tilde{r}_{j} 
+\right)
+\label{eq:n-tilde-dagger-ij}
+\end{equation}
+
+\begin{equation}
+h_{i} = \frac{1}{\left( e_{i}^{2} + \lambda \right) R(\lambda)}
+\label{eq:hi}
+\end{equation}
+
+\begin{equation}
+g_{i} = \int_{\lambda}^{\infty} \frac{1}{\left( e_{i}^{2} + u \right) R(u)} du
+\label{eq:gi}
+\end{equation}
+
+\subparagraph*{Triaxial ellipsoids}
+
+TEXT
+
+\subparagraph*{Prolate and oblate ellipsoids}
+
+TEXT
 
@@
 main coordinate system to a local coordinate system.
-For convenience, let us rewrite Equation 
+For convenience, let us rewrite Eq. 
 \ref{eq:coord_transformation} as follows:
@@
 \end{equation*}
-which, from Equation \ref{eq:r-tilde-k}, can be given by
+which, from Eq. \ref{eq:r-tilde-k}, can be given by
 \begin{equation}
@@
 {\partial \tilde{r}_{i} \, \partial \tilde{r}_{j}}$.
-From Equation \ref{eq:d2f-dridrj}, we obtain
+From Eq. \ref{eq:d2f-dridrj}, we obtain
 \begin{equation}
@@
 By properly using the orthogonality of the matrix
-$\mathbf{V}$, we may rewrite Equation \ref{eq:F-V-F-tilde-VT}
+$\mathbf{V}$, we may rewrite Eq. \ref{eq:F-V-F-tilde-VT}
 as follows:
@@
 \end{equation}
-Finally, by multiplying both sides of Equation \ref{eq:F-tilde-VT-F-V}
-by $-\frac{1}{4 \pi}$ and using Equation \ref{eq:N-F},
+Finally, by multiplying both sides of Eq. \ref{eq:F-tilde-VT-F-V}
+by $-\frac{1}{4 \pi}$ and using Eq. \ref{eq:N-F},
 we conclude that 
@@
 hyperboloid of two sheets) which is confocal with the ellipsoid 
-defined in Equation \ref{eq:reference-triaxial-ell} can be 
+defined in Eq. \ref{eq:reference-triaxial-ell} can be 
 described as follows:
@@
 points $(x, y, z)$ lying on the surface of an ellipsoid which is confocal 
-with that one defined in Equation \ref{eq:reference-triaxial-ell}. 
+with that one defined in Eq. \ref{eq:reference-triaxial-ell}. 
 Now, consider the problem of determining the ellipsoid which is confocal 
@@
 given $a$, $b$, $c$, $\tilde{x}$, $\tilde{y}$, and $\tilde{z}$, 
-satisfies Equation \ref{eq:quadric-confocal-triaxial-ell} and
-the condition expressed by Equation \ref{eq:condition-triaxial-ell}.
-By rearranging Equation \ref{eq:quadric-confocal-triaxial-ell}, 
+satisfies Eq. \ref{eq:quadric-confocal-triaxial-ell} and
+the condition expressed by Eq. \ref{eq:condition-triaxial-ell}.
+By rearranging Eq. \ref{eq:quadric-confocal-triaxial-ell}, 
 we obtain the following cubic equation for $u$:
@@
 Remember that we are interested in a $u$ satisfying 
-the condition expressed by Equation \ref{eq:condition-triaxial-ell}. 
-Consequently, according to the signal analysis shown in Equation
+the condition expressed by Eq. \ref{eq:condition-triaxial-ell}. 
+Consequently, according to the signal analysis shown in Eq.
 \ref{eq:cubic-equation-signals-triaxial-ell}, we are interested in 
@@
 
-From Equation \ref{eq:cubic-equation-triaxial-ell}, we obtain a
+From Eq. \ref{eq:cubic-equation-triaxial-ell}, we obtain a
 simpler one given by
@@
 where $a > b = c > 0$. 
-In this case, the Equation defining the surface of the ellipsoid
-is obtained by substituting $c = b$ in Equation \ref{eq:reference-triaxial-ell}.
+In this case, the Eq. defining the surface of the ellipsoid
+is obtained by substituting $c = b$ in Eq. \ref{eq:reference-triaxial-ell}.
 Consequently, the equation defining the respective confocal quadric
@@
 and the new condition that must be fulfilled by the variable
-$u$ so that Equation \ref{eq:quadric-confocal-prolate-ell}
+$u$ so that Eq. \ref{eq:quadric-confocal-prolate-ell}
 represent an ellipsoid is
@@
 given $a$, $b$, $\tilde{x}$, $\tilde{y}$, and $\tilde{z}$, 
-satisfies Equation \ref{eq:quadric-confocal-prolate-ell} and
-the condition expressed by Equation \ref{eq:condition-prolate-ell}.
-From Equation \ref{eq:quadric-confocal-prolate-ell}, 
+satisfies Eq. \ref{eq:quadric-confocal-prolate-ell} and
+the condition expressed by Eq. \ref{eq:condition-prolate-ell}.
+From Eq. \ref{eq:quadric-confocal-prolate-ell}, 
 we obtain the following quadratic equation for $u$:
@@
 Therefore, according to the condition established by
-Equation \ref{eq:condition-prolate-ell} and the signal analysis 
-shown in Equation \ref{eq:quadratic-equation-signals-prolate-ell}, 
+Eq. \ref{eq:condition-prolate-ell} and the signal analysis 
+shown in Eq. \ref{eq:quadratic-equation-signals-prolate-ell}, 
 we are interested in the largest root $\lambda$ of the quadratic 
@@
 
-By properly manipulating Equation \ref{eq:quadratic-equation-prolate-ell},
+By properly manipulating Eq. \ref{eq:quadratic-equation-prolate-ell},
 we obtain a simpler one given by
@@
 the quadratic equation for the variable $u$, which is also 
-calculated by using Equation \ref{eq:lambda-prolate-ell}.
+calculated by using Eq. \ref{eq:lambda-prolate-ell}.
 
@@
 prolate or oblate ellipsoids can also be calculated by using
-Equation \ref{eq:dlambda} for the particular case in
+Eq. \ref{eq:dlambda} for the particular case in
 with $b = c$.

### 2017-01-27 manuscript/manuscript.tex
function g1 for triaxial ellipsoids

@@
 \end{equation}
-where $\kappa = \left[ \left( a^{2} - b^{2} \right) / 
-\left( a^{2} - c^{2} \right) \right]^{\frac{1}{2}}$,
-$\cos \phi = c/a$,
+where
 \begin{equation}
@@
 \left( 1 - \kappa^{2} \sin^{2} \psi \right)^{\frac{1}{2}}
-d\psi \: .
+d\psi \: ,
 \label{eq:E-kappa-phi}
 \end{equation}
+with $\kappa = \left[ \left( a^{2} - b^{2} \right) / 
+\left( a^{2} - c^{2} \right) \right]^{\frac{1}{2}}$ and
+$\cos \phi = c/a$.
 The functions $F(\kappa, \phi)$ (Eq. \ref{eq:F-kappa-phi}) and 
@@
 (Eq. \ref{eq:fe-tilde}).
-
+By following \citet{clark1986}, the diagonal elements $\tilde{n}^{\ddagger}_{ii}$
+and the off-diagonal elements $\tilde{n}^{\ddagger}_{ij}$, $i = 1, 2, 3$,
+$j = 1, 2, 3$, are given by
 \begin{equation}
@@
 \end{equation}
-
+and
 \begin{equation}
@@
 \frac{\partial \lambda}{\partial \tilde{r}_{i}} \, h_{j} \, \tilde{r}_{j} 
-\right)
+\right) \: ,
 \label{eq:n-tilde-dagger-ij}
 \end{equation}
-
-\begin{equation}
-h_{i} = \frac{1}{\left( e_{i}^{2} + \lambda \right) R(\lambda)}
+where
+\begin{equation}
+h_{i} = \frac{1}{\left( e_{i}^{2} + \lambda \right) R(\lambda)} \: ,
 \label{eq:hi}
 \end{equation}
-
-\begin{equation}
-g_{i} = \int_{\lambda}^{\infty} \frac{1}{\left( e_{i}^{2} + u \right) R(u)} du
+\begin{equation}
+g_{i} = \int_{\lambda}^{\infty} \frac{1}{\left( e_{i}^{2} + u \right) R(u)} du \: ,
 \label{eq:gi}
 \end{equation}
+$e_{1} = a$, $e_{2} = b$, $e_{3} = c$, and 
+$\frac{\partial \lambda}{\partial \tilde{r}_{i}}$
+is defined in Appendix B (Eq. \ref{eq:dlambda}).
+The functions $g_{i}$ (Eq. \ref{eq:gi}) are defined according
+to the ellipsoid type.
 
@@
 
+For triaxial ellipsoids (e.g., $a > b > c$), the functions
+$g_{i}$ (Eq. \ref{eq:gi}) are defined as follows
+\citep{clark1986}:
+
+\begin{equation}
+g_{1} = \frac{2}{\left( a^{2} - b^{2} \right) \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
+\left[ F(\kappa, \phi) - E(\kappa, \phi) \right] \: ,
+\label{eq:g1-triaxial}
+\end{equation}
+\begin{equation}
+g_{2} = 
+\label{eq:g2-triaxial}
+\end{equation}
+and
+\begin{equation}
+g_{3} = \: ,
+\label{eq:g3-triaxial}
+\end{equation}
+where $F(\kappa, \phi)$ and $E(\kappa, \phi)$ are defined by
+Eqs. \ref{eq:E-kappa-phi} and \ref{eq:F-kappa-phi},
+but with 
+$\sin \phi = \sqrt{\left( a^{2} - c^{2} \right)/\left( a^{2} + \lambda \right)}$.
+
+\subparagraph*{Prolate and oblate ellipsoids}
+
 TEXT
 
-\subparagraph*{Prolate and oblate ellipsoids}
+\section{Numerical simulations}
+
+\subsection{Demagnetization factors}
+
+Figure \ref{fig:fig1} TEXT TEXT TEXT Fig. \ref{fig:fig1} TEXT TEXT TEXT (Fig. \ref{fig:fig1})
+
+\subsection{Ellipsoidal models}
 
@@
 
+\subsection{Susceptibility}
+
+TEXT
+
 \conclusions  %% \conclusions[modified heading if necessary]
+TEXT
+
+\section{Code availability}
+
 TEXT
@@
 %
+
+%f
+\begin{figure}[t]
+\includegraphics[width=8.3cm]{figures/n_triaxial.pdf}
+\caption{TEXT}
+\label{fig:fig1}
+\end{figure}
+
 %%% TWO-COLUMN FIGURES

### 2017-01-30 manuscript/manuscript.tex
introduce a preliminary version of the figure 1

@@
 uniformly magnetized in the presence of a uniform
-inducing field \citep{jahren1963, schlomann1965, clark1999}.
+inducing field.
 
@@
 
-For triaxial ellipsoids (e.g., $a > b > c$), the demagnetization
+For triaxial ellipsoids (e.g., $a > b > c$), the demagnetizing
 factors obtained by solving Eq. \ref{eq:n-tilde-dagger-ii} 
@@
 second kind, respectivelly. \citet{stoner1945} presented a 
-detailed deduction of the demagnetization factors $\tilde{n}^{\dagger}_{11}$
+detailed deduction of the demagnetizing factors $\tilde{n}^{\dagger}_{11}$
 (Eq. \ref{eq:n-tilde-dagger-11-triaxial}), $\tilde{n}^{\dagger}_{22}$
@@
 
-For prolate ellipsoids (e.g., $a > b = c$), the demagnetization
+For prolate ellipsoids (e.g., $a > b = c$), the demagnetizing
 factors obtained by solving Eq. \ref{eq:n-tilde-dagger-ii} 
@@
 Eq. \ref{eq:n-tilde-dagger-11-prolate}, and $m = a/b$.
-The detailed deduction of the demagnetization factors 
+The detailed deduction of the demagnetizing factors 
 $\tilde{n}^{\dagger}_{11}$ (Eq. \ref{eq:n-tilde-dagger-11-prolate}) 
@@
 
-For oblate ellipsoids (e.g., $a < b = c$), the demagnetization
+For oblate ellipsoids (e.g., $a < b = c$), the demagnetizing
 factors obtained by solving Eq. \ref{eq:n-tilde-dagger-ii} 
@@
 and $m = a/b$.
-The detailed deduction of these demagnetization factors 
+The detailed deduction of these demagnetizing factors 
 can be found, for example, in \citet{stoner1945}. These formulas can also be found
@@
 \begin{equation}
-g_{2} = 
+g_{2} = \frac{2 \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
+{\left( a^{2} - b^{2} \right)\left( b^{2} - c^{2} \right)}
+\left[ E\left(\kappa, \phi \right) 
+- \frac{\left( b^{2} - c^{2} \right)}{\left( a^{2} - c^{2} \right)}
+F\left(\kappa, \phi \right) 
+- \frac{\kappa^{2} \sin\phi \, \cos\phi}
+{\left( 1 - \kappa^{2} \sin^{2}\phi \right)^{\frac{1}{2}}}
+\right]
 \label{eq:g2-triaxial}
@@
 \begin{equation}
-g_{3} = \: ,
+g_{3} = \frac{2}{\left( a^{2} - b^{2} \right) \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
+\left[ \frac{\sin\phi \left( 1 - \kappa^{2} \sin^{2}\phi \right)^{\frac{1}{2}}}
+{\cos\phi}  - E\left(\kappa, \phi \right) \right]
+\: ,
 \label{eq:g3-triaxial}
 \end{equation}
+CHECAR A EQUACAO ACIMA - TEM UM PARANTESES A MAIS NO ARTIGO DO CLARK86
 where $F(\kappa, \phi)$ and $E(\kappa, \phi)$ are defined by
@@
 
-TEXT
+For prolate (e.g., $a > b = c$) and oblate (e.g., $a < b = c$)
+ellipsoids, the functions
+$g_{i}$ (Eq. \ref{eq:gi}) are defined as follows
+\citep{emerson1985}:
+
+\begin{equation}
+g_{1} =  \frac{1}{\left( b^{2} - a^{2} \right)^{\frac{3}{2}}} 
+\left[ \tan^{-1} \left( \sqrt{\frac{b^{2} - a^{2}}{a^{2} + \lambda}} \right)
+- \frac{\sqrt{\left( b^{2} - a^{2} \right)\left( a^{2} + \lambda \right)}}
+{\left( b^{2} + \lambda \right)} \right]
+\label{eq:g1-prolate-oblate}
+\end{equation}
+\begin{equation}
+g_{2} = \frac{2}{\left( b^{2} - a^{2} \right)^{\frac{3}{2}}} 
+\left[ \sqrt{\frac{b^{2} - a^{2}}{a^{2} + \lambda}}
+- \tan^{-1} \left( \sqrt{\frac{b^{2} - a^{2}}{a^{2} + \lambda}} \right) \right] \: ,
+\label{eq:g2-prolate-oblate}
+\end{equation}
+where $g_{3} = g_{2}$.
 
@@
 
-\subsection{Demagnetization factors}
+\subsection{Demagnetizing factors}
 
@@
 \begin{equation}
-p(u) =  u^{u} + p_{2} \, u^{2} + p_{1} \, u + p_{0} \: ,
+p(u) =  u^{3} + p_{2} \, u^{2} + p_{1} \, u + p_{0} \: ,
 \label{eq:cubic-equation-triaxial-ell-simpler}
@@
 \begin{figure}[t]
-\includegraphics[width=8.3cm]{figures/n_triaxial.pdf}
+\includegraphics[width=8.3cm]{figures/demag_factors.pdf}
 \caption{TEXT}

### 2017-02-01 manuscript/manuscript.tex
examples of code availability sections
include examples of code availability texts
preliminary version of code availability

@@
 
-\introduction  %% \introduction[modified heading if necessary]
+%\introduction  %% \introduction[modified heading if necessary]
+\section{Introduction}
 
@@
 %por toda a comunidade geofísica. 
-%VER COMO AQUELE CARA DA ISOSTASIA ESCREVEU
+%exemplo1:
+%Isostasy is one of the oldest and most widely applied
+%concepts in the geosciences, but the geoscientific community
+%lacks a coherent, easy-to-use tool to simulate flexure
+%of a realistic (i.e., laterally heterogeneous) lithosphere under
+%an arbitrary set of surface loads. Such a model is needed for
+%studies of mountain building, sedimentary basin formation,
+%glaciation, sea-level change, and other tectonic, geodynamic,
+%and surface processes.
+%exemplo2:
+%In spite of these efforts,
+%the community currently lacks a robust, easy-to-use,
+%generalized tool for flexural isostatic solutions that can be
+%used by modelers and data-driven scientists alike.
 
@@
 \end{equation}
-CHECAR A EQUACAO ACIMA - TEM UM PARANTESES A MAIS NO ARTIGO DO CLARK86
 where $F(\kappa, \phi)$ and $E(\kappa, \phi)$ are defined by
@@
 
-TEXT
+The code is freely distributed under 
+BSD 3-clause licence as part of Fatiando a Terra 
+\citep{uieda2013}, which is an open-source Python 
+library for modelling and inversion in geophysics.
+Documentation and installation instructions for 
+the most current release version of Fatiando a Terra 
+are provided at \url http://www.fatiando.org.
 
 \appendix
-\section{Relationship between the derivatives of the functions $f(\mathbf{r})$ and $\tilde{f}(\tilde{\mathbf{r}})$}    %% Appendix A
+\section{Derivatives of the functions $f(\mathbf{r})$ and $\tilde{f}(\tilde{\mathbf{r}})$} %% Appendix A
 
@@
 \begin{equation}
-\theta = \cos^{-1} \left( \frac{R}{\sqrt{Q^{3}}} \right) \: ,
+\theta = \cos^{-1} \left( \frac{R}{\sqrt{-Q^{3}}} \right) \: ,
 \label{eq:theta-triaxial-ell}

### 2017-02-03 code/ellipsoid_oblate.py
novos testes para a dissertacao

@@ -1,264 +1,494 @@
+"""
+The potential fields of a triaxial ellipsoid.
+"""
+
+from __future__ import division
 import numpy as np
 from scipy import linalg
-from matplotlib import pyplot as plt
 
-from fatiando import mesher, gridder, utils
+from .. import utils
 
 import scipy.special
 
-def ellipsoid (xp,yp,zp,xc,yc,zc,a,b,azimuth,delta,declirem,inclirem,intensity,decT,incT,intT,k):
+def bx_c(xp,yp,zp,inten,inc,dec,ellipsoids):
     '''
-    Calculates the three componentes of magnetic field generated by an ellipsoid.
+    Calculates the X component of the magnetic field generated by n-ellipsoid.
     
-    input:
-    xp,yp - Origin of the ellipsoid in the geographic coordinate.
-    zp - Depth of the the ellipsoid.
-    a,b - Minor and major axis, respectively.
-    azimuth - angle in relation to the major-axe and the geographic north (0<=alpha<=360, radians).
-    delta - Inclination between the major-axe and the horizontal plane (0<=delta<=90, radians).
-    xc,yc,zc - point in the grid that has the center of the ellipsoid.
-    declirem - declination of the remanent vector.
-    inclirem - inclination of the remanent vector.
-    intensity - intensity of the remanent vector.
-    intT - Intensity of the Earth's magnetic field.
-    incT - Inclination of the Earth's magnetic field.
-    decT - Declination of the Earth's magnetic field.
-    k - 3x3 matrix where each line has the intensity, declination and inclination of the three susceptibilities vectors.
+    Parameters:
     
-    output:
-    Bx, By, Bz, Tf - components of magnetic field generated by an ellipsoid and the total-field anomaly.
+    * xp,yp,zp: arrays
+        Grid of observation points x, y, and z.
+    * inten,inc,dec: floats
+        Intensity, inclination and declination of the Earth's magnetic field.
[…]

### 2017-02-03 code/ellipsoid_prolate.py

@@ -1,263 +1,496 @@
+"""
+The potential fields of a triaxial ellipsoid.
+"""
+
+from __future__ import division
 import numpy as np
 from scipy import linalg
-from matplotlib import pyplot as plt
 
-from fatiando import mesher, gridder, utils
+from .. import utils
 
 import scipy.special
 
-def ellipsoid (xp,yp,zp,xc,yc,zc,a,b,azimuth,delta,declirem,inclirem,intensity,decT,incT,intT,k):
+def bx_c(xp,yp,zp,inten,inc,dec,ellipsoids):
     '''
-    Calculates the three componentes of magnetic field generated by an ellipsoid.
+    Calculates the X component of the magnetic field generated by n-ellipsoid.
     
-    input:
-    xp,yp - Origin of the ellipsoid in the geographic coordinate.
-    zp - Depth of the the ellipsoid.
-    a,b - Major and minor axis, respectively.
-    azimuth - angle in relation to the major-axe and the geographic north (0<=alpha<=360, radians).
-    delta - Inclination between the major-axe and the horizontal plane (0<=delta<=90, radians).
-    xc,yc,zc - point in the grid that has the center of the ellipsoid.
-    declirem - declination of the remanent vector.
-    inclirem - inclination of the remanent vector.
-    intensity - intensity of the remanent vector.
-    intT - Intensity of the Earth's magnetic field.
-    incT - Inclination of the Earth's magnetic field.
-    decT - Declination of the Earth's magnetic field.
-    k - 3x3 matrix where each line has the intensity, declination and inclination of the three susceptibilities vectors.
+    Parameters:
     
-    output:
-    Bx, By, Bz, Tf - componentes of magnetic field generated by an ellipsoid and the total-field anomaly.
+    * xp,yp,zp: arrays
+        Grid of observation points x, y, and z.
+    * inten,inc,dec: floats
+        Intensity, inclination and declination of the Earth's magnetic field.
[…]

### 2017-02-03 code/ellipsoid_triaxial.py

@@ -1,64 +1,181 @@
+"""
+The potential fields of a triaxial ellipsoid.
+"""
+
+from __future__ import division
 import numpy as np
 from scipy import linalg
-from matplotlib import pyplot as plt
 
-from fatiando import mesher, gridder, utils
+from .. import utils
 
 import scipy.special
 
-def ellipsoid (xp,yp,zp,xc,yc,zc,a,b,c,azimuth,delta,gamma,declirem,inclirem,intensity,decT,incT,intT,k):
+def bx_c(xp,yp,zp,inten,inc,dec,ellipsoids):
     '''
-    Calculates the three componentes of magnetic field generated by an ellipsoid.
+    Calculates the X component of the magnetic field generated by n-ellipsoid.
     
-    input:
-    xp,yp - Origin of the ellipsoid in the geographic coordinate.
-    zp - Depth of the the ellipsoid.
-    a,b - Minor and major axis, respectively.
-    azimuth - angle in relation to the major-axe and the geographic north (0<=alpha<=360, radians).
-    delta - Inclination between the major-axe and the horizontal plane (0<=delta<=90, radians).
-    gamma - Angle between the intermediate-axe and the vertical projection of the horizontal plane to the
-    center of the ellipsoid(radians).
-    xc,yc,zc - point in the grid that has the center of the ellipsoid.
-    declirem - declination of the remanent vector.
-    inclirem - inclination of the remanent vector.
-    intensity - intensity of the remanent vector.
-    intT - Intensity of the Earth's magnetic field.
-    incT - Inclination of the Earth's magnetic field.
-    decT - Declination of the Earth's magnetic field.
-    k - 3x3 matrix where each line has the intensity, declination and inclination of the three susceptibilities vectors.
-    Bx_T, By_T, Bz_T, Tf_T - componentes of magnetic field generated by an ellipsoid and the total-field anomaly.
+    Parameters:
+    
+    * xp,yp,zp: arrays
+        Grid of observation points x, y, and z.
[…]

### 2017-02-07 manuscript/manuscript.tex
small changes
identify an error in the g functions of prolate and oblate ellipsoids
define the susceptibility tensor and the correct g for prolate and oblate ellipsoids

@@
 constant and symmetrical 2nd-order tensor representing the 
-magnetic susceptibility of the body. In this case, Equation 
-\ref{eq:H} can be rewritten as follows:
+magnetic susceptibility of the body. 
+In general, the susceptibility tensor $\mathbf{K}$ is represented as
+follows:
+\begin{equation}
+\mathbf{K} = \mathbf{U}
+\left[ \begin{array}{ccc}
+k_{1} & 0 & 0 \\
+0 & k_{2} & 0 \\
+0 & 0 & k_{3} 
+\end{array} \right] \mathbf{U}^{\top} \: ,
+\label{eq:K}
+\end{equation}
+where $k_{1} > k_{2} > k_{3}$ are the 
+\textit{principal susceptibilities} and $\mathbf{U}$ is
+an orthogonal matrix whose columns $\mathbf{u}_{i}$,
+$i = 1, 2, 3$, are unit vectors called 
+\textit{principal directions} \citep{hrouda1982}.
+For the particular case in which the principal directions 
+coincide with the ellipsoid axes, $\mathbf{U} = \mathbf{V}$
+where $\mathbf{V}$ is defined by Eq. \ref{eq:V_triaxial_prolate} 
+or \ref{eq:V_oblate}), depending on the ellipsoid type.
+
+By using the magnetization $\mathbf{M}$ defined by Eq. \ref{eq:M-KH}, 
+the total magnetic field $\mathbf{H}(\mathbf{r})$ (Eq. \ref{eq:H}) 
+can be rewritten as follows:
 \begin{equation}
@@
 lowes1974,  peake1953, chang1961, clark1986, tejedor1995, sttraton2007}.
+
 It is convenient to use $\tilde{f}^{\dagger}(\tilde{\mathbf{r}})$
@@
 ellipsoidal body.
-
 The scalar function $\tilde{f}^{\dagger}(\tilde{\mathbf{r}})$
@@
 - \frac{\tilde{z}^{2}}{c^{2} + u} \right)
-\frac{1}{R(u)} \, du \: , \quad \tilde{\mathbf{r}} \in V \: ,
+\frac{1}{R(u)} \, du \: , \quad \tilde{\mathbf{r}} \in \vartheta \: ,
 \label{eq:fi-tilde}
@@
 - \frac{\tilde{z}^{2}}{c^{2} + u} \right)
-\frac{1}{R(u)} \, du \: , \quad \tilde{\mathbf{r}} \not\in V \: ,
+\frac{1}{R(u)} \, du \: , \quad \tilde{\mathbf{r}} \not\in \vartheta \: ,
 \label{eq:fe-tilde}
@@
 \tilde{n}^{\ddagger}_{ii}(\tilde{\mathbf{r}}) =
-\frac{abc}{2}
+-\frac{abc}{2}
 \left( \frac{\partial \lambda}{\partial \tilde{r}_{i}} \, h_{i} \, \tilde{r}_{i}
-- g_{i} \right)
++ g_{i} \right)
 \label{eq:n-tilde-dagger-ii}
@@
 \tilde{n}^{\ddagger}_{ij}(\tilde{\mathbf{r}}) =
-\frac{abc}{2} \left(
+-\frac{abc}{2} \left(
 \frac{\partial \lambda}{\partial \tilde{r}_{i}} \, h_{j} \, \tilde{r}_{j} 
@@
 \begin{equation}
-h_{i} = \frac{1}{\left( e_{i}^{2} + \lambda \right) R(\lambda)} \: ,
+h_{i} = -\frac{1}{\left( e_{i}^{2} + \lambda \right) R(\lambda)} \: ,
 \label{eq:hi}
@@
 \begin{equation}
-g_{3} = \frac{2}{\left( a^{2} - b^{2} \right) \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
+g_{3} = \frac{2}{\left( b^{2} - c^{2} \right) \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
 \left[ \frac{\sin\phi \left( 1 - \kappa^{2} \sin^{2}\phi \right)^{\frac{1}{2}}}
@@
 
-\subparagraph*{Prolate and oblate ellipsoids}
-
-For prolate (e.g., $a > b = c$) and oblate (e.g., $a < b = c$)
-ellipsoids, the functions
-$g_{i}$ (Eq. \ref{eq:gi}) are defined as follows
+FALAR DO \citet{tejedor1995}
+
+\subparagraph*{Prolate ellipsoids}
+
+For prolate (e.g., $a > b = c$) ellipsoids, the functions
+$g_{i}$ (Eq. \ref{eq:gi}) are given by
 \citep{emerson1985}:
@@
 \begin{equation}
-g_{1} =  \frac{1}{\left( b^{2} - a^{2} \right)^{\frac{3}{2}}} 
-\left[ \tan^{-1} \left( \sqrt{\frac{b^{2} - a^{2}}{a^{2} + \lambda}} \right)
-- \frac{\sqrt{\left( b^{2} - a^{2} \right)\left( a^{2} + \lambda \right)}}
-{\left( b^{2} + \lambda \right)} \right]
-\label{eq:g1-prolate-oblate}
-\end{equation}
-\begin{equation}
-g_{2} = \frac{2}{\left( b^{2} - a^{2} \right)^{\frac{3}{2}}} 
-\left[ \sqrt{\frac{b^{2} - a^{2}}{a^{2} + \lambda}}
-- \tan^{-1} \left( \sqrt{\frac{b^{2} - a^{2}}{a^{2} + \lambda}} \right) \right] \: ,
-\label{eq:g2-prolate-oblate}
+g_{1} =  \frac{2}{\left( a^{2} - b^{2} \right)^{\frac{3}{2}}}
+\left\lbrace
+\ln \left[ \frac{\left( a^{2} - b^{2} \right)^{\frac{1}{2}} + 
+                 \left( a^{2} + \lambda \right)^{\frac{1}{2}}}{
+                 \left( b^{2} + \lambda \right)^{\frac{1}{2}}} \right] -
+\left( \frac{a^{2} - b^{2}}{a^{2} + \lambda} \right)^{\frac{1}{2}}
+\right\rbrace
+\label{eq:g1-prolate}
+\end{equation}
+and
+\begin{equation}
+g_{2} =  \frac{1}{\left( a^{2} - b^{2} \right)^{\frac{3}{2}}}
+\left\lbrace
+\frac{\left[ \left( a^{2} - b^{2} \right)
+             \left( a^{2} + \lambda \right) \right]^{\frac{1}{2}}}
+     {b^{2} + \lambda} -
+\ln \left[ \frac{\left( a^{2} - b^{2} \right)^{\frac{1}{2}} + 
+                 \left( a^{2} + \lambda \right)^{\frac{1}{2}}}{
+                 \left( b^{2} + \lambda \right)^{\frac{1}{2}}} \right]
+\right\rbrace \: ,
+\label{eq:g2-prolate}
+\end{equation}
+where $g_{3} = g_{2}$.
+
+\subparagraph*{Oblate ellipsoids}
+
+For oblate (e.g., $a < b = c$) ellipsoids, the functions
+$g_{i}$ (Eq. \ref{eq:gi}) are given by
+\citep{emerson1985}:
+
+\begin{equation}
+g_{1} =  \frac{2}{\left( b^{2} - a^{2} \right)^{\frac{3}{2}}}
+\left\lbrace
+\left( \frac{b^{2} - a^{2}}{a^{2} + \lambda}\right)^{\frac{1}{2}} -
+\tan^{-1} \left[ \left( \frac{b^{2} - a^{2}}{a^{2} + \lambda}\right)^{\frac{1}{2}} \right]
+\right\rbrace
+\label{eq:g1-oblate}
+\end{equation}
+and
+\begin{equation}
+g_{2} =  \frac{1}{\left( b^{2} - a^{2} \right)^{\frac{3}{2}}}
+\left\lbrace
+\tan^{-1} \left[ \left( \frac{b^{2} - a^{2}}{a^{2} + \lambda}\right)^{\frac{1}{2}} \right] -
+\frac{\left[ \left( b^{2} - a^{2} \right)
+             \left( a^{2} + \lambda \right) \right]^{\frac{1}{2}}}
+     {b^{2} + \lambda}
+\right\rbrace \: ,
+\label{eq:g2-oblate}
 \end{equation}

### 2017-02-08 manuscript/manuscript.tex
modify the end of the introduction, correct elements n-tilde-dagger and put some alerts

@@
 in the presence of a uniform magnetic field.
-
 This property can be extended to other bodies
-whose shape derives from an ellipsoid 
+defined as limiting cases of an ellipsoid
 (e.g., spheres, elliptic cylinders), however all the
@@
 hillan2013}.
-
 However, neglecting the self-demagnetization in
 geological bodies with high susceptibilities (> 0.1 SI) 
-may strongly mislead the results obtained from
+may strongly mislead the interpretation obtained from
 magnetic methods.
-
 \citet{farrar1979} demonstrated the importance of the
@@
 Australia.
-
 Posteriorly, \citet{hoschke1991} also showed how the
@@
 Tennant Creek field.
-
 \citet{clark2000} provides a good discussion about the
@@
 in the interpreted dip. 
-
-Based on magnetic modelling and rock property 
-measurements, \citet{austin2014} showed that,
+Recently, \citet{austin2014} used magnetic modelling 
+and rock property measurements to show that,
 contrary to previous interpretations, the magnetization
@@
 self-demagnetization.
-
-These examples show the practical importance of
-self-demagnetization for the correct interpretation
-of magnetic data produced by geological bodies having
-high susceptibilities.
-
-These examples also show the importance of the ellipsoidal
-model in producing trustworthy geological models of orebodies,
-which may save significant cost associated with drilling.
-
-%The ellipsoidal model ability in analytically
-%incorporating the self-demagnetization...
-%FALAR DA APLICACAO DIDATICA
-
-%Apesar da grande aplicabilidade do modelo elipsoidal 
-%na geofísica, apenas alguns softwares proprietários 
-%possuem sua implementação. Neste sentido, este trabalho 
-%tem a finalidade de disponibilizar uma ferramenta de 
-%código aberto, que poderá ser utilizada livremente 
-%por toda a comunidade geofísica. 
-%exemplo1:
-%Isostasy is one of the oldest and most widely applied
-%concepts in the geosciences, but the geoscientific community
-%lacks a coherent, easy-to-use tool to simulate flexure
-%of a realistic (i.e., laterally heterogeneous) lithosphere under
-%an arbitrary set of surface loads. Such a model is needed for
-%studies of mountain building, sedimentary basin formation,
-%glaciation, sea-level change, and other tectonic, geodynamic,
-%and surface processes.
-%exemplo2:
-%In spite of these efforts,
-%the community currently lacks a robust, easy-to-use,
-%generalized tool for flexural isostatic solutions that can be
-%used by modelers and data-driven scientists alike.
+These examples show the importance of the ellipsoidal
+model in producing trustworthy geological models of
+high-susceptibility orebodies, which may save significant 
+cost associated with drilling.
+
+As we can see, a vast literature about the magnetic
+modelling of ellipsoidal bodies was developed in which 
+are to be found the names of many brilliant researchers.
+Nevertheless, interest in this subject has not yet died
+out, as is evidenced by the list of modern papers in this
+field.
+Besides, the geoscientific community lacks an easy-to-use 
+tool to simulate the magnetic field produced by uniformly 
+magnetized ellipsoids.
+Such a tool could prove to be useful either for teaching
+and researching geophysics.
+
+To fill this gap, we provide here a set of routines to 
+model the magnetic field produced by ellipsoids.
+The routines are written in Python language as part of
+the Fatiando a Terra \citep{uieda2013}, which is an 
+open-source library for modelling and inversion in geophysics.
+We attempt to use the best practices of continuous 
+integration, documentation, unit-testing, and version-control
+for the purpose of providing a reliable and easy-to-use
+code.
+It is hoped that the presentation of the theoretical and
+practical aspects given here will be found useful to the
+wide community of geoscientists.
 
@@
 magnetic susceptibility of the body. 
-In general, the susceptibility tensor $\mathbf{K}$ is represented as
-follows:
+In general, the susceptibility tensor $\mathbf{K}$ is represented,
+in the main coordinate system, as follows:
 \begin{equation}
@@
 For the particular case in which the principal directions 
-coincide with the ellipsoid axes, $\mathbf{U} = \mathbf{V}$
-where $\mathbf{V}$ is defined by Eq. \ref{eq:V_triaxial_prolate} 
-or \ref{eq:V_oblate}), depending on the ellipsoid type.
+coincide with the ellipsoid axes, the matrix $\mathbf{U}$ is
+equal to the matrix $\mathbf{V}$ (Eqs. \ref{eq:V_triaxial_prolate}
+and \ref{eq:V_oblate}), depending on the ellipsoid type.
 
@@
 peirce1902, webster1904, kellogg1929, stoner1945, osborn1945,
-lowes1974,  peake1953, chang1961, clark1986, tejedor1995, sttraton2007}.
+macmillan1958, lowes1974,  peake1953, chang1961, clark1986, 
+tejedor1995, sttraton2007}.
 
@@
 \citet[Eq. ~38]{clark1986}.
+
+FALAR QUE ESTA EQUACAO REPRESENTA O CASO HOMOGENEO ANISOTROPICO. 
+FALAR QUE A MAIORIA DOS TRABALHOS DISCUTE O CASO HOMOGENEO ISOTROPICO
+(CITAR TRABALHOS)
+O CASO ANISOTROPICO FOI APRESENTADO PELA PRIMEIRA VEZ POR \citet{soliverez1981} and
+posteriorly by \citet{emerson1985} and \citet{clark1986} (CHECAR).
+
+FALAR DO CASO PARTICULAR EM QUE A SUSCETIBILIDADE EH MUITO FRACA E
+A REMANENCIA EH NULA. NESTE CASO, A MAGNETIZACAO EH A FORMULA CLASSICA
+DE MAGNETIZACAO INDUZIDA ENCONTRADA NOS LIVROS.
+
+FALAR TAMBEM SOBRE O CASO ISOTROPICO E CITAR O TRABALHO DO GUO 2001.
+USAR OS TERMOS INTRINSIC E EFFECTIVE MAGNETIZATIONS.
 
@@
 (Eq. \ref{eq:n-tilde-dagger-33-triaxial}). \citet{clark1986} presented similar
-formulas, but without any proof.
+formulas.
 
@@
 These formulas were posteriorly 
-presented by \citet{emerson1985}, but without any mathematical proof.
+presented by \citet{emerson1985}.
 
@@
 The detailed deduction of these demagnetizing factors 
-can be found, for example, in \citet{stoner1945}. These formulas can also be found
-in \citet{emerson1985}, but without any mathematical proof.
+can be found, for example, in \citet{stoner1945}.
+These formulas can also be found in \citet{emerson1985}.
 The only difference, however, is that \citet{emerson1985} replaced
@@
 For triaxial ellipsoids (e.g., $a > b > c$), the functions
-$g_{i}$ (Eq. \ref{eq:gi}) are defined as follows
-\citep{clark1986}:
-
+$g_{i}$ (Eq. \ref{eq:gi}) are defined as follows:
 \begin{equation}
@@
 \end{equation}
+%\begin{equation}
+%g_{2} = \frac{2 \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
+%{\left( a^{2} - b^{2} \right)\left( b^{2} - c^{2} \right)}
+%\left[ E\left(\kappa, \phi \right) 
+%- \frac{\left( b^{2} - c^{2} \right)}{\left( a^{2} - c^{2} \right)}
+%F\left(\kappa, \phi \right) 
+%- \frac{\kappa^{2} \sin\phi \, \cos\phi}
+%{\left( 1 - \kappa^{2} \sin^{2}\phi \right)^{\frac{1}{2}}}
+%\right]
+%\label{eq:g2-triaxial}
+%\end{equation}
 \begin{equation}
@@
 {\left( a^{2} - b^{2} \right)\left( b^{2} - c^{2} \right)}
-\left[ E\left(\kappa, \phi \right) 
-- \frac{\left( b^{2} - c^{2} \right)}{\left( a^{2} - c^{2} \right)}
-F\left(\kappa, \phi \right) 
-- \frac{\kappa^{2} \sin\phi \, \cos\phi}
-{\left( 1 - \kappa^{2} \sin^{2}\phi \right)^{\frac{1}{2}}}
-\right]
+\left\lbrace
+E\left(\kappa, \phi \right) 
+- \left( \frac{b^{2} - c^{2}}{a^{2} - c^{2}} \right)
+F\left(\kappa, \phi \right) -
+\frac{a^{2} - b^{2}}{\left( a^{2} - c^{2} \right)^{\frac{1}{2}}} \left[
+\frac{c^{2} + \lambda}{\left( a^{2} + \lambda \right)\left( b^{2} + \lambda \right)}
+\right]^{\frac{1}{2}} \right\rbrace
 \label{eq:g2-triaxial}
@@
 and
+%\begin{equation}
+%g_{3} = \frac{2}{\left( b^{2} - c^{2} \right) \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
+%\left[ \frac{\sin\phi \left( 1 - \kappa^{2} \sin^{2}\phi \right)^{\frac{1}{2}}}
+%{\cos\phi}  - E\left(\kappa, \phi \right) \right]
+%\: ,
+%\label{eq:g3-triaxial}
+%\end{equation}
 \begin{equation}
 g_{3} = \frac{2}{\left( b^{2} - c^{2} \right) \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
-\left[ \frac{\sin\phi \left( 1 - \kappa^{2} \sin^{2}\phi \right)^{\frac{1}{2}}}
-{\cos\phi}  - E\left(\kappa, \phi \right) \right]
+E\left(\kappa, \phi \right) +
+\frac{2}{b^{2} - c^{2}}
+\left[
+\frac{b^{2} + \lambda}{\left( a^{2} + \lambda \right)\left( c^{2} + \lambda \right)}
+\right]^{\frac{1}{2}}
 \: ,
@@
 where $F(\kappa, \phi)$ and $E(\kappa, \phi)$ are defined by
-Eqs. \ref{eq:E-kappa-phi} and \ref{eq:F-kappa-phi},
-but with 
+Eqs. \ref{eq:E-kappa-phi} and \ref{eq:F-kappa-phi}, but with 
 $\sin \phi = \sqrt{\left( a^{2} - c^{2} \right)/\left( a^{2} + \lambda \right)}$.
-
-FALAR DO \citet{tejedor1995}
+A deduction of these formulas was presented by \citet{tejedor1995}.
+Despite the small differences, these formulas can also be found in
+\citet{clark1986}.
 
@@
 For prolate (e.g., $a > b = c$) ellipsoids, the functions
-$g_{i}$ (Eq. \ref{eq:gi}) are given by
-\citep{emerson1985}:
-
+$g_{i}$ (Eq. \ref{eq:gi}) are given by:
 \begin{equation}
@@
 where $g_{3} = g_{2}$.
+These formulas can be obtained by properly manipulating those
+presented by \citep{emerson1985}.
 
@@
 For oblate (e.g., $a < b = c$) ellipsoids, the functions
-$g_{i}$ (Eq. \ref{eq:gi}) are given by
-\citep{emerson1985}:
-
+$g_{i}$ (Eq. \ref{eq:gi}) are given by:
 \begin{equation}
@@
 where $g_{3} = g_{2}$.
+Similarly to the case of prolate ellipsoid shown previously,
+these formulas can be obtained by properly manipulating those
+presented by \citep{emerson1985}.
 
@@
 The code is freely distributed under 
-BSD 3-clause licence as part of Fatiando a Terra 
+BSD 3-clause licence as part of the Fatiando a Terra 
 \citep{uieda2013}, which is an open-source Python 

### 2017-02-08 manuscript/manuscript.tex
include the isotropic susceptibility case

@@
 and \ref{eq:V_oblate}), depending on the ellipsoid type.
+Another important particular case is that in which the
+susceptibility is isotropic and, consequently, the principal
+susceptibilities $k_{1}$, $k_{2}$, and $k_{3}$ (Eq. \ref{eq:K})
+are equal to a constant $\chi$. In this case, the susceptibility
+tensor $\mathbf{K}$ (Eq. \ref{eq:K}) assumes the particular form
+\begin{equation}
+\mathbf{K} = \chi \, \mathbf{I} \: ,
+\label{eq:K-isotropic}
+\end{equation}
+where $\mathbf{I}$ represents the identity matrix.
 
@@
 where $\mathbf{I}$ is the identity matrix and 
-$\tilde{\mathbf{N}}^{\dagger}$ represents the
-transformed depolarization tensor evaluated within 
-the volume $\vartheta$ of the ellipsoidal body. The elements
-of $\tilde{\mathbf{N}}^{\dagger}$ will be presented in a 
-latter section.
+$\tilde{\mathbf{N}}^{\dagger}$ is a diagonal matrix
+representing the transformed depolarization tensor 
+evaluated within the volume $\vartheta$ of the ellipsoidal body. 
+The elements of $\tilde{\mathbf{N}}^{\dagger}$ will be 
+presented in a latter section.
 
@@
 \ref{eq:M-tilde} is given by \citet[p. ~151]{searle1982}.
+For the particular case in which the susceptibility is isotropic
+(Eq. \ref{eq:K-isotropic}) and $\chi << 1$, the magnetization
+$\tilde{\mathbf{M}}$ (Eq. \ref{eq:M-tilde}) can be approximated
+as follows:
+\begin{equation}
+\tilde{\mathbf{M}} \approx \chi \, \tilde{\mathbf{H}}_{0} \: ,
+\label{eq:M-tilde-chi-H0}
+\end{equation}
+which is the classical equation describing the induced
+magnetization in applied geophysics \citep[p. 87]{blakely1996}.
+Notice that, in this particular case, the magnetization is
+parallel to the inducing field $\tilde{\mathbf{H}}_{0}$.
+
+FALAR DO CASO EM QUE A INDUCAO EH PARALELA A UM EIXO DO ELIPSOIDE
 
@@
 \citet[Eq. ~38]{clark1986}.
-
-FALAR QUE ESTA EQUACAO REPRESENTA O CASO HOMOGENEO ANISOTROPICO. 
-FALAR QUE A MAIORIA DOS TRABALHOS DISCUTE O CASO HOMOGENEO ISOTROPICO
-(CITAR TRABALHOS)
-O CASO ANISOTROPICO FOI APRESENTADO PELA PRIMEIRA VEZ POR \citet{soliverez1981} and
-posteriorly by \citet{emerson1985} and \citet{clark1986} (CHECAR).
-
-FALAR DO CASO PARTICULAR EM QUE A SUSCETIBILIDADE EH MUITO FRACA E
-A REMANENCIA EH NULA. NESTE CASO, A MAGNETIZACAO EH A FORMULA CLASSICA
-DE MAGNETIZACAO INDUZIDA ENCONTRADA NOS LIVROS.
-
-FALAR TAMBEM SOBRE O CASO ISOTROPICO E CITAR O TRABALHO DO GUO 2001.
-USAR OS TERMOS INTRINSIC E EFFECTIVE MAGNETIZATIONS.
 
@@
 and are defined according to the ellipsoid type.
+Here, we calculate the demagnetizing factors in the SI
+system. Consequently, they satisfies the condition
+$\tilde{n}^{\dagger}_{11} + \tilde{n}^{\dagger}_{22} + 
+\tilde{n}^{\dagger}_{33} = 1$, independently of the
+ellipsoid type.
 Notice that, according to Eqs. \ref{eq:H-tilde} 
@@
 to the ellipsoid type.
+Notice that the elements $\tilde{n}^{\ddagger}_{ij}$
+(Eqs. \ref{eq:n-tilde-dagger-ii} and \ref{eq:n-tilde-dagger-ij}) 
+are proportional to the second derivatives of the function
+$\tilde{f}^{\ddagger}(\tilde{\mathbf{r}})$ (Eq. \ref{eq:fe-tilde}),
+which is harmonic. Consequently, the diagonal elements defined
+in Eq. \ref{eq:n-tilde-dagger-ii} satisfies the condition
+$\tilde{n}^{\ddagger}_{11}(\tilde{\mathbf{r}}) +
+\tilde{n}^{\ddagger}_{22}(\tilde{\mathbf{r}}) +
+\tilde{n}^{\ddagger}_{33}(\tilde{\mathbf{r}}) = 0$ for any
+point $\tilde{\mathbf{r}}$ outside the ellipsoid, independently
+of the ellipsoid type.
 
@@
 
+\section{Computational implementation and testing}
+
+The code is implemented in Python language,
+by using use the NumPy and SciPy libraries \citep{vanderwalt2011},
+as part of the open-source source library
+Fatiando a Terra \citep{uieda2013}.
+Because of that, it is very modular and has a
+test suite formed by a considerable number of 
+assertions, unit tests, doc tests and integration tests.
+For readers interested in automated code testing,
+we recommend taking a look at the 
+freely reusable lessons of the Software Carpentry 
+(\url{https://software-carpentry.org/}) and at the
+description of the doctest module that is available
+in the documentation for Python 2.X 
+(\url{https://docs.python.org/2/library/doctest.html}).
+
 \section{Numerical simulations}
@@
 
-\conclusions  %% \conclusions[modified heading if necessary]
+\section{Conclusions}  %% \conclusions[modified heading if necessary]
 TEXT

### 2017-02-09 manuscript/manuscript.tex
include particular cases of magnetization

@@
 evaluated within the volume $\vartheta$ of the ellipsoidal body.
-The elements of $\tilde{\mathbf{N}}^{\dagger}$ will be 
-presented in a latter section.
+For a given ellipsoid, the elements of $\tilde{\mathbf{N}}^{\dagger}$ 
+are constants which are expressed in terms of the ellipsoid semi-axes.
+These elements are presented in detail in a latter section.
 
@@
 \ref{eq:M-tilde} is given by \citet[p. ~151]{searle1982}.
-For the particular case in which the susceptibility is isotropic
-(Eq. \ref{eq:K-isotropic}) and $\chi << 1$, the magnetization
+
+555555555555555555555555555
+
+For the particular case in which the susceptibility is isotropic,
+the susceptibility tensor is defined according to Eq. \ref{eq:K-isotropic}.
+In this case, the magnetization $\tilde{\mathbf{M}}$ (Eq. \ref{eq:M-tilde})
+can be rewritten as follows:
+\begin{equation}
+\tilde{\mathbf{M}} = \left[ \begin{array}{ccc}
+\frac{\chi}{1 - \chi \, \tilde{n}^{\dagger}_{11}} & 0 & 0 \\
+0 & \frac{\chi}{1 - \chi \, \tilde{n}^{\dagger}_{22}} & 0 \\
+0 & 0 & \frac{\chi}{1 - \chi \, \tilde{n}^{\dagger}_{33}}
+\end{array} \right]
+\tilde{\mathbf{H}}_{0} \: ,
+\label{eq:M-tilde-K-isotropic}
+\end{equation}
+where $\tilde{n}^{\dagger}_{ii}$, $i = 1, 2, 3$, are the constant
+elements of the transformed depolarization tensor
+$\tilde{\mathbf{N}}^{\dagger}$.
+Equation \ref{eq:M-tilde-K-isotropic} reveals that,
+the magnetization $\tilde{\mathbf{M}}$ is parallel to
+the inducing field $\tilde{\mathbf{H}}_{0}$
+is parallel to an ellipsoid axis, the magnetization is
+
+If we additionally consider that $\chi << 1$, the magnetization
 $\tilde{\mathbf{M}}$ (Eq. \ref{eq:M-tilde}) can be approximated
@@
 
-FALAR DO CASO EM QUE A INDUCAO EH PARALELA A UM EIXO DO ELIPSOIDE
+555555555555555555555555555555555555555555
 

### 2017-02-10 manuscript/manuscript.tex
particular cases of magnetization

--- 2017-02-08 manuscript/manuscript.tex
@@
 evaluated within the volume $\vartheta$ of the ellipsoidal body.
-The elements of $\tilde{\mathbf{N}}^{\dagger}$ will be 
-presented in a latter section.
+For a given ellipsoid, the elements $\tilde{n}^{\dagger}_{ii}$, 
+$i = 1, 2, 3$, of $\tilde{\mathbf{N}}^{\dagger}$ are constants 
+which are expressed in terms of the ellipsoid semi-axes.
+These elements are presented in detail in a latter section.
 
@@
 \ref{eq:M-tilde} is given by \citet[p. ~151]{searle1982}.
-For the particular case in which the susceptibility is isotropic
-(Eq. \ref{eq:K-isotropic}) and $\chi << 1$, the magnetization
-$\tilde{\mathbf{M}}$ (Eq. \ref{eq:M-tilde}) can be approximated
-as follows:
-\begin{equation}
-\tilde{\mathbf{M}} \approx \chi \, \tilde{\mathbf{H}}_{0} \: ,
-\label{eq:M-tilde-chi-H0}
-\end{equation}
-which is the classical equation describing the induced
-magnetization in applied geophysics \citep[p. 87]{blakely1996}.
-Notice that, in this particular case, the magnetization is
-parallel to the inducing field $\tilde{\mathbf{H}}_{0}$.
-
-FALAR DO CASO EM QUE A INDUCAO EH PARALELA A UM EIXO DO ELIPSOIDE
 
@@
 \citet[Eq. ~38]{clark1986}.
+
+For the particular case in which the susceptibility is isotropic,
+the susceptibility tensor is defined according to Eq. \ref{eq:K-isotropic}.
+In this case, the magnetization $\tilde{\mathbf{M}}$ (Eq. \ref{eq:M-tilde-remanence})
+can be rewritten as follows:
+\begin{equation}
+\tilde{\mathbf{M}} = \left[ \begin{array}{ccc}
+\frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{11}} & 0 & 0 \\
+0 & \frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{22}} & 0 \\
+0 & 0 & \frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{33}}
+\end{array} \right] \left( \chi \, \tilde{\mathbf{H}}_{0} +
+\tilde{\mathbf{M}}_{R} \right) \: .
+\label{eq:M-tilde-K-isotropic}
+\end{equation}
+This equation is in perfect agreement with those presented 
+by \citet[Eqs. ~13--15]{guo2001}.
+The first term, depending on the inducing field $\tilde{\mathbf{H}}_{0}$, 
+represents the induced magnetization whereas the term depending on
+$\tilde{\mathbf{M}}_{R}$ is the remanent magnetization.
+Equation \ref{eq:M-tilde-K-isotropic} reveals that, as pointed out by \citet{maxwell1873},
+the induced magnetization opposes the inducing field 
+if it is parallel to an ellipsoid axis, 
+independently of the ellipsoid type. Otherwise, the
+magnetization is not necessarily parallel to
+the inducing field.
+If we additionally consider that $\chi << 1$, the magnetization
+$\mathbf{M}$ (Eq. \ref{eq:M-KH}), defined in the main coordinate system,
+can be approximated as follows:
+\begin{equation}
+\mathbf{M} \approx \chi \, \mathbf{H}_{0} +
+\mathbf{M}_{R} \: ,
+\label{eq:M-approx}
+\end{equation}
+which is the classical equation describing the resultant
+magnetization in applied geophysics \citep[p. ~89]{blakely1996}.
+Notice that, in this particular case, the induced magnetization
+is parallel to the inducing field $\mathbf{H}_{0}$,
+whether it is parallel to an ellipsoid axis or not.
 
@@
 The code is implemented in Python language,
-by using use the NumPy and SciPy libraries \citep{vanderwalt2011},
+by using the NumPy and SciPy libraries \citep{vanderwalt2011},
 as part of the open-source source library
@@
 (\url{https://software-carpentry.org/}) and at the
-description of the doctest module that is available
+description of the doctest module available
 in the documentation for Python 2.X 

### 2017-02-14 manuscript/manuscript.tex
include refs about anisotropy

@@
 By presuming that this uniform magnetization is due to
-induction, he postulated that the resulting magnetic
-field (intensity) at all points within the body must
-also be uniform and parallel to the magnetization.
-As a consequence, the gravitational potential 
-$U$ at points within the body must be a quadratic 
+induction and that it is proportional to the resulting
+magnetic field (intensity) inside the body, he postulated 
+that the resulting field must also be uniform and 
+parallel to the magnetization. This uniformity is due to
+the fact that the resulting field is defined as the
+negative gradient of the magnetic scalar potential
+within the body.
+As a consequence of this uniformity, 
+the gravitational potential $U$ at points within the 
+body must be a quadratic 
 function of the spatial coordinates.
@@
 
-Self-demagnetization demagnetization gives rise to shape 
-anisotropy.
-
-Self-demagnetization is a function of the shape of 
-the body.
-
+Another particularity of ellipsoids are that they are
+the only bodies which enable an analytical computation 
+of its self-demagnetization.
 The self-demagnetization contributes to decrease the
 magnitude of the magnetization along the shortest 
-dimensions of a body.
-
-Ellipsoids are the only bodies which enable an
-analytical computation of its self-demagnetization.
-
-Ellipsoids can assume a wide range of shapes and
-therefore can be used to represent different geological
-bodies.
-
+axes of a body.
+It is a function of the shape of the body and gives rise
+to shape anisotropy \citep{thompson1986, clark1999, tauxe2003}.
 It is well-known by that the self-demagnetization can 
@@
 
-As we can see, a vast literature about the magnetic
+A vast literature about the magnetic
 modelling of ellipsoidal bodies was developed in which 
@@
 Nevertheless, interest in this subject has not yet died
-out, as is evidenced by the list of modern papers in this
+out, as is evidenced by a list of modern papers in this
 field.
@@
 and researching geophysics.
-
 To fill this gap, we provide here a set of routines to 
@@
 three angles $\alpha$, $\beta$, and $\gamma$.
+
+DESCREVER A ORIENTACAO EM FUNCAO DOS ANGULOS DE GEOLOGIA ESTRUTURAL
+\citep{clark1986, allmendinger2012}
+
 The points $(x, y, z)$ located on the surface of this ellipsoidal body

### 2017-02-14 manuscript/manuscript.tex
orientation angles strike, dip and rake

@@
 For convenience, we denominate this coordinate system as 
-\textit{main coordinate system}.
+\textit{main coordinate system} (Fig. \ref{fig:orientation-angles}a).
 Let us consider an ellipsoidal body with centre at the point $(x_{c}, y_{c}, z_{c})$,
-semi-axes defined by positive constants $a$, $b$, $c$, 
-where $a > b > c$, and orientation defined by
-three angles $\alpha$, $\beta$, and $\gamma$.
-
-DESCREVER A ORIENTACAO EM FUNCAO DOS ANGULOS DE GEOLOGIA ESTRUTURAL
-\citep{clark1986, allmendinger2012}
+orientation defined by angles \textit{strike}, \textit{dip}, and
+\textit{rake} (Fig. \ref{fig:orientation-angles}a), and semi-axes defined by
+positive constants $a$, $b$, $c$ (Fig. \ref{fig:orientation-angles}b).
+The angles strike, dip and rake are commonly used to
+define the orientation of lines in structural geology
+\citep{clark1986, allmendinger2012}.
+
+PAREI AQUI
 
@@
 
-Figure \ref{fig:fig1} TEXT TEXT TEXT Fig. \ref{fig:fig1} TEXT TEXT TEXT (Fig. \ref{fig:fig1})
+Figure \ref{fig:figxxx} TEXT TEXT TEXT Fig. \ref{fig:figxxx} TEXT TEXT TEXT (Fig. \ref{fig:figxxx})
 
@@
 \begin{figure}[t]
+\includegraphics[width=8.3cm]{figures/structural_orientation_angles.png}
+\caption{Schematic representation of the coordinate systems used to
+represent an ellipsoidal body. 
+(a) Main coordinate system with axes $x$, $y$, and $z$.
+The dark gray plane contains the center $(x_{c}, y_{c}, z_{c})$
+(white circle) and two unit vectors, $\mathbf{u}$ and $\mathbf{w}$, defining two
+semi-axes of the ellipsoidal body. For triaxial and prolate ellipsoids,
+$\mathbf{u}$ and $\mathbf{w}$ define, respectively, 
+the semi-axes $a$ and $b$. For oblate ellipsoids, $\mathbf{u}$ and 
+$\mathbf{w}$ define the semi-axes $b$ and $c$, respectively.
+The strike direction is defined by the intersection of the
+dark gray plane and the horizontal plane (represented in light gray),
+which contains the $x$ and $y$ axes. The angle between "minus $x$"
+and the strike direction is called \textit{strike}. The angle
+between the horizontal plane and the dark gray plane
+is called \textit{dip}. The line containing the unit vector
+$\mathbf{u}$ defines the \textit{plunge direction}. The projection
+of the plunge direction on the horizontal plane is called
+\textit{plunge azimuth direction}. (b) Local coordinate system
+with origin at the ellipsoid center $(x_{c}, y_{c}, z_{c})$
+(black dot) and axes defined by unit vectors $\mathbf{v}_{1}$,
+$\mathbf{v}_{2}$, and $\mathbf{v}_{3}$. These unit vectors
+define the semi-axes $a$, $b$, and $c$ of triaxial, prolate,
+and oblate ellipsoids. Notice that, for triaxial and prolate ellipsoids,
+the unit vectors $\mathbf{u}$ and $\mathbf{w}$ shown in (a) coincide
+with $\mathbf{v}_{1}$ and $\mathbf{v}_{2}$, respectively. For 
+oblate ellipsoids, the unit vectors $\mathbf{u}$ and $\mathbf{w}$ 
+shown in (a) coincide with $\mathbf{v}_{2}$ and $\mathbf{v}_{3}$,
+respectively.}
+\label{fig:orientation-angles}
+\end{figure}
+
+\begin{figure}[t]
 \includegraphics[width=8.3cm]{figures/demag_factors.pdf}
 \caption{TEXT}
-\label{fig:fig1}
+\label{fig:figxxx}
 \end{figure}

### 2017-02-15 manuscript/manuscript.tex
include the relationship between alpha, gamma and delta and strike, dip and rake

@@
 \textit{main coordinate system} (Fig. \ref{fig:orientation-angles}a).
-Let us consider an ellipsoidal body with centre at the point $(x_{c}, y_{c}, z_{c})$,
-orientation defined by angles \textit{strike}, \textit{dip}, and
-\textit{rake} (Fig. \ref{fig:orientation-angles}a), and semi-axes defined by
+Let us consider an ellipsoidal body with centre at the point 
+$(x_{c}, y_{c}, z_{c})$, orientation defined by three angles 
+$\varepsilon$, $\zeta$, and $\eta$ (Fig. \ref{fig:orientation-angles}a), 
+and semi-axes defined by
 positive constants $a$, $b$, $c$ (Fig. \ref{fig:orientation-angles}b).
-The angles strike, dip and rake are commonly used to
+The angles $\varepsilon$, $\zeta$, and $\eta$ are called \textit{strike}, 
+\textit{dip}, and \textit{rake}, respectively, and are commonly used to
 define the orientation of lines in structural geology
 \citep{clark1986, allmendinger2012}.
-
-PAREI AQUI
-
 The points $(x, y, z)$ located on the surface of this ellipsoidal body
@@
 \end{equation}
-and $\mathbf{V}$ is an orthogonal matrix whose columns are defined
-by unit vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$, and $\mathbf{v}_{3}$.
-
-The vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$, and $\mathbf{v}_{3}$ 
-depend on the orientation angles 
-$\alpha$, $\beta$, $\gamma$ and are defined 
+and $\mathbf{V}$ is an orthogonal matrix whose first, second and third columns 
+are defined by unit vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$, and $\mathbf{v}_{3}$
+(Fig. \ref{fig:orientation-angles}b), respectively, depending on the ellipsoid type.
+These unit vectors depend on orientation angles $\alpha$, 
+$\beta$, and $\gamma$, which are not commonly used in
+geosciences. These angles, however, can be defined from
+$\varepsilon$, $\zeta$, and $\eta$ (Fig. \ref{fig:orientation-angles}a)
 as follows \citep{clark1986}:
+\begin{equation}
+\alpha = \varepsilon - \cos^{-1} \left[ \frac{\cos \eta}
+{\left( 1 - \sin^{2} \zeta \, \sin^{2} \eta \right)^{\frac{1}{2}}}\right] \: ,
+\label{eq:alpha}
+\end{equation}
+\begin{equation}
+\gamma = \tan^{-1} \left( \frac{\cos \zeta}{\sin \zeta \, \cos \eta}\right)
+\label{eq:gamma}
+\end{equation}
+and
+\begin{equation}
+\delta = \sin^{-1} \left( \sin \zeta \, \sin \eta \right) \: ,
+\label{eq:delta}
+\end{equation}
+where $-90^{\circ} \leq \gamma \leq 90^{\circ}$ and
+$0 \leq \delta \leq 90^{\circ}$.
+Then, given the orientation angles $\varepsilon$, $\zeta$, and $\eta$ (Fig. \ref{fig:orientation-angles}a and Eqs. \ref{eq:alpha}, \ref{eq:gamma}, and
+\ref{eq:delta}), we define the unit vectors
+$\mathbf{v}_{1}$, $\mathbf{v}_{2}$, and $\mathbf{v}_{3}$
+(Fig. \ref{fig:orientation-angles}b) according to the ellipsoid type.
+For triaxial ellipsoids (i.e., $a > b > c$), these unit vectors are 
+given by \citep{clark1986}:
 \begin{equation}
@@
 \end{equation}
-For triaxial ellipsoids (i.e., $a > b > c$), the orthogonal matrix
-$\mathbf{V}$ (Eq. \ref{eq:A}) is calculated by using Eqs.
-\ref{eq:v1_triaxial_prolate}, \ref{eq:v2_triaxial_prolate}, and
-\ref{eq:v3_triaxial_prolate} as follows:
-\begin{equation}
-\mathbf{V} = \left[ \begin{array}{ccc}
-\mathbf{v}_{1} & \mathbf{v}_{2} & \mathbf{v}_{3}
-\end{array} \right] \: .
-\label{eq:V_triaxial_prolate}
-\end{equation}
-Similarly, the matrix $\mathbf{V}$ (Eq. \ref{eq:A}) for
-prolate ellipsoids (i.e., $a > b = c$) is calculated according
-to Eq. \ref{eq:V_triaxial_prolate} by using Eqs.
-\ref{eq:v1_triaxial_prolate}, \ref{eq:v2_triaxial_prolate}, and
+Similarly, the unit vectors defining the matrix $\mathbf{V}$ (Eq. \ref{eq:A}) for
+prolate ellipsoids (i.e., $a > b = c$) are calculated
+by using Eqs. \ref{eq:v1_triaxial_prolate}, \ref{eq:v2_triaxial_prolate}, and
 \ref{eq:v3_triaxial_prolate}, but with $\gamma = 0^{\circ}$
 \citep{emerson1985}.
-Finally, the matrix $\mathbf{V}$ (Eq. \ref{eq:A}) for
-oblate ellipsoids (i.e., $a < b = c$) is calculated by 
-using Eqs. \ref{eq:v1_triaxial_prolate}, \ref{eq:v2_triaxial_prolate}, and
-\ref{eq:v3_triaxial_prolate}, with $\gamma = 0^{\circ}$, as follows
-\citep{emerson1985}:
-\begin{equation}
-\mathbf{V} = \left[ \begin{array}{ccc}
-\mathbf{v}_{2} & \mathbf{v}_{1} & -\mathbf{v}_{3}
+Finally, the unit vectors defining the matrix $\mathbf{V}$ (Eq. \ref{eq:A}) for
+oblate ellipsoids (i.e., $a < b = c$) are calculated as follows:
+\begin{equation}
+\mathbf{v}_{1} = \left[\begin{array}{c} 
+                  -\cos\alpha \; \sin\gamma \; \sin\delta + \sin\alpha \; \cos\gamma \\               
+                  -\sin\alpha \; \sin\gamma \; \sin\delta - \cos\alpha \; \cos\gamma \\ 
+                  \sin\gamma \; \cos\delta
+                  \end{array} \right] \: ,
+\label{eq:v1_oblate}
+\end{equation}
+\begin{equation}
+\mathbf{v}_{2} = \left[\begin{array}{c} 
+                  -\cos\alpha \; \cos\delta \\
+                  -\sin\alpha \; \cos\delta \\
+                  -\sin\delta
+                  \end{array} \right] \: ,
+\label{eq:v2_oblate}
+\end{equation}                   
+\begin{equation}                    
+\mathbf{v}_{3} = \left[\begin{array}{c} 
+                  \sin\alpha \; \sin\gamma + \cos\alpha \; \cos\gamma \; \sin\delta \\                    
+                  -\cos\alpha \; \sin\gamma + \sin\alpha \; \cos\gamma \; \sin\delta \\
+                  -\cos\gamma \; \cos\delta
                   \end{array} \right] \: .
-\label{eq:V_oblate}
-\end{equation}
-The orientation of the semi-axes $a$, $b$, and $c$ are defined 
-by the first, second, and third columns of the matrix 
-$\mathbf{V}$ given by Eq. \ref{eq:V_triaxial_prolate},
-in the case of a triaxial or prolate ellipsoid, or the
-matrix $\mathbf{V}$ given by Eq. \ref{eq:V_oblate},
-in the case of an oblate ellipsoid.
-
+\label{eq:v3_oblate}
+\end{equation}
+These formulas are similar to those presented by \citep{emerson1985}.
+
+%The orientation of the semi-axes $a$, $b$, and $c$ are defined 
+%by the first, second, and third columns of the matrix 
+%$\mathbf{V}$ given by Eq. \ref{eq:V_triaxial_prolate},
+%in the case of a triaxial or prolate ellipsoid, or the
+%matrix $\mathbf{V}$ given by Eq. \ref{eq:V_oblate},
+%in the case of an oblate ellipsoid.
 The magnetic modelling of an ellipsoidal body is commonly performed
@@
 with the body semi-axes
-and has the origin coincident with the body centre.
+and has the origin coincident with the body centre
+(Fig. \ref{fig:orientation-angles}b).
 For convenience, we denominate this particular coordinate 
@@
 are defined in Eq. \ref{eq:ellipsoid_surface} and the matrix $\mathbf{V}$
-is defined according to Eqs. \ref{eq:V_triaxial_prolate} or
-\ref{eq:V_oblate}, depending on the ellipsoid type.
-%Similarly, we may properly use the orthogonality of 
-%matrix $\mathbf{V}$ to transform a generic 
-%linear system $\mathbf{M} \mathbf{p} = \mathbf{d}$,
-%referred to the main coordinate system, into a new
-%linear system 
-%$\tilde{\mathbf{M}} \, \tilde{\mathbf{p}} = \tilde{\mathbf{d}}$,
-%referred to a local coordinate system, 
-%as follows:
-%\begin{equation}
-%\underbrace{\mathbf{V}^{\top} \mathbf{M} \mathbf{V}}_{\tilde{\mathbf{M}}} \, 
-%\underbrace{\mathbf{V}^{\top} \mathbf{p}}_{\tilde{\mathbf{p}}} = 
-%\underbrace{\mathbf{V}^{\top} \mathbf{d}}_{\tilde{\mathbf{d}}} \: .
-%\label{eq:matrix-transformation}
-%\end{equation}
+(Eq. \ref{eq:A}) is defined according to the ellipsoid type.
 
@@
 In general, the susceptibility tensor $\mathbf{K}$ is represented,
-in the main coordinate system, as follows:
+in the main coordinate system (Fig. \ref{fig:orientation-angles}a), as follows:
 \begin{equation}
@@
 body. However, the mathematical developments are conveniently 
-performed in the local coordinate system related to the
-respective ellipsoidal body.
+performed in the local coordinate system (Fig. \ref{fig:orientation-angles}b)
+related to the respective ellipsoidal body.
 
@@
 $f(\mathbf{r})$ (Eq. \ref{eq:f}) from the 
-main coordinate system into a new scalar function 
+main coordinate system (Fig. \ref{fig:orientation-angles}a)
+into a new scalar function 
 $\tilde{f}(\tilde{\mathbf{r}})$ referred to the
-local coordinate system.
+local coordinate system (Fig. \ref{fig:orientation-angles}b).
 The function $\tilde{f}(\tilde{\mathbf{r}})$ was first 
@@
 (Eq. \ref{eq:H-M-uniform}) can be transformed
-from the main coordinate system to a local coordinate system
-as follows:
+from the main coordinate system (Fig. \ref{fig:orientation-angles}a) 
+to the local coordinate system (Fig. \ref{fig:orientation-angles}b) as follows:
 \begin{equation}
@@
 function $f(\mathbf{r})$ (Eq. \ref{eq:f}),
-which is defined in the main coordinate system.
+which is defined in the main coordinate system (Fig. \ref{fig:orientation-angles}a).
 It can be shown (Appendix A), however, that the
@@
 If we additionally consider that $\chi << 1$, the magnetization
-$\mathbf{M}$ (Eq. \ref{eq:M-KH}), defined in the main coordinate system,
+$\mathbf{M}$ (Eq. \ref{eq:M-KH}), defined in the main coordinate system
+(Fig. \ref{fig:orientation-angles}a),
 can be approximated as follows:
@@
 (Eq. \ref{eq:f}) from the
-main coordinate system to a local coordinate system.
+main coordinate system (Fig. \ref{fig:orientation-angles}a)
+to the local coordinate system (Fig. \ref{fig:orientation-angles}b).
 For convenience, let us rewrite Eq. 
@@
 the $\tilde{x}$-, $\tilde{y}$-, and $\tilde{z}$-axis, respectively, 
-of its local coordinate system, where $a > b > c > 0$. 
+of its local coordinate system (Fig. \ref{fig:orientation-angles}b), where $a > b > c > 0$. 
 This ellipsoid is defined by the following equation:
@@
 $c$ oriented along the $\tilde{x}$-, $\tilde{y}$-, and 
-$\tilde{z}$-axis, respectively, of its local coordinate system, 
-where $a > b = c > 0$. 
+$\tilde{z}$-axis, respectively, of its local coordinate system
+(Fig. \ref{fig:orientation-angles}b), where $a > b = c > 0$. 
 In this case, the Eq. defining the surface of the ellipsoid
@@
 represent an ellipsoidal body. 
-(a) Main coordinate system with axes $x$, $y$, and $z$.
-The dark gray plane contains the center $(x_{c}, y_{c}, z_{c})$
+(a) Main coordinate system with axes $x$, $y$, and $z$ pointing to
+North, East, ans down, respectively.
+The dark gray plane contains the centre $(x_{c}, y_{c}, z_{c})$
 (white circle) and two unit vectors, $\mathbf{u}$ and $\mathbf{w}$, defining two
@@
 dark gray plane and the horizontal plane (represented in light gray),
-which contains the $x$ and $y$ axes. The angle between "minus $x$"
-and the strike direction is called \textit{strike}. The angle
-between the horizontal plane and the dark gray plane
+which contains the $x$ and $y$ axes. The angle $\varepsilon$ 
+between "minus $x$" and the strike direction is called \textit{strike}.
+The angle $\zeta$ between the horizontal plane and the dark gray plane
 is called \textit{dip}. The line containing the unit vector
-$\mathbf{u}$ defines the \textit{plunge direction}. The projection
+$\mathbf{u}$ defines the \textit{plunge direction}. 
+The angle $\eta$ between the strike direction and the plunge direction
+is called \textit{rake}. The projection
 of the plunge direction on the horizontal plane is called
 \textit{plunge azimuth direction}. (b) Local coordinate system
-with origin at the ellipsoid center $(x_{c}, y_{c}, z_{c})$
+with origin at the ellipsoid centre $(x_{c}, y_{c}, z_{c})$
 (black dot) and axes defined by unit vectors $\mathbf{v}_{1}$,
@@
 define the semi-axes $a$, $b$, and $c$ of triaxial, prolate,
-and oblate ellipsoids. Notice that, for triaxial and prolate ellipsoids,
+and oblate ellipsoids in the same way.
+For triaxial and prolate ellipsoids,
 the unit vectors $\mathbf{u}$ and $\mathbf{w}$ shown in (a) coincide

### 2017-02-15 manuscript/manuscript.tex
include the demagnetizing factors test

@@
 are defined by unit vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$, and $\mathbf{v}_{3}$
-(Fig. \ref{fig:orientation-angles}b), respectively, depending on the ellipsoid type.
+(Fig. \ref{fig:orientation-angles}b), respectively.
 These unit vectors depend on orientation angles $\alpha$, 
@@
 \end{equation}
-Similarly, the unit vectors defining the matrix $\mathbf{V}$ (Eq. \ref{eq:A}) for
-prolate ellipsoids (i.e., $a > b = c$) are calculated
+Similarly, the unit vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$, and $\mathbf{v}_{3}$
+for prolate ellipsoids (i.e., $a > b = c$) are calculated
 by using Eqs. \ref{eq:v1_triaxial_prolate}, \ref{eq:v2_triaxial_prolate}, and
@@
 \citep{emerson1985}.
-Finally, the unit vectors defining the matrix $\mathbf{V}$ (Eq. \ref{eq:A}) for
-oblate ellipsoids (i.e., $a < b = c$) are calculated as follows:
+Finally, the unit vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$, and $\mathbf{v}_{3}$
+for oblate ellipsoids (i.e., $a < b = c$) are calculated as follows:
 \begin{equation}
@@
 
-%The orientation of the semi-axes $a$, $b$, and $c$ are defined 
-%by the first, second, and third columns of the matrix 
-%$\mathbf{V}$ given by Eq. \ref{eq:V_triaxial_prolate},
-%in the case of a triaxial or prolate ellipsoid, or the
-%matrix $\mathbf{V}$ given by Eq. \ref{eq:V_oblate},
-%in the case of an oblate ellipsoid.
 The magnetic modelling of an ellipsoidal body is commonly performed
@@
 coincide with the ellipsoid axes, the matrix $\mathbf{U}$ is
-equal to the matrix $\mathbf{V}$ (Eqs. \ref{eq:V_triaxial_prolate}
-and \ref{eq:V_oblate}), depending on the ellipsoid type.
+equal to the matrix $\mathbf{V}$ (Eq. \ref{eq:A}),
+depending on the ellipsoid type.
 Another important particular case is that in which the
@@
 By properly using the orthogonality of matrix $\mathbf{V}$ 
-(Eqs. \ref{eq:V_triaxial_prolate} and \ref{eq:V_oblate}),
+(Eq. \ref{eq:A}),
 the magnetic field $\mathbf{H}(\mathbf{r})$ 
@@
 \ref{eq:M-tilde} and \ref{eq:M-tilde-remanence}) is a diagonal 
-matrix and $\mathbf{V}$ (Eqs. \ref{eq:V_triaxial_prolate} and
-\ref{eq:V_oblate}) is an orthogonal matrix.
+matrix and $\mathbf{V}$ (Eq. \ref{eq:A}) is an orthogonal matrix.
 This equation shows that, for the particular case 
@@
 (Eq. \ref{eq:n-tilde-dagger-33-triaxial}). \citet{clark1986} presented similar
-formulas.
+formulas. It can be shown that these demagnetizing factors
+satisfy the conditions
+$\tilde{n}^{\dagger}_{11} + \tilde{n}^{\dagger}_{22} + \tilde{n}^{\dagger}_{33} = 1$
+and
+$\tilde{n}^{\dagger}_{11} < \tilde{n}^{\dagger}_{22} < \tilde{n}^{\dagger}_{33}$.
 
@@
 where $\tilde{n}^{\dagger}_{33} = \tilde{n}^{\dagger}_{22}$, 
-which uses the $\tilde{n}^{\dagger}_{11}$ defined in 
-Eq. \ref{eq:n-tilde-dagger-11-prolate}, and $m = a/b$.
+with $\tilde{n}^{\dagger}_{11}$ defined in 
+Eq. \ref{eq:n-tilde-dagger-11-prolate} and $m = a/b$.
 The detailed deduction of the demagnetizing factors 
@@
 can be found, for example, in \citet{stoner1945}. 
-These formulas were posteriorly 
-presented by \citet{emerson1985}.
+These formulas were posteriorly presented by \citet{emerson1985}.
+It can be shown that these demagnetizing factors
+satisfy the conditions
+$\tilde{n}^{\dagger}_{11} + 2 \; \tilde{n}^{\dagger}_{22} = 1$
+and
+$\tilde{n}^{\dagger}_{11} < \tilde{n}^{\dagger}_{22}$.
 
@@
 1 - \frac{m}{\left( 1 - m^{2} \right)^{\frac{1}{2}}} \cos^{-1}m
-\right] \: ,
+\right]
 \label{eq:n-tilde-dagger-11-oblate}
 \end{equation}
-where $\tilde{n}^{\dagger}_{22}$ and $\tilde{n}^{\dagger}_{33}$ 
-are calculated according to Eq.
-\ref{eq:n-tilde-dagger-22-prolate}, but with $\tilde{n}^{\dagger}_{11}$ 
-defined in Equation \ref{eq:n-tilde-dagger-11-oblate}, 
-and $m = a/b$.
+and
+\begin{equation}
+\tilde{n}^{\dagger}_{22} = \frac{1}{2} \left(1 - \tilde{n}^{\dagger}_{11} \right) \: ,
+\label{eq:n-tilde-dagger-22-oblate}
+\end{equation}
+where $\tilde{n}^{\dagger}_{33} = \tilde{n}^{\dagger}_{22}$, 
+with $\tilde{n}^{\dagger}_{11}$ defined in 
+Eq. \ref{eq:n-tilde-dagger-11-oblate} and $m = a/b$.
 The detailed deduction of these demagnetizing factors 
@@
 $\tan^{-1}x = \cos^{-1}(1/\sqrt{x^{2} + 1})$, $x > 0$.
+It can be shown that these demagnetizing factors
+satisfy the conditions
+$\tilde{n}^{\dagger}_{11} + 2 \; \tilde{n}^{\dagger}_{22} = 1$
+and
+$\tilde{n}^{\dagger}_{11} > \tilde{n}^{\dagger}_{22}$.
 
@@
 
-Figure \ref{fig:figxxx} TEXT TEXT TEXT Fig. \ref{fig:figxxx} TEXT TEXT TEXT (Fig. \ref{fig:figxxx})
+We simulate a triaxial ellipsoid with semi-axes 
+$a_{0} = 1000$ \unit{m}, $b_{0} = 700$ \unit{m}, and $c_{0} = 200$ \unit{m}.
+Then we use this ellipsoid as a reference to generate
+100 different triaxial ellipsoids and calculate
+their demagnetizing factors $\tilde{n}^{\dagger}_{11}$,
+$\tilde{n}^{\dagger}_{22}$, and $\tilde{n}^{\dagger}_{33}$ 
+by using Eqs. \ref{eq:n-tilde-dagger-11-triaxial},
+\ref{eq:n-tilde-dagger-22-triaxial}, and \ref{eq:n-tilde-dagger-33-triaxial}.
+The semi-axes of these 100 ellipsoids are given by
+$a = a_{0} + u \; b_{0}$, $b = b_{0} + u \; b_{0}$, and 
+$c = c_{0} + u \; b_{0}$, where $0 \leq u \leq 10$.
+Notice that, for $u = 0$, the resulting semi-axes are equal those
+of the reference ellipsoid.
+The larger the variable $u$, the larger the resulting semi-axes
+$a$, $b$, and $c$, but the smaller the relative difference between
+them.
+Consequently, the resulting ellipsoids obtained from the semi-axes
+$a$, $b$, and $c$ become more spherical as $u$ increases.
+In this case, the demagnetizing factors $\tilde{n}^{\dagger}_{11}$
+(Eq. \ref{eq:n-tilde-dagger-11-triaxial}),
+$\tilde{n}^{\dagger}_{22}$ (Eq. \ref{eq:n-tilde-dagger-22-triaxial}),
+and
+$\tilde{n}^{\dagger}_{33}$ (Eq. \ref{eq:n-tilde-dagger-33-triaxial})
+tend to $1/3$ \citep[e.g.,][]{stoner1945}.
+
+Figure \ref{fig:demag-factors}a shows the calculated 
+demagnetizing factors $\tilde{n}^{\dagger}_{11}$ (in red),
+$\tilde{n}^{\dagger}_{22}$ (in green), and
+$\tilde{n}^{\dagger}_{33}$ (in blue) for the 
+100 triaxial ellipsoids.
+The result shows that the relative difference
+between the demagnetizing factors is large for
+small values of $u$ and decreases as $u$ increases.
+In this case, all demagnetizing factors tend to $1/3$, according
+to what we know from theory. 
+Besides, Fig. \ref{fig:demag-factors}a confirms that the demagnetizing
+factors satisfy the condition
+$\tilde{n}^{\dagger}_{11} < \tilde{n}^{\dagger}_{22} < \tilde{n}^{\dagger}_{33}$
+independently of the value of $u$.
+
+We have also simulated 100 different prolate
+ellipsoids with semi-axes $a = m \; b_{0}$ and $b = b_{0}$,
+where $1.02 \leq m \leq 10$ and $b_{0} = 1000$ \unit{m},
+and calculate their demagnetizing factors 
+$\tilde{n}^{\dagger}_{11}$ and $\tilde{n}^{\dagger}_{22}$
+by using Eqs. \ref{eq:n-tilde-dagger-11-prolate} and
+\ref{eq:n-tilde-dagger-22-prolate}, respectively.
+Similarly, we simulated 100 different oblate
+ellipsoids with semi-axes $a = m \; b_{0}$ and $b = b_{0}$,
+where $0.02 \leq m \leq 0.98$ and $b_{0} = 1000$ \unit{m},
+and calculate their demagnetizing factors 
+$\tilde{n}^{\dagger}_{11}$ and $\tilde{n}^{\dagger}_{22}$
+by using Eqs. \ref{eq:n-tilde-dagger-11-oblate} and
+\ref{eq:n-tilde-dagger-22-oblate}, respectively.
+
+Figures \ref{fig:demag-factors}b and c show the results obtained for
+the 100 prolate and the 100 oblate ellipsoids, respectively.
+As expected from theory, the demagnetizing factors
+$\tilde{n}^{\dagger}_{11}$ (red line in Fig. \ref{fig:demag-factors}b)
+and
+$\tilde{n}^{\dagger}_{22}$ (green line in Fig. \ref{fig:demag-factors}b)
+calculated for the prolate ellipsoids are close to $1/3$ for $m$ close to $1$.
+Besides, these demagnetizing factors satisfy the condition 
+$\tilde{n}^{\dagger}_{11} < \tilde{n}^{\dagger}_{22}$ for all values
+of $m$.
+The result obtained for the oblate ellipsoids (Fig. \ref{fig:demag-factors}c)
+are also in perfect agreement with theory.
+The demagnetizing factors
+$\tilde{n}^{\dagger}_{11}$ (in red) and
+$\tilde{n}^{\dagger}_{22}$ (in green), which were calculated by using
+Eqs. \ref{eq:n-tilde-dagger-11-oblate} and \ref{eq:n-tilde-dagger-22-oblate},
+respectively, 
+are close to $1/3$ for $m$ close to $0$ and satisfy the condition 
+$\tilde{n}^{\dagger}_{11} > \tilde{n}^{\dagger}_{22}$ for all values
+of $m$.
 
@@
 $v_{kj}$, $j = 1, 2, 3$, are the elements of the matrix
-$\mathbf{V}$ (Eq. \ref{eq:V_triaxial_prolate} or \ref{eq:V_oblate}),
+$\mathbf{V}$ (Eq. \ref{eq:A}),
 and $c_{k}$ is a constant defined by the coordinates
@@
 {\partial r_{i} \, \partial r_{j}}$ and
-$\mathbf{V}$ is defined by Eqs. 
-\ref{eq:V_triaxial_prolate} or
-\ref{eq:V_oblate}, depending on the ellipsoid
-type. As one may noticed, the matrices $\mathbf{F}(\mathbf{r})$ and
+$\mathbf{V}$ (Eq. \ref{eq:A}) is defined according
+to the ellipsoid type. As one may noticed, 
+the matrices $\mathbf{F}(\mathbf{r})$ and
 $\tilde{\mathbf{F}}(\tilde{\mathbf{r}})$ represent the Hessians
@@
 By properly using the orthogonality of the matrix
-$\mathbf{V}$, we may rewrite Eq. \ref{eq:F-V-F-tilde-VT}
+$\mathbf{V}$ (Eq. \ref{eq:A}), we may rewrite Eq. \ref{eq:F-V-F-tilde-VT}
 as follows:
@@
 \includegraphics[width=8.3cm]{figures/demag_factors.pdf}
-\caption{TEXT}
-\label{fig:figxxx}
+\caption{(a) Comparison between the demagnetizing factors
+$\tilde{n}^{\dagger}_{11}$ (in red),
+$\tilde{n}^{\dagger}_{22}$ (in green), and
+$\tilde{n}^{\dagger}_{33}$ (in blue)
+produced by 100 triaxial ellipsoids with semi-axes
+$a = a_{0} + u \; b_{0}$, $b = b_{0} + u \; b_{0}$, and 
+$c = c_{0} + u \; b_{0}$, where $0 \leq u \leq 10$ and
+$b_{0} = 700$ \unit{m}.
+The demagnetizing factors were calculated
+by using Eqs. \ref{eq:n-tilde-dagger-11-triaxial},
+\ref{eq:n-tilde-dagger-22-triaxial}, and \ref{eq:n-tilde-dagger-33-triaxial}.
+(b) Comparison between the demagnetizing factors
+$\tilde{n}^{\dagger}_{11}$ (in red) and
+$\tilde{n}^{\dagger}_{22}$ (in green)
+produced by 100 prolate ellipsoids with semi-axes
+$a = m \; b_{0}$ and $b = b_{0}$, where $1.02 \leq m \leq 10$ and
+$b_{0} = 1000$ \unit{m}.
+The demagnetizing factors were calculated
+by using Eqs. \ref{eq:n-tilde-dagger-11-prolate} and
+\ref{eq:n-tilde-dagger-22-prolate}.
+(c) Comparison between the demagnetizing factors
+$\tilde{n}^{\dagger}_{11}$ (in red) and
+$\tilde{n}^{\dagger}_{22}$ (in green)
+produced by 100 oblate ellipsoids with semi-axes
+$a = m \; b_{0}$ and $b = b_{0}$, where $0.02 \leq m \leq 0.98$ and
+$b_{0} = 1000$ \unit{m}.
+The demagnetizing factors were calculated
+by using Eqs. \ref{eq:n-tilde-dagger-11-oblate} and
+\ref{eq:n-tilde-dagger-22-oblate}.
+The horizontal black line represent the value $1/3$.}
+\label{fig:demag-factors}
 \end{figure}

### 2017-02-16 manuscript/manuscript.tex
include a geophysical descritpion of the susceptibility tensor in term of the orientation of magnetic minerals

@@
 of determining the magnetic scalar potential produced
-by any body uniformly magnetized in a given direction.
+by any uniformly magnetized body in a given direction.
 By presuming that this uniform magnetization is due to
@@
 the fact that the resulting field is defined as the
-negative gradient of the magnetic scalar potential
-within the body.
+negative gradient of the magnetic scalar potential.
 As a consequence of this uniformity, 
@@
 
-Another particularity of ellipsoids are that they are
+Another particularity of ellipsoids is that they are
 the only bodies which enable an analytical computation 
@@
 axes of a body.
-It is a function of the shape of the body and gives rise
+It is a function of the body shape and gives rise
 to shape anisotropy \citep{thompson1986, clark1999, tauxe2003}.
-It is well-known by that the self-demagnetization can 
+It is well-established in the literature that
+the self-demagnetization can
 be neglected if the body has a susceptibility lower 
@@
 self-demagnetization.
-These examples show the importance of the ellipsoidal
-model in producing trustworthy geological models of
+These examples show the importance of the self-demagnetization 
+and the ellipsoidal model in 
+producing trustworthy geological models of
 high-susceptibility orebodies, which may save significant 
@@
 magnetic susceptibility of the body. 
-In general, the susceptibility tensor $\mathbf{K}$ is represented,
-in the main coordinate system (Fig. \ref{fig:orientation-angles}a), as follows:
+This is a good approximation for bodies at room temperature,
+subjected to an inducing field $\mathbf{H}_{0}$ with 
+strength $\leq 1$ \unit{mT} \citep{rochette1992}.
+In this case, the susceptibility tensor $\mathbf{K}$ is commonly
+represented, in the main coordinate system (Fig. \ref{fig:orientation-angles}a),
+as follows:
 \begin{equation}
@@
 $i = 1, 2, 3$, are unit vectors called 
-\textit{principal directions} \citep{hrouda1982}.
+\textit{principal directions}.
+If the principal susceptibilities are different from
+each other, we say that the body has an
+anisotropy of magnetic susceptibility (AMS).
+The AMS is generally associated to the preferred orientation
+of the grains of magnetic minerals forming the rock
+\citep{fuller1963, uyeda1963, janak1972, hrouda1982, macdonald1987,
+rochette1992}.
 For the particular case in which the principal directions 

### 2017-02-16 manuscript/manuscript.tex
identify the terms related to AMS and shape anisotropy in the resulting magnetization

@@
 It is a function of the body shape and gives rise
-to shape anisotropy \citep{thompson1986, clark1999, tauxe2003}.
+to shape anisotropy \citep{uyeda1963, thompson1986,
+dunlop1997, clark1999, tauxe2003}.
 It is well-established in the literature that
@@
 be neglected if the body has a susceptibility lower 
-than 0.1 SI \citep{austin2014, clark2014, clark1986, 
-emerson1985, eskola1980, guo1998, guo2001, purss2005,
-hillan2013}.
+than 0.1 SI 
+\citep{emerson1985, clark1986, eskola1980, guo1998,
+guo2001, purss2005, hillan2013, austin2014, clark2014}.
 However, neglecting the self-demagnetization in
@@
 of the grains of magnetic minerals forming the rock
-\citep{fuller1963, uyeda1963, janak1972, hrouda1982, macdonald1987,
-rochette1992}.
+\citep{fuller1963, uyeda1963, janak1972, hrouda1982, 
+thompson1986, macdonald1987, rochette1992, dunlop1997,
+tauxe2003}.
 For the particular case in which the principal directions 
@@
 peirce1902, webster1904, kellogg1929, stoner1945, osborn1945,
-macmillan1958, lowes1974,  peake1953, chang1961, clark1986, 
+peake1953, chang1961, macmillan1958, lowes1974,  clark1986, 
 tejedor1995, sttraton2007}.
@@
 Equation \ref{eq:M-tilde-remanence} is consistent with that given by
-\citet[Eq. ~38]{clark1986}.
+\citet[Eq. ~38]{clark1986}. It shows the combined effect of the
+anisotropy of magnetic susceptibility, which is represented by the 
+susceptibility tensor $\tilde{\mathbf{K}}$ and reflects the
+preferred orientation of the magnetic minerals forming the
+body, and the shape anisotropy, which is represented by the
+depolarization tensor $\tilde{\mathbf{N}}^{\dagger}$ and
+reflects the self-demagnetization associated to the body shape.
 

### 2017-02-16 manuscript/manuscript.tex
small change in the text
small changes in text

@@
 (Fig. \ref{fig:orientation-angles}b), respectively.
-These unit vectors depend on orientation angles $\alpha$, 
-$\beta$, and $\gamma$, which are not commonly used in
-geosciences. These angles, however, can be defined from
+These unit vectors are commonly described in terms of auxiliary 
+orientation angles $\alpha$, $\beta$, and $\gamma$, which are not used
+by the geoscientific community. These angles, however, can be defined from
 $\varepsilon$, $\zeta$, and $\eta$ (Fig. \ref{fig:orientation-angles}a)
@@
 Consider a magnetized ellipsoid immersed in
-a uniform magnetic field $\mathbf{H}_{0}$ (in $\unit{Am^{-1}}$).
+a uniform magnetic field $\mathbf{H}_{0}$ (in $\unit{Am^{-1}}$)
+given by
+\begin{equation}
+\mathbf{H}_{0} = \| \mathbf{H}_{0} \| \left[
+\begin{array}{c}
+\cos I \: \cos D \\
+\cos I \: \sin D \\
+\sin I
+\end{array}
+\right] \: ,
+\label{eq:H0}
+\end{equation}
+where $\| \cdot \|$ denotes the Euclidean norm and
+$D$ and $I$ are respectively, the declination and inclination of the 
+local-geomagnetic field in the main coordinate system
+(Fig. \ref{fig:orientation-angles}a).
 This uniform field can be, for example, the main component of the
@@
 the integral is conducted over the variables 
-$x^{\prime}$, $y^{\prime}$ and, $z^{\prime}$ representing
-the coordinates of a point located within the volume $\vartheta$
-of the ellipsoid, $\| \cdot \|$ denotes the Euclidean norm and 
+$x^{\prime}$, $y^{\prime}$ and, $z^{\prime}$ and 
 $\mathbf{M}(\mathbf{r}^{\prime})$ is the magnetization vector
@@
 a point located inside or outside the magnetized body
-\citep{dubois1896}.
+\citep{dubois1896, reitz1992, sttraton2007}.
 
@@
 \textit{principal directions}.
+The unit vectors $\mathbf{u}_{i}$ may be defined
+similarly to $\mathbf{v}_{1}$, $\mathbf{v}_{2}$,
+and $\mathbf{v}_{3}$ (Eqs. \ref{eq:v1_triaxial_prolate},
+\ref{eq:v2_triaxial_prolate}, \ref{eq:v3_triaxial_prolate},
+\ref{eq:v1_oblate}, \ref{eq:v2_oblate}, and \ref{eq:v3_oblate}),
+by a given set of orientation angles $\varepsilon$, $\zeta$,
+and $\eta$ (Eqs. \ref{eq:alpha}, \ref{eq:gamma}, and
+\ref{eq:delta}).
+
 If the principal susceptibilities are different from
@@
 reflects the self-demagnetization associated to the body shape.
+Notice that the resultant magnetization $\tilde{\mathbf{M}}$
+(Eq. \ref{eq:M-tilde-remanence}) does not necessarily have
+the same direction as the inducing field $\tilde{\mathbf{H}}_{0}$.
+The angular difference $\theta$ between the resultant magnetization
+and the inducing field is the same, whether the quantities
+are defined in the main coordinate system (Fig. \ref{fig:orientation-angles}a)
+or local coordinate system (Fig. \ref{fig:orientation-angles}b).
+For convenience, we define $\theta$ (in degrees) in the main coordinate system
+by using the scalar product definition as follows:
+\begin{equation}
+\theta = \frac{180}{\pi} \, \cos^{-1} \left( 
+\frac{\mathbf{M}^{\top}\mathbf{H}_{0}}
+{\| \mathbf{M} \| \; \| \mathbf{H}_{0} \|}\right) \: ,
+\label{eq:theta}
+\end{equation}
+where $\mathbf{M}$ is obtained by pre-multiplying the
+magnetization $\tilde{\mathbf{M}}$ (Eq. \ref{eq:M-tilde-remanence})
+by the orthogonal matrix $\mathbf{V}$ (Eq. \ref{eq:A}),
+which is defined according to the ellipsoid type, and
+$\mathbf{H}_{0}$ is given by Eq. \ref{eq:H0}.
 
@@
 If we additionally consider that $\chi << 1$, the magnetization
-$\mathbf{M}$ (Eq. \ref{eq:M-KH}), defined in the main coordinate system
-(Fig. \ref{fig:orientation-angles}a),
-can be approximated as follows:
+$\mathbf{M}$ (Eq. \ref{eq:M-KH}) defined in the main coordinate system
+(Fig. \ref{fig:orientation-angles}a) can be approximated as follows:
 \begin{equation}
@@
 Notice that, in this particular case, the induced magnetization
-is parallel to the inducing field $\mathbf{H}_{0}$,
+is parallel to the inducing field $\mathbf{H}_{0}$ (Eq. \ref{eq:H0}),
 whether it is parallel to an ellipsoid axis or not.
+Usually, Eq. \ref{eq:M-approx}
+is considered a good approximation for $\chi \leq 0.1$ SI.
 
@@
 magnetic constant (in \unit{H \, m^{-1}}).
-
 For geophysical applications, it is preferable to
 calculate the total-field anomaly produced by the
-magnetic sources. This scalar quantity is defined 
-as follows \citep{blakely1996}:
-\begin{equation}
-\Delta \tilde{T}(\tilde{\mathbf{r}}) = \| 
-\tilde{\mathbf{B}}_{0} + \Delta \tilde{\mathbf{B}}(\tilde{\mathbf{r}}) \|
-- \| \tilde{\mathbf{B}}_{0} \| \: ,
-\label{eq:delta-T-tilde}
-\end{equation}
-where $\tilde{\mathbf{B}}_{0} = k_{m} \, \tilde{\mathbf{H}}_{0}$
-and $\Delta \tilde{\mathbf{B}}(\tilde{\mathbf{r}}) = 
-k_{m} \, \Delta \tilde{\mathbf{H}}(\tilde{\mathbf{r}})$
-(Eq. \ref{eq:delta-H-tilde}).
+magnetic sources. This scalar quantity is given by
+\citep{blakely1996}:
+\begin{equation}
+\Delta T(\mathbf{r}) = \| 
+\mathbf{B}_{0} + \Delta \mathbf{B}(\mathbf{r}) \|
+- \| \mathbf{B}_{0} \| \: ,
+\label{eq:delta-T}
+\end{equation}
+where $\mathbf{B}_{0} = k_{m} \, \mathbf{H}_{0}$
+(Eq. \ref{eq:H0}) and $\Delta \mathbf{B}(\mathbf{r}) = 
+k_{m} \, \mathbf{V} \; \Delta \tilde{\mathbf{H}}(\tilde{\mathbf{r}})$,
+with $\mathbf{V}$ defined according to the ellipsoid type and
+$\Delta \tilde{\mathbf{H}}(\tilde{\mathbf{r}})$ defined by
+Eq. \ref{eq:delta-H-tilde}.
 In practical situations, however, 
-$\| \tilde{\mathbf{B}}_{0} \| >> \| \Delta \tilde{\mathbf{B}}(\tilde{\mathbf{r}}) \|$
+$\| \mathbf{B}_{0} \| >> \| \Delta \mathbf{B}(\mathbf{r}) \|$
 and, consequently, the following approximation is valid \citep{blakely1996}:
 \begin{equation}
-\Delta \tilde{T}(\tilde{\mathbf{r}}) \approx  
-\frac{\tilde{\mathbf{B}}_{0}^{\top} \Delta \tilde{\mathbf{B}}(\tilde{\mathbf{r}})}{\| \tilde{\mathbf{B}}_{0} \|} \: .
-\label{eq:delta-T-tilde-approx}
+\Delta T(\mathbf{r}) \approx  
+\frac{\mathbf{B}_{0}^{\top} \Delta \mathbf{B}(\mathbf{r})}{\| \mathbf{B}_{0} \|} \: .
+\label{eq:delta-T-approx}
 \end{equation}
@@
 (Eq. \ref{eq:delta-H-tilde}) and
-the total-field anomaly $\Delta \tilde{T}(\tilde{\mathbf{r}})$
-(Eqs. \ref{eq:delta-T-tilde} and \ref{eq:delta-T-tilde-approx}) 
+the total-field anomaly $\Delta T(\mathbf{r})$
+(Eqs. \ref{eq:delta-T} and \ref{eq:delta-T-approx}) 
 are calculated according to Eq. \ref{eq:nij-tilde}, with 
@@
 \begin{equation}
-\lambda = 2 \, \sqrt{-Q} \, \cos \left( \frac{\theta}{3}\right) - \frac{p_{2}}{3} \: ,
+\lambda = 2 \, \sqrt{-Q} \, \cos \left( \frac{\varphi}{3}\right) - \frac{p_{2}}{3} \: ,
 \label{eq:lambda-triaxial-ell}
@@
 \begin{equation}
-\theta = \cos^{-1} \left( \frac{R}{\sqrt{-Q^{3}}} \right) \: ,
-\label{eq:theta-triaxial-ell}
+\varphi = \cos^{-1} \left( \frac{R}{\sqrt{-Q^{3}}} \right) \: ,
+\label{eq:varphi-triaxial-ell}
 \end{equation}

### 2017-02-17 manuscript/manuscript.tex
include the lambda matrix

@@
 the susceptibility tensor is defined according to Eq. \ref{eq:K-isotropic}.
-In this case, the magnetization $\tilde{\mathbf{M}}$ (Eq. \ref{eq:M-tilde-remanence})
-can be rewritten as follows:
-\begin{equation}
-\tilde{\mathbf{M}} = \left[ \begin{array}{ccc}
-\frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{11}} & 0 & 0 \\
-0 & \frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{22}} & 0 \\
-0 & 0 & \frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{33}}
-\end{array} \right] \left( \chi \, \tilde{\mathbf{H}}_{0} +
-\tilde{\mathbf{M}}_{R} \right) \: .
-\label{eq:M-tilde-K-isotropic}
+In this case, the magnetization $\mathbf{M}$ (Eq. \ref{eq:M-KH}),
+referred to the main coordinate system (Fig. \ref{fig:orientation-angles}a),
+can be written as follows:
+\begin{equation}
+\mathbf{M} = \mathbf{\Lambda} \left( \chi \, \mathbf{H}_{0} +
+\mathbf{M}_{R} \right) \: ,
+\label{eq:M-K-isotropic}
+\end{equation}
+where
+\begin{equation}
+\mathbf{\Lambda} = \mathbf{V}
+\left[ \begin{array}{ccc}
+\frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{11}} &  &  \\
+ & \frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{22}} &  \\
+ &  & \frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{33}}
+\end{array} \right] \mathbf{V}^{\top} \: .
+\label{eq:Lambda}
 \end{equation}
@@
 by \citet[Eqs. ~13--15]{guo2001}.
-The first term, depending on the inducing field $\tilde{\mathbf{H}}_{0}$, 
+The first term, depending on the inducing field $\mathbf{H}_{0}$
+(Eq. \ref{eq:H0}), 
 represents the induced magnetization whereas the term depending on
-$\tilde{\mathbf{M}}_{R}$ is the remanent magnetization.
-Equation \ref{eq:M-tilde-K-isotropic} reveals that, as pointed out by \citet{maxwell1873},
+$\mathbf{M}_{R}$ is the remanent magnetization.
+Equation \ref{eq:M-K-isotropic} reveals that, as pointed out by
+many authors
+\citep[e.g.,][]{maxwell1873, dubois1896, stoner1945, clark1986, sttraton2007},
 the induced magnetization opposes the inducing field 
@@
 the inducing field.
-If we additionally consider that $\chi << 1$, the magnetization
-$\mathbf{M}$ (Eq. \ref{eq:M-KH}) defined in the main coordinate system
-(Fig. \ref{fig:orientation-angles}a) can be approximated as follows:
+If we additionally consider that $\chi << 1$, the matrix 
+$\mathbf{\Lambda}$ (Eqs. \ref{eq:M-K-isotropic} and \ref{eq:Lambda})
+approaches to the identity and the magnetization
+$\mathbf{M}$ (Eqs. \ref{eq:M-KH} and \ref{eq:M-K-isotropic})
+can be approximated as follows:
 \begin{equation}

### 2017-02-17 manuscript/manuscript.tex
remove the theta and describe the magnetization in the main coordinate system

@@
 \right) \, dx^{\prime}dy^{\prime}dz^{\prime} \: .
-\label{eq:phi-potential}
+\label{eq:V-potential}
 \end{equation}
@@
 (in $\unit{Am^{-1}}$).
-Eq. \ref{eq:phi-potential} is valid anywhere, 
+Eq. \ref{eq:V-potential} is valid anywhere, 
 independently if the position vector $\mathbf{r}$ represents
@@
 coincide with the ellipsoid axes, the matrix $\mathbf{U}$ is
-equal to the matrix $\mathbf{V}$ (Eq. \ref{eq:A}),
-depending on the ellipsoid type.
+equal to the matrix $\mathbf{V}$ (Eq. \ref{eq:A}).
 Another important particular case is that in which the
@@
 \ref{eq:M-tilde} is given by \citet[p. ~151]{searle1982}.
-
 Equation \ref{eq:M-tilde} can be easily generalized for the case in 
@@
 \begin{equation}
-\tilde{\mathbf{M}} =  
+\mathbf{M} = \mathbf{\Lambda}
+\left(\mathbf{K} \, \mathbf{H}_{0} + \mathbf{M}_{R} \right) \: ,
+\label{eq:M-remanence}
+\end{equation}
+where
+\begin{equation}
+\mathbf{\Lambda} = \mathbf{V}
 \left( \mathbf{I} - \tilde{\mathbf{K}} \, \tilde{\mathbf{N}}^{\dagger} \right)^{-1}
-\left( \tilde{\mathbf{K}} \, \tilde{\mathbf{H}}_{0} + \tilde{\mathbf{M}}_{R} \right) \: .
-\label{eq:M-tilde-remanence}
-\end{equation}
-Equation \ref{eq:M-tilde-remanence} is consistent with that given by
+\mathbf{V}^{\top} \: .
+\label{eq:Lambda}
+\end{equation}
+Despite of the coordinate system transformation represented by the
+matrix $\mathbf{V}$ (Eq. \ref{eq:A}),
+Eq. \ref{eq:M-remanence} is consistent with that given by
 \citet[Eq. ~38]{clark1986}. It shows the combined effect of the
-anisotropy of magnetic susceptibility, which is represented by the 
-susceptibility tensor $\tilde{\mathbf{K}}$ and reflects the
+anisotropy of magnetic susceptibility (AMS) and the shape anisotropy.
+The AMS is represented by the susceptibility tensor $\mathbf{K}$ 
+(Eq. \ref{eq:K}) and reflects the
 preferred orientation of the magnetic minerals forming the
-body, and the shape anisotropy, which is represented by the
+body. The susceptibility tensor appears in Eq. \ref{eq:M-remanence},
+defined in the main coordinate system (Fig. \ref{fig:orientation-angles}a),
+and Eq. \ref{eq:Lambda}, defined in the local coordinate system
+(Fig. \ref{fig:orientation-angles}b).
+The shape anisotropy is represented, in Eq.\ref{eq:M-remanence} by the
 depolarization tensor $\tilde{\mathbf{N}}^{\dagger}$ and
 reflects the self-demagnetization associated to the body shape.
-Notice that the resultant magnetization $\tilde{\mathbf{M}}$
-(Eq. \ref{eq:M-tilde-remanence}) does not necessarily have
-the same direction as the inducing field $\tilde{\mathbf{H}}_{0}$.
+Notice that the resultant magnetization $\mathbf{M}$
+(Eq. \ref{eq:M-remanence}) does not necessarily have
+the same direction as the inducing field $\mathbf{H}_{0}$
+(Eq. \ref{eq:H0}).
 The angular difference $\theta$ between the resultant magnetization
-and the inducing field is the same, whether the quantities
-are defined in the main coordinate system (Fig. \ref{fig:orientation-angles}a)
-or local coordinate system (Fig. \ref{fig:orientation-angles}b).
-For convenience, we define $\theta$ (in degrees) in the main coordinate system
-by using the scalar product definition as follows:
-\begin{equation}
-\theta = \frac{180}{\pi} \, \cos^{-1} \left( 
-\frac{\mathbf{M}^{\top}\mathbf{H}_{0}}
-{\| \mathbf{M} \| \; \| \mathbf{H}_{0} \|}\right) \: ,
-\label{eq:theta}
-\end{equation}
-where $\mathbf{M}$ is obtained by pre-multiplying the
-magnetization $\tilde{\mathbf{M}}$ (Eq. \ref{eq:M-tilde-remanence})
-by the orthogonal matrix $\mathbf{V}$ (Eq. \ref{eq:A}),
-which is defined according to the ellipsoid type, and
-$\mathbf{H}_{0}$ is given by Eq. \ref{eq:H0}.
-
+and the inducing field depends on the combined effect of the
+anisotropy of magnetic susceptibility and the shape anisotropy.
+
+%The angular difference $\theta$ between the resultant magnetization
+%and the inducing field is the same, whether the quantities
+%are defined in the main coordinate system (Fig. \ref{fig:orientation-angles}a)
+%or local coordinate system (Fig. \ref{fig:orientation-angles}b).
+%For convenience, we define $\theta$ (in degrees) in the main coordinate system
+%by using the scalar product definition as follows:
+%\begin{equation}
+%\theta = \frac{180}{\pi} \, \cos^{-1} \left( 
+%\frac{\mathbf{M}^{\top}\mathbf{H}_{0}}
+%{\| \mathbf{M} \| \; \| \mathbf{H}_{0} \|}\right) \: ,
+%\label{eq:theta}
+%\end{equation}
+%where $\mathbf{M}$ is obtained by pre-multiplying the
+%magnetization $\tilde{\mathbf{M}}$ (Eq. \ref{eq:M-tilde-remanence})
+%by the orthogonal matrix $\mathbf{V}$ (Eq. \ref{eq:A}),
+%which is defined according to the ellipsoid type, and
+%$\mathbf{H}_{0}$ is given by Eq. \ref{eq:H0}.
+%
 For the particular case in which the susceptibility is isotropic,
 the susceptibility tensor is defined according to Eq. \ref{eq:K-isotropic}.
-In this case, the magnetization $\mathbf{M}$ (Eq. \ref{eq:M-KH}),
+In this case, the magnetization $\mathbf{M}$ (Eqs. \ref{eq:M-KH} and \ref{eq:M-remanence}),
 referred to the main coordinate system (Fig. \ref{fig:orientation-angles}a),
-can be written as follows:
+and the matrix $\mathbf{\Lambda}$ (Eq. \ref{eq:Lambda})
+can be rewritten as follows:
 \begin{equation}
@@
 \end{equation}
-where
+and
 \begin{equation}
@@
 \end{array} \right] \mathbf{V}^{\top} \: .
-\label{eq:Lambda}
+\label{eq:Lambda-K-isotropic}
 \end{equation}
@@
 If we additionally consider that $\chi << 1$, the matrix 
-$\mathbf{\Lambda}$ (Eqs. \ref{eq:M-K-isotropic} and \ref{eq:Lambda})
+$\mathbf{\Lambda}$ (Eq. \ref{eq:Lambda-K-isotropic})
 approaches to the identity and the magnetization
-$\mathbf{M}$ (Eqs. \ref{eq:M-KH} and \ref{eq:M-K-isotropic})
+$\mathbf{M}$ (Eq. \ref{eq:M-K-isotropic})
 can be approximated as follows:

### 2017-02-17 manuscript/manuscript.tex
write the fields in the main coordinate system

@@
 property and hence can be uniformly magnetized 
-in the presence of a uniform magnetic field.
+in the presence of a uniform inducing magnetic field.
 This property can be extended to other bodies
@@
 (Eq. \ref{eq:A}) is defined according to the ellipsoid type.
+Subsequently, quantities referred to the local coordinate system
+(Fig. \ref{fig:orientation-angles}b) are represented with
+the simbol "$\sim$".
 
@@
 Consider a magnetized ellipsoid immersed in
-a uniform magnetic field $\mathbf{H}_{0}$ (in $\unit{Am^{-1}}$)
+a uniform inducing magnetic field $\mathbf{H}_{0}$ (in $\unit{Am^{-1}}$)
 given by
@@
 (Fig. \ref{fig:orientation-angles}a).
-This uniform field can be, for example, the main component of the
+This field represents the main component of the
 Earth's magnetic field, which is usually assumed to be generated
@@
 peirce1902, webster1904, kellogg1929, stoner1945, osborn1945,
-peake1953, chang1961, macmillan1958, lowes1974,  clark1986, 
+peake1953, macmillan1958, chang1961, lowes1974,  clark1986, 
 tejedor1995, sttraton2007}.
@@
 in Eqs. \ref{eq:Hi-tilde} and \ref{eq:M-tilde},
-is in fact the sum of the uniform magnetic field $\tilde{\mathbf{H}}_{0}$ 
+is in fact the sum of the inducing magnetic field $\tilde{\mathbf{H}}_{0}$ 
 and the hypothetical ancient field $\tilde{\mathbf{H}}_{A}$, we obtain the 
@@
 (Eq. \ref{eq:H0}).
-The angular difference $\theta$ between the resultant magnetization
+The angular difference between the resultant magnetization
 and the inducing field depends on the combined effect of the
@@
 
-The magnetic field $\Delta \tilde{\mathbf{H}}(\tilde{\mathbf{r}})$ 
+The magnetic field $\Delta \mathbf{H}(\mathbf{r})$ 
 produced by an ellipsoid at external points is calculated from 
-Eqs. \ref{eq:H-tilde} and \ref{eq:M-tilde-remanence} as the difference
-between the resultant field $\tilde{\mathbf{H}}(\tilde{\mathbf{r}})$ 
-and the uniform field $\tilde{\mathbf{H}}_{0}$:
-\begin{equation}
-\Delta \tilde{\mathbf{H}}(\tilde{\mathbf{r}}) = 
-- \tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}}) \, \tilde{\mathbf{M}} \: .
-\label{eq:delta-H-tilde}
+Eqs. \ref{eq:H-tilde} and \ref{eq:M-remanence} as the difference
+between the resultant field $\mathbf{H}(\mathbf{r})$ 
+and the inducing field $\mathbf{H}_{0}$:
+\begin{equation}
+\Delta \mathbf{H}(\mathbf{r}) = 
+- \mathbf{V} \tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}}) \, \mathbf{V}^{\top}
+\mathbf{M} \: .
+\label{eq:delta-H}
 \end{equation}
@@
 $\tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}})$ used in 
-Eq. \ref{eq:delta-H-tilde} will be presented in
+Eq. \ref{eq:delta-H} will be presented in
 the following section.
 
-The $\Delta \tilde{\mathbf{H}}(\tilde{\mathbf{r}})$ 
-can be interpreted as a uniformly magnetized body located in the
-crust while the uniform field $\tilde{\mathbf{H}}_{0}$ can
-be interpreted as the main component of the geomagnetic field
-on the study area, which is commonly assumed to be
-generated at the liquid part of the Earth's core.
-Equation \ref{eq:delta-H-tilde} gives the magnetic field
+The $\Delta \mathbf{H}(\mathbf{r})$ 
+represents the magnetic field produced by a uniformly magnetized 
+body located in the crust.
+Equation \ref{eq:delta-H} gives the magnetic field
 (in \unit{A \, m^{-1}}) produced by an ellipsoid. However,
@@
 induction (in \unit{nT}). Fortunately, this conversion can
-be easily done by multiplying Eq. \ref{eq:delta-H-tilde}
+be easily done by multiplying Eq. \ref{eq:delta-H}
 by $k_{m}~=~10^{9}~\mu_{0}$, where $\mu_{0}$ represents the
@@
 where $\mathbf{B}_{0} = k_{m} \, \mathbf{H}_{0}$
-(Eq. \ref{eq:H0}) and $\Delta \mathbf{B}(\mathbf{r}) = 
-k_{m} \, \mathbf{V} \; \Delta \tilde{\mathbf{H}}(\tilde{\mathbf{r}})$,
-with $\mathbf{V}$ defined according to the ellipsoid type and
-$\Delta \tilde{\mathbf{H}}(\tilde{\mathbf{r}})$ defined by
-Eq. \ref{eq:delta-H-tilde}.
+and $\Delta \mathbf{B}(\mathbf{r}) = 
+k_{m} \, \Delta \mathbf{H}(\mathbf{r})$,
+with $\mathbf{H}_{0}$ and $\Delta \mathbf{H}(\mathbf{r})$ defined,
+respectively, by Eqs. \ref{eq:H0} and \ref{eq:delta-H}.
 In practical situations, however, 
@@
 The elements of the transformed depolarization tensor 
-$\tilde{\mathbf{N}}^{\dagger}$ used to compute the 
-uniform magnetic field $\tilde{\mathbf{H}}^{\dagger}$
-(Eq. \ref{eq:Hi-tilde}) and the magnetization $\tilde{\mathbf{M}}$ 
-(Eqs. \ref{eq:M-tilde} and \ref{eq:M-tilde-remanence})
+$\tilde{\mathbf{N}}^{\dagger}$ used in the previous sections
 are calculated according to Eq. \ref{eq:nij-tilde}, with 
@@
 $j = 1, 2, 3$, of $\tilde{\mathbf{N}}^{\dagger}$ 
-do not depend on the transformed position
+do not depend on the elements of the transformed position
 vector $\tilde{\mathbf{r}}$ (equation \ref{eq:coord_transformation}). 
@@
 \end{equation}
-where $\tilde{\mathbf{N}}^{\dagger}$ (Eqs. \ref{eq:Hi-tilde}, 
-\ref{eq:M-tilde} and \ref{eq:M-tilde-remanence}) is a diagonal 
+where $\tilde{\mathbf{N}}^{\dagger}$ is a diagonal 
 matrix and $\mathbf{V}$ (Eq. \ref{eq:A}) is an orthogonal matrix.
@@
 $\tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}})$ used to compute
-the magnetic field $\Delta \tilde{\mathbf{H}}(\tilde{\mathbf{r}})$ 
-(Eq. \ref{eq:delta-H-tilde}) and
+the magnetic field $\Delta \mathbf{H}(\mathbf{r})$ 
+(Eq. \ref{eq:delta-H}) and
 the total-field anomaly $\Delta T(\mathbf{r})$

### 2017-02-17 manuscript/manuscript.tex
demagnetization measure theta

@@
 \end{equation}
-This equation is in perfect agreement with those presented 
+Despite the coordinate transformation represented by
+matrix $\mathbf{V}$ (Eq. \ref{eq:A}),
+this equation is in perfect agreement with those presented 
 by \citet[Eqs. ~13--15]{guo2001}.
@@
 
+INCLUIR A MEDIDA THETA
+\begin{equation}
+\theta = \frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{11}} +
+\frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{22}} +
+\frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{33}} - 3 \: .
+\label{eq:theta}
+\end{equation}
+
 \subsection{External magnetic field and total-field anomaly}
@@
 For readers interested in automated code testing,
-we recommend taking a look at the 
-freely reusable lessons of the Software Carpentry 
+we recommend the freely reusable lessons of the Software Carpentry 
 (\url{https://software-carpentry.org/}) and at the
@@
 
-\subsection{Ellipsoidal models}
+\subsection{Susceptibility}
 
@@
 
-\subsection{Susceptibility}
+\subsection{Simulation of a geological body}
 

### 2017-02-20 manuscript/manuscript.tex
include the new limit for the isotropic susceptibility

@@
 \mathbf{\Lambda} = \mathbf{V}
-\left[ \begin{array}{ccc}
-\frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{11}} &  &  \\
- & \frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{22}} &  \\
- &  & \frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{33}}
-\end{array} \right] \mathbf{V}^{\top} \: .
+\left( \mathbf{I} - \chi \, \tilde{\mathbf{N}}^{\dagger} \right)^{-1}
+\mathbf{V}^{\top} \: .
 \label{eq:Lambda-K-isotropic}
@@
 $\mathbf{M}$ (Eq. \ref{eq:M-K-isotropic})
-can be approximated as follows:
-\begin{equation}
-\mathbf{M} \approx \chi \, \mathbf{H}_{0} +
+can be approximated by:
+\begin{equation}
+\breve{\mathbf{M}} = \chi \, \mathbf{H}_{0} +
 \mathbf{M}_{R} \: ,
@@
 is considered a good approximation for $\chi \leq 0.1$ SI.
-
-INCLUIR A MEDIDA THETA
-\begin{equation}
-\theta = \frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{11}} +
-\frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{22}} +
-\frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{33}} - 3 \: .
-\label{eq:theta}
-\end{equation}
+Although this value has been largely used in the literature,
+there have been few empirical and/or theoretical investigations 
+about it.
+
+\subsubsection{Relationship between $\chi$ and the magnetization error}
+
+In the case of isotropic susceptibility, the resultant magnetization
+$\mathbf{M}$ (Eq. \ref{eq:M-K-isotropic}) may be determined by solving the
+following linear system:
+\begin{equation}
+\mathbf{\Lambda}^{-1} \, \mathbf{M} = \chi \, \mathbf{H}_{0} +
+\mathbf{M}_{R} \: ,
+\label{eq:M-K-isotropic-inverse-Lambda}
+\end{equation}
+where, according to Eq. \ref{eq:Lambda-K-isotropic},
+\begin{equation}
+\mathbf{\Lambda}^{-1} = \mathbf{V}
+\left( \mathbf{I} - \chi \, \tilde{\mathbf{N}}^{\dagger} \right)
+\mathbf{V}^{\top} \: .
+\label{eq:inverse-Lambda}
+\end{equation}
+
+Consider a perturbed matrix $\delta \mathbf{\Lambda}^{-1}$ given by
+\begin{equation}
+\delta \mathbf{\Lambda}^{-1} = \mathbf{\Lambda}^{-1} - \mathbf{I}
+\label{eq:perturbed-inverse-Lambda}
+\end{equation}
+and, similarly, a perturbed magnetization vector $\delta \mathbf{M}$
+given by
+\begin{equation}
+\delta \mathbf{M} = \mathbf{M} - \breve{\mathbf{M}} \: ,
+\label{eq:perturbed-M}
+\end{equation}
+where $\mathbf{M}$ is the true magnetization obtained from Eq. 
+\ref{eq:M-K-isotropic-inverse-Lambda} and $\breve{\mathbf{M}}$
+is the approximated magnetization obtained from Eq. \ref{eq:M-approx}.
 

### 2017-02-21 manuscript/manuscript.tex
define the norm of the perturbed inverse Lambda matrix

@@
 \end{equation}
-where $\| \cdot \|$ denotes the Euclidean norm and
+where $\| \cdot \|$ denotes the Euclidean norm (or 2-norm) and
 $D$ and $I$ are respectively, the declination and inclination of the 
@@
 \end{equation}
+As we have already pointed out, the approximated
+magnetization $\breve{\mathbf{M}}$ (Eq. \ref{eq:M-approx})
+represents the particular case in which the matrix 
+$\mathbf{\Lambda}$ (Eq. \ref{eq:Lambda-K-isotropic}),
+and consequently the matrix $\mathbf{\Lambda}^{-1}$
+(Eq. \ref{eq:inverse-Lambda}), are close to the identity.
+Our goal in this subsection is to bound the norm of the
+difference between the true magnetization $\mathbf{M}$
+(Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda})
+and the approximated magnetization $\breve{\mathbf{M}}$
+(Eq. \ref{eq:M-approx}).
 
@@
 \begin{equation}
-\delta \mathbf{M} = \mathbf{M} - \breve{\mathbf{M}} \: ,
+\delta \mathbf{M} = \mathbf{M} - \breve{\mathbf{M}} \: .
 \label{eq:perturbed-M}
 \end{equation}
-where $\mathbf{M}$ is the true magnetization obtained from Eq. 
-\ref{eq:M-K-isotropic-inverse-Lambda} and $\breve{\mathbf{M}}$
-is the approximated magnetization obtained from Eq. \ref{eq:M-approx}.
+By using these two equations, we may rewrite that of the approximated
+magnetization $\breve{\mathbf{M}}$ (Eq. \ref{eq:M-approx}) as follows:
+\begin{equation}
+\left( \mathbf{\Lambda}^{-1} - \delta \mathbf{\Lambda}^{-1} \right)
+\left( \mathbf{M} - \delta \mathbf{M} \right) = 
+\chi \, \mathbf{H}_{0} +
+\mathbf{M}_{R} \: .
+\label{eq:perturbed-system}
+\end{equation}
+Now, by subtracting the true magnetization 
+$\mathbf{M}$ (Eq. \ref{eq:M-K-isotropic-inverse-Lambda})
+from this linear system (Eq. \ref{eq:perturbed-system})
+and rearranging the terms, we obtain the following linear
+system for the perturbed magnetization $\delta \mathbf{M}$
+(Eq. \ref{eq:perturbed-M}):
+\begin{equation}
+\delta \mathbf{M} = - \delta \mathbf{\Lambda}^{-1} \mathbf{M} \: .
+\label{eq:perturbed-M-system}
+\end{equation}
+
+By using the concept of vector norm and its corresponding
+operator norm \citep{demmel1997, golub2013}, we may use Eq.
+\ref{eq:perturbed-M-system} to write the following inequality:
+\begin{equation}
+\frac{\| \delta \mathbf{M} \|}{\| \mathbf{M} \|} \leq
+\| \delta \mathbf{\Lambda}^{-1} \| \: .
+\label{eq:perturbed-M-inequality}
+\end{equation}
+where $\| \delta \mathbf{M} \|$ and $\| \mathbf{M} \|$
+denote Euclidean norms (or 2-norms) and the term 
+$\| \delta \mathbf{\Lambda}^{-1} \|$ denotes the matrix 2-norm
+of $\delta \mathbf{\Lambda}^{-1}$, which is given by
+\begin{equation}
+\| \delta \mathbf{\Lambda}^{-1} \| = \chi \,
+\tilde{n}^{\dagger}_{33} \: ,
+\label{eq:norm-perturbed-inverse-Lambda}
+\end{equation}
+where $\tilde{n}^{\dagger}_{33}$ is defined in the 
+following sections, depending on the ellipsoid
+type.
 

### 2017-02-21 manuscript/manuscript.tex
preliminary version of the subsection defining chi max

@@
 
-\subsubsection{Relationship between $\chi$ and the magnetization error}
+\subsubsection{Relationship between $\chi$ and the relative error in $\breve{\mathbf{M}}$}
 
@@
 (Eq. \ref{eq:inverse-Lambda}), are close to the identity.
-Our goal in this subsection is to bound the norm of the
-difference between the true magnetization $\mathbf{M}$
-(Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda})
-and the approximated magnetization $\breve{\mathbf{M}}$
-(Eq. \ref{eq:M-approx}).
+%Our goal in this subsection is to bound the norm of the
+%difference between the true magnetization $\mathbf{M}$
+%(Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda})
+%and the approximated magnetization $\breve{\mathbf{M}}$
+%(Eq. \ref{eq:M-approx}).
 
@@
 $\| \delta \mathbf{\Lambda}^{-1} \|$ denotes the matrix 2-norm
-of $\delta \mathbf{\Lambda}^{-1}$, which is given by
+of $\delta \mathbf{\Lambda}^{-1}$.
+By using Eqs. \ref{eq:inverse-Lambda} and \ref{eq:perturbed-inverse-Lambda}
+and the orthogonal invariance of the matrix 2-norm
+\citep{demmel1997, golub2013}, we define
+$\| \delta \mathbf{\Lambda}^{-1} \|$ as follows:
 \begin{equation}
@@
 type.
+It is worth, however, to stress that $\tilde{n}^{\dagger}_{33}$ is
+a scalar function of the ellipsoid semi-axes.
+In Eq. \ref{eq:perturbed-M-inequality}, the ratio
+$\| \delta \mathbf{M} \| \, \| \mathbf{M} \|^{-1}$ represents the
+\textit{relative error} in the approximated magnetization
+$\breve{\mathbf{M}}$ (Eq. \ref{eq:M-approx}) with respect
+to the true magnetization $\mathbf{M}$ (Eqs. \ref{eq:M-K-isotropic}
+and \ref{eq:M-K-isotropic-inverse-Lambda}).
+
+Given a target relative error
+$\epsilon = \| \delta \mathbf{M} \| \, \| \mathbf{M} \|^{-1}$
+and an ellipsoid
+with given semi-axes, we may use the inequality
+represented by Eq. \ref{eq:norm-perturbed-inverse-Lambda}
+to define
+\begin{equation}
+\chi_{max} = \frac{\epsilon}{\tilde{n}^{\dagger}_{33}} \: ,
+\label{eq:max-chi}
+\end{equation}
+which represents the maximum isotropic susceptibility 
+that the ellipsoidal body can assume in order o guarantee
+a relative error lower than or equal to $\epsilon$.
+For isotropic susceptibilities greater than $\chi_{max}$,
+there is no guarantee that the relative error in the
+approximated magnetization $\breve{\mathbf{M}}$ (Eq. \ref{eq:M-approx})
+with respect to the true magnetization $\mathbf{M}$ 
+(Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda})
+is lower than or equal to $\epsilon$. The geoscientific community
+has been using $\chi_{max} = 0.1$ SI as a limit value for
+neglecting the self-demagnetization and, consequently,
+use magnetization $\breve{\mathbf{M}}$ (Eq. \ref{eq:M-approx})
+as a good approximation of the true magnetization $\mathbf{M}$ 
+(Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda}).
+Equation \ref{eq:max-chi}, on the other hand, defines $\chi_{max}$ 
+as a function of the ellipsoid semi-axes, according to a
+user-specified relative error $\epsilon$.
 
@@
 
-\subsection{Susceptibility}
+\subsection{Relative error in neglecting the self-demagnetization}
 

### 2017-02-21 manuscript/manuscript.tex
change the position of the depolarization tensor section

@@
 
+\subsection{Transformed depolarization tensors $\tilde{\mathbf{N}}(\tilde{\mathbf{r}})$}
+
+\subsubsection{Depolarization tensor $\tilde{\mathbf{N}}^{\dagger}$}
+
+Let $\tilde{\mathbf{N}}^{\dagger}$ be the transformed
+depolarization tensor calculated for the case in which
+$\tilde{\mathbf{r}}$ (Eq. \ref{eq:coord_transformation})
+represents a point located outside
+the ellipsoidal body. In this case, 
+the elements of $\tilde{\mathbf{N}}^{\dagger}$
+are calculated according to Eq. \ref{eq:nij-tilde}, 
+with $\tilde{f}(\tilde{\mathbf{r}})$ given by 
+$\tilde{f}^{\dagger}(\tilde{\mathbf{r}})$ (Eq. \ref{eq:fi-tilde}).
+As we have already pointed out, the  
+$\tilde{f}^{\dagger}(\tilde{\mathbf{r}})$ (Eq. \ref{eq:fi-tilde}) is a
+quadratic function of the spatial coordinates $\tilde{x}$,
+$\tilde{y}$ and $\tilde{z}$. Consequently, the 
+elements $\tilde{n}^{\dagger}_{ij}$, $i = 1, 2, 3$, 
+$j = 1, 2, 3$, of $\tilde{\mathbf{N}}^{\dagger}$ 
+do not depend on the elements of the transformed position
+vector $\tilde{\mathbf{r}}$ (Eq. \ref{eq:coord_transformation}). 
+Besides, the off-diagonal elements are zero and
+the diagonal elements are given by \citep{stoner1945}:
+\begin{equation}
+\tilde{n}^{\dagger}_{ii} = \frac{abc}{2}
+\int_{0}^{\infty} \frac{1}{\left( e_{i}^{2} 
++ u \right) R(u)} \, du \: , \quad i = 1, 2, 3 \: ,
+\label{eq:n-tilde-dagger-ii}
+\end{equation}
+where $R(u)$ is defined by Eq. \ref{eq:R} and
+$e_{1} = a$, $e_{2} = b$, and $e_{3} = c$. These elements 
+are commonly known as \textit{demagnetizing factors}
+and are defined according to the ellipsoid type.
+Here, we calculate the demagnetizing factors in the SI
+system. Consequently, they satisfies the condition
+$\tilde{n}^{\dagger}_{11} + \tilde{n}^{\dagger}_{22} + 
+\tilde{n}^{\dagger}_{33} = 1$, independently of the
+ellipsoid type.
+It is worth stressing that, according to Eq. \ref{eq:n-tilde-dagger-ii},
+the demagnetizing factors $\tilde{n}^{\dagger}_{ii}$ are 
+constants defined by the ellipsoid semi-axes $a$, $b$, and $c$.
+
+Notice that, according to Eqs. \ref{eq:H-tilde} 
+and \ref{eq:N-tilde-VT-N-V},
+\begin{equation}
+\mathbf{N}(\mathbf{r}) = 
+\mathbf{V} \, \tilde{\mathbf{N}}^{\dagger} \, 
+\mathbf{V}^{\top} \: ,
+\label{eq:N-V-N-dagger-VT}
+\end{equation}
+where $\tilde{\mathbf{N}}^{\dagger}$ is a diagonal 
+matrix and $\mathbf{V}$ (Eq. \ref{eq:A}) is an orthogonal matrix.
+This equation shows that, for the particular case 
+in which $\mathbf{r}$ and consequently $\tilde{\mathbf{r}}$
+represent a point inside the
+volume $\vartheta$ of the ellipsoid, the elements 
+$\tilde{n}^{\dagger}_{ii}$
+of $\tilde{\mathbf{N}}^{\dagger}$ represent the eigenvalues while the 
+columns of $\mathbf{V}$ represent the eigenvectors of the 
+original depolarization tensor $\mathbf{N}(\mathbf{r})$.
+
+\subparagraph*{Triaxial ellipsoids}
+
+For triaxial ellipsoids (e.g., $a > b > c$), the demagnetizing
+factors obtained by solving Eq. \ref{eq:n-tilde-dagger-ii}
+are given by:
+\begin{equation}
+\tilde{n}^{\dagger}_{11} = \frac{abc}
+{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
+\left( a^{2} - b^{2} \right)} 
+\left[ F(\kappa, \phi) - E(\kappa, \phi) \right] \: ,
+\label{eq:n-tilde-dagger-11-triaxial}
+\end{equation}
+\begin{equation}
+\tilde{n}^{\dagger}_{22} = 
+-\frac{abc}
+{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
+\left( a^{2} - b^{2} \right)} 
+\left[ F(\kappa, \phi) - E(\kappa, \phi) \right] + 
+\frac{abc}
+{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
+\left( b^{2} - c^{2} \right)} E(\kappa, \phi)
+- \frac{c^{2}}{b^{2} - c^{2}}
+\label{eq:n-tilde-dagger-22-triaxial}
+\end{equation}
+and
+\begin{equation}
+\tilde{n}^{\dagger}_{33} = 
+-\frac{abc}
+{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
+\left( b^{2} - c^{2} \right)} E(\kappa, \phi) +
+\frac{b^{2}}{b^{2} - c^{2}} \: ,
+\label{eq:n-tilde-dagger-33-triaxial}
+\end{equation}
+where
+\begin{equation}
+F(\kappa, \phi) = 
+\int^{\phi}_{0} 
+\frac{1}{\left( 1 - \kappa^{2} \sin^{2} \psi \right)^{\frac{1}{2}}}
+d\psi \: ,
+\label{eq:F-kappa-phi}
+\end{equation}
+and
+\begin{equation}
+E(\kappa, \phi) = 
+\int^{\phi}_{0} 
+\left( 1 - \kappa^{2} \sin^{2} \psi \right)^{\frac{1}{2}}
+d\psi \: ,
+\label{eq:E-kappa-phi}
+\end{equation}
+with $\kappa = \left[ \left( a^{2} - b^{2} \right) / 
+\left( a^{2} - c^{2} \right) \right]^{\frac{1}{2}}$ and
+$\cos \phi = c/a$.
+The functions $F(\kappa, \phi)$ (Eq. \ref{eq:F-kappa-phi}) and 
+$E(\kappa, \phi)$ (Eq. \ref{eq:E-kappa-phi}) are
+called Legendre's normal elliptic integrals of the first and 
+second kind, respectivelly. \citet{stoner1945} presented a 
+detailed deduction of the demagnetizing factors $\tilde{n}^{\dagger}_{11}$
+(Eq. \ref{eq:n-tilde-dagger-11-triaxial}), $\tilde{n}^{\dagger}_{22}$
+(Eq. \ref{eq:n-tilde-dagger-22-triaxial}) and $\tilde{n}^{\dagger}_{33}$
+(Eq. \ref{eq:n-tilde-dagger-33-triaxial}). \citet{clark1986} presented similar
+formulas. It can be shown that these demagnetizing factors
+satisfy the conditions
+$\tilde{n}^{\dagger}_{11} + \tilde{n}^{\dagger}_{22} + \tilde{n}^{\dagger}_{33} = 1$
+and
+$\tilde{n}^{\dagger}_{11} < \tilde{n}^{\dagger}_{22} < \tilde{n}^{\dagger}_{33}$.
+
+\subparagraph*{Prolate ellipsoids}
+
+For prolate ellipsoids (e.g., $a > b = c$), the demagnetizing
+factors obtained by solving Eq. \ref{eq:n-tilde-dagger-ii}
+are given by:
+\begin{equation}
+\tilde{n}^{\dagger}_{11} = \frac{1}{m^{2} - 1}
+\left\lbrace \frac{m}{\left( m^{2} - 1 \right)^{\frac{1}{2}}}
+\ln \left[ m + \left( m^{2} - 1 \right)^{\frac{1}{2}} \right]
+- 1 \right\rbrace
+\label{eq:n-tilde-dagger-11-prolate}
+\end{equation}
+and
+\begin{equation}
+\tilde{n}^{\dagger}_{22} = \frac{1}{2} \left(1 - \tilde{n}^{\dagger}_{11} \right) \: ,
+\label{eq:n-tilde-dagger-22-prolate}
+\end{equation}
+where $\tilde{n}^{\dagger}_{33} = \tilde{n}^{\dagger}_{22}$, 
+with $\tilde{n}^{\dagger}_{11}$ defined in 
+Eq. \ref{eq:n-tilde-dagger-11-prolate} and $m = a/b$.
+The detailed deduction of the demagnetizing factors 
+$\tilde{n}^{\dagger}_{11}$ (Eq. \ref{eq:n-tilde-dagger-11-prolate}) 
+and $\tilde{n}^{\dagger}_{22}$ (Eq. \ref{eq:n-tilde-dagger-22-prolate})
+can be found, for example, in \citet{stoner1945}. 
+These formulas were posteriorly presented by \citet{emerson1985}.
+It can be shown that these demagnetizing factors
+satisfy the conditions
+$\tilde{n}^{\dagger}_{11} + 2 \; \tilde{n}^{\dagger}_{22} = 1$
+and
+$\tilde{n}^{\dagger}_{11} < \tilde{n}^{\dagger}_{22}$.
+
+\subparagraph*{Oblate ellipsoids}
+
+For oblate ellipsoids (e.g., $a < b = c$), the demagnetizing
+factors obtained by solving Eq. \ref{eq:n-tilde-dagger-ii}
+are given by:
+\begin{equation}
+\tilde{n}^{\dagger}_{11} = 
+\frac{1}{1 - m^{2}} \left[
+1 - \frac{m}{\left( 1 - m^{2} \right)^{\frac{1}{2}}} \cos^{-1}m
+\right]
+\label{eq:n-tilde-dagger-11-oblate}
+\end{equation}
+and
+\begin{equation}
+\tilde{n}^{\dagger}_{22} = \frac{1}{2} \left(1 - \tilde{n}^{\dagger}_{11} \right) \: ,
+\label{eq:n-tilde-dagger-22-oblate}
+\end{equation}
+where $\tilde{n}^{\dagger}_{33} = \tilde{n}^{\dagger}_{22}$, 
+with $\tilde{n}^{\dagger}_{11}$ defined in 
+Eq. \ref{eq:n-tilde-dagger-11-oblate} and $m = a/b$.
+The detailed deduction of these demagnetizing factors 
+can be found, for example, in \citet{stoner1945}.
+These formulas can also be found in \citet{emerson1985}.
+The only difference, however, is that \citet{emerson1985} replaced
+the term $\cos^{-1}$ by a term $\tan^{-1}$, according to 
+the trigonometric identity 
+$\tan^{-1}x = \cos^{-1}(1/\sqrt{x^{2} + 1})$, $x > 0$.
+It can be shown that these demagnetizing factors
+satisfy the conditions
+$\tilde{n}^{\dagger}_{11} + 2 \; \tilde{n}^{\dagger}_{22} = 1$
+and
+$\tilde{n}^{\dagger}_{11} > \tilde{n}^{\dagger}_{22}$.
+
+\subsubsection{Depolarization tensor $\tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}})$}
+
+The elements $\tilde{n}^{\ddagger}_{ij}(\tilde{\mathbf{r}})$,
+$i = 1, 2, 3$, $j = 1, 2, 3$, of the transformed depolarization tensor 
+$\tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}})$ 
+are calculated according to Eq. \ref{eq:nij-tilde}, with 
+$\tilde{f}(\tilde{\mathbf{r}})$ given by $\tilde{f}^{\ddagger}(\tilde{\mathbf{r}})$
+(Eq. \ref{eq:fe-tilde}).
+By following \citet{clark1986}, the diagonal elements 
+$\tilde{n}^{\ddagger}_{ii}(\tilde{\mathbf{r}})$
+and the off-diagonal elements 
+$\tilde{n}^{\ddagger}_{ij}(\tilde{\mathbf{r}})$, $i = 1, 2, 3$,
+$j = 1, 2, 3$, are given by
+\begin{equation}
+\tilde{n}^{\ddagger}_{ii}(\tilde{\mathbf{r}}) =
+-\frac{abc}{2}
+\left( \frac{\partial \lambda}{\partial \tilde{r}_{i}} \, h_{i} \, \tilde{r}_{i}
++ g_{i} \right)
+\label{eq:n-tilde-ddagger-ii}
+\end{equation}
+and
+\begin{equation}
+\tilde{n}^{\ddagger}_{ij}(\tilde{\mathbf{r}}) =
+-\frac{abc}{2} \left(
+\frac{\partial \lambda}{\partial \tilde{r}_{i}} \, h_{j} \, \tilde{r}_{j} 
+\right) \: ,
+\label{eq:n-tilde-ddagger-ij}
+\end{equation}
+where
+\begin{equation}
+h_{i} = -\frac{1}{\left( e_{i}^{2} + \lambda \right) R(\lambda)} \: ,
+\label{eq:hi}
+\end{equation}
+\begin{equation}
+g_{i} = \int_{\lambda}^{\infty} \frac{1}{\left( e_{i}^{2} + u \right) R(u)} du \: ,
+\label{eq:gi}
+\end{equation}
+$e_{1} = a$, $e_{2} = b$, $e_{3} = c$, and 
+$\frac{\partial \lambda}{\partial \tilde{r}_{i}}$
+is defined in Appendix B (Eq. \ref{eq:dlambda}).
+The functions $g_{i}$ (Eq. \ref{eq:gi}) are defined according
+to the ellipsoid type.
+Notice that the elements $\tilde{n}^{\ddagger}_{ii}(\tilde{\mathbf{r}})$
+(Eq. \ref{eq:n-tilde-ddagger-ii}) and 
+$\tilde{n}^{\ddagger}_{ij}(\tilde{\mathbf{r}})$
+(Eq. \ref{eq:n-tilde-ddagger-ij}) 
+are proportional to the second derivatives of the function
+$\tilde{f}^{\ddagger}(\tilde{\mathbf{r}})$ (Eq. \ref{eq:fe-tilde}),
+which is harmonic. Consequently, the diagonal elements 
+$\tilde{n}^{\ddagger}_{ii}(\tilde{\mathbf{r}})$ satisfy the condition
+$\tilde{n}^{\ddagger}_{11}(\tilde{\mathbf{r}}) +
+\tilde{n}^{\ddagger}_{22}(\tilde{\mathbf{r}}) +
+\tilde{n}^{\ddagger}_{33}(\tilde{\mathbf{r}}) = 0$ for any
+point $\tilde{\mathbf{r}}$ outside the ellipsoid, independently
+of the ellipsoid type.
+
+\subparagraph*{Triaxial ellipsoids}
+
+For triaxial ellipsoids (e.g., $a > b > c$), the functions
+$g_{i}$ (Eq. \ref{eq:gi}) are defined as follows:
+\begin{equation}
+g_{1} = \frac{2}{\left( a^{2} - b^{2} \right) \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
+\left[ F(\kappa, \phi) - E(\kappa, \phi) \right] \: ,
+\label{eq:g1-triaxial}
+\end{equation}
+%\begin{equation}
+%g_{2} = \frac{2 \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
+%{\left( a^{2} - b^{2} \right)\left( b^{2} - c^{2} \right)}
+%\left[ E\left(\kappa, \phi \right) 
+%- \frac{\left( b^{2} - c^{2} \right)}{\left( a^{2} - c^{2} \right)}
+%F\left(\kappa, \phi \right) 
+%- \frac{\kappa^{2} \sin\phi \, \cos\phi}
+%{\left( 1 - \kappa^{2} \sin^{2}\phi \right)^{\frac{1}{2}}}
+%\right]
+%\label{eq:g2-triaxial}
+%\end{equation}
+\begin{equation}
+g_{2} = \frac{2 \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
+{\left( a^{2} - b^{2} \right)\left( b^{2} - c^{2} \right)}
+\left\lbrace
+E\left(\kappa, \phi \right) 
+- \left( \frac{b^{2} - c^{2}}{a^{2} - c^{2}} \right)
+F\left(\kappa, \phi \right) -
+\frac{a^{2} - b^{2}}{\left( a^{2} - c^{2} \right)^{\frac{1}{2}}} \left[
+\frac{c^{2} + \lambda}{\left( a^{2} + \lambda \right)\left( b^{2} + \lambda \right)}
+\right]^{\frac{1}{2}} \right\rbrace
+\label{eq:g2-triaxial}
+\end{equation}
+and
+%\begin{equation}
+%g_{3} = \frac{2}{\left( b^{2} - c^{2} \right) \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
+%\left[ \frac{\sin\phi \left( 1 - \kappa^{2} \sin^{2}\phi \right)^{\frac{1}{2}}}
+%{\cos\phi}  - E\left(\kappa, \phi \right) \right]
+%\: ,
+%\label{eq:g3-triaxial}
+%\end{equation}
+\begin{equation}
+g_{3} = \frac{2}{\left( b^{2} - c^{2} \right) \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
+E\left(\kappa, \phi \right) +
+\frac{2}{b^{2} - c^{2}}
+\left[
+\frac{b^{2} + \lambda}{\left( a^{2} + \lambda \right)\left( c^{2} + \lambda \right)}
+\right]^{\frac{1}{2}}
+\: ,
+\label{eq:g3-triaxial}
+\end{equation}
+where $F(\kappa, \phi)$ and $E(\kappa, \phi)$ are defined by
+Eqs. \ref{eq:E-kappa-phi} and \ref{eq:F-kappa-phi}, but with 
+$\sin \phi = \sqrt{\left( a^{2} - c^{2} \right)/\left( a^{2} + \lambda \right)}$.
+A detailed deduction of these formulas was presented by \citet{tejedor1995}.
+Similar formulas can also be found in \citet{clark1986}.
+
+\subparagraph*{Prolate ellipsoids}
+
+For prolate (e.g., $a > b = c$) ellipsoids, the functions
+$g_{i}$ (Eq. \ref{eq:gi}) are given by:
+\begin{equation}
+g_{1} =  \frac{2}{\left( a^{2} - b^{2} \right)^{\frac{3}{2}}}
+\left\lbrace
+\ln \left[ \frac{\left( a^{2} - b^{2} \right)^{\frac{1}{2}} + 
+                 \left( a^{2} + \lambda \right)^{\frac{1}{2}}}{
+                 \left( b^{2} + \lambda \right)^{\frac{1}{2}}} \right] -
+\left( \frac{a^{2} - b^{2}}{a^{2} + \lambda} \right)^{\frac{1}{2}}
+\right\rbrace
+\label{eq:g1-prolate}
+\end{equation}
+and
+\begin{equation}
+g_{2} =  \frac{1}{\left( a^{2} - b^{2} \right)^{\frac{3}{2}}}
+\left\lbrace
+\frac{\left[ \left( a^{2} - b^{2} \right)
+             \left( a^{2} + \lambda \right) \right]^{\frac{1}{2}}}
+     {b^{2} + \lambda} -
+\ln \left[ \frac{\left( a^{2} - b^{2} \right)^{\frac{1}{2}} + 
+                 \left( a^{2} + \lambda \right)^{\frac{1}{2}}}{
+                 \left( b^{2} + \lambda \right)^{\frac{1}{2}}} \right]
+\right\rbrace \: ,
+\label{eq:g2-prolate}
+\end{equation}
+where $g_{3} = g_{2}$.
+These formulas can be obtained by properly manipulating those
+presented by \citep{emerson1985}.
+
+\subparagraph*{Oblate ellipsoids}
+
+For oblate (e.g., $a < b = c$) ellipsoids, the functions
+$g_{i}$ (Eq. \ref{eq:gi}) are given by:
+\begin{equation}
+g_{1} =  \frac{2}{\left( b^{2} - a^{2} \right)^{\frac{3}{2}}}
+\left\lbrace
+\left( \frac{b^{2} - a^{2}}{a^{2} + \lambda}\right)^{\frac{1}{2}} -
+\tan^{-1} \left[ \left( \frac{b^{2} - a^{2}}{a^{2} + \lambda}\right)^{\frac{1}{2}} \right]
+\right\rbrace
+\label{eq:g1-oblate}
+\end{equation}
+and
+\begin{equation}
+g_{2} =  \frac{1}{\left( b^{2} - a^{2} \right)^{\frac{3}{2}}}
+\left\lbrace
+\tan^{-1} \left[ \left( \frac{b^{2} - a^{2}}{a^{2} + \lambda}\right)^{\frac{1}{2}} \right] -
+\frac{\left[ \left( b^{2} - a^{2} \right)
+             \left( a^{2} + \lambda \right) \right]^{\frac{1}{2}}}
+     {b^{2} + \lambda}
+\right\rbrace \: ,
+\label{eq:g2-oblate}
+\end{equation}
+where $g_{3} = g_{2}$.
+Similarly to the case of prolate ellipsoid shown previously,
+these formulas can be obtained by properly manipulating those
+presented by \citep{emerson1985}.
+
 \subsection{Internal magnetic field and magnetization}
@@
 where $\mathbf{I}$ is the identity matrix and 
-$\tilde{\mathbf{N}}^{\dagger}$ is a diagonal matrix
-representing the transformed depolarization tensor 
-evaluated within the volume $\vartheta$ of the ellipsoidal body.
-For a given ellipsoid, the elements $\tilde{n}^{\dagger}_{ii}$, 
-$i = 1, 2, 3$, of $\tilde{\mathbf{N}}^{\dagger}$ are constants 
-which are expressed in terms of the ellipsoid semi-axes.
-These elements are presented in detail in a latter section.
+$\tilde{\mathbf{N}}^{\dagger}$ is defined in the
+previous section.
 
@@
 (Fig. \ref{fig:orientation-angles}b).
-The shape anisotropy is represented, in Eq.\ref{eq:M-remanence} by the
+The shape anisotropy is represented, in Eq. \ref{eq:M-remanence}, by the
 depolarization tensor $\tilde{\mathbf{N}}^{\dagger}$ and
@@
 \| \delta \mathbf{\Lambda}^{-1} \| = \chi \,
-\tilde{n}^{\dagger}_{33} \: ,
+\tilde{n}^{\dagger}_{max} \: ,
 \label{eq:norm-perturbed-inverse-Lambda}
 \end{equation}
-where $\tilde{n}^{\dagger}_{33}$ is defined in the 
-following sections, depending on the ellipsoid
-type.
-It is worth, however, to stress that $\tilde{n}^{\dagger}_{33}$ is
+where $\tilde{n}^{\dagger}_{max}$ is the demagnetization
+factor associated to the shortest ellipsoid semi-axis.
+For a triaxial ellipsoid, 
+$\tilde{n}^{\dagger}_{max} \equiv \tilde{n}^{\dagger}_{33}$
+(Eq. \ref{eq:n-tilde-dagger-33-triaxial}). For a prolate ellipsoid,
+$\tilde{n}^{\dagger}_{max} \equiv \tilde{n}^{\dagger}_{22}$
+(Eq. \ref{eq:n-tilde-dagger-22-prolate}). 
+For an oblate ellipsoid,
+$\tilde{n}^{\dagger}_{max} \equiv \tilde{n}^{\dagger}_{11}$
+(Eq. \ref{eq:n-tilde-dagger-11-oblate}).
+It is worth stressing that, independently of the ellipsoid
+type, $\tilde{n}^{\dagger}_{max}$ is
 a scalar function of the ellipsoid semi-axes.
@@
 \begin{equation}
-\chi_{max} = \frac{\epsilon}{\tilde{n}^{\dagger}_{33}} \: ,
+\chi_{max} = \frac{\epsilon}{\tilde{n}^{\dagger}_{max}} \: ,
 \label{eq:max-chi}
@@
 - \mathbf{V} \tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}}) \, \mathbf{V}^{\top}
-\mathbf{M} \: .
+\mathbf{M} \: ,
 \label{eq:delta-H}
 \end{equation}
-The elements of the transformed depolarization tensor 
-$\tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}})$ used in 
-Eq. \ref{eq:delta-H} will be presented in
-the following section.
-
-The $\Delta \mathbf{H}(\mathbf{r})$ 
+where $\tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}})$ is
+the transformed depolarization tensor whose elements 
+$\tilde{n}^{\ddagger}_{ii}(\tilde{\mathbf{r}})$ and
+$\tilde{n}^{\ddagger}_{ij}(\tilde{\mathbf{r}})$ are defined,
+respectively, by Eqs. \ref{eq:n-tilde-ddagger-ii} and
+\ref{eq:n-tilde-ddagger-ij}.
+$\Delta \mathbf{H}(\mathbf{r})$ 
 represents the magnetic field produced by a uniformly magnetized 
@@
 \end{equation}
-
-\subsection{Transformed depolarization tensors $\tilde{\mathbf{N}}(\tilde{\mathbf{r}})$}
-
-\subsubsection{Depolarization tensor $\tilde{\mathbf{N}}^{\dagger}$}
-
-The elements of the transformed depolarization tensor 
-$\tilde{\mathbf{N}}^{\dagger}$ used in the previous sections
-are calculated according to Eq. \ref{eq:nij-tilde}, with 
-$\tilde{f}(\tilde{\mathbf{r}})$ given by 
-$\tilde{f}^{\dagger}(\tilde{\mathbf{r}})$ (Eq. \ref{eq:fi-tilde}).
-As we have already pointed out, the  
-$\tilde{f}^{\dagger}(\tilde{\mathbf{r}})$ (Eq. \ref{eq:fi-tilde}) is a
-quadratic function of the spatial coordinates $\tilde{x}$,
-$\tilde{y}$ and $\tilde{z}$. Consequently, the 
-elements $\tilde{n}^{\dagger}_{ij}$, $i = 1, 2, 3$, 
-$j = 1, 2, 3$, of $\tilde{\mathbf{N}}^{\dagger}$ 
-do not depend on the elements of the transformed position
-vector $\tilde{\mathbf{r}}$ (equation \ref{eq:coord_transformation}). 
-Besides, the off-diagonal elements are zero and
-the diagonal elements are given by \citep{stoner1945}:
-\begin{equation}
-\tilde{n}^{\dagger}_{ii} = \frac{abc}{2}
-\int_{0}^{\infty} \frac{1}{\left( e_{i}^{2} 
-+ u \right) R(u)} \, du \: , \quad i = 1, 2, 3 \: ,
-\label{eq:n-tilde-dagger-ii}
-\end{equation}
-where $R(u)$ is defined by Eq. \ref{eq:R} and
-$e_{1} = a$, $e_{2} = b$, and $e_{3} = c$. These elements 
-are commonly known as \textit{demagnetizing factors}
-and are defined according to the ellipsoid type.
-Here, we calculate the demagnetizing factors in the SI
-system. Consequently, they satisfies the condition
-$\tilde{n}^{\dagger}_{11} + \tilde{n}^{\dagger}_{22} + 
-\tilde{n}^{\dagger}_{33} = 1$, independently of the
-ellipsoid type.
-Notice that, according to Eqs. \ref{eq:H-tilde} 
-and \ref{eq:N-tilde-VT-N-V},
-\begin{equation}
-\mathbf{N}(\mathbf{r}) = 
-\mathbf{V} \, \tilde{\mathbf{N}}^{\dagger} \, 
-\mathbf{V}^{\top} \: ,
-\label{eq:N-V-N-dagger-VT}
-\end{equation}
-where $\tilde{\mathbf{N}}^{\dagger}$ is a diagonal 
-matrix and $\mathbf{V}$ (Eq. \ref{eq:A}) is an orthogonal matrix.
-This equation shows that, for the particular case 
-in which $\mathbf{r}$ and consequently $\tilde{\mathbf{r}}$
-represent a point inside the
-volume $\vartheta$ of the ellipsoid, the elements 
-$\tilde{n}^{\dagger}_{ii}$ (Eq. \ref{eq:n-tilde-dagger-ii})
-of $\tilde{\mathbf{N}}^{\dagger}$ represent the eigenvalues while the 
-columns of $\mathbf{V}$ represent the eigenvectors of the 
-original depolarization tensor $\mathbf{N}(\mathbf{r})$.
-
-\subparagraph*{Triaxial ellipsoids}
-
-For triaxial ellipsoids (e.g., $a > b > c$), the demagnetizing
-factors obtained by solving Eq. \ref{eq:n-tilde-dagger-ii} 
-are given by:
-\begin{equation}
-\tilde{n}^{\dagger}_{11} = \frac{abc}
-{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
-\left( a^{2} - b^{2} \right)} 
-\left[ F(\kappa, \phi) - E(\kappa, \phi) \right] \: ,
-\label{eq:n-tilde-dagger-11-triaxial}
-\end{equation}
-\begin{equation}
-\tilde{n}^{\dagger}_{22} = 
--\frac{abc}
-{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
-\left( a^{2} - b^{2} \right)} 
-\left[ F(\kappa, \phi) - E(\kappa, \phi) \right] + 
-\frac{abc}
-{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
-\left( b^{2} - c^{2} \right)} E(\kappa, \phi)
-- \frac{c^{2}}{b^{2} - c^{2}}
-\label{eq:n-tilde-dagger-22-triaxial}
-\end{equation}
-and
-\begin{equation}
-\tilde{n}^{\dagger}_{33} = 
--\frac{abc}
-{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
-\left( b^{2} - c^{2} \right)} E(\kappa, \phi) +
-\frac{b^{2}}{b^{2} - c^{2}} \: ,
-\label{eq:n-tilde-dagger-33-triaxial}
-\end{equation}
-where
-\begin{equation}
-F(\kappa, \phi) = 
-\int^{\phi}_{0} 
-\frac{1}{\left( 1 - \kappa^{2} \sin^{2} \psi \right)^{\frac{1}{2}}}
-d\psi \: ,
-\label{eq:F-kappa-phi}
-\end{equation}
-and
-\begin{equation}
-E(\kappa, \phi) = 
-\int^{\phi}_{0} 
-\left( 1 - \kappa^{2} \sin^{2} \psi \right)^{\frac{1}{2}}
-d\psi \: ,
-\label{eq:E-kappa-phi}
-\end{equation}
-with $\kappa = \left[ \left( a^{2} - b^{2} \right) / 
-\left( a^{2} - c^{2} \right) \right]^{\frac{1}{2}}$ and
-$\cos \phi = c/a$.
-The functions $F(\kappa, \phi)$ (Eq. \ref{eq:F-kappa-phi}) and 
-$E(\kappa, \phi)$ (Eq. \ref{eq:E-kappa-phi}) are
-called Legendre's normal elliptic integrals of the first and 
-second kind, respectivelly. \citet{stoner1945} presented a 
-detailed deduction of the demagnetizing factors $\tilde{n}^{\dagger}_{11}$
-(Eq. \ref{eq:n-tilde-dagger-11-triaxial}), $\tilde{n}^{\dagger}_{22}$
-(Eq. \ref{eq:n-tilde-dagger-22-triaxial}) and $\tilde{n}^{\dagger}_{33}$
-(Eq. \ref{eq:n-tilde-dagger-33-triaxial}). \citet{clark1986} presented similar
-formulas. It can be shown that these demagnetizing factors
-satisfy the conditions
-$\tilde{n}^{\dagger}_{11} + \tilde{n}^{\dagger}_{22} + \tilde{n}^{\dagger}_{33} = 1$
-and
-$\tilde{n}^{\dagger}_{11} < \tilde{n}^{\dagger}_{22} < \tilde{n}^{\dagger}_{33}$.
-
-\subparagraph*{Prolate ellipsoids}
-
-For prolate ellipsoids (e.g., $a > b = c$), the demagnetizing
-factors obtained by solving Eq. \ref{eq:n-tilde-dagger-ii} 
-are given by:
-\begin{equation}
-\tilde{n}^{\dagger}_{11} = \frac{1}{m^{2} - 1}
-\left\lbrace \frac{m}{\left( m^{2} - 1 \right)^{\frac{1}{2}}}
-\ln \left[ m + \left( m^{2} - 1 \right)^{\frac{1}{2}} \right]
-- 1 \right\rbrace
-\label{eq:n-tilde-dagger-11-prolate}
-\end{equation}
-and
-\begin{equation}
-\tilde{n}^{\dagger}_{22} = \frac{1}{2} \left(1 - \tilde{n}^{\dagger}_{11} \right) \: ,
-\label{eq:n-tilde-dagger-22-prolate}
-\end{equation}
-where $\tilde{n}^{\dagger}_{33} = \tilde{n}^{\dagger}_{22}$, 
-with $\tilde{n}^{\dagger}_{11}$ defined in 
-Eq. \ref{eq:n-tilde-dagger-11-prolate} and $m = a/b$.
-The detailed deduction of the demagnetizing factors 
-$\tilde{n}^{\dagger}_{11}$ (Eq. \ref{eq:n-tilde-dagger-11-prolate}) 
-and $\tilde{n}^{\dagger}_{22}$ (Eq. \ref{eq:n-tilde-dagger-22-prolate})
-can be found, for example, in \citet{stoner1945}. 
-These formulas were posteriorly presented by \citet{emerson1985}.
-It can be shown that these demagnetizing factors
-satisfy the conditions
-$\tilde{n}^{\dagger}_{11} + 2 \; \tilde{n}^{\dagger}_{22} = 1$
-and
-$\tilde{n}^{\dagger}_{11} < \tilde{n}^{\dagger}_{22}$.
-
-\subparagraph*{Oblate ellipsoids}
-
-For oblate ellipsoids (e.g., $a < b = c$), the demagnetizing
-factors obtained by solving Eq. \ref{eq:n-tilde-dagger-ii} 
-are given by:
-\begin{equation}
-\tilde{n}^{\dagger}_{11} = 
-\frac{1}{1 - m^{2}} \left[
-1 - \frac{m}{\left( 1 - m^{2} \right)^{\frac{1}{2}}} \cos^{-1}m
-\right]
-\label{eq:n-tilde-dagger-11-oblate}
-\end{equation}
-and
-\begin{equation}
-\tilde{n}^{\dagger}_{22} = \frac{1}{2} \left(1 - \tilde{n}^{\dagger}_{11} \right) \: ,
-\label{eq:n-tilde-dagger-22-oblate}
-\end{equation}
-where $\tilde{n}^{\dagger}_{33} = \tilde{n}^{\dagger}_{22}$, 
-with $\tilde{n}^{\dagger}_{11}$ defined in 
-Eq. \ref{eq:n-tilde-dagger-11-oblate} and $m = a/b$.
-The detailed deduction of these demagnetizing factors 
-can be found, for example, in \citet{stoner1945}.
-These formulas can also be found in \citet{emerson1985}.
-The only difference, however, is that \citet{emerson1985} replaced
-the term $\cos^{-1}$ by a term $\tan^{-1}$, according to 
-the trigonometric identity 
-$\tan^{-1}x = \cos^{-1}(1/\sqrt{x^{2} + 1})$, $x > 0$.
-It can be shown that these demagnetizing factors
-satisfy the conditions
-$\tilde{n}^{\dagger}_{11} + 2 \; \tilde{n}^{\dagger}_{22} = 1$
-and
-$\tilde{n}^{\dagger}_{11} > \tilde{n}^{\dagger}_{22}$.
-
-\subsubsection{Depolarization tensor $\tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}})$}
-
-The elements $\tilde{n}^{\ddagger}_{ij}(\tilde{\mathbf{r}})$,
-$i = 1, 2, 3$, $j = 1, 2, 3$, of the transformed depolarization tensor 
-$\tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}})$ used to compute
-the magnetic field $\Delta \mathbf{H}(\mathbf{r})$ 
-(Eq. \ref{eq:delta-H}) and
-the total-field anomaly $\Delta T(\mathbf{r})$
-(Eqs. \ref{eq:delta-T} and \ref{eq:delta-T-approx}) 
-are calculated according to Eq. \ref{eq:nij-tilde}, with 
-$\tilde{f}(\tilde{\mathbf{r}})$ given by $\tilde{f}^{\ddagger}(\tilde{\mathbf{r}})$
-(Eq. \ref{eq:fe-tilde}).
-By following \citet{clark1986}, the diagonal elements $\tilde{n}^{\ddagger}_{ii}$
-and the off-diagonal elements $\tilde{n}^{\ddagger}_{ij}$, $i = 1, 2, 3$,
-$j = 1, 2, 3$, are given by
-\begin{equation}
-\tilde{n}^{\ddagger}_{ii}(\tilde{\mathbf{r}}) =
--\frac{abc}{2}
-\left( \frac{\partial \lambda}{\partial \tilde{r}_{i}} \, h_{i} \, \tilde{r}_{i}
-+ g_{i} \right)
-\label{eq:n-tilde-dagger-ii}
-\end{equation}
-and
-\begin{equation}
-\tilde{n}^{\ddagger}_{ij}(\tilde{\mathbf{r}}) =
--\frac{abc}{2} \left(
-\frac{\partial \lambda}{\partial \tilde{r}_{i}} \, h_{j} \, \tilde{r}_{j} 
-\right) \: ,
-\label{eq:n-tilde-dagger-ij}
-\end{equation}
-where
-\begin{equation}
-h_{i} = -\frac{1}{\left( e_{i}^{2} + \lambda \right) R(\lambda)} \: ,
-\label{eq:hi}
-\end{equation}
-\begin{equation}
-g_{i} = \int_{\lambda}^{\infty} \frac{1}{\left( e_{i}^{2} + u \right) R(u)} du \: ,
-\label{eq:gi}
-\end{equation}
-$e_{1} = a$, $e_{2} = b$, $e_{3} = c$, and 
-$\frac{\partial \lambda}{\partial \tilde{r}_{i}}$
-is defined in Appendix B (Eq. \ref{eq:dlambda}).
-The functions $g_{i}$ (Eq. \ref{eq:gi}) are defined according
-to the ellipsoid type.
-Notice that the elements $\tilde{n}^{\ddagger}_{ij}$
-(Eqs. \ref{eq:n-tilde-dagger-ii} and \ref{eq:n-tilde-dagger-ij}) 
-are proportional to the second derivatives of the function
-$\tilde{f}^{\ddagger}(\tilde{\mathbf{r}})$ (Eq. \ref{eq:fe-tilde}),
-which is harmonic. Consequently, the diagonal elements defined
-in Eq. \ref{eq:n-tilde-dagger-ii} satisfies the condition
-$\tilde{n}^{\ddagger}_{11}(\tilde{\mathbf{r}}) +
-\tilde{n}^{\ddagger}_{22}(\tilde{\mathbf{r}}) +
-\tilde{n}^{\ddagger}_{33}(\tilde{\mathbf{r}}) = 0$ for any
-point $\tilde{\mathbf{r}}$ outside the ellipsoid, independently
-of the ellipsoid type.
-
-\subparagraph*{Triaxial ellipsoids}
-
-For triaxial ellipsoids (e.g., $a > b > c$), the functions
-$g_{i}$ (Eq. \ref{eq:gi}) are defined as follows:
-\begin{equation}
-g_{1} = \frac{2}{\left( a^{2} - b^{2} \right) \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
-\left[ F(\kappa, \phi) - E(\kappa, \phi) \right] \: ,
-\label{eq:g1-triaxial}
-\end{equation}
-%\begin{equation}
-%g_{2} = \frac{2 \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
-%{\left( a^{2} - b^{2} \right)\left( b^{2} - c^{2} \right)}
-%\left[ E\left(\kappa, \phi \right) 
-%- \frac{\left( b^{2} - c^{2} \right)}{\left( a^{2} - c^{2} \right)}
-%F\left(\kappa, \phi \right) 
-%- \frac{\kappa^{2} \sin\phi \, \cos\phi}
-%{\left( 1 - \kappa^{2} \sin^{2}\phi \right)^{\frac{1}{2}}}
-%\right]
-%\label{eq:g2-triaxial}
-%\end{equation}
-\begin{equation}
-g_{2} = \frac{2 \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
-{\left( a^{2} - b^{2} \right)\left( b^{2} - c^{2} \right)}
-\left\lbrace
-E\left(\kappa, \phi \right) 
-- \left( \frac{b^{2} - c^{2}}{a^{2} - c^{2}} \right)
-F\left(\kappa, \phi \right) -
-\frac{a^{2} - b^{2}}{\left( a^{2} - c^{2} \right)^{\frac{1}{2}}} \left[
-\frac{c^{2} + \lambda}{\left( a^{2} + \lambda \right)\left( b^{2} + \lambda \right)}
-\right]^{\frac{1}{2}} \right\rbrace
-\label{eq:g2-triaxial}
-\end{equation}
-and
-%\begin{equation}
-%g_{3} = \frac{2}{\left( b^{2} - c^{2} \right) \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
-%\left[ \frac{\sin\phi \left( 1 - \kappa^{2} \sin^{2}\phi \right)^{\frac{1}{2}}}
-%{\cos\phi}  - E\left(\kappa, \phi \right) \right]
-%\: ,
-%\label{eq:g3-triaxial}
-%\end{equation}
-\begin{equation}
-g_{3} = \frac{2}{\left( b^{2} - c^{2} \right) \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
-E\left(\kappa, \phi \right) +
-\frac{2}{b^{2} - c^{2}}
-\left[
-\frac{b^{2} + \lambda}{\left( a^{2} + \lambda \right)\left( c^{2} + \lambda \right)}
-\right]^{\frac{1}{2}}
-\: ,
-\label{eq:g3-triaxial}
-\end{equation}
-where $F(\kappa, \phi)$ and $E(\kappa, \phi)$ are defined by
-Eqs. \ref{eq:E-kappa-phi} and \ref{eq:F-kappa-phi}, but with 
-$\sin \phi = \sqrt{\left( a^{2} - c^{2} \right)/\left( a^{2} + \lambda \right)}$.
-A deduction of these formulas was presented by \citet{tejedor1995}.
-Despite the small differences, these formulas can also be found in
-\citet{clark1986}.
-
-\subparagraph*{Prolate ellipsoids}
-
-For prolate (e.g., $a > b = c$) ellipsoids, the functions
-$g_{i}$ (Eq. \ref{eq:gi}) are given by:
-\begin{equation}
-g_{1} =  \frac{2}{\left( a^{2} - b^{2} \right)^{\frac{3}{2}}}
-\left\lbrace
-\ln \left[ \frac{\left( a^{2} - b^{2} \right)^{\frac{1}{2}} + 
-                 \left( a^{2} + \lambda \right)^{\frac{1}{2}}}{
-                 \left( b^{2} + \lambda \right)^{\frac{1}{2}}} \right] -
-\left( \frac{a^{2} - b^{2}}{a^{2} + \lambda} \right)^{\frac{1}{2}}
-\right\rbrace
-\label{eq:g1-prolate}
-\end{equation}
-and
-\begin{equation}
-g_{2} =  \frac{1}{\left( a^{2} - b^{2} \right)^{\frac{3}{2}}}
-\left\lbrace
-\frac{\left[ \left( a^{2} - b^{2} \right)
-             \left( a^{2} + \lambda \right) \right]^{\frac{1}{2}}}
-     {b^{2} + \lambda} -
-\ln \left[ \frac{\left( a^{2} - b^{2} \right)^{\frac{1}{2}} + 
-                 \left( a^{2} + \lambda \right)^{\frac{1}{2}}}{
-                 \left( b^{2} + \lambda \right)^{\frac{1}{2}}} \right]
-\right\rbrace \: ,
-\label{eq:g2-prolate}
-\end{equation}
-where $g_{3} = g_{2}$.
-These formulas can be obtained by properly manipulating those
-presented by \citep{emerson1985}.
-
-\subparagraph*{Oblate ellipsoids}
-
-For oblate (e.g., $a < b = c$) ellipsoids, the functions
-$g_{i}$ (Eq. \ref{eq:gi}) are given by:
-\begin{equation}
-g_{1} =  \frac{2}{\left( b^{2} - a^{2} \right)^{\frac{3}{2}}}
-\left\lbrace
-\left( \frac{b^{2} - a^{2}}{a^{2} + \lambda}\right)^{\frac{1}{2}} -
-\tan^{-1} \left[ \left( \frac{b^{2} - a^{2}}{a^{2} + \lambda}\right)^{\frac{1}{2}} \right]
-\right\rbrace
-\label{eq:g1-oblate}
-\end{equation}
-and
-\begin{equation}
-g_{2} =  \frac{1}{\left( b^{2} - a^{2} \right)^{\frac{3}{2}}}
-\left\lbrace
-\tan^{-1} \left[ \left( \frac{b^{2} - a^{2}}{a^{2} + \lambda}\right)^{\frac{1}{2}} \right] -
-\frac{\left[ \left( b^{2} - a^{2} \right)
-             \left( a^{2} + \lambda \right) \right]^{\frac{1}{2}}}
-     {b^{2} + \lambda}
-\right\rbrace \: ,
-\label{eq:g2-oblate}
-\end{equation}
-where $g_{3} = g_{2}$.
-Similarly to the case of prolate ellipsoid shown previously,
-these formulas can be obtained by properly manipulating those
-presented by \citep{emerson1985}.
 

### 2017-02-21 manuscript/manuscript.tex
remove the beta

@@
 These unit vectors are commonly described in terms of auxiliary 
-orientation angles $\alpha$, $\beta$, and $\gamma$, which are not used
+orientation angles $\alpha$, $\gamma$, and $delta$, which are not used
 by the geoscientific community. These angles, however, can be defined from
@@
 Fatiando a Terra \citep{uieda2013}.
-Because of that, it is very modular and has a
+Our code is very modular and has a
 test suite formed by a considerable number of 

### 2017-02-22 manuscript/manuscript.tex
include the text simulating the warrego magnetite body

@@
 \mathbf{H}(\mathbf{r}) = \mathbf{H}_{0} 
-- \mathbf{N}(\mathbf{r}) \, \mathbf{K} \, \mathbf{H}^{\dagger} \: ,
++ \mathbf{N}(\mathbf{r}) \, \mathbf{K} \, \mathbf{H}^{\dagger} \: ,
 \label{eq:H-M-uniform}
@@
 \begin{equation}
-n_{ij}(\mathbf{r}) = - 
+n_{ij}(\mathbf{r}) = 
 \frac{1}{4\pi} \frac{\partial^{2} \, f(\mathbf{r})}
@@
 \underbrace{\mathbf{V}^{\top} \mathbf{H}_{0}}_{\tilde{\mathbf{H}}_{0}}
-- \underbrace{\mathbf{V}^{\top} \mathbf{N}(\mathbf{r}) \mathbf{V}}
++ \underbrace{\mathbf{V}^{\top} \mathbf{N}(\mathbf{r}) \mathbf{V}}
 _{\tilde{\mathbf{N}}(\tilde{\mathbf{r}})} \;
@@
 \begin{equation}
-\tilde{n}_{ij}(\tilde{\mathbf{r}}) = - 
+\tilde{n}_{ij}(\tilde{\mathbf{r}}) = 
 \frac{1}{4\pi} \frac{\partial^{2} \, \tilde{f}(\tilde{\mathbf{r}})}
@@
 \tilde{\mathbf{H}}^{\dagger} = 
-\left( \mathbf{I} - \tilde{\mathbf{N}}^{\dagger} \, \tilde{\mathbf{K}} \right)^{-1}
+\left( \mathbf{I} + \tilde{\mathbf{N}}^{\dagger} \, \tilde{\mathbf{K}} \right)^{-1}
 \tilde{\mathbf{H}}_{0} \: ,
@@
 &= \tilde{\mathbf{K}} 
-\left( \mathbf{I} - \tilde{\mathbf{N}}^{\dagger} \, \tilde{\mathbf{K}} \right)^{-1}
+\left( \mathbf{I} + \tilde{\mathbf{N}}^{\dagger} \, \tilde{\mathbf{K}} \right)^{-1}
 \tilde{\mathbf{H}}_{0} \\
 &=  
-\left( \mathbf{I} - \tilde{\mathbf{K}} \, \tilde{\mathbf{N}}^{\dagger} \right)^{-1}
+\left( \mathbf{I} + \tilde{\mathbf{K}} \, \tilde{\mathbf{N}}^{\dagger} \right)^{-1}
 \tilde{\mathbf{K}} \, \tilde{\mathbf{H}}_{0}
@@
 \mathbf{\Lambda} = \mathbf{V}
-\left( \mathbf{I} - \tilde{\mathbf{K}} \, \tilde{\mathbf{N}}^{\dagger} \right)^{-1}
+\left( \mathbf{I} + \tilde{\mathbf{K}} \, \tilde{\mathbf{N}}^{\dagger} \right)^{-1}
 \mathbf{V}^{\top} \: .
@@
 \mathbf{\Lambda} = \mathbf{V}
-\left( \mathbf{I} - \chi \, \tilde{\mathbf{N}}^{\dagger} \right)^{-1}
+\left( \mathbf{I} + \chi \, \tilde{\mathbf{N}}^{\dagger} \right)^{-1}
 \mathbf{V}^{\top} \: .
@@
 \mathbf{\Lambda}^{-1} = \mathbf{V}
-\left( \mathbf{I} - \chi \, \tilde{\mathbf{N}}^{\dagger} \right)
+\left( \mathbf{I} + \chi \, \tilde{\mathbf{N}}^{\dagger} \right)
 \mathbf{V}^{\top} \: .
@@
 \chi_{max} = \frac{\epsilon}{\tilde{n}^{\dagger}_{max}} \: ,
-\label{eq:max-chi}
+\label{eq:chi-max}
 \end{equation}
@@
 (Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda}).
-Equation \ref{eq:max-chi}, on the other hand, defines $\chi_{max}$ 
+Equation \ref{eq:chi-max}, on the other hand, defines $\chi_{max}$ 
 as a function of the ellipsoid semi-axes, according to a
@@
 \Delta \mathbf{H}(\mathbf{r}) = 
-- \mathbf{V} \tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}}) \, \mathbf{V}^{\top}
+\mathbf{V} \tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}}) \, \mathbf{V}^{\top}
 \mathbf{M} \: ,
@@
 \begin{equation}
-\mathbf{N}(\mathbf{r}) = - \frac{1}{4 \pi} \mathbf{F}(\mathbf{r}) \: .
+\mathbf{N}(\mathbf{r}) = \frac{1}{4 \pi} \mathbf{F}(\mathbf{r}) \: .
 \label{eq:N-F}
@@
 Finally, by multiplying both sides of Eq. \ref{eq:F-tilde-VT-F-V}
-by $-\frac{1}{4 \pi}$ and using Eq. \ref{eq:N-F},
+by $\frac{1}{4 \pi}$ and using Eq. \ref{eq:N-F},
 we conclude that 
@@
 
+%f
 \begin{figure}[t]
@@
 
+%f
+\begin{figure}[t]
+\includegraphics[width=8.3cm]{figures/total-field_anomaly.pdf}
+\caption{Total-field anomaly produced by the synthetic orebody
+defined in Tab. \ref{tab:parameters-warrego}. The synthetic data
+are calculated on a regular grid of $100 \times 100$ points
+at the constant vertical coordinate $z = 0$ \unit{m}.}
+\label{fig:tfa-warrego}
+\end{figure}
+
+%f
+\begin{figure}[t]
+\includegraphics[width=8.3cm]{figures/field_differences.pdf}
+\caption{Differences between the total-field 
+anomaly obtained by using the approximated magnetization $\breve{\mathbf{M}}$
+(Eq. \ref{eq:M-approx}) and that obtained by using the 
+true magnetization $\mathbf{M}$
+(Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda}).
+The total-field anomalies are calculated with Eq. \ref{eq:delta-T-approx},
+on a regular grid of $100 \times 100$ points
+at the constant vertical coordinate $z = 0$ \unit{m},
+for three synthetic bodies.
+(a) Differences produced by the synthetic orebody defined in
+Tab. \ref{tab:parameters-warrego}.
+(b) Differences produced by the synthetic orebody defined in
+Tab. \ref{tab:parameters-warrego}, but with an isotropic
+susceptibility $\chi = 0.1$ SI.
+(c) Differences produced by the synthetic orebody defined in
+Tab. \ref{tab:parameters-warrego}, but with an isotropic
+susceptibility $\chi = 0.044$ SI. This value was calculated
+with Eq. \ref{eq:chi-max}, by using $\epsilon = 2 \%$.}
+\label{fig:tfa-warrego}
+\end{figure}
+
 %%% TWO-COLUMN FIGURES
@@
 %
+
+%t
+\begin{table}[t]
+\caption{Parameters defining a synthetic orebody. This model is
+based on the that presented by \citet{farrar1979} to simulate
+the Warrego orebody, Tennant Creek field, Australia.}
+%\begin{tabular}{column = lcr}
+\begin{tabular}{lcr}
+\tophline
+Parameter & Value & Unit \\
+\middlehline
+Semi-axis $a$ & $490.7$ & \unit{m} \\
+Semi-axis $b$ & $69.7$ & \unit{m} \\
+Semi-axis $c$ & $30.0$ & \unit{m} \\
+Coordinate of the centre $x_{c}$ & 0 & \unit{m} \\
+Coordinate of the centre $y_{c}$ & 0 & \unit{m} \\
+Coordinate of the centre $z_{c}$ & 500 & \unit{m} \\
+Orientation angle $\varepsilon$ $^{\ast}$ & $-34.0$ & $^{\circ}$ \\
+Orientation angle $\zeta$ $^{\ast}$ & $66.1$ & $^{\circ}$ \\
+Orientation angle $\eta$ $^{\ast}$ & $45.0$ & $^{\circ}$ \\
+Isotropic susceptibility $\chi$ & $1.69$ & SI \\
+$x$-component of the inducing field $\mathbf{B}_{0}$ $^{\dagger}$ & 32610 & \unit{nT} \\
+$y$-component of the inducing field $\mathbf{B}_{0}$ $^{\dagger}$ & 0 & \unit{nT} \\
+$z$-component of the inducing field $\mathbf{B}_{0}$ $^{\dagger}$ & 39450 & \unit{nT} \\
+\bottomhline
+\end{tabular}
+\belowtable{$^{\ast}$ Defined in Fig. \ref{fig:orientation-angles}a \newline
+$^{\dagger}$ Defined in Eq. \ref{eq:delta-T}} % Table Footnotes
+\label{tab:parameters-warrego}
+\end{table}
+
 %%% TWO-COLUMN TABLE

### 2017-02-23 manuscript/manuscript.tex
conclusion

@@
 It is well-established in the literature that
-the self-demagnetization can
-be neglected if the body has a susceptibility lower 
-than 0.1 SI 
+the self-demagnetization can be neglected if the 
+body has a susceptibility lower than 0.1 \unit{SI} 
 \citep{emerson1985, clark1986, eskola1980, guo1998,
 guo2001, purss2005, hillan2013, austin2014, clark2014}.
-However, neglecting the self-demagnetization in
-geological bodies with high susceptibilities (> 0.1 SI) 
+On the other hand, neglecting the self-demagnetization in
+geological bodies with high susceptibilities (> 0.1 \unit{SI}) 
 may strongly mislead the interpretation obtained from
 magnetic methods.
+This limiting value, however, seems to be determined empirically
+and, so far, there has been little discussion about
+how it was determined.
+
 \citet{farrar1979} demonstrated the importance of the
@@
 modelling of ellipsoidal bodies was developed in which 
-are to be found the names of many brilliant researchers.
+are to be found the names of many researchers.
 Nevertheless, interest in this subject has not yet died
@@
 and researching geophysics.
-To fill this gap, we provide here a set of routines to 
+
+In this work, we present a review of the vast literature
+about the magnetic modelling of ellipsoidal bodies and a
+theoretical discussion about the determination of the 
+isotropic susceptibility value above which
+the self-demagnetization must be taken into consideration.
+We propose an alternative way of determining this value
+based on the body shape and the maximum relative error
+allowed in the resultant magnetization.
+This alternative approach is validated
+by the results obtained with numerical simulations.
+We also provide a set of routines to 
 model the magnetic field produced by ellipsoids.
@@
 code.
-It is hoped that the presentation of the theoretical and
-practical aspects given here will be found useful to the
-wide community of geoscientists.
 
@@
 and are defined according to the ellipsoid type.
-Here, we calculate the demagnetizing factors in the SI
+Here, we calculate the demagnetizing factors in the \unit{SI}
 system. Consequently, they satisfies the condition
@@
 Usually, Eq. \ref{eq:M-approx}
-is considered a good approximation for $\chi \leq 0.1$ SI.
+is considered a good approximation for $\chi \leq 0.1$ \unit{SI}.
 Although this value has been largely used in the literature,
@@
 $\tilde{n}^{\dagger}_{max} \equiv \tilde{n}^{\dagger}_{33}$
-(Eq. \ref{eq:n-tilde-dagger-33-triaxial}). For a prolate ellipsoid,
+(Eq. \ref{eq:n-tilde-dagger-33-triaxial}), for a prolate ellipsoid,
 $\tilde{n}^{\dagger}_{max} \equiv \tilde{n}^{\dagger}_{22}$
-(Eq. \ref{eq:n-tilde-dagger-22-prolate}). 
-For an oblate ellipsoid,
+(Eq. \ref{eq:n-tilde-dagger-22-prolate}), and,
+for an oblate ellipsoid,
 $\tilde{n}^{\dagger}_{max} \equiv \tilde{n}^{\dagger}_{11}$
@@
 and \ref{eq:M-K-isotropic-inverse-Lambda}).
-
-Given a target relative error
-$\epsilon = \| \delta \mathbf{M} \| \, \| \mathbf{M} \|^{-1}$
-and an ellipsoid
+Given a target relative error $\epsilon$ and an ellipsoid
 with given semi-axes, we may use the inequality
@@
 is lower than or equal to $\epsilon$. The geoscientific community
-has been using $\chi_{max} = 0.1$ SI as a limit value for
+has been using $\chi_{max} = 0.1$ \unit{SI} as a limit value for
 neglecting the self-demagnetization and, consequently,
@@
 
-\subsection{Relative error in neglecting the self-demagnetization}
-
-TEXT
-
 \subsection{Simulation of a geological body}
 
-TEXT
+\citet{farrar1979} represented the Warrego orebody as a triaxial
+ellipsoid having a high isotropic susceptibility.
+In this case, the self-demagnetization strongly impacts the
+magnetic modelling of this body.
+According to \citet{wedekind1990}, the Warrego orebody is a combination of
+two major and several small ironstone lodes, which are discrete bodies
+comprised predominantly of magnetite or hematite above the base of
+oxidation.
+The Warrego orebody was the resource on which the Warrego mine was
+developed. After nearly a decade as one of the most important 
+gold and copper mines in Australia, the Warrego mine was closed 
+in late 1989.
+
+Table \ref{tab:parameters-warrego} shows the parameters defining
+a synthetic orebody which is based on that presented by
+\citet{farrar1979} to represent the Warrego orebody.
+Figure \ref{fig:tfa-warrego} shows the total-field anomaly
+$\Delta T (\mathbf{r})$ (Eq. \ref{eq:delta-T-approx}) produced
+by the synthetic body on a regular grid of $100 \times 100$
+points at a constant vertical coordinate $z = 0$ \unit{m}.
+The total-field anomaly varies from $\approx -295.3$ \unit{nT}
+to $\approx 149.5$ \unit{nT}, resulting in a peak-to-peak amplitude
+of $\approx 444.9$ \unit{nT}, and was calculated by using the 
+true magnetization $\mathbf{M}$ defined in Eqs. 
+\ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda}.
+
+We have calculated the difference between the total-field anomaly
+$\Delta T (\mathbf{r})$ (Eq. \ref{eq:delta-T-approx}) calculated with the
+true magnetization $\mathbf{M}$ (Eqs. 
+\ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda})
+and that calculated with the approximated magnetization
+$\breve{\mathbf{M}}$ (Eq. \ref{eq:M-approx}).
+The differences were calculated by using the synthetic body 
+defined in Tab. \ref{tab:parameters-warrego}, but with three
+different isotropic susceptibilities.
+Figures \ref{fig:tfa-differences-warrego}a, \ref{fig:tfa-differences-warrego}b
+and \ref{fig:tfa-differences-warrego}c show the differences calculated
+by using, respectively, isotropic susceptibilities $\chi = 1.69$ \unit{SI} 
+(Tab. \ref{tab:parameters-warrego}), $\chi_{1} = 0.1$ \unit{SI} and 
+$\chi_{2} = 0.116$ \unit{SI}.
+
+As expected, the differences calculated by using the higher isotropic
+susceptibility (Fig. \ref{fig:tfa-differences-warrego}a) are very large.
+The peak-to-peak amplitude is $\approx 212.0$ \unit{nT}
+and represents $\approx 48 \%$ of the peak-to-peak amplitude of
+the total-field anomaly shown in Fig. \ref{fig:tfa-warrego}.
+This result reinforces that the use of the approximated magnetization
+$\breve{\mathbf{M}}$ (Eq. \ref{eq:M-approx}) may negatively impact
+the magnetic modelling of bodies with high isotropic susceptibility.
+
+Figure \ref{fig:tfa-differences-warrego}b shows the differences calculated
+by using $\chi_{1} = 0.1$ \unit{SI}.
+It is commonly accepted that, for bodies having isotropic susceptibilities
+lower than or equal to $0.1$ \unit{SI}, the self-demagnetization can be neglected and,
+consequently, the magnetization $\breve{\mathbf{M}}$ (Eq. \ref{eq:M-approx})
+is a good approximation of the true magnetization $\mathbf{M}$
+(Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda}).
+In our test, the use of $\chi_{1} = 0.1$ \unit{SI} leads to a relative error
+$\| \delta \mathbf{M} \| \, \| \mathbf{M} \|^{-1} \approx 4.2 \%$
+(Eq. \ref{eq:perturbed-M-inequality}) in the magnetization.
+The peak-to-peak amplitude of the differences in the total-field anomaly
+(Fig. \ref{fig:tfa-differences-warrego}b) is $\approx 1.5$ \unit{nT},
+which represents $\approx 4.5 \%$ of the peak-to-peak amplitude of the
+total-field anomaly calculates by using the true magnetization $\mathbf{M}$
+(Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda}).
+
+Finally, Fig. \ref{fig:tfa-differences-warrego}c shows the differences
+calculated by using $\chi_{2} = 0.116$ \unit{SI}.
+This value was calculated by using Eq. \ref{eq:chi-max} with a
+target relative error $\epsilon = 8 \%$ and the $\tilde{n}^{\dagger}_{max}$
+defined by Eq. \ref{eq:n-tilde-dagger-33-triaxial}.
+By using this isotropic susceptibility, it is expected that the
+calculated relative error 
+$\| \delta \mathbf{M} \| \, \| \mathbf{M} \|^{-1}$
+(Eq. \ref{eq:perturbed-M-inequality}) in the magnetization be
+lower than or equal to the target relative error $\epsilon = 8 \%$.
+In this test, the use of $\chi_{2} = 0.116$ \unit{SI} leads to a relative error
+$\| \delta \mathbf{M} \| \, \| \mathbf{M} \|^{-1} \approx 4.9 \%$
+(Eq. \ref{eq:perturbed-M-inequality}) in the magnetization.
+The peak-to-peak amplitude of the differences in the total-field anomaly
+(Fig. \ref{fig:tfa-differences-warrego}c) is $\approx 2.0$ \unit{nT},
+which represents $\approx 5.1 \%$ of the peak-to-peak amplitude of the
+total-field anomaly calculates by using the true magnetization $\mathbf{M}$
+(Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda}).
+In this case, the use an isotropic susceptibility greater than the usual
+limit $0.1$ \unit{SI} does not mislead the magnetic modelling
+dramatically. On the contrary, it shows small discrepancies in the
+magnetic modelling and validates Eq. \ref{eq:chi-max}.
 
 \section{Conclusions}  %% \conclusions[modified heading if necessary]
-TEXT
+
+We present an integrated review of the vast literature 
+about the magnetic modelling of triaxial, prolate and
+oblate ellipsoids.
+We also present a theoretical discussion about the
+determination of the isotropic susceptibility value above which
+the self-demagnetization must be taken into consideration.
+We propose an alternative way of determining this value
+based on the body shape and the maximum relative error
+allowed in the resultant magnetization.
+Our approach is an alternative to the constant value which
+seems to be determined empirically and
+has been used by the geoscientific community.
+Our alternative approach is validated
+by the results obtained with numerical simulations.
+In a future work,
+it would be interesting to use a similar approach to
+to bound the maximum relative error in the
+magnetic field calculated by neglecting the self-demagnetization.
+
+This work also provide a set of routines to model the magnetic 
+field produced by ellipsoids.
+The routines are written in Python language as part of
+the Fatiando a Terra \citep{uieda2013}, which is an 
+open-source library for modelling and inversion in geophysics.
+The current version of our code is freely distributed
+in a repository of GitHub. We are working to integrate our
+routines in the following stable release of Fatiando a Terra.
+We hope that these routines be useful to the wide geoscientific
+community either in researching and teaching.
 
@@
 
-The code is freely distributed under 
-BSD 3-clause licence as part of the Fatiando a Terra 
+The current code is freely distributed, under 
+BSD 3-clause licence, in a repository of GitHub
+(\url{https://github.com/pinga-lab/magnetic-elipsoid}).
+The code was developed as part of the Fatiando a Terra 
 \citep{uieda2013}, which is an open-source Python 
 library for modelling and inversion in geophysics.
+Instructions for running the current version of our code
+in the Fatiando a Terra are provided at its repository
+in GitHub.
 Documentation and installation instructions for 
@@
 \includegraphics[width=8.3cm]{figures/field_differences.pdf}
-\caption{Differences between the total-field 
-anomaly obtained by using the approximated magnetization $\breve{\mathbf{M}}$
-(Eq. \ref{eq:M-approx}) and that obtained by using the 
+\caption{Difference between the total-field 
+anomaly calculated with the approximated magnetization $\breve{\mathbf{M}}$
+(Eq. \ref{eq:M-approx}) and with the 
 true magnetization $\mathbf{M}$
@@
 The total-field anomalies are calculated with Eq. \ref{eq:delta-T-approx},
-on a regular grid of $100 \times 100$ points
-at the constant vertical coordinate $z = 0$ \unit{m},
-for three synthetic bodies.
-(a) Differences produced by the synthetic orebody defined in
-Tab. \ref{tab:parameters-warrego}.
-(b) Differences produced by the synthetic orebody defined in
-Tab. \ref{tab:parameters-warrego}, but with an isotropic
-susceptibility $\chi = 0.1$ SI.
-(c) Differences produced by the synthetic orebody defined in
-Tab. \ref{tab:parameters-warrego}, but with an isotropic
-susceptibility $\chi = 0.044$ SI. This value was calculated
+on a regular grid of $100 \times 100$ points,
+at the constant vertical coordinate $z = 0$ \unit{m}.
+The differences are produced by the synthetic orebody defined in
+Tab. \ref{tab:parameters-warrego}, but with different
+isotropic susceptibilities:
+(a) the isotropic susceptibility defined in 
+Tab. \ref{tab:parameters-warrego},
+(b) an isotropic susceptibility $\chi = 0.1$ \unit{SI}, and
+(c) an isotropic susceptibility $\chi = 0.116$ \unit{SI}.
+This last value was calculated
 with Eq. \ref{eq:chi-max}, by using $\epsilon = 2 \%$.}
-\label{fig:tfa-warrego}
+\label{fig:tfa-differences-warrego}
 \end{figure}
@@
 %
+
+\newpage
 
@@
 Orientation angle $\eta$ $^{\ast}$ & $45.0$ & $^{\circ}$ \\
-Isotropic susceptibility $\chi$ & $1.69$ & SI \\
+Isotropic susceptibility $\chi$ & $1.69$ & \unit{SI} \\
 $x$-component of the inducing field $\mathbf{B}_{0}$ $^{\dagger}$ & 32610 & \unit{nT} \\
